---
title: "obsDat"
output:
  pdf_document:
    keep_tex: yes
    number_sections: yes
    toc: yes
  word_document:
    toc: yes
  html_document:
    df_print: paged
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
events <- read.csv("../raw/ecpn_events.csv")
markets <- read.csv("../raw/ecpn_markets.csv")
library(lubridate)
library(dplyr)
library(estimatr)

```

# Overview

This file cleans the observational data.  The outcomes are the raw number of people attending the market/event or engaging in some behavior at the market/event.  The outcomes are non-normal and skewed.  As a result of this skew, outcomes are rank rescaled.  Later, the unmodified raw outcomes may be analyzed using quantile regression or robust regression.  COULD create a new version of the raw outcome to modify large outliers.  

We want to know if treatment communities improved more than control communities over time.  We can do this in two ways: (1) code observations as 0 or 1 on a "time" variable, where 0 is early/baseline and 1 is late/endline; (2) code observations by month using a "month number" variable that is 1 for the first month of observation, 2 for the second, month, 3 for the third month, etc.

# Markets

## Cleaning

Fixing community names (ie making aguda and Agudu and agudu all the same thing).  Telling R that the outcomes are numeric.

```{r, include=F} 
# clean white space, make lower case
markets$Community.Name <- trimws(tolower(markets$Community.Name))
markets$site <- markets$Community.Name

# make outcomes numeric
outcomes <- names(markets)[grepl("(market|farm|past)", names(markets))]
markets[,outcomes] <- sapply(markets[,outcomes], function(x) {as.numeric(as.character(x))}) # warning is fine, just making empty cells like <NA> into NA.

# fix treatment assignment
#tapply(markets$treatment, markets$site, mean)
markets[markets$site %in% "ushata", "treatment"] <- 0

# fix state
markets[markets$site %in% "sabon gida agan", "State"] <- "benue"
```

## New Vars

### Time

Making a 0-1 variable for if the observations are between July 2016 - Feb 2017 (0) or Sept 2017 - End of study (1).  Making a time variable that increases each month, and predicting that treatment areas get better over time wheres control stays the same.

```{r, include=F}
# dichotomous before/after
##july 2016 - feb 2017
## sept 2017 - end
class(markets$date.of.observation..M.D.Y.)
markets$date <- lubridate::mdy(markets$date.of.observation..M.D.Y.)
markets$time <- ifelse(markets$date > "2017-03-01", 1, 0)

# date as numeric with 0 as first month and max(month) as last month
## make a "month" variable
markets$month <- sub("-[0-9]*$", "", markets$date)
table(markets$Community.Name, markets$month)
markets$month_num <- car::recode(as.character(markets$month),
                                 "'2016-07'=0;
                                 '2016-08'=1;
                                 '2016-09'=2;
                                 '2016-10'=3;
                                 '2016-11'=4;
                                 '2016-12'=5;
                                 '2017-01'=6;
                                 '2017-02'=7;
                                 '2017-09'=14;
                                 '2017-10'=15;
                                 '2017-11'=16;
                                 '2017-12'=17")
#03=8, 04=9, 05=10, 06=11, 07=12, 08=13

```

### Outcomes

Making variables representing (1) farmers behavior and (2) pastoralists behavior.  Refer to it as farmers index and pastoralists index.

First looked at the skew and decided these outcomes need to be transformed.  Went with ranks & additive index. Might create indices other ways: factors?  ICW?  
    - Would I do that on the ranked or raw variable?
    - raw makes no sense
    - could SD-scale the raw var and then cut it at -3/+3 SDs...still problem of a lot of values at +3 SDs.

```{r, eval=F}
# first look at skew
## extremely right-skewed
summary(markets[,outcomes])
## see biggest 10 values for each outcome (could loop outcomes but not worth it)
#markets[order(markets[,outcomes[4]]),outcomes][(nrow(markets)-10):nrow(markets),]
sapply(markets[outcomes], function(x) quantile(x, seq(0,1,0.1), na.rm=T))

# what kind of distribution are these?
testvar1 <- sample(markets[,outcomes[4],], 3000, replace=T)
plot(density(testvar1, na.rm=T))
## maybe weird poisson-type?
```

Rank the outcomes.

```{r}
# rank the outcomes
# Rank-based outcomes since the raw outcomes are everywhere
## separate t1-t2 ranks
rankOutcomes <- paste0(outcomes, "_rank")
markets[, rankOutcomes] <- NA
markets[markets$time %in% 0,rankOutcomes] <- sapply(markets[markets$time %in% 0,outcomes], dense_rank)
markets[markets$time %in% 1,rankOutcomes] <- sapply(markets[markets$time %in% 1,outcomes], dense_rank)
#summary(markets[,rankOutcomes])
## combined -- I don't like this, don't want outcomes at t1 ranked with outcomes at t2.
#rankOutcomes <- paste0(outcomes, "_rank")
#markets[, rankOutcomes] <- NA
#markets[,rankOutcomes] <- sapply(markets[,outcomes], dense_rank)

# make sure ranked works
markets[order(markets$pastoralist_sellers),c("pastoralist_sellers", "pastoralist_sellers_rank")][1:10,]
```

#### Additive Index

Now make the pastoralists index and the farmers index.

```{r}
# Make a "pastoralist" index and a "Farmer" index
### Rank
markPastor <- names(markets)[grepl("pastor", names(markets))]
markPastor_rank <- markPastor[grepl("_rank", markPastor)]
markets$pastoralists_index_rank <- rowMeans(markets[,markPastor_rank], na.rm=T) # remove NA?

markFarmers <- names(markets)[grepl("farm", names(markets))]
markFarmers_rank <- markFarmers[grepl("_rank", markFarmers)]
markets$farmers_index_rank <- rowMeans(markets[,markFarmers_rank], na.rm=T) # remove NA?
```

Also making raw outcomes for robustness check.

```{r}
### Raw outcome (but cut above 95th percentile because crazy right-skew)
#sapply(markets[outcomes], function(x) quantile(x, seq(0,1,0.05), na.rm=T))
markets[,outcomes] <- lapply(markets[,outcomes], function(x){
  ifelse(x>quantile(x, 0.95, na.rm=T), quantile(x, 0.95, na.rm=T), x)
})
#sapply(markets[outcomes], function(x) quantile(x, seq(0,1,0.05), na.rm=T))

markPastor_raw <- markPastor[!grepl("_rank", markPastor)]
markets$pastoralists_index_raw <- rowMeans(markets[,markPastor_raw], na.rm=T) # remove NA?

markFarmers_raw <- markFarmers[!grepl("_rank", markFarmers)]
markets$farmers_index_raw <- rowMeans(markets[,markFarmers_raw], na.rm=T) # remove NA?


# Revise outcome list to include the indices
outcomes <- names(markets)[grepl("(market|farm|past)", names(markets))]

```

#### Explore other indices

Look at covariance & factor loads.

```{r}


```






<!--
## Stuff to Look at

What do we have?  How many observations for each community in the before (0) and after (1) time categories?

```{r}
(thetab1 <- as.matrix(table(markets$site, markets$time)))
```

Only use a community if it has at least 2 obs before and after.

```{r, include=F}
sigh <- data.frame(comm = rownames(thetab1), bef = thetab1[,1], end = thetab1[,2])

dropsies <- na.omit(ifelse(sigh$bef < 2 | sigh$end < 2, as.character(sigh$comm), NA))
markets <- droplevels(markets[!markets$site %in% dropsies,])
```
-->



************************






# Events

This cleans the event data in the same way as the market data ws cleaned.  It also uses the same analyses as the _Markets_ data: (i) a before-after analysis, and (ii) a panel analysis.

## Cleaning

Here we clean the data, collapse event types (i.e. all festivals as "festival" and wedding/marriage as "marriage"), and other stuff.

```{r, include=F}
# get rid of nothing columns
events <- events[,!grepl("^X", names(events))]

#lower case all non-numerics
typeList <- sapply(events, class)
lowNames <- names(typeList)[!typeList %in% "integer"]
events[,names(events) %in% lowNames] <- as.data.frame(sapply(events[,names(events) %in% lowNames], tolower))

#trim white space
events[,names(events) %in% lowNames] <- as.data.frame(sapply(events[,names(events) %in% lowNames], trimws))

# chris: if events has "marriage|wedding" in the level, just make it "marriage"
# chris: since so few events are not naming ceremonies and weddings, make "other" category.
events$event_type1 <- as.factor(events$event_type)
levels(events$event_type1) <- c("Other", "Marriage", "Marriage", "Naming", 'Other', "Marriage")

# check treatment assignment and state
#tapply(events$treatment, events$site, mean)
events[events$Community.Name %in% "torkula", "State"] <- "benue"

# what's up with totals?
events$test <- events$attend_farm + events$attend_past
test <- events[!events$test %in% events$attend_total,]
test[,c(10:12,20)]
events$test1 <- events$eat_farm + events$eat_past
test <- events[!events$test1 %in% events$eat_total,]
test[,c(13:15,21)]


## making "attend_total" the sum of attend_farm and attend_past in the 7 cases it is slightly different.
events$attend_total <- events$test
events$eat_total <- events$test1
events[,c('test', 'test1')] <- NULL
rm(test)
```


## New Vars

Making a 0-1 variable for if the observations are between July 2016 - Feb 2017 (0) or Sept 2017 - End of study (1).  Make a variable that is 0 in the first month of the study, 10 in the 10th month, 20 in the 20th, etc.

```{r, include=F}
# dichotomous before/after
##july 2016 - feb 2017
## sept 2017 - end
class(events$date.of.observation..M.D.Y.)
events$date <- lubridate::mdy(events$date.of.observation..M.D.Y.)
events$time <- ifelse(events$date > "2017-03-01", 1, 0)

# site
events$site <- events$Community.Name

# date as numeric with 0 as first month and max(month) as last month
## make a "month" variable
events$month <- sub("-[0-9]*$", "", events$date)
table(events$Community.Name, events$month)
events$month_num <- car::recode(as.character(events$month),
                                 "'2016-07'=0;
                                 '2016-08'=1;
                                 '2016-09'=2;
                                 '2016-10'=3;
                                 '2016-11'=4;
                                 '2016-12'=5;
                                 '2017-01'=6;
                                 '2017-02'=7;
                                 '2017-09'=14;
                                 '2017-10'=15;
                                 '2017-11'=16;
                                 '2017-12'=17")

```

Make outcomes numeric and make outcome variables.
- farmers index and pastoralists index to combine attendance & eating of farmers/pastoralists.
- % variables and index that asks what % of attendees are farmers/pastoralists
- rank variables and index that ranks the number of farmers/pastoralists in attendance and who ate (instead of the raw number, which is super skewed).

```{r}
# make outcomes numeric
eventOutcomes <- names(events)[grepl("(attend|eat)_", names(events))]
events[,eventOutcomes] <- sapply(events[,eventOutcomes], function(x) {as.numeric(as.character(x))}) # i think is already integer

# make pastoralist/farmers index outcomes - attend_grp, eat_grp
eventPastor <- names(events)[grepl("past", names(events))]
events$pastoralists_index <- rowMeans(events[,eventPastor])
eventFarmers <- names(events)[grepl("farm", names(events))]
events$farmers_index <- rowMeans(events[,eventFarmers])

# remake outcomes obj
eventOutcomes <- names(events)[grepl("(attend|eat)_|index", names(events))]

# make percentage outcomes: % of attendees who were farm/past & % of eaters who were farm/past
## sort of a farmers/pastoralists "per capita" variable
events[,paste0(eventOutcomes[2:3],"_presPerc")] <- events[,eventOutcomes[2:3]]/events[,eventOutcomes[1]]
events[,paste0(eventOutcomes[5:6],"_eatPerc")] <- events[,eventOutcomes[5:6]]/events[,eventOutcomes[4]]

# make perc index
eventPastorp <- names(events)[grepl("past_(pres|eat)Perc", names(events))]
events$pastoralistsPerc_index <- rowMeans(events[,eventPastorp])
eventFarmerp <- names(events)[grepl("farm_(pres|eat)Perc", names(events))]
events$farmersPerc_index <- rowMeans(events[,eventFarmerp])

# add %s to "eventOutcomes"
eventOutcomes <- names(events)[grepl("(attend|eat)_|index", names(events))]

#rank outcomes
events[,paste0(eventOutcomes, "_rank")] <- sapply(events[,eventOutcomes], dense_rank)
rankEventOutcomes <- paste0(eventOutcomes, "_rank")

summary(events[,eventOutcomes])
```

Now make variable for each observation that is the % of attendees/eaters who are members of the OTHER COMMUNITY.  Main outcome variable created below should be: outgroupPerc_index and outgroup_index_rank.  But need to fix all the outgroup rank variables because they rank within farmer/pastoralist and not within outgroup.

```{r}
farmVars <- names(events)[grepl("farm", names(events))]
pastVars <- names(events)[grepl("past", names(events))]
outgroupVars <- gsub("(farm|farmers)", "outgroup", farmVars)
for(i in 1:length(outgroupVars))
{
  events[,outgroupVars[i]] <- ifelse(events$Host.Community %in% "farmer", events[,pastVars[i]], events[,farmVars[i]])
}

#events[,c("Host.Community", "attend_outgroup", "attend_farm", "attend_past")]

# fix ranks so it ranks within outgroup, not within farmer and pastoralist separately.
outgroupRankVars <- outgroupVars[grepl("rank", outgroupVars)]
outgroupOtherVars <- setdiff(outgroupVars, outgroupRankVars)
markets[markets$time %in% 0,rankOutcomes] <- sapply(markets[markets$time %in% 0,outcomes], dense_rank)
events[,outgroupRankVars] <- sapply(events[,outgroupOtherVars], dense_rank)

#chris: look at ranks to make sure they make sense.
## code correct
events[,c("Host.Community", "pastoralists_index", "farmers_index", "outgroup_index", "outgroup_index_rank")]
## farmers/pastoralists tend to be higher? nope, about same. More farmers attend farmer events than pastoralists attend pastoralist events, but outgroup is about equal.
#mosaic::mean(events$outgroup_index~events$Host.Community, na.rm=T)
#tapply(events$attend_farm, events$Host.Community, mean, na.rm=T)
#tapply(events$attend_past, events$Host.Community, mean, na.rm=T)

tapply(events$attend_farm, events$Host.Community, sd, na.rm=T)
tapply(events$attend_past, events$Host.Community, sd, na.rm=T)
```


<!--
## Stuff to look at

What do we have?  How many observations per community before/after?

```{r}
(thetab <- as.matrix(table(events$Community.Name, events$time)))
#table(events$Community.Name, events$time, events$treatment)
```

Again, only use a community if it has at least 2 obs before and after.

```{r, include=F}
sigh <- data.frame(comm = rownames(thetab), bef = thetab[,1], end = thetab[,2])

dropsies <- na.omit(ifelse(sigh$bef < 2 | sigh$end < 2, as.character(sigh$comm), NA))
events <- droplevels(events[!events$Community.Name %in% dropsies,])
```

```{r, include=F, eval=F}
#with(events[events$treatment %in% 0 & events$time %in% 0,], summary(Number.of.People..in.atttenddance))
#with(events[events$treatment %in% 0 & events$time %in% 1,], summary(Number.of.People..in.atttenddance))

#with(events[events$treatment %in% 1 & events$time %in% 0,], summary(Number.of.People..in.atttenddance))
#with(events[events$treatment %in% 1 & events$time %in% 1,], summary(Number.of.People..in.atttenddance))

# number of pppl in attendance has a huge mean for control at endline, but low median because some people had numbers in the thousands.
##chris: changed var name after this because var names sooo long
#events[events$treatment %in% 0 & events$time %in% 1, c('Number.of.People..in.atttenddance', "event_type", "Community.Name", "Observer.Name", "time")]

#events[events$Observer.Name %in% "alayin apakhi moses", c('Number.of.People..in.atttenddance', "event_type", "Community.Name", "Observer.Name", "time")]
#events[events$event_type %in% "festival", c('Number.of.People..in.atttenddance', "event_type", "Community.Name", "Observer.Name", "time")]

```
-->

# Save clean files

```{r}
save(events, file="a_events_clean.rda")
save(markets, file="a_markets_clean.rda")
save.image("a_obsDat_clean.rda")
```