---
title: 'ObsDat coefficient plots: bstrap coefs'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
load("../clean/a_obsDat_clean.rda")

library(tidyr)
library(dplyr)
library(broom)
#library(HSPSUtils)

# function to sample groups after dplyr::group_by
sample_n_groups = function(tbl, size, replace = TRUE, weight = NULL) {
  # regroup when done
  grps = tbl %>% groups %>% lapply(as.character) %>% unlist
  # check length of groups non-zero
  keep = tbl %>% summarise() %>% ungroup() %>% sample_n(size, replace, weight)
  keep$new_site <- paste0(keep$site, rownames(keep))
  # keep only selected groups, regroup because joins change count.
  # regrouping may be unnecessary but joins do something funky to grouping variable
  tbl %>% inner_join(keep, by=grps) %>% group_by(.dots = grps)
}
```

# Plan

Cluster bootstrap.  SAMPLE SITES WITHIN STATES!!!  SAMPLE WITHIN TR AND CO.

1. Calc coefficients
2. Boostrap SEs
3. Save

When doing residual bootstrapping
- resampling residuals (also doing within state & exp group)
- check assumptions: residual distribution iid?


# Code time

## Markets

### Case resampling

case resample bootstrapping. The thing I know best, though slower (and safer from assumptions!) than residual bootstrap.
    - get coef
    - resamples sites within states; take all obs from those sites
        - needs to mimic sampling: 9 in NAS, 6 in BEN
            - actually only 5 in BEN because no observations in Adaka.
            - Adaka was one of the 2 control sites in Benue...
    - regress outcome on explantory vars for new sample
    - repeat to make bootstrap distribution

```{r, eval=F}
set.seed(1234)

# the lm to get the coefs
#fit.star<-lm(pastoralists_index_rank~treatment*time + site, data=markets)
fit.star<-lm(pastoralists_index_rank~treatment*time, data=markets)

R<-500 # Number of Repetitions
h<-matrix(NA, R, 1)
for (i in 1:R){
  # sample sites within states
  nas_samp1 <- markets[markets$State %in% "nasarawa" & markets$treatment %in% 1,] %>% group_by(site) %>%
    sample_n_groups(size=6) %>%
    as.data.frame()
  nas_samp0 <- markets[markets$State %in% "nasarawa" & markets$treatment %in% 0,] %>% group_by(site) %>%
    sample_n_groups(size=3) %>%
    as.data.frame()
  ben_samp1 <- markets[markets$State %in% "benue" & markets$treatment %in% 1,] %>% group_by(site) %>%
    sample_n_groups(size=4) %>%
    as.data.frame()
  ben_samp0 <- markets[markets$site %in% "sabon gida agan",]
  ben_samp0$new_site <- "sabon gida agan"
  markets1 <- rbind(nas_samp1, nas_samp0, ben_samp1, ben_samp0)
 
  #b<-lm(pastoralists_index_rank~treatment*time + new_site, data=markets1)$coef["treatment:time"]
  b<-lm(pastoralists_index_rank~treatment*time, data=markets1)$coef["treatment:time"]
  h[i,] <- b
}
c1_treat1_ci_case<-quantile(h[,1],c(0.025,0.975))
c1_coefs <- fit.star$coefficients['treatment:time']

# vs canned
estimatr::lm_robust(pastoralists_index_rank ~ treatment*time + site, data=markets, cluster = site, se="CR2")
```

#### Now repeat it for all Obs outcomes.

Start by getting the coefs in a df

```{r}
# get coefs and SDs so coefplot can be effect size
#marketVars <- names(markets)[c(grepl("index", names(markets)))]
#outcomes <- names(markets)[grepl("(market|farm|past)", names(markets))] # already made in loaded .rda

#get coefficient from ols and SD from data
markCoefs <- matrix(NA, nrow=length(outcomes), ncol=3)
for(i in 1:length(outcomes))
{
  #thecoef <- lm(markets[,outcomes[i]]~treatment*time + site + State, data=markets)$coefficients["treatment:time"]
  thecoef <- lm(markets[,outcomes[i]]~treatment*time, data=markets)$coefficients["treatment:time"]
  markCoefs[i,1] <- outcomes[i]
  markCoefs[i,2] <- thecoef
  markCoefs[i,3] <- sd(markets[,outcomes[i]], na.rm=T)
  
}
markCoefs <- as.data.frame(markCoefs)
names(markCoefs) <- c("var", "coef", "sd")
markCoefs[,2:3] <- sapply(markCoefs[,2:3], function(x) {as.numeric(as.character(x))})

```

Now bootstrap the CIs

```{r, eval=F}
set.seed(1234)

bsCIs.fun <- function(var, reps)
{
  R <- reps
  h <- matrix(NA, R, 1)
  for(i in 1:R)
  {
    # sample sites within states
    nas_samp1 <- markets[markets$State %in% "nasarawa" & markets$treatment %in% 1,] %>% group_by(site) %>%
      sample_n_groups(size=6) %>%
      as.data.frame()
    nas_samp0 <- markets[markets$State %in% "nasarawa" & markets$treatment %in% 0,] %>% group_by(site) %>%
      sample_n_groups(size=3) %>%
      as.data.frame()
  ben_samp1 <- markets[markets$State %in% "benue" & markets$treatment %in% 1,] %>% group_by(site) %>%
    sample_n_groups(size=4) %>%
    as.data.frame()
  ben_samp0 <- markets[markets$site %in% "sabon gida agan",]
  ben_samp0$new_site <- "sabon gida agan"
  markets1 <- rbind(nas_samp1, nas_samp0, ben_samp1, ben_samp0)
  
  #b<-lm(markets1[,var]~treatment*time + new_site, data=markets1)$coef["treatment:time"]
  b<-lm(markets1[,var]~treatment*time, data=markets1)$coef["treatment:time"]
  h[i,] <- b
  }
  # get bootstrap CIs from distribution of coefs
  bs_CIs<-quantile(h[,1],c(0.025,0.975))
  #c1_coefs <- thelm$coefficients['treatment:time']
  
  return(bs_CIs)
}
system.time(
for(i in 1:length(outcomes))
{
  CIs <- bsCIs.fun(var=outcomes[i], reps=1000)
  markCoefs[i, c("ll", "ul")] <- bsCIs.fun(var=outcomes[i], reps=1000)
}
)
```

Save.

```{r, eval=F}
#save(markCoefs, file="marketCoefs.rda") #with site and state FEs (biased)
save(markCoefs, file="marketCoefs1.rda") # without FEs
```

Don't run that time-consuming code repeatedly, just load the output.

```{r}
load("marketCoefs.rda")
```

Looking to see why the bootstrap distirbution is bimodal: change over time in some places really different than others -- hugely negative in some CO sites.  When those control sites get bootstrapped in, the estimated treatment effect is pretty large.  When those control sites are not selected, the estimated effect is pretty small.
```{r, eval=F}
test <- markets %>% group_by(site) %>%
  do(test=estimatr::lm_robust(pastoralist_sellers_rank~time, data=.))
```

### Residual bootstrap

CHRIS: NOT DONE

Resample residuals from *sites* within *states*.
    - resample residuals the way we sampled (9 sites in Nas, 6 sites in Ben).
        - actually 5 in Ben, since we didn't observe in Adaka.
    - Then do lm(outcome~treatment) for each resample to make a distribution
    - then take 2.5th quartile and 97.5th quartile from that distribution
    - Repeat for every outcome; add to dataset (chris: not done)







## Events

### Case resampling

case resample bootstrapping. The thing I know best, though slower (and safer from assumptions!) than residual bootstrap.
    - get coef
    - resamples sites within states; take all obs from those sites
        - needs to mimic sampling: 9 in NAS, 6 in BEN
            - no Adaka in Benue, no Gidan Buba in Nassarawa, so actually only 5 (4 treated, 1 control) in BEN and 8 (5 TR, 3 CO) in NAS.
            - Adaka was one of the 2 control sites in Benue...
    - regress outcome on explantory vars for new sample
    - repeat to make bootstrap distribution

```{r, eval=F}
set.seed(1234)

# the lm to get the coefs
#fit.star<-lm(outgroup_index_rank~treatment*time + site, data=events)
fit.star<-lm(outgroup_index_rank~treatment*time, data=events)

R<-500 # Number of Repetitions
h<-matrix(NA, R, 1)
for (i in 1:R){
  # sample sites within states
  nas_samp1 <- events[events$State %in% "nasarawa" & events$treatment %in% 1,] %>% group_by(site) %>%
    sample_n_groups(size=5) %>%
    as.data.frame()
  nas_samp0 <- events[events$State %in% "nasarawa" & events$treatment %in% 0,] %>% group_by(site) %>%
    sample_n_groups(size=3) %>%
    as.data.frame()
  ben_samp1 <- events[events$State %in% "benue" & events$treatment %in% 1,] %>% group_by(site) %>%
    sample_n_groups(size=4) %>%
    as.data.frame()
  ben_samp0 <- events[events$site %in% "sabon gida agan",]
  ben_samp0$new_site <- "sabon gida agan"
  events1 <- rbind(nas_samp1, nas_samp0, ben_samp1, ben_samp0)
 
  #b<-lm(outgroup_index_rank~treatment*time + new_site, data=events1)$coef["treatment:time"]
  b<-lm(outgroup_index_rank~treatment*time, data=events1)$coef["treatment:time"]
  h[i,] <- b
}
c1_treat1_ci_case<-quantile(h[,1],c(0.025,0.975))
c1_coefs <- fit.star$coefficients['treatment:time']

# vs canned
#estimatr::lm_robust(pastoralists_index_rank ~ treatment*time + site, data=events, cluster = site, se="CR2")
estimatr::lm_robust(pastoralists_index_rank ~ treatment*time, data=events, cluster = site, se="CR2")
```

#### Now repeat it for all Obs outcomes.

Start by getting the coefs in a df

```{r}
# get coefs
outgroupVars

#get coefficient from ols
eventCoefs <- matrix(NA, nrow=length(outgroupVars), ncol=3)
for(i in 1:length(outgroupVars))
{
  #thecoef <- lm(events[,outgroupVars[i]]~treatment*time + site + State, data=events)$coefficients["treatment:time"]
  thecoef <- lm(events[,outgroupVars[i]]~treatment*time, data=events)$coefficients["treatment:time"]
  eventCoefs[i,1] <- outgroupVars[i]
  eventCoefs[i,2] <- thecoef
  eventCoefs[i,3] <- sd(events[,outgroupVars[i]], na.rm=T)
  
}
eventCoefs <- as.data.frame(eventCoefs)
names(eventCoefs) <- c("var", "coef", "sd")
eventCoefs[,2:3] <- sapply(eventCoefs[,2:3], function(x) {as.numeric(as.character(x))})

```

Now bootstrap the CIs

```{r}
set.seed(1234)

bsCIs.fun <- function(var, reps)
{
  R <- reps
  h <- matrix(NA, R, 1)
  for(i in 1:R)
  {
    # sample sites within states
    nas_samp1 <- events[events$State %in% "nasarawa" & events$treatment %in% 1,] %>% group_by(site) %>%
      sample_n_groups(size=6) %>%
      as.data.frame()
    nas_samp0 <- events[events$State %in% "nasarawa" & events$treatment %in% 0,] %>% group_by(site) %>%
      sample_n_groups(size=3) %>%
      as.data.frame()
  ben_samp1 <- events[events$State %in% "benue" & events$treatment %in% 1,] %>% group_by(site) %>%
    sample_n_groups(size=4) %>%
    as.data.frame()
  ben_samp0 <- events[events$site %in% "sabon gida agan",]
  ben_samp0$new_site <- "sabon gida agan"
  events1 <- rbind(nas_samp1, nas_samp0, ben_samp1, ben_samp0)
  
  #b<-lm(events1[,var]~treatment*time + new_site, data=events1)$coef["treatment:time"]
  b<-lm(events1[,var]~treatment*time + new_site, data=events1)$coef["treatment:time"]
  h[i,] <- b
  }
  # get bootstrap CIs from distribution of coefs
  bs_CIs<-quantile(h[,1],c(0.025,0.975))
  #c1_coefs <- thelm$coefficients['treatment:time']
  
  return(bs_CIs)
}
system.time(
for(i in 1:length(outgroupVars))
{
  CIs <- bsCIs.fun(var=outgroupVars[i], reps=1000)
  eventCoefs[i, c("ll", "ul")] <- bsCIs.fun(var=outgroupVars[i], reps=1000)
}
)
```

Save.

```{r, eval=F}
#save(eventCoefs, file="eventCoefs.rda") # with site/state FEs
save(eventCoefs, file="eventCoefs1.rda") # without site/state FEs
```

********
#############################################
#############################################










# OLD

#### sample PSUs within state

```{r, eval=F}
set.seed(1234)
#markets.cc <- markets[complete.cases(markets[,c("pastoralists_index_rank", "treatment", "time", "site", "State")]),]

# regression
fit.star<-lm(pastoralists_index_rank~treatment*time + site, data=markets.cc)

# get fitted values and residuals
markets$fit <- fit.star$fitted.values[match(rownames(markets), names(fit.star$fitted.values))]
markets$resid<-fit.star$resid

R<-1000 # Number of Repetitions
h<-matrix(NA, R, 1)
for (i in 1:R){
  # sample residuals
  ## randomly select sites within states, then resample all residuals from a site together, then assign them within that state
  ### or should I assign them 
  sites <- unique(markets$site)
  index <- sample(1:length(sites), length(sites), replace=TRUE)
  aa <- sites[index]
  bb <- table(aa)
  
  markets <- markets %>% dplyr::group_by(State) %>%
    mutate(new_y = fit + sample(resid, replace=TRUE)) %>%
    as.data.frame()
  
  b<-lm(new_y~treatment*time+ site, data=markets)$coef["treatment:time"]
  h[i,] <- b
}
c1_treat1_ci_site<-quantile(h[,1],c(0.025,0.975))
c1_coefs <- fit.star$coefficients['treatment:time']

# vs canned
#estimatr::lm_robust(pastoralists_index_rank ~ treatment*time + site, data=markets, cluster = site, se="CR2")
```



## Make the plot

```{r, eval=F}
outcome <- c(c1_coefs, c1_treat1_ci_site)
names(outcome) <- c("coef", "ll", "ul")
outcome <- as.data.frame(outcome)
outcome <- outcome/sd(markets.cc$pastoralists_index_rank)

png(file="ecpn_obsDat.png")

par(mar=c(5,10,5,2),oma=c(0,0,0,0),mgp=c(1.5,.5,0),mfrow=c(1,1))
maxmods <- ncol(outcome)

## observational data
plot(range(0,2),c(0.5,maxmods),type="n",
     axes=FALSE,ylab="",xlab="Est. Effect Size and 95% CI",
     main="Observational outcomes: Pastoralists Index")
axis(1)
abline(v=0,col="gray",lwd=.5)
points(outcome["coef",],maxmods,pch=19)
segments(outcome["ll",],maxmods, outcome["ul",],maxmods)
axis(2,at=maxmods,labels="Pastoralists Index",las=2)
dev.off()
  
```

Make simpler plot from lm

```{r, eval=F}
# run a regression compatible with tidy
m1 <- estimatr::lm_robust(pastoralists_index_rank ~ treatment*time + site, data=markets, cluster = site, se="CR2")

m1 <- broom::tidy(m1) %>%
    filter(!grepl('site*', term))

# draw a dot-and-whisker plot
png(file="ecpn_obsDat_can.png")
dwplot(m1)
dev.off()
```


*******
#########################################################
#########################################################

## Other versions

No clustered/blocked resampling

```{r, eval=F}
set.seed(1234)
fit.star<-lm(pastoralists_index_rank~treatment*time + site + State, data=markets)
uhat<-fit.star$resid
R<-10000 # Number of Repetitions
h<-matrix(NA, 10000, 2)
for (i in 1:R){
  new_y<-fit.star$fit+sample(uhat,replace=TRUE)
  b<-lm(new_y~markets.cc$treatment*markets.cc$time+markets.cc$site+markets.cc$State)$coef[c("(Intercept)", "markets.cc$treatment:markets.cc$time")]
  h[i,] <- b
}
c1_int_ci_2<-quantile(h[,1],c(0.025,0.975))
c1_treat1_ci_2 <- quantile(h[,2],c(0.025,0.975))
c1_coefs_2 <- fit.star$coefficients

```

Resampling within state

```{r, eval=F}
set.seed(1234)
# if NAs on any variable, then new_y will be diff length.
## so complete.cases only.
markets.cc <- markets[complete.cases(markets[,c("pastoralists_index_rank", "treatment", "time", "site", "State")]),]
fit.star<-lm(pastoralists_index_rank~treatment*time + site + State, data=markets.cc)

markets.cc$fit <- fit.star$fitted.values[match(rownames(markets.cc), names(fit.star$fitted.values))]
markets.cc$resid<-fit.star$resid

R<-10000 # Number of Repetitions
h<-matrix(NA, R, 1) # instead of 1, could do this for mult outcomes
for (i in 1:R){
  # sample within state because randomization at state-level
  markets.cc$new_y <- NA
  markets.cc[markets.cc$State %in% "nasarawa", "new_y"] <- markets.cc[markets.cc$State %in% "nasarawa", "fit"] + sample(markets.cc[markets.cc$State %in% "nasarawa", "resid"], replace=TRUE)
  markets.cc[markets.cc$State %in% "benue", "new_y"] <- markets.cc[markets.cc$State %in% "benue", "fit"] + sample(markets.cc[markets.cc$State %in% "benue", "resid"], replace=TRUE)
  
  b<-lm(new_y~treatment*time+ site + State, data=markets.cc)$coef["treatment:time"]
  h[i,] <- b
}
#c1_int_ci<-quantile(h[,1],c(0.025,0.975))
c1_treat1_ci <- quantile(h[,1],c(0.025,0.975))
c1_coefs <- fit.star$coefficients['treatment:time']

# vs canned
estimatr::lm_robust(pastoralists_index_rank ~ treatment*time + site, data=markets, clusters = site)
```

Site-level resampling

```{r, eval=F}
set.seed(1234)
# if NAs on any variable, then new_y will be diff length.
## so complete.cases only.
markets.cc <- markets[complete.cases(markets[,c("pastoralists_index_rank", "treatment", "time", "site", "State")]),]
fit.star<-lm(pastoralists_index_rank~treatment*time + site, data=markets.cc)

markets.cc$fit <- fit.star$fitted.values[match(rownames(markets.cc), names(fit.star$fitted.values))]
markets.cc$resid<-fit.star$resid

R<-10000 # Number of Repetitions
h<-matrix(NA, R, 1)
for (i in 1:R){
  # sample within Site because that's lowest-level cluster
  markets.cc <- markets.cc %>% dplyr::group_by(site) %>%
    mutate(new_y = fit + sample(resid, replace=TRUE)) %>%
    as.data.frame()
  
  b<-lm(new_y~treatment*time+ site, data=markets.cc)$coef["treatment:time"]
  h[i,] <- b
}
c1_treat1_ci_site<-quantile(h[,1],c(0.025,0.975))
c1_coefs <- fit.star$coefficients['treatment:time']

# vs canned
#estimatr::lm_robust(pastoralists_index_rank ~ treatment*time + site, data=markets, cluster = site, se="CR2")
```

Resampling within Site-time pair

```{r, eval=F}
set.seed(1234)
# if NAs on any variable, then new_y will be diff length.
## so complete.cases only.
markets.cc <- markets[complete.cases(markets[,c("pastoralists_index_rank", "treatment", "time", "site", "State")]),]
fit.star<-lm(pastoralists_index_rank~treatment*time + site + State, data=markets.cc)

markets.cc$fit <- fit.star$fitted.values[match(rownames(markets.cc), names(fit.star$fitted.values))]
markets.cc$resid<-fit.star$resid

R<-10000 # Number of Repetitions
h<-matrix(NA, R, 1)
for (i in 1:R){
  # sample within Site because that's lowest-level cluster
  markets.cc <- markets.cc %>% dplyr::group_by(site,time) %>%
    mutate(new_y = fit + sample(resid, replace=TRUE)) %>%
    as.data.frame()
  
  b<-lm(new_y~treatment*time+ site, data=markets.cc)$coef["treatment:time"]
  h[i,] <- b
}
c1_treat1_ci_time<-quantile(h[,1],c(0.025,0.975))
c1_coefs <- fit.star$coefficients['treatment:time']

```

case resample bootstrapping. same but slow.

```{r, eval=F}
set.seed(1234)
# if NAs on any variable, then new_y will be diff length.
## so complete.cases only.
markets.cc <- markets[complete.cases(markets[,c("pastoralists_index_rank", "treatment", "time", "site", "State")]),]
fit.star<-lm(pastoralists_index_rank~treatment*time + site + State, data=markets.cc)
R<-10000 # Number of Repetitions
h<-matrix(NA, R, 1)
for (i in 1:R){
  # sample within Site because that's lowest-level cluster
  markets.cc1 <- markets.cc %>% dplyr::group_by(site) %>%
    mutate(num=n()) %>%
    sample_n(size=num, replace=TRUE) %>%
    as.data.frame()
  
  b<-lm(pastoralists_index_rank~treatment*time+ site, data=markets.cc1)$coef["treatment:time"]
  h[i,] <- b
}
c1_treat1_ci_case<-quantile(h[,1],c(0.025,0.975))
c1_coefs <- fit.star$coefficients['treatment:time']

# vs canned
estimatr::lm_robust(pastoralists_index_rank ~ treatment*time + site, data=markets, cluster = site, se="CR2")
```

### Other attempts to sample sites within states

```{r, eval=F}

  boot.nas2 <- markets[markets$State %in% "nasarawa",] %>% group_by(site) %>%
    nest() %>%
    sample_n(size=5, replace=T) %>%
    unnest() %>%
    as.data.frame(.)
  boot.ben2 <- panel.df[panel.df$state %in% "ben",] %>% group_by(psu) %>%
    nest() %>%
    sample_n(size=6, replace=T) %>%
    unnest() %>%
    as.data.frame(.)
  boot.samp2 <- rbind(boot.nas2, boot.ben2)
  
  nas_samp <- sample(unique(markets$site), replace=TRUE)
  table(nas_samp)
  
  markets1 <- markets %>% dplyr::group_by(State) %>%
    mutate(num=n()) %>%
    sample_n(size=num, replace=TRUE) %>%
    as.data.frame()

```



# Reference

Nuole original residual bstrap.

```{r, eval=F}
# nuole original
set.seed(1234)
fit.star<-lm(consensus_dec1~as.factor(group_treat), data=analysis_dat_group)
uhat<-fit.star$resid
R<-10000 # Number of Repetitions
h<-matrix(NA, 10000, 3)
for (i in 1:R){
  new_y<-fit.star$fit+sample(uhat,replace=TRUE)
  b<-lm(new_y~as.factor(analysis_dat_group$group_treat))$coef
  h[i,] <- b
}
c1_int_ci<-quantile(h[,1],c(0.025,0.975))
c1_treat1_ci <- quantile(h[,2],c(0.025,0.975))
c1_treat2_ci <- quantile(h[,3],c(0.025,0.975))
c1_coefs <- fit.star$coefficients
```

