---
title: "b-endlineRecode"
author: "cdgrady21"
date: "May 15, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
load("a_ecpn_endline.Rdata")
```

Make the NAs NA instead of "---" so that R knows they are numeric

```{r}
test=end # the test df to mess with
dates <- end[,c("start", "end", "done_calc", "start_calc")]
end[,c("start", "end", "done_calc", "start_calc")] <- NULL
end[end == "---"] <- NA
end <- droplevels(cbind(end, dates))

stopifnot(end[,names(end) %in% names(dates)]==test[,names(test) %in% names(dates)])
```

Some things should still be numeric but are not

```{r}
numVars <- c("income_month", "income_year", "house_num", 
             "how_interact_group.contact_market","contact_group.inHome_group.contact_home_num",
             "contact_group.theirHome_group.contact_home_x_num", 
             "contact_group.social_event_group.contact_event_num",
             "clash_group.violence_number", 'clash_details_group.violence_killed',
             "clash_details_group.violence_injured", "clash_details_group.violence_burned",
             "clash_details_group.violence_when", "insecurity_group.work_days",
             "forum_group.forum_num", "list_exp1a","list_exp1b",
             "rndm1", "rndm2", "rndm3", "duration"
             )

end[, numVars] <- sapply(end[,numVars], function(x) as.numeric(as.character(x)))


#summary(end$clash_details_group.violence_burned)
```

Some open-ended things should be character but are not

```{r}
charTest <- sapply(end, is.character)
charTest[charTest %in% T] # only one var is char

levs.fun <- function(var)
{
  x <- length(levels(var))
  if(x>100){
    TRUE
  }
  else
    FALSE
}

# chris: here.  Make sure open-ended char vars are left as chars by the recode function?
charVars <- c(names(sapply(end, levs.fun)[sapply(end, levs.fun) %in% T]), "ethnic_other")
#head(end[,charVars])
end[,charVars] <- as.data.frame(lapply(end[,charVars], tolower))
end[, charVars] <- sapply(end[,charVars], as.character)
class(end$violence_cause)

```


# Recode functions

```{r}
#########################################
# endline Recode Functions
#########################################
test <- end
end_comf.fun<-function(var)
{
  car::recode(as.character(var),
              "'compcomf'=4;
                      'comf'=3;
                      'neither'=2;
                      'uncomf'=1;
                      'compuncomf'=0;
                      else=NA")
}
#table(test$comfort_group.marry)
#test$marry_x <- end_comf.fun(test$comfort_group.marry)
#table(test$marry_x)
#class(test$marry_x)

end_agree.fun<-function(var)
{
  car::recode(as.character(var), 
              "'stragree'=3;
                      'soagree'=2;
                      'sodisagree'=1;
                      'strdisagree'=0;
                      else=NA")
}
#table(end$econ_benefit_group.benefit_econ)
#test$ben_con <- end_agree.fun(test$econ_benefit_group.benefit_econ)
#table(test$ben_con, exclude=c())
#class(test$ben_con)

end_vio.fun<-function(var)
{
  car::recode(as.character(var), 
              "'always'=0;
                            'sometimes'=1;
                            'rarely'=2;
                            'never'=3;
                            else=NA")
}
#table(end$violence_group.criminals)
#end$vio_crim <- end_vio.fun(end$violence_group.criminals)
#table(end$vio_crim)
#class(end$vio_crim)

end_trust.fun<-function(var)
{
  car::recode(as.character(var), 
              "'notrust'=0;
                      'trustcomplete'=5;
                      '---'=NA;
              'ref'=NA")
}
#table(end$outgroup_atts_group.trust_x)
#end$trust_x <- end_trust.fun(end$outgroup_atts_group.trust_x)
#table(end$trust_x)
#class(end$trust_x)

end_yn.fun<-function(var)
{
  car::recode(as.character(var), 
              "'yes'=1;
              'no'=0;
              else=NA")
}
#table(end$insecurity_group.in_field)
#end$insec_field <- end_yn.fun(end$insecurity_group.in_field)
#table(end$insec_field, exclude=c())
#class(end$insec_field)

end_contr.fun <- function(var)
{
  car::Recode(as.character(var),
                            "'none'=0;
                            'lesshalf'=1;
                            'half'=2;
                            'morehalf'=3;
                            'everyone'=4;
                            else=NA")
}
#table(end$social_cohesion_group2.contribute_x)
#end$sc_contr_x <- end_contr.fun(end$social_cohesion_group2.contribute_x)
#table(end$sc_contr_x)
#class(end$sc_contr_x)

radio.fun <- function(var)
{
  car::Recode(as.character(var),
              "'rare'=0;
              'monthly'=1;
              'weekly'=2;
              '2+week'=3;
              'daily'=4;
              else=NA")
}
#table(test$radio)
#test$rad <- radio.fun(test$radio)
#table(test$rad)

likely.fun <- function(var)
{
  car::Recode(as.character(var),
              "'veryunlikely'=0;
              'somewhatunlikely'=1;
              'neither'=3;
              'somewhatlikely'=4;
              'verylikely'=5;
              else=NA")
}
#table(test$social_cohesion_group2.water_prob)
#test$water <- likely.fun(test$social_cohesion_group2.water_prob)
#table(test$water)

resp.fun <- function(var) # note the threat vars are the ONLY vars where HIGH scores are BAD
{
  car::Recode(as.character(var),
              "'xresp'=0;
              'bothx'=1;
              'bothresp'=2;
              else=NA")
}
#table(test$threat_group.x_responsible)
#test$resp <- resp.fun(test$threat_group.x_responsible)
#table(test$resp)

pos.fun <- function(var)
{
  car::Recode(as.character(var),
              "'veryneg'=0;
              'somewhatneg'=1;
              'neither'=2;
              'somewhatpos'=3;
              'verypos'=4;
              else=NA")
}
#table(test$contact_market_pos)
#test$newvar <- pos.fun(test$contact_market_pos)
#table(test$newvar,exclude=c())

resolve.fun <- function(var)
{
  car::Recode(as.character(var),
              "'never'=0;
              'rare'=1;
              'some'=2;
              'most'=3;
              'all'=4;
              else=NA")
}
#table(end$market_disputes_resolved)
#test$newvar <- resolve.fun(test$market_disputes_resolved)
#table(test$newvar)

effect.fun <- function(var)
{
  car::Recode(as.character(var),
              "'not'=0;
              'somewhat'=1;
              'effective'=2;
              'very'=3;
              else=NA")
}
#table(test$ews_comm_grp.ews_comm_effect)
#test$newvar <- effect.fun(test$ews_comm_grp.ews_comm_effect)
#table(test$newvar)

sat.fun <- function(var)
{
  car::Recode(as.character(var),
              "'not'=0;
              'some'=1;
              'very'=2;
              else=NA")
}
#table(end$pcome_use_group.peace_comm_sat)
#test$newvar <- sat.fun(end$pcome_use_group.peace_comm_sat)
#table(test$newvar)

address.fun <- function(var)
{
  car::Recode(as.character(var),
              "'vsmall'=0;
              'small'=1;
              'medium'=2;
              'great'=3;
              'vgreat'=4;
              else=NA")
}
#table(end$local_gov_address)
#test$newvar<-address.fun(test$local_gov_address)
#table(test$newvar)

endorse.fun <- function(var)
{
  car::Recode(as.character(var),
              "'stroppose'=0;
              'sooppose'=1;
              'indiff'=2;
              'sosupport'=3;
              'strsupport'=4;
              else=NA")
}
#table(test$end_exp1a)
#test$newvar <- endorse.fun(test$end_exp1a)
#table(test$newvar)

# Combining the functions
end_code.fun=function(var)
{
  if(is.character(var) %in% TRUE){ # tell it to ignore char vars
    var
  }
  else if(length(grep("comf",levels(var)))>0){
    end_comf.fun(var)
  }
  else if(length(grep("disagree",levels(var)))>0){
    end_agree.fun(var)
  }
  else if(length(grep("always",levels(var)))>0){
    end_vio.fun(var)
  }
  else if(length(grep("notrust",levels(var)))>0){
    end_trust.fun(var)
  }
  else if(length(grep("yes", levels(var)))>0){
    end_yn.fun(var)
  }
  else if(length(grep("lesshalf", levels(var)))>0){
    end_contr.fun(var)
  }
  else if(length(grep("2.week", levels(var)))>0){
    radio.fun(var)
  }
  else if(length(grep("somewhatunlikely", levels(var)))>0){
    likely.fun(var)
  }
  else if(length(grep("most", levels(var)))>0){
    resolve.fun(var)
  }
  else if(length(grep("effective", levels(var)))>0){
    effect.fun(var)
  }
  else if(length(grep("not", levels(var)))>0){ # has to come after effect.fun ("not" level is in both)
    sat.fun(var)
  }
  else if(length(grep("medium", levels(var)))>0){
    address.fun(var)
  }
  else if(length(grep("strsupport", levels(var)))>0){
    endorse.fun(var)
  }
  else if(length(grep("somewhatpos", levels(var)))>0){
    pos.fun(var)
  }
  else if(length(grep("xresp", levels(var)))>0){
    resp.fun(var)
  }
  else
  var
}
```

Now test the mass recode functions!

```{r}
test$newvar=end_code.fun(test$social_cohesion_group2.contribute_x)
stopifnot(table(test$newvar)['3']==table(test$social_cohesion_group2.contribute_x)['morehalf'])
stopifnot(class(test$newvar) %in% "numeric")

test$newvar <- end_code.fun(test$violence_cause)
stopifnot(class(test$newvar) %in% "character")

test$newvar <- end_code.fun(test$local_gov_address)
#table(test$newvar); table(test$local_gov_address)

test$newvar <- end_code.fun(test$radio)
#table(test$newvar); table(test$radio)


rm(test)

##########
# Recoding endline
#########
df2<-end # keep around for actual wording in responses
end<-data.frame(lapply(end,end_code.fun))

stopifnot(nrow(end)==nrow(df2))
typetest=sapply(end,is.numeric)
stopifnot(typetest['list_exp1a']==TRUE)
stopifnot(typetest['leader_influence']==FALSE)
#stopifnot(length(sapply(df2,class)[sapply(df2,class) %in% "character"]) == length(sapply(end,class)[sapply(end,class) %in% "character"])) # it does not leave character vars as characters, but it does not replace them with NA, either. So, huzzah!

# note chris: end_code.fun needs variables to be FACTORS so it can read the levels.
#typeFacs <- sapply(df2, is.character)
#typeFacs[typeFacs %in% TRUE] # the only character vars in df2 were coerced to factors and then left alone by the recode function.
```

# Some questions need to be reverse coded

get_along
values
share_farmland/pasture/market_tension/dispute
dispute_persist

NOT the threat vars, which are all coded so HIGH is BAD:
x_threat
x_influence
x_values

All 4 category 0-3 vars.

```{r}
##########
# Reverse code questions that need to be reversed
##########
rev.fun<-function(var)
{
  var <- abs(var-max(var, na.rm=T))
}

revVars <- c('social_cohesion_group.get_along', 'social_cohesion_group.values', "dispute_persist",
             names(end)[grepl("share_.*_(tension|dispute)", names(end))]
             #'threat_group.threat_dis_group.x_threat', 'threat_group.threat_dis_group.x_influence',
             #'threat_group.threat_dis_group.x_values'
             )
end[,revVars] <- sapply(end[,revVars], rev.fun)

```





# Save

The things like "treatment community" will be added when baseline and endline are combined.

Rescale all vars 0-1 will be done when baseline and endline are combined.

A-arewa_data_recode.R in the NigeriaTV/Endline/wrkfolder can help.

```{r}
save(end, df2, file="b_endlineRecode.Rdata")

```

