---
title: "c-baselineRecode"
author: "cdgrady21"
date: "May 15, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
load('a_ecpn_baseline.Rdata')
```

Make the NAs NA instead of "---" so that R knows they are numeric

```{r}
test=base # the test df to mess with
base[base == "---"] <- NA
base <- droplevels(base)
```

Some things should still be numeric but are not

```{r}
thing <- sapply(base,class); table(thing); thing[thing %in% "integer"]
base$hours <- as.numeric(as.character(sub(":.*", "", base$duration)))
base$minutes <- as.numeric(as.character(sub(".*:", "", base$duration)))
base$duration <- (base$hours * 60) + base$minutes
#base[1:10,c("duration", "hours", "minutes")]


numVars <- c("income_month", "income_year", "age", 
             "contact_market","contact_group.contact_home_num",
             "contact_group.contact_home_x_num", 
             "contact_group.contact_event_num",
             "clash_group.violence_number", 'clash_group.violence_killed',
             "clash_group.violence_when", "insecurity_group.work_days",
             "list_exp1a","list_exp1b", "rndm1", "rndm2", "rndm3",
             "duration"
             )

base[, numVars] <- sapply(base[,numVars], function(x) as.numeric(as.character(x)))


#summary(base$clash_group.violence_killed)
```

Some open-ended things should be character but are not

```{r}
charTest <- sapply(base, is.character)
charTest[charTest %in% T] # only name var is char

levs.fun <- function(var)
{
  x <- length(levels(var))
  if(x>100){
    TRUE
  }
  else
    FALSE
}

# chris: here.  Make sure open-baseed char vars are left as chars by the recode function?
charVars <- c(names(sapply(base, levs.fun)[sapply(base, levs.fun) %in% T]), "ethnic_other", "name.1")
#head(base[,charVars])
base[,charVars] <- as.data.frame(lapply(base[,charVars], tolower))
base[, charVars] <- sapply(base[,charVars], as.character)
class(base$clash_group.violence_cause)
class(base$ethnic_other)
```



# Recode functions

```{r}
#########################################
# baseline Recode Functions
#########################################
test <- base
base_comf.fun<-function(var)
{
  car::recode(as.character(var),
              "'compcomf'=4;
                      'comf'=3;
                      'neither'=2;
                      'uncomf'=1;
                      'compuncomf'=0;
                      else=NA")
}
#table(test$comfort_group.marry)
#test$marry_x <- base_comf.fun(test$comfort_group.marry)
#table(test$marry_x)
#class(test$marry_x)

base_agree.fun<-function(var)
{
  car::recode(as.character(var), 
              "'stragree'=3;
                      'soagree'=2;
                      'sodisagree'=1;
                      'strdisagree'=0;
                      else=NA")
}
#table(base$econ_benefit_group.benefit_econ)
#test$ben_con <- base_agree.fun(test$econ_benefit_group.benefit_econ)
#table(test$ben_con, exclude=c())
#class(test$ben_con)

base_vio.fun<-function(var)
{
  car::recode(as.character(var), 
              "'always'=0;
                            'sometimes'=1;
                            'rarely'=2;
                            'never'=3;
                            else=NA")
}
#table(base$violence_group.criminals)
#base$vio_crim <- base_vio.fun(base$violence_group.criminals)
#table(base$vio_crim)
#class(base$vio_crim)

base_trust.fun<-function(var)
{
  car::recode(as.character(var), 
              "'notrust'=0;
                      'trustcomplete'=5;
                      '---'=NA;
              'ref'=NA")
}
#table(base$outgroup_atts_group.trust_x)
#base$trust_x <- base_trust.fun(base$outgroup_atts_group.trust_x)
#table(base$trust_x)
#class(base$trust_x)

base_yn.fun<-function(var)
{
  car::recode(as.character(var), 
              "'yes'=1;
              'no'=0;
              else=NA")
}
#table(base$insecurity_group.in_field)
#base$insec_field <- base_yn.fun(base$insecurity_group.in_field)
#table(base$insec_field, exclude=c())
#class(base$insec_field)

base_contr.fun <- function(var)
{
  car::Recode(as.character(var),
                            "'none'=0;
                            'lesshalf'=1;
                            'half'=2;
                            'morehalf'=3;
                            'everyone'=4;
                            else=NA")
}
#table(base$social_cohesion_group2.contribute_x)
#base$sc_contr_x <- base_contr.fun(base$social_cohesion_group2.contribute_x)
#table(base$sc_contr_x)
#class(base$sc_contr_x)

radio.fun <- function(var)
{
  car::Recode(as.character(var),
              "'rare'=0;
              'monthly'=1;
              'weekly'=2;
              '2+week'=3;
              'daily'=4;
              else=NA")
}
#table(test$radio)
#test$rad <- radio.fun(test$radio)
#table(test$rad)

likely.fun <- function(var)
{
  car::Recode(as.character(var),
              "'veryunlikely'=0;
              'somewhatunlikely'=1;
              'neither'=3;
              'somewhatlikely'=4;
              'verylikely'=5;
              else=NA")
}
#table(test$social_cohesion_group2.water_prob)
#test$water <- likely.fun(test$social_cohesion_group2.water_prob)
#table(test$water)

resp.fun <- function(var)
{
  car::Recode(as.character(var),
              "'xresp'=0;
              'bothx'=1;
              'bothresp'=2;
              else=NA")
}
#table(test$threat_group.x_responsible)
#test$resp <- resp.fun(test$threat_group.x_responsible)
#table(test$resp)

pos.fun <- function(var)
{
  car::Recode(as.character(var),
              "'veryneg'=0;
              'somewhatneg'=1;
              'neither'=2;
              'somewhatpos'=3;
              'verypos'=4;
              else=NA")
}
#table(test$contact_market_pos, exclude=c())
#test$newvar <- pos.fun(test$contact_market_pos)
#table(test$newvar,exclude=c())

resolve.fun <- function(var)
{
  car::Recode(as.character(var),
              "'never'=0;
              'rare'=1;
              'some'=2;
              'most'=3;
              'all'=4;
              else=NA")
}
#table(base$market_disputes_resolved)
#test$newvar <- resolve.fun(test$market_disputes_resolved)
#table(test$newvar)

# Effectiveness, satisfaction are endline only
#thing <- sapply(base, function(x) length(grep("sat", levels(x)))>0)
#thing[thing %in% T] #nothing

address.fun <- function(var)
{
  car::Recode(as.character(var),
              "'vsmall'=0;
              'small'=1;
              'medium'=2;
              'great'=3;
              'vgreat'=4;
              else=NA")
}
#table(base$local_gov_address)
#test$newvar<-address.fun(test$local_gov_address)
#table(test$newvar)

endorse.fun <- function(var)
{
  car::Recode(as.character(var),
              "'stroppose'=0;
              'sooppose'=1;
              'indiff'=2;
              'sosupport'=3;
              'strsupport'=4;
              else=NA")
}
#table(test$end_exp1a)
#test$newvar <- endorse.fun(test$end_exp1a)
#table(test$newvar)

# Combining the functions
base_code.fun=function(var)
{
  if(is.character(var) %in% TRUE){ # tell it to ignore char vars
    var
  }
  else if(length(grep("comf",levels(var)))>0){
    base_comf.fun(var)
  }
  else if(length(grep("disagree",levels(var)))>0){
    base_agree.fun(var)
  }
  else if(length(grep("always",levels(var)))>0){
    base_vio.fun(var)
  }
  else if(length(grep("notrust",levels(var)))>0){
    base_trust.fun(var)
  }
  else if(length(grep("yes", levels(var)))>0){
    base_yn.fun(var)
  }
  else if(length(grep("lesshalf", levels(var)))>0){
    base_contr.fun(var)
  }
  else if(length(grep("2.week", levels(var)))>0){
    radio.fun(var)
  }
  else if(length(grep("somewhatunlikely", levels(var)))>0){
    likely.fun(var)
  }
  else if(length(grep("most", levels(var)))>0){
    resolve.fun(var)
  }
  else if(length(grep("medium", levels(var)))>0){
    address.fun(var)
  }
  else if(length(grep("strsupport", levels(var)))>0){
    endorse.fun(var)
  }
  else if(length(grep("somewhatpos", levels(var)))>0){
    pos.fun(var)
  }
  else if(length(grep("xresp", levels(var)))>0){
    resp.fun(var)
  }
  else
  var
}
```


Now test and run the mass recode functions!

```{r}
test$newvar=base_code.fun(test$social_cohesion_group2.contribute_x)
stopifnot(table(test$newvar)['3']==table(test$social_cohesion_group2.contribute_x)['morehalf'])
stopifnot(class(test$newvar) %in% "numeric")

test$newvar <- base_code.fun(test$clash_group.violence_cause)
stopifnot(class(test$newvar) %in% "character")

test$newvar <- base_code.fun(test$list_exp1a)
table(test$newvar)
table(test$list_exp1a)

#
rm(test)

##########
# Recoding baseline
#########
df1<-base # keep around for actual wording in responses
base<-as.data.frame(lapply(base,base_code.fun))

stopifnot(nrow(base)==nrow(df1))
typetest=sapply(base,is.numeric)
stopifnot(typetest['list_exp1a']==TRUE)
stopifnot(typetest['leader_influence']==FALSE)

```



# Some questions need to be reverse coded

get_along
values
share_farmland/pasture/market_dispute/tension

NOT the threat vars (these are handled later), which are all coded so HIGH is BAD:
x_threat
x_influence
x_values

All 4 category 0-3 vars.

```{r}
##########
# Reverse code questions that need to be reversed
##########
rev.fun<-function(var)
{
  var <- abs(var-max(var, na.rm=T))
}

revVars <- c('social_cohesion_group.get_along', 'social_cohesion_group.values', "dispute_persist",
             names(base)[grepl("share_.*_(tension|dispute)", names(base))]
             #'threat_group.x_threat', 'threat_group.x_influence',
             #'threat_group.x_values'
             )
# summary(base[,revVars])
base[,revVars] <- sapply(base[,revVars], rev.fun)

```

# Save

The things like "treatment community" will be added when baseline and endline are combined.

Rescale all vars 0-1 will be done when baseline and endline are combined.

A-arewa_data_recode.R in the NigeriaTV/Endline/wrkfolder can help.

```{r}
save(base, df1, file="b_baselineRecode.Rdata")

```
