---
title: "d-baselineEndlineCombine"
author: "cdgrady21"
date: "May 15, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
load("b_endlineRecode.Rdata")
load("b_baselineRecode.Rdata")
```

# Choose cols I want

Stuff like getting the big "ethnic_other" categories into "ethnic"

```{r}
# base
sort(table(end$ethnic_other))
end$ethnic_other[grepl("rago", end$ethnic_other) | grepl("lago", end$ethnic_other)] <- "alago"
end$ethnic_other[grepl("oro", end$ethnic_other) | grepl("ili", end$ethnic_other)] <- "koro"
end$ethnic_other[grepl("juku", end$ethnic_other)] <- "jukun"
#end$ethnic_other[grepl("aho", end$ethnic_other) | grepl("awo", end$ethnic_other)] <- "afo" # cannot be sure these are afo and not awori people (yoruba tribe) or something
end$community[end$ethnic_other %in% "afo"]

# end
sort(table(base$ethnic_other))
base$ethnic_other[grepl("rago", base$ethnic_other) | grepl("lago", base$ethnic_other)] <- "alago"
base$ethnic_other[grepl("oro", base$ethnic_other) | grepl("ili", base$ethnic_other)] <- "koro"
base$ethnic_other[grepl("afo", base$ethnic_other)] <- "afo"

groups <- c("eggon", "agatu", "jukun", "koro", "afo", "alago")
end$ethnic <- as.character(end$ethnic)
base$ethnic <- as.character(base$ethnic)
end$ethnic2 <- ifelse(end$ethnic %in% "other" & end$ethnic_other %in% groups, as.character(end$ethnic_other), end$ethnic)
base$ethnic2 <- ifelse(base$ethnic %in% "other" & base$ethnic_other %in% groups, as.character(base$ethnic_other), base$ethnic)

#table(end$ethnic, end$ethnic2)
#table(base$ethnic, base$ethnic2)
```


Grab the endline cols I want

```{r}
#end$conf_group <- # I suspect I'll need to make the most common ~6 of these binary.  Will recode conf_group to be one of the ~6 most common, or "other", then make binary with model.matrix.

# qip groups combine -- chris: note that some of the ushata ppl were asked this questino because an enumerator said they were in Loko, and 5 of the Ushata people knew about the qip project.
awCols <- names(end)[grepl("qip_aware",names(end))]
qips<-end[,c('num',awCols)]
qip.df=cbind(qips[1], unlist(qips[-1],use.names = F))
names(qip.df)<-c("num","qip_aware")
qip.df<-droplevels(na.omit(qip.df))

benCols <- names(end)[grepl("qip_ben",names(end))]
qips2<-end[,c('num',benCols)]
qip.df2=cbind(qips2[1], unlist(qips2[-1],use.names = F))
names(qip.df2)<-c("num","qip_ben")
qip.df2<-droplevels(na.omit(qip.df2))
qip <- merge(qip.df, qip.df2, by="num", all=T)

end<-merge(end, qip, by="num",all=T)


# Lastly, colnames
names(end)
endVars <- c("username", "state", "farm_pastor", "comm_leader", "pre_selected", "id_num", "select_grp.house_size",
             "gender", "age", "ethnic2", "religion", "occupation", 'radio', "income_year", 'income_month',
             "group_group_conflict.conflict_group", 
             names(end)[grepl("social_cohesion_group", names(end))],
             names(end)[grepl("outgroup_atts", names(end))], 
             names(end)[grepl("comfort_group", names(end))],
             names(end)[grepl("econ_benefit", names(end))],
             names(end)[grepl("threat_group[.]", names(end))],
             "x_at_market", "how_interact_group.contact_market", "how_interact_group.how_interact_type", "contact_market_pos",
             "contact_nonmarket", "contact_group.social_event_group.contact_event", "contact_group.social_event_group.contact_event_num",
             "contact_group.inHome_group.contact_home", "contact_group.inHome_group.contact_home_num",
             "contact_group.theirHome_group.contact_home_x", "contact_group.theirHome_group.contact_home_x_num",
             "contact_group.contact_other_group.contact_other", "contact_pos",
             names(end)[grepl("clash", names(end))], "violence_effect", "violence_work_effect",
             names(end)[grepl("avoid", names(end))],
             names(end)[grepl("insecurity", names(end))],
             names(end)[grepl("^share_", names(end))], names(end)[grepl("_resolve", names(end))], "resolve_peace",
             names(end)[grepl("violence_group", names(end))], "violence_cause",
             "pgp_amount",
             names(end)[grepl("^dispute_", names(end))][-3],
             names(end)[grepl("(peace|ews)_comm_", names(end))],
             "leader_influence", "local_gov_address",
             names(end)[grepl("_exp[0-9]", names(end))],
             names(end)[grepl("(ecpn|MC)_group", names(end))][-3],
             names(end)[grepl("(committee|forum)_group", names(end))][-3],
             names(end)[grepl("borehole", names(end))], "qip_aware", "qip_ben",
             "duration", "psu", "community"
             )
end <- end[,endVars]
```


Grab the baseline cols I want

```{r}
baseVars <- intersect(endVars, names(base))
notIn <- setdiff(names(base) ,baseVars)
needIn <- setdiff(endVars, names(base))

baseVars <- c(baseVars,
              'info.username', "site_num", "name", 'farm.pastor', 
              names(base)[grepl("threat_group[.]", names(base))][-1],
              "contact_market",  notIn[grepl("(event|home)", notIn)], "contact_other",
              notIn[grepl("clash_group", notIn)],
              "violence_affect", "name.1"
              )
base <- base[,baseVars]

```


# Make cols have same names and combine

Could have fuzzy matched this, but it wasn't much work to just match them myself.

```{r}
diffNames <- setdiff(names(base), names(end)) # psu is site_num, community is name.
setdiff(names(end), names(base))
names(base)[names(base) %in% diffNames] <- c("username", "psu", "community", "farm_pastor",
                                             "threat_group.threat_dis_group.x_threat", 
                                             "threat_group.threat_dis_group.x_influence",
                                             "threat_group.threat_dis_group.x_values",
                                             'how_interact_group.contact_market', 
                                             "contact_group.social_event_group.contact_event", 
                                             "contact_group.social_event_group.contact_event_num",
                                             "contact_group.inHome_group.contact_home",
                                             "contact_group.inHome_group.contact_home_num",
                                             "contact_group.theirHome_group.contact_home_x",
                                             "contact_group.theirHome_group.contact_home_x_num",
                                             "contact_group.contact_other_group.contact_other",
                                             "clash_details_group.violence_when", "clash_details_group.violence_killed",
                                             "violence_cause", "violence_effect", "name.1"
                                             )


# make as NA the cols that are not in base or end
notInBase <- setdiff(names(end), names(base))
base[,notInBase] <- NA
notInEnd <- setdiff(names(base), names(end)) # this should be only name.1 (and is)
end[,notInEnd] <- NA
stopifnot(length(notInEnd)==1)

base$survey <- 0
end$survey <- 1

# make same order
end <- end[, sort(names(end))]
base <- base[, sort(names(base))]
stopifnot(names(end)==names(base))


# Combine
df <- rbind(base,end)

# remove useless vars that remain
df$share_market1 <- NULL
names(df)[names(df)=="share_market2"] <- "share_market"

# make colnames shorter?
# names(df) <- sub() # only keep things after last period, if there is a period. # decided against, these names are fine

```


Change some variables' levels/response options

```{r}
# mixed up 20f and 20f1 at endline.  At baseline, 20f is eggon and 20f1 is alago.  At endline, 20f is alago and 20f1 (eggon) is gone.
##twenty <- droplevels(df[df$psu %in% 20,])
#table(twenty$community,twenty$ethnic2)
df$community <- car::Recode(df$community, 
                            "'20f1'='20f';
                            '20f'='20f1'")

levels(df$community)[grepl("[1-9]*(f|p)$", levels(df$community))]
levels(df$community)[grepl("p$", levels(df$community))] <- paste0(sub("p", "", levels(df$community)[grepl("p$", levels(df$community))]), ".pastoralists")
levels(df$community)[grepl("f$", levels(df$community))] <- paste0(sub("f", "", levels(df$community)[grepl("f$", levels(df$community))]), ".farmers")

```

Now drop from baseline the communities we lost between baseline and endline

```{r}
# drop community 20f1 & comm 30, who we did not survey at endline. Should drop 152 respondents.
## only alago in 20f; eggon are gone at endline.
df <- droplevels(df[!df$community %in% c("20f1", "30.farmers", "30.pastoralists"),])
# in base df, drop 20f and 30f/p
base <- droplevels(base[!base$community %in% c("20f", "30f", "30p"),])
df1 <- droplevels(df1[!df1$name %in% c("20f", "30f", "30p"),])
```


Add comm-level variables, like treatment

```{r}
# Add treatment comm var
df$treatment <- ifelse(df$psu %in% c(1,4,10,20,50,51,21,22,32,35), 1, 0)
```


# Save

```{r}
save(df,df1,df2,base,end, file="c_dataCombine.Rdata")

```