---
title: "g-aggAnalysis for academic paper"
output:
  word_document:
    toc: yes
  pdf_document:
    number_sections: yes
    toc: yes
  html_document:
    df_print: paged
    toc: yes
---

<!--Chris: notes

Want to replace all lm() with lm_lin() but lm_lin() does not allow me to vary treatment in a function.-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(76465)
rm(list=ls())
load("../c_creating_dataframes/f-aggregateComms_ap.Rdata")
load("../c_creating_dataframes/rand_df.Rdata")
#load("f-aggregateData_together.Rdata")
#load("rand_df_together.Rdata")

library(NPC)
library(dplyr)
library(mosaic)
library(estimatr)
library(robustbase)
library(quantreg)
library(sandwich)
library(clubSandwich)
library(lmtest)
library(coin)

#author: "cdgrady21"
#date: '`r format(Sys.Date(), "%B %d, %Y")`'


#True p-value function.  Don't need covariate adjustment to absorb error.  True p's Especially necessary with community level analysis, because we have a small number of clusters.  Treatment assigned at PSU level.

# Differencing
true.fun1 <- function(var, tr, nsims=3000, dat=ag.df)
{
  if(grepl("resid", var)){
    thelm <- lm(dat[,var]~dat[,tr], data=dat)
    thecoef <-coef(thelm)[2]
    
    rand.coef = rep(NA,nsims)
    for(i in 1:nsims){
      rand.nas <- sample(unique(dat$psu[dat$state %in% "nas"]), size=6)
      rand.ben <- sample(unique(dat$psu[dat$state %in% "ben"]), size=4)
      rand <- c(as.character(rand.nas), as.character(rand.ben))
      rand.samp <- dat
      rand.samp$treatment <- ifelse(rand.samp$psu %in% rand, 1, 0)
      tr.lm <- lm(tr_fmla,rand.samp)
      lm.tr_resid<-resid(tr.lm)
      rand.samp[names(lm.tr_resid),"tr_resid"]<-lm.tr_resid
      
      lm.null <- lm(rand.samp[,var]~rand.samp[,tr], data=rand.samp)
      rand.coef[i] <- summary(lm.null)$coefficients[2,1]
    }
  }
  else if(tr=="treatment"){
    thelm <- lm(dat[,var]~dat[,tr]+state, data=dat)
    thecoef <-coef(thelm)[2]
    
    rand.coef = rep(NA,nsims)
    for(i in 1:nsims){
      rand.nas <- sample(unique(dat$psu[dat$state %in% "nas"]), size=6)
      rand.ben <- sample(unique(dat$psu[dat$state %in% "ben"]), size=4)
      rand <- c(as.character(rand.nas), as.character(rand.ben))
      rand.samp <- dat
      rand.samp[,tr] <- ifelse(rand.samp$psu %in% rand, 1, 0)
     
      lm.null <- lm(rand.samp[,var]~rand.samp[,tr]+state, data=rand.samp)
      rand.coef[i] <- summary(lm.null)$coefficients[2,1]
      }
  }
  else{
    thelm <- lm(dat[,var]~dat[,tr]+state, data=dat)
    thecoef <-coef(thelm)[2]
    
    rand.coef = rep(NA,nsims)
    for(i in 1:nsims){
      rand.samp <- dat %>% dplyr::group_by(state) %>% # for indices predicting indices, just shuffle within state.
        mutate(newtr = shuffle(.data[[tr]])) %>%
        as.data.frame(.)
      
      lm.null <- lm(rand.samp[,var]~rand.samp[,'newtr']+state, data=rand.samp)
      rand.coef[i] <- summary(lm.null)$coefficients[2,1]
    }
  }
  thep <- mean(rand.coef>thecoef)
  thedf <- data.frame(coef=thecoef,truep=thep)
  rownames(thedf) <- paste0(var, "~",tr)
  return(thedf)
}
#true.fun(var='x_index', tr='treatment')
#true.fun(var='x_cw', tr='treatment')
#true.fun(var='cohes_cw', tr='bene_cw')
#true.fun(var='x_cw_resid', tr='tr_resid') # doing this with resids #1 doesn't make sense to me, #2 doesn't change results, and #3 takes a long time.
## would make sense if there was a confounder, but this is a randomized experiment so should not have confounders. Could maybe use error reduction.


######## Controlling For
true.fun <- function(var, tr, nsims=3000, dat=ag.df)
{
  if(grepl("resid", var)){
    thelm <- lm(dat[,var]~dat[,tr], data=dat)
    thecoef <-coef(thelm)[2]
    
    rand.coef = rep(NA,nsims)
    for(i in 1:nsims){
      rand.nas <- sample(unique(dat$psu[dat$state %in% "nas"]), size=6)
      rand.ben <- sample(unique(dat$psu[dat$state %in% "ben"]), size=4)
      rand <- c(as.character(rand.nas), as.character(rand.ben))
      rand.samp <- dat
      rand.samp$treatment <- ifelse(rand.samp$psu %in% rand, 1, 0)
      tr.lm <- lm(tr_fmla,rand.samp)
      lm.tr_resid<-resid(tr.lm)
      rand.samp[names(lm.tr_resid),"tr_resid"]<-lm.tr_resid
      
      lm.null <- lm(rand.samp[,var]~rand.samp[,tr], data=rand.samp)
      rand.coef[i] <- summary(lm.null)$coefficients[2,1]
    }
  }
  else if(tr=="treatment" & (grepl("end", var) | grepl("y1", var))){
    thelm <- lm(dat[,var]~dat[,tr]+state, data=dat)
    thecoef <-coef(thelm)[2]
    
    rand.coef = rep(NA,nsims)
    for(i in 1:nsims){
      rand.nas <- sample(unique(dat$psu[dat$state %in% "nas"]), size=6)
      rand.ben <- sample(unique(dat$psu[dat$state %in% "ben"]), size=4)
      rand <- c(as.character(rand.nas), as.character(rand.ben))
      rand.samp <- dat
      rand.samp[,tr] <- ifelse(rand.samp$psu %in% rand, 1, 0)
     
      lm.null <- lm(rand.samp[,var]~rand.samp[,tr]+state, data=rand.samp)
      rand.coef[i] <- summary(lm.null)$coefficients[2,1]
      }
  }
  else if(tr=="treatment" & !(grepl("end", var) | grepl("y1", var))){
    thelm <- lm(dat[,paste0(var,"_end")]~dat[,tr]+dat[,paste0(var,"_base")]+state, data=dat)
    thecoef <-coef(thelm)[2]
    
    rand.coef = rep(NA,nsims)
    for(i in 1:nsims){
      rand.nas <- sample(unique(dat$psu[dat$state %in% "nas"]), size=6)
      rand.ben <- sample(unique(dat$psu[dat$state %in% "ben"]), size=4)
      rand <- c(as.character(rand.nas), as.character(rand.ben))
      rand.samp <- dat
      rand.samp[,tr] <- ifelse(rand.samp$psu %in% rand, 1, 0)
     
      lm.null <- lm(rand.samp[,paste0(var,"_end")]~rand.samp[,tr]+dat[,paste0(var,"_base")]+state, data=rand.samp)
      rand.coef[i] <- summary(lm.null)$coefficients[2,1]
      }
  }
  else if(grepl("end", var) | grepl("y1", var)){
    thelm <- lm(dat[,var]~dat[,tr]+state, data=dat)
    thecoef <-coef(thelm)[2]
    
    rand.coef = rep(NA,nsims)
    for(i in 1:nsims){
      rand.samp <- dat %>% dplyr::group_by(state) %>% # for indices predicting indices, just shuffle within state.
        mutate(newtr = shuffle(.data[[tr]])) %>%
        as.data.frame(.)
      
      lm.null <- lm(rand.samp[,var]~rand.samp[,'newtr']+state, data=rand.samp)
      rand.coef[i] <- summary(lm.null)$coefficients[2,1]
    }
  }
  else if(!grepl("end", var) | grepl("y1", var)){
    thelm <- lm(dat[,paste0(var,"_end")]~dat[,tr]+dat[,paste0(var,"_base")]+state, data=dat)
    thecoef <-coef(thelm)[2]
    
    rand.coef = rep(NA,nsims)
    for(i in 1:nsims){
      rand.samp <- dat %>% dplyr::group_by(state) %>% # for indices predicting indices, just shuffle within state.
        mutate(newtr = shuffle(.data[[tr]])) %>%
        as.data.frame(.)
      
      lm.null <- lm(rand.samp[,paste0(var,"_end")]~rand.samp[,'newtr']+dat[,paste0(var,"_base")]+state, data=rand.samp)
      rand.coef[i] <- summary(lm.null)$coefficients[2,1]
    }
  }
  
  thep <- mean(rand.coef>thecoef)
  thedf <- data.frame(coef=thecoef,truep=thep)
  rownames(thedf) <- paste0(var, "~",tr)
  return(thedf)
}
#true.fun(var='x_index', tr='treatment')
#true.fun(var='x_cw', tr='treatment')
#true.fun(var='cohes_cw', tr='bene_cw')
#true.fun(var='x_cw_resid', tr='tr_resid') # doing this with resids #1 doesn't make sense, #2 doesn't change results, and #3 takes a long time.
## would make sense if there was a confounder, but this is a randomized experiment so should not have confounders.
#true.fun(var="pgp_amount_end", tr="treatment")
#true.fun('pgp_donate_end', 'bene_cw')
#true.fun('rMean', 'treatment')
#true.fun1('rMean', 'treatment')



# Which function to use?
strat.fun <- function(var){
  thesd <- sd(ag.df[[var]])*.2
  thediff <- abs(mosaic::mean(ag.df[[var]]~ag.df$treatment)[1]-mosaic::mean(ag.df[[var]]~ag.df$treatment)[2])
  thebal <- thediff-thesd
  if(thebal<0){
    return("Controlling-for: true.fun")
  }
  if(thebal>=0){
    return("Difference: true.fun1")
  }
  else(return("Fail"))
}
#strat.fun("x_cw_base")

```
```{r, eval=F, include=F}
# I prefer the SD method, but could also use lin hypothesis test or an equivalence test.
## issue with these: we are super low powered, so no baseline differences will be stat sig.  And equivalence test will always say "not same, not diff"

# Hypothesis test
(x1_test <- lm_lin(x_cw_base~treatment, covariates= ~state, data=ag.df, clusters=psu))

# equivalence
TOSTtwo(m1=mean(ag.df$x_cw_base[ag.df$treatment %in% 0]), m2=mean(ag.df$x_cw_base[ag.df$treatment %in% 1]), 
        sd1=sd(ag.df$x_cw_base[ag.df$treatment %in% 0]), sd2=sd(ag.df$x_cw_base[ag.df$treatment %in% 1]), 
        n1=length(unique(ag.df$comm[ag.df$treatment %in% 0])), n2=length(unique(ag.df$comm[ag.df$treatment %in% 1])),
        low_eqbound_d=-0.1, high_eqbound_d=0.1, alpha = 0.05)

TOSTtwo(m1=mean(ag.df$contactOnly_cw_base[ag.df$treatment %in% 0]), m2=mean(ag.df$contactOnly_cw_base[ag.df$treatment %in% 1]), 
        sd1=sd(ag.df$contactOnly_cw_base[ag.df$treatment %in% 0]), sd2=sd(ag.df$contactOnly_cw_base[ag.df$treatment %in% 1]), 
        n1=length(unique(ag.df$comm[ag.df$treatment %in% 0])), n2=length(unique(ag.df$comm[ag.df$treatment %in% 1])),
        low_eqbound_d=-0.01, high_eqbound_d=0.01, alpha = 0.05)
```

# Subsets

Look at farmers and pastoralists separately.

```{r}
farmers <- ag.df[grepl(".farmers", ag.df$comm),]
pastors <- ag.df[grepl(".pastor", ag.df$comm),]
```

Look at states separately.

```{r}
nas <- ag.df[ag.df$state %in% "nas",]
ben <- ag.df[ag.df$state %in% "ben",]

```

# Variable list

- bargaining: bargVars, 
- Awareness: awareVars and/or clashVars, 
- Threat: threatVars
- Ingroup expansion: cohesVars1
- Empathy: cohes2vars OR empVars and perspVars
- benefit: beneVar OR beneVarsReal (endline only)

# Testing Outcomes

We will use the differencing strategy when treatment and control are not balanced at baseline.  We will use the controlling-for strategy when treatment and control are balanced at baseline.  We say the groups are balanced if they are within 0.2 SDs of eachother at baseline.

true.fun1 is with differencing. true.fun is controlling-for. strat.fun tells us which to use.


************


## Awareness

```{r}
# select
strat.fun("clash_cw_base")

# true pvals
(clash1 <- true.fun1('clash_cw', 'treatment'))

#aware
strat.fun("clash_group.violence_base")

# true pvals
(aware1 <- true.fun1('clash_group.violence', 'treatment'))

```

TR knows more about clashes.

## Bargaining

```{r}
# select
strat.fun("barg_cw_base")

# true pvals
(barg <- true.fun('barg_cw', 'treatment'))
```


******

# Mechanisms

Things that ECPN could work through.  If ECPN improves them,  Do they correlate with attitudes/contact/security?

## Threat

Variables: `r threatVars`

```{r con}
strat.fun("threat_cw_base")
(threat1 <- true.fun('threat_cw', 'treatment'))
#true.fun("threat_group.threat_dis_group.x_threat", 'treatment')

true.fun('allTrust_cw', 'threat_cw')
true.fun('contactOnly_cw', 'threat_cw')
true.fun('in_cw', 'threat_cw')
```

Nothing.  Cannot work through reduced feelings of threat because ECPN does not correlate with feelings of threat.  The coefficient of `r round(threat1$coef,5)` is  `r round(threat1$coef/sd(ag.df$threat_cw),3)` standard deviations.

Threat is negatively correlated with intergroup affect, though.


## Empathy/Perspective-Taking

```{r}
# select
strat.fun("emp_cw_base")

# true pvals
(emp1 <- true.fun1('emp_cw', 'treatment'))
# true.fun1('emp_index', 'treatment') # confirm with index

# empathy and outcomes
(emp_trust <- true.fun('allTrust_cw', 'emp_cw'))
(emp_contact <- true.fun('contactOnly_cw', 'emp_cw'))
(emp_in <- true.fun('in_cw', 'emp_cw'))



# select
strat.fun("persp_cw_base")

# true pvals persp
(persp1 <- true.fun1('persp_cw', 'treatment'))
#true.fun1('persp_cw', 'treatment') # diff coef because _cw is standardized 0-1
#true.fun1('threat_group.x_responsible', 'treatment') #check to make sure identical

# persp and outcomes
(persp_trust <- true.fun('allTrust_cw', 'persp_cw'))
(persp_contact <- true.fun('contactOnly_cw', 'persp_cw'))
(persp_in <- true.fun('in_cw', 'persp_cw'))

```

ECPN maybe increases empathy increases, by these measures (Below 0.10 pvalue).  Empathy correlates with intergroup attitudes; some correlation with security.

ECPN does not cause perspective-taking, but again only one question.  Perspective-taking does correlated with intergroup attitudes, contact, and somewhat security (p<.10).


## Ingroup Expansion

Variables: `r cohesVars1`

```{r con}
strat.fun("expand_cw_base")
(expan1 <- true.fun('expand_cw', 'treatment'))

# expansion and outcomes
(expand_trust <- true.fun('allTrust_cw', 'expand_cw'))
(expand_contact <- true.fun('contactOnly_cw', 'expand_cw'))
(expand_in <- true.fun('in_cw', 'expand_cw'))
```

Nope, ECPN does not increase this.  But change here correlates with intergroup attitudes.


## Benefit

Variables: `r beneVars`

```{r con}
strat.fun("econ_benefit_group.benefit_econ_base")
(bene1 <- true.fun('econ_benefit_group.benefit_econ', 'treatment'))


strat.fun("bene_cw_base")
(bene2 <- true.fun('bene_cw', 'treatment'))

```

Not more likely to say currently benefitting!

```{r, eval=F}
(bene2 <- true.fun1('x_cw', 'bene_cw'))
(bene3 <- true.fun1('cohes_cw', 'bene_cw'))
```


# Save 

For appendices.  chris: need to add con1.1 for alternative contact coding.

```{r save3}
save(trust_ind, in_ind, con_ind,
     vio1,
     threat1, emp1, persp1, expan1,
     file="z_appendices_ag.Rdata")

```
