---
title: "g-aggAnalysis for academic paper"
output:
  word_document:
    toc: yes
  pdf_document:
    number_sections: yes
    toc: yes
  html_document:
    df_print: paged
    toc: yes
---

<!--Chris: notes

could replace all lm() with lm_lin() but lm_lin() does not allow me to vary treatment in a function.-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(962022)
rm(list=ls())
load("../c_creating_dataframes/f-aggregateComms_ap.Rdata")
load("../c_creating_dataframes/rand_df.Rdata")
rm(list=ls(pattern="Var|var|Cols"))

#True p-value function.  Don't need covariate adjustment to absorb error.  True p's Especially necessary with community level analysis, because we have a small number of clusters.  Treatment assigned at PSU level.
load("true_fun.rda")

#library(NPC)
library(dplyr)
library(mosaic)
library(estimatr)
library(robustbase)
library(quantreg)
library(sandwich)
library(clubSandwich)
library(lmtest)
library(coin)

# Subsets
## Look at farmers and pastoralists separately.

farmers <- ag.df[grepl(".farmers", ag.df$comm),]
pastors <- ag.df[grepl(".pastor", ag.df$comm),]

## Look at states separately.
nas <- ag.df[ag.df$state %in% "nas",]
ben <- ag.df[ag.df$state %in% "ben",]

```

# Variable list

- Attitudes: attitude, endorsement experiment
- Insecurity: in
- Coordination: pgp_donate, pgp_amount, 
- Contact: contactOnly, randExp/percExp, market/social observation

# Testing Outcomes

We will use the differencing strategy when treatment and control are not balanced at baseline.  We will use the controlling-for strategy when treatment and control are balanced at baseline.  We say the groups are balanced if they are within 0.2 SDs of eachother at baseline.

true.fun1 is with differencing. true.fun is controlling-for. strat.fun tells us which to use.


************

# Make a table of all outcomes with coefs and pvalues for the diff ways of making indices and estimating models.

- Rows as outcomes; columns for CW-Cont, CW-diff, Ind-Cont, Ind-diff; each column shows coef & pvalue.

- index: inverse-covariance weights ("cw") or additive ("ind")
- model: controlling-for ("cont") or differencing ("diff")

```{r}
analysis.fun <- function(var)
{
  if(paste0(var, "_cw_end") %in% names(ag.df))
  {
    var_cw_cont <- true.fun(paste0(var, "_cw"), 'treatment')
    var_ind_cont <- true.fun(paste0(var, "_index"), 'treatment')
    var_cw_diff <- true.fun1(paste0(var, "_cw"), 'treatment')
    var_ind_diff <- true.fun1(paste0(var, "_index"), 'treatment')
    
    which1 <- strat.fun(paste0(var, "_cw_base"))
    thebase <- ifelse(grepl("Contr", which1), "cw_cont", "cw_diff")
  }
  else if(grepl("pgp", var))
  {
    var_cw_cont <- true.fun(var, 'treatment')
    var_ind_cont <- NA
    var_cw_diff <- NA
    var_ind_diff <- NA
    which1 <- NA
    thebase <- NA
  }
  else
  {
    var_cw_cont <- true.fun(var, 'treatment')
    var_ind_cont <- NA
    var_cw_diff <- true.fun1(var, 'treatment')
    var_ind_diff <- NA
    
    which1 <- strat.fun(var)
    thebase <- ifelse(grepl("Contr", which1), "cw_cont", "cw_diff")
  }
  
  var_tab <- rbind(var_cw_cont, var_ind_cont, var_cw_diff, var_ind_diff)
  var_tab <- cbind (var_tab, c("cw_cont", "ind_cont", "cw_diff", "ind_diff"))
  var_tab[4] <- thebase
  colnames(var_tab)[3:4] <- c("version", "base")
  var_tab[4] <- ifelse(var_tab[[4]] == var_tab[[3]], 1, 0)
  
  return(var_tab)
}

#(trust_tab <- analysis.fun(var='attitude'))
#(in_tab <- analysis.fun('in'))
#con_tab <- analysis.fun('contactOnly')
#r_tab <- analysis.fun(var='rMean')
#pgp_tab <- analysis.fun(var='pgp_amount_end')

```

loop over outcomes.  note: rmean and end_exp don't have index & cw versions. Can still do true.fun1 and true.fun, but cannot do icw and index.  

Note: takes awhile to run (like 10 minutes) so ran once and now loading.

```{r}
# loop over all outcomes
outcome_list <- c("attitude", "in", 'contactOnly',
                  'rMean', "end_exp",
                  "pgp_donate_end", "pgp_amount_end")
newList <- vector(mode="list", length=length(outcome_list))
```
```{r, eval=F}
for(i in 1:length(outcome_list))
{
  newList[[i]] <- analysis.fun(outcome_list[i])
}
save(newList, file="list_of_coefs_and_ps.Rda")
```
```{r}
load("list_of_coefs_and_ps.Rda")
```


****************

Now do it for raw vs binary category vs ranked contact outcomes.

```{r, eval=F}
table(ag.df$contactOnly_raw_cw)
table(ag.df$contactOnly_cats_cw)
table(ag.df$contactOnly_cw)

var_cw_cont <- true.fun(paste0("contactOnly", "_cw"), 'treatment')
var_cats_cont <- true.fun(paste0("contactOnly_cats", "_cw"), 'treatment')
var_raw_cont <- true.fun(paste0("contactOnly_raw", "_cw"), 'treatment')

var_cw_diff <- true.fun1(paste0("contactOnly", "_cw"), 'treatment')
var_cats_diff <- true.fun1(paste0("contactOnly_cats", "_cw"), 'treatment')
var_raw_diff <- true.fun1(paste0("contactOnly_raw", "_cw"), 'treatment')

var_tab <- rbind(var_cw_cont, var_cats_cont, var_raw_cont, 
                 var_cw_diff, var_cats_diff, var_raw_diff)
save(var_tab, file="list_of_rank_bin_raw.Rda")
```
```{r}
load("list_of_rank_bin_raw.Rda")
```

Now NPC (NPC now defunct, not on CRAN, i am using an old version.)

```{r, eval=F}
npc <- NPC::NPC(ag.df, tr.var = "treatment", tr.label = 1, 
                    clust.var = "psu", block.var = "state", 
                    y.vars = c("attitude_cw", "in_cw", 'contactOnly_cw',
                  'rMean', "end_exp"), 
                alternative = "greater", test.statistic = "StudentsT",n.perms=10000, seed=952022,
             print.steps=FALSE)
(combP <- npc$p.values['NPC']) # cumulative
npc # all of them

```

******************

# State-level diffs

```{r}
outcome_list_state <- c(paste0(outcome_list[1:3], "_cw"), outcome_list[4:length(outcome_list)])
stateList <- vector(mode="list", length=length(outcome_list_state))
for(i in 1:length(outcome_list_state))
{
  thelm <- lm_robust(ag.df[,outcome_list_state[i]]~ag.df[,"treatment"]*state,
                            clusters = psu, data=ag.df)
  stateList[[i]] <- tidy(thelm)[, c(1,2,5)]
}
names(stateList) <- outcome_list_state
save(stateList, file="state_list.Rda")
```


# Farmer-pastoralist diffs

```{r}
ag.df$farm_past <- ifelse(grepl(".farmers", ag.df$comm), "farm", "past")
#table(ag.df$comm, ag.df$farm_past)

farmList <- vector(mode="list", length=length(outcome_list_state))
for(i in 1:length(outcome_list_state))
{
  thelm <- lm_robust(ag.df[,outcome_list_state[i]]~ag.df[,"treatment"]*farm_past,
                            clusters = psu, fixed_effects = state, data=ag.df)
  farmList[[i]] <- tidy(thelm)[, c(1,2,5)]
}
names(farmList) <- outcome_list_state
save(farmList, file="farm_list.Rda")

```



# Placebos

```{r, eval=F}
# loop over all placebo outcomes
placebo_list <- c("vio", 
                  "violence_group.criminals",
                  "violence_group.defend_group",
                  "violence_group.defend_religion",
                  "violence_group.government", 
                  "violence_group.maintain_culture",
                  "violence_group.retaliate",
                  'outgroup_atts_group.trust_rel',
                  "radio")
#analysis.fun(var=placebo_list[1])
#analysis.fun(var=placebo_list[9])

placeboList <- vector(mode="list", length=length(placebo_list))
for(i in 1:length(placebo_list))
{
  placeboList[[i]] <- analysis.fun(placebo_list[i])
}
save(placeboList, file="pl_list_of_coefs_and_ps.Rda")
```
```{r}
load("pl_list_of_coefs_and_ps.Rda")
```


**Attitudes towards actors in dispute resolution**

```{r}
# dispute resolution
ag.df$disp_index
strat.fun("disp_index_base")
disp1 <- true.fun("disp_index", "treatment")

```







*****************

Old


# Save 

For use to make coefplots

```{r}
save(ag.df, newList, placeboList, file="g-aggAnal_coefplots.Rdata")

```

For combining pvals across levels of analysis.

```{r save1, eval=F}
save(ag.df, combP, file="g-aggAnal.Rdata")

```

For referencing these values

```{r save2}
rm(thelm, i)
save.image("g-aggAnalComplete.Rdata")
```