---
title: "g2-panelAnalysis"
output:
  word_document:
    toc: yes
  pdf_document:
    number_sections: yes
    toc: yes
  html_document:
    df_print: paged
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(7867564)
rm(list=ls())
load("../b_creating_outcomes/f2-panelData.Rdata")

#library(NPC) # archived
library(estimatr)
library(mosaic)
library(coin)
library(robustbase)

#True p-value function.
load("true_fun_ind.rda")

#true.fun(var='x_cw', tr='treatment')
#true.fun(var='cohes_cw_resid', tr='tr_resid') # Could be useful if confounders
#true.fun(var='cohes_cw', tr='bene_cw')
#true.fun(var="pgp_amount_y1", tr='treatment')
#true.fun(var="pgp_amount_y1", tr='bene_cw')

#com.fun(var="x_cw", nsims=1000)
#com.fun1(var="x_cw", nsims=1000)

#strat.fun("cohes_cw_y0")
#strat.fun("x_cw_y0")
```

# ECPN Hypotheses

 1. Individuals involved in the planning and implementing of projects that benefit both farmers and
pastoralists will trust each other more and feel more positively towards the outgroup than individuals
 2. Individuals involved in the planning and implementing of projects that benefit both farmers and
pastoralists will cooperate more in the PGG than individuals who did not participate in these activities.
 3. Individuals involved in the planning and implementing of projects that benefit both farmers and
pastoralists will interact more with the outgroup than individuals who did not participate in these
activities.
 4. Individuals involved in more ECPN activities will cooperate more, trust each other more, have more
positive attitudes about the outgroup, and interact more than those who participated in fewer ECPN
activities. More specifically, we will see the most change in participants who participated in the
joint projects, followed by the non-participants in the treatment communities, and then the control
participants who we expect to have no change^[The data for this hypothesis is limited.  Many of the pre-identified respondents who were supposed to be participating in ECPN did not say they were participating in the survey.  Many of the pre-identified respondents who were not supposed to be participating in ECPN said they were participating in the survey. I am marking as a full participant/committee member everyone who said they were on a committee in the survey OR who was in the "full participant" group on the spreadsheet John sent.  Otherwise just 21 people, which makes me think they did not understand the survey question.]

The first set of analyses is about people in treatment sites compared to people in control sites.  The second set of analyses will compare treatment people on committees, non-committee treatment people, and control people.

************

# Committee vs Non-committee vs. Control

chris: note that this is NOT WHAT THE CODE IS DOING ANYMORE.  I did not understand ordered hypothesis testing.  Now we are just looking at a linear effect where control==1, nonparticipants==2, participants==3.

Here we directly deal with our ordered hypothesis that effects should be committee members > non-committee members > controls.

## Differences from Baseline-Endline by Committee, Non-committee, and Control

To analyze our ordered hypothesis that effects should be committee members > non-committee members > controls, we want to do: (1) lm(outcome ~ treatment+committee+state), which gives us the effect estimate for committee members in treatment area, non-committee members in treatment areas, and control people.  (2) Then we simulate a world where the program had no effect by shuffling treatment assignment, which breaks its relationship to outcomes. We do that thousands of times to obtain a distribution of possible effects and p-values in the world where ECPN did nothing.  (3) Then we compare the real p-value estimates to that null distribution of no effects.

_Both_ null coefficients need to be greater than their respective real coefficients.  I've also added that the sum of the two null coefficients should not be greater than the sum of the real coefficients.  Otherwise, if our real coefs are both 0.10, we still say the null distribution is NOT more extreme if it's two coefs are 0.20 and 0.09, because one is lower.

We will use the differencing strategy when groups are not balanced at baseline.  We will use the controlling-for strategy when groups are balanced at baseline.  We say the groups are balanced if all groups are within 0.2 SDs of eachother at baseline.

```{r}
# make treatment variables
panel.df$tr_f <- droplevels(interaction(panel.df$treatment, panel.df$committee))
panel.df$tr_n <- as.numeric(panel.df$tr_f)
```

# Make a table of all outcomes with coefs and pvalues for the diff ways of making indices and estimating models.

- Rows as outcomes; columns for CW-Cont, CW-diff, Ind-Cont, Ind-diff; each column shows coef & pvalue.

- index: inverse-covariance weights ("cw") or additive ("ind")
- model: controlling-for ("cont") or differencing ("diff")

```{r}
# matrices sooooo fast
system.time(replicate(10000, data.frame(thecoef=c(NA, NA), truep=c(NA, NA))))
system.time(replicate(10000, matrix(NA, nrow=2, ncol=2, dimnames=list(NULL, c("thecoef", "truep")))))

#chris: doesnt work with pgp
analysis.fun <- function(var,nsims)
{
  if(paste0(var, "_cw_y1") %in% names(panel.df))
  {
    var_cw_cont <- comp.fun(paste0(var, "_cw"), nsims)
    var_ind_cont <- comp.fun(paste0(var, "_index"), nsims)
    var_cw_diff <- comp.fun1(paste0(var, "_cw"), nsims)
    var_ind_diff <- comp.fun1(paste0(var, "_index"), nsims)
    
    which1 <- strat.fun(paste0(var, "_cw_y0"))
    thebase <- ifelse(grepl("Contr", which1), "cw_cont", "cw_diff")
  }
  else if(grepl("pgp", var))
  {
    var_cw_cont <- comp.fun1(var, nsims)
    var_ind_cont <- matrix(NA, nrow=2, ncol=2, dimnames=list(NULL, c("thecoef", "truep")))
    var_cw_diff <- matrix(NA, nrow=2, ncol=2, dimnames=list(NULL, c("thecoef", "truep")))
    var_ind_diff <- matrix(NA, nrow=2, ncol=2, dimnames=list(NULL, c("thecoef", "truep")))
    which1 <- NA
    thebase <- NA
  }
  else
  {
    var_cw_cont <- comp.fun(var, nsims)
    var_ind_cont <- matrix(NA, nrow=2, ncol=2, dimnames=list(NULL, c("thecoef", "truep")))
    var_cw_diff <- comp.fun1(var, nsims)
    var_ind_diff <- matrix(NA, nrow=2, ncol=2, dimnames=list(NULL, c("thecoef", "truep")))
    
    which1 <- strat.fun(var)
    thebase <- ifelse(grepl("Contr", which1), "cw_cont", "cw_diff")
  }
  
  var_tab <- rbind(var_cw_cont, var_ind_cont, var_cw_diff, var_ind_diff)
  var_tab <- cbind (var_tab, c(rep("cw_cont", 2), 
                               rep("ind_cont",2), 
                               rep("cw_diff",2), 
                               rep("ind_diff",2)))
  var_tab[4] <- thebase
  colnames(var_tab)[3:4] <- c("version", "base")
  var_tab[4] <- ifelse(var_tab[[4]] == var_tab[[3]], 1, 0)
  
  return(var_tab)
}

#(trust_tab <- analysis.fun(var='attitude', nsims=100))
#(in_tab <- analysis.fun('in', nsims=100))
#(con_tab <- analysis.fun('contactOnly', nsims=100))
#(pgp_tab <- analysis.fun(var='pgp_amount_y1', nsims=100))

```

loop over outcomes.  note: rmean and end_exp don't have index & cw versions. Can still do true.fun1 and true.fun, but cannot do icw and index.

Note: takes awhile to run (like 10 minutes) so ran once and now loading.

```{r, eval=F}
# loop over all outcomes
outcome_list <- c("attitude", "in", 'contactOnly',
                  #'rand_outcome', "end_exp", # dont make sense at ind-level
                  "pgp_donate_y1", "pgp_amount_y1")
newList_ind <- vector(mode="list", length=length(outcome_list))
for(i in 1:length(outcome_list))
{
  newList_ind[[i]] <- analysis.fun(outcome_list[i], nsims=3000)
}
save(newList_ind, file="list_of_coefs_and_ps_ind.Rda")
```
```{r}
load("list_of_coefs_and_ps_ind.Rda")
```


Now do it for raw vs binary category vs ranked contact outcomes.

```{r, eval=F}
#table(panel.df$contactOnly_raw_cw)
#table(panel.df$contactOnly_cats_cw)
#table(panel.df$contactOnly_cw)

nsims=3000
var_cw_cont <- comp.fun(paste0("contactOnly", "_cw"), nsims)
var_cats_cont <- comp.fun(paste0("contactOnly_cats", "_cw"), nsims)
var_raw_cont <- comp.fun(paste0("contactOnly_raw", "_cw"), nsims)

var_cw_diff <- comp.fun1(paste0("contactOnly", "_cw"), nsims)
var_cats_diff <- comp.fun1(paste0("contactOnly_cats", "_cw"), nsims)
var_raw_diff <- comp.fun1(paste0("contactOnly_raw", "_cw"), nsims)

var_tab_ind <- rbind(var_cw_cont, var_cats_cont, var_raw_cont, 
                 var_cw_diff, var_cats_diff, var_raw_diff)
save(var_tab_ind, file="list_of_rank_bin_raw_ind.Rda")
```
```{r}
load("list_of_rank_bin_raw_ind.Rda")
```

# Placebos

```{r, eval=F}
# loop over all placebo outcomes
placebo_list <- c("vio", 
                  "violence_group.criminals",
                  "violence_group.defend_group",
                  "violence_group.defend_religion",
                  "violence_group.government", 
                  "violence_group.maintain_culture",
                  "violence_group.retaliate",
                  'outgroup_atts_group.trust_rel',
                  "radio",
                  "disp_index")
#analysis.fun(var=placebo_list[1], nsims=100)
#analysis.fun(var=placebo_list[10],nsims=100)

placeboList_ind <- vector(mode="list", length=length(placebo_list))
for(i in 1:length(placebo_list))
{
  placeboList_ind[[i]] <- analysis.fun(placebo_list[i], nsims=3000)
}
save(placeboList_ind, file="pl_list_of_coefs_and_ps_ind.Rda")
```
```{r}
load("pl_list_of_coefs_and_ps_ind.Rda")
```


*************








### Percent Experiment / Rand Exp

```{r}
strat.fun("rand_outcome_y0")
(p_randp1 <- com.fun(var="rand_outcome", nsims=1000))
#(p_randp1 <- com.fun1(var="rand_outcome_y1", nsims=1000))

```


### Intergroup Affect

 1. Individuals involved in the planning and implementing of projects that benefit both farmers and
pastoralists will trust each other more and feel more positively towards the outgroup than individuals

Variables: `r paste(xVars, collapse=", ")`

```{r}
strat.fun("x_cw_y0")
(p_xp1 <- com.fun1(var="x_cw", nsims=1000))
trustp_ind <- com.fun1(var="x_index", nsims=1000)
```

The p-value is `r p_xp1$truep`.

### Social Cohesion

 1. Individuals involved in the planning and implementing of projects that benefit both farmers and
pastoralists will trust each other more and feel more positively towards the outgroup than individuals

Cohesion1 Vars: `r paste(cohesVars1, collapse=", ")`

Cohesion2 Vars: `r paste(cohesVars2, collapse=", ")`

```{r}
strat.fun("cohes_cw_y0")
(p_cohesp <- com.fun('cohes_cw', nsims=1000))
```

The p-value is `r p_cohesp$truep`.

This index has two components.  The first set of questions are abstract things like "Are people in this area willing to help their neighbors across ethnic and religious lines?".  Before we ask these questions we say "I am going to ask you about people in this area, including people from the outgroup."

The second set are concrete hypothetical situations that directly relate to the outgroup, like "If something unfortunate happened to someone from your group in this community, such as a serious illness or the death of a parent, how likely is it that some people in the community from the outgroup would get together to help them?"

#### Cohesion 1, abstract questions

```{r}
strat.fun("cohes1_cw_y0")
com.fun('cohes1_cw', nsims=1000)
```


#### Cohesion 2, concrete hypotheticals

```{r}
strat.fun("cohes2_cw_y0")
(p_cohesp2 <- com.fun('cohes2_cw', nsims=1000))
```

The p-value is `r p_cohesp2$truep`.


### PGG

 2. Individuals involved in the planning and implementing of projects that benefit both farmers and
pastoralists will cooperate more in the PGG than individuals who did not participate in these activities.

#### Donation Amount

```{r pgg1}
## no baseline, so differencing
(p_pgpp1 <- com.fun1('pgp_amount_y1', nsims=1000))
```

The p-value is `r p_pgpp1$truep`.

#### Donate yes/no

```{r}
(p_pgpp2 <- com.fun1('pgp_donate_y1', 1000))
```

The p-value is `r p_pgpp2$truep`.

<!--
#### Donation variance

```{r, eval=F}
com.fun('pgp_meanDist_y1', 1000)
```

All people in treatment communities have lower donation variance, but there is no difference between committee members and non-committee members in treatment areas.
-->

### Intergroup Contact / Interaction

 3. Individuals involved in the planning and implementing of projects that benefit both farmers and
pastoralists will interact more with the outgroup than individuals who did not participate in these
activities.

**Note: this is also a mechanism and is in the mechanism section.**

Intergroup interaction variables: `r paste(contactVars[c(1:4,7)], collapse=", ")`

```{r}
strat.fun("contactOnly_cw_y0")
(p_conp1 <- com.fun1('contactOnly_cw', 1000))
strat.fun("contactOnly_index_y0")
conp_ind <- com.fun1('contactOnly_index', 1000)
```

The p-value of `r p_conp1$truep` suggests the relationship we see between committee members, non-committee treatment members, and control communities on our contact index is very unlikely to arise due to chance alone.  People in treatment communities, _especially committee members_, have a greater increased in intergroup interaction than people in control areas.

**Robustness check** with alternative measure

```{r, eval=F}
strat.fun("contactOnly_cats_cw_y0")
(p_conp1.1 <- com.fun1('contactOnly_cats_cw', 1000))
strat.fun("contactOnly_cats_index_y0")
conp_ind.1 <- com.fun1('contactOnly_cats_index', 1000)

lm_robust(contactOnly_cats_cw~tr_n, clusters=community, data=panel.df)
```


### Insecurity 

Insecurity Vars: `r paste(inVars, collapse=", ")`

```{r}
strat.fun("in_cw_y0")
(p_inp1 <- com.fun1('in_cw', 1000))
inp_ind <- com.fun1('in_index', 1000)
```

All people in treatment areas became more secure relative to control areas, and there is only a small difference between committee and non-committee members.  The p-value of `r p_inp1$truep` suggests the relationship we see between committee members, non-committee treatment members, and control communities on our insecurity index could arise due to chance alone.


## Placebo - attitudes about violence.

Attitudes about violence: `r vioVars`

```{r resolve}
strat.fun("vio_cw_y0")
(p_viop1 <- com.fun1('vio_cw', 1000))
(p_viop1 <- com.fun1('vio_index', 1000))
vio1p <- p_viop1
```




