---
title: "ecpn_coefplot_coefs"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
set.seed(357436)

library(plyr)
library(dplyr)
library(tidyr)

load("../../d_analysis/g-aggAnal_coefplots.Rdata")
load("../../d_analysis/g2-panelAnal_coefplots.Rdata")
# don't need so many things
#load("../../d_analysis/g-aggAnalComplete.Rdata")
#load("../../d_analysis/g2-panelAnalComplete.Rdata")

# Setup Wanted Vars

# coef name list
## aggregate
ag.vars <- c("attitude_cw", "in_cw", 'contactOnly_cw',
                  'rMean', "end_exp",
                  "pgp_donate_end", "pgp_amount_end")
setdiff(ag.vars, names(ag.df))

## individual
ind.vars <- c('attitude_cw', "in_cw", 'contactOnly_cw',
              'pgp_donate_y1', 'pgp_amount_y1')
setdiff(ind.vars, names(panel.df))


#Standardize outcomes to effect size, instead of raw.  Since want standardized effect size in coefplot.
## done when made indices
#ag.df[,ag.vars] <- scale(ag.df[,ag.vars])
#panel.df[,ind.vars] <- scale(panel.df[,ind.vars])


# make multi-DF strat.fun
strat.fun <- function(var,thedf){
  thesd <- sd(thedf[[var]])*.2
  thediff <- abs(mosaic::mean(thedf[[var]]~thedf[['treatment']])[1]-mosaic::mean(thedf[[var]]~thedf[["treatment"]])[2])
  thebal <- thediff-thesd
  if(thebal<0){
    return("Controlling-for: true.fun")
  }
  if(thebal>=0){
    return("Difference: true.fun1")
  }
  else(return("Fail"))
}
#strat.fun("x_cw_base", ag.df)
#strat.fun("x_cw_y0", panel.df)
```

## Effect Sizes

Get coefficient from OLS and SD of each variable

```{r}
## add "base" var to PGG outcomes
newList[[6]]$base <- c(1,rep(0,3))
newList[[7]]$base <- c(1,rep(0,3))
# get coefs
ag_coef <- sapply(newList, function(x) x$coef[x$base %in% 1])
names(ag_coef) <- ag.vars

# get SD of _base
ag_sd <- sapply(ag.df[,c(paste0(ag.vars[1:5], "_base"),ag.vars[6:7])],
       sd, na.rm=T)

# same for individual-level panel data
## add "base" var to PGG outcomes
newList_ind[[4]]$base <- c(rep(1,2),rep(0,6))
newList_ind[[5]]$base <- c(rep(1,2),rep(0,6))
pan_coef <- sapply(newList_ind, function(x) x$thecoef[x$base %in% 1])
rownames(pan_coef) <- c("non", "part")
colnames(pan_coef) <- ind.vars

pan_sd <- sapply(panel.df[,c(paste0(ind.vars[1:3], "_y0"),ind.vars[4:5])],
       sd, na.rm=T)
```

Put together as coefs and SDs.

Aggregate df

```{r}
#var name, coef, and sd
ag.coefs <- matrix(NA, nrow=length(ag.vars), ncol=3)
for(i in 1:length(ag.vars))
{
  ag.coefs[i,1] <- ag.vars[i]
  ag.coefs[i,2] <- ag_coef[i]
  ag.coefs[i,3] <- ag_sd[i]
  
}
ag.coefs <- as.data.frame(ag.coefs)
names(ag.coefs) <- c("var", "coef", "sd")

# make numeric
ag.coefs[,2:3] <- sapply(ag.coefs[,2:3], function(x) {as.numeric(as.character(x))})

```

Panel - tr_f (participants and nonparticipants)

```{r}
# var name, coef, sd
ind.coefs <- matrix(NA, nrow=length(ind.vars), ncol=4)
for(i in 1:length(ind.vars))
{
  ind.coefs[i,1] <- ind.vars[i]
  ind.coefs[i,2:3] <- pan_coef[1:2,i]
  ind.coefs[i,4] <- pan_sd[i]
}

ind.coefs <- as.data.frame(ind.coefs)
names(ind.coefs) <- c("var", "coef_non", "coef_part", "sd")

# make numeric
ind.coefs[,2:4] <- sapply(ind.coefs[,2:4], function(x) {as.numeric(as.character(x))})
```

## Bootstrap Conf Intervals


### Aggregate DF: Bootstrap standardized outcomes.

Need to resample the way we sampled (sample 9 sites in Nas, sample 6 sites in Ben).  Then do lm(outcome~treatment) newly for each resample to make a distribution, then take 2.5th quartile and 97.5th quartile from that distribution.  Do that for every variable in ag.vars and add it to ag.coefs as ll and ul.

```{r, eval=F}
# takes awhile to run
# function to resample and lm 1,000 times, then take 0.025 and 0.975 quantiles.
agBoot.fun <- function(var)
{
  boot.coef <- rep(NA,1000)
  for(i in 1:1000)
  {
    # sample PSUs within state
  boot.nas <- ag.df %>%
    filter(state %in% "nas") %>%
    distinct(psu) %>%
    sample_n(size = 9, replace = TRUE) %>%
    inner_join(ag.df, by = "psu")
  boot.ben <- ag.df %>%
    filter(state %in% "ben") %>%
    distinct(psu) %>%
    sample_n(size = 6, replace = TRUE) %>%
    inner_join(ag.df, by = "psu")
  boot.samp <- rbind(boot.nas, boot.ben)
  
  # do regression
  ## pgg
  if(grepl("_end", var)){
    lm.boot <- lm(boot.samp[,var]~treatment+state, data=boot.samp)
    boot.coef[i] <- summary(lm.boot)$coefficients[2,1]
    }
  ## differecing
  else if(!grepl("_end", var) & strat.fun(paste0(var, "_base"), thedf=ag.df)=="Difference: true.fun1"){
    lm.boot <- lm(boot.samp[,var]~treatment+state, data=boot.samp)
    boot.coef[i] <- summary(lm.boot)$coefficients[2,1]
    }
  
  ## controlling-for
  else if(!grepl("_end", var) & strat.fun(paste0(var, "_base"), thedf=ag.df)=="Controlling-for: true.fun"){
    lm.boot <- lm(boot.samp[,paste0(var, "_end")]~treatment+state+boot.samp[,paste0(var, "_base")], data=boot.samp)
    boot.coef[i] <- summary(lm.boot)$coefficients[2,1]
    }
  }
  
  #mn <- mean(boot.coef)
  #med <- median(boot.coef)
  ll <- quantile(boot.coef,0.025)
  ul <- quantile(boot.coef,0.975)
  
  #return(cbind(mn,med,ll,ul))
  return(cbind(ll,ul))
  
}
#agBoot.fun(var="x_cw")
#agBoot.fun(var="in_cw")
#agBoot.fun(var="pgp_amount_end")
#agBoot.fun(var="contactOnly_cw")


# apply function to ag.vars and add to ag.coefs as columns ll and ul
set.seed(867564)
system.time(ag.coefs[,c("ll", "ul")] <- t(sapply(ag.vars, agBoot.fun)))

# make the cols in terms of sd
ag.coefs[,c("size", "ll_size", "ul_size")] <- ag.coefs[,c(2,4:5)]/ag.coefs[,3]

save(ag.coefs, file="ag.coefs.Rdata")
```
```{r}
load("ag.coefs.Rdata")
```


### Participant - Nonparticipant - Control Comparison


Linear effect (tr_n) and effects for each group (tr_f).

Also want a plot showing full participants and nonparticipants vs control.

Need to resample the way we sampled (sample ~10 individuals within each comm).  Then do lm(outcome~treatment) newly for each resample to make a distribution, then take 2.5th quartile and 97.5th quartile from that distribution.  Do that for every variable in ind.vars and add it to ind.coefs as ll and ul.


```{r, eval=F}
# will need to do sep regs for part-control and non-control to get SEs.
## the one-model SEs will give me the wrong SEs for participants, since it will be participants vs Non, instead of participants vs control.
require(purrr)

indBoot.fun <- function(var)
{
  boot.coef <- rep(NA,1000)
  non.coef <- rep(NA,1000)
  part.coef <- rep(NA,1000)
  for(i in 1:1000)
  {
    # Resample communities
  boot.nas2 <- panel.df %>%
    filter(state %in% "nas") %>%
    distinct(psu) %>%
    sample_n(size = 9, replace = TRUE) %>%
    inner_join(panel.df, by = "psu")
  boot.ben2 <- panel.df %>%
    filter(state %in% "ben") %>%
    distinct(psu) %>%
    sample_n(size = 6, replace = TRUE) %>%
    inner_join(panel.df, by = "psu")
  boot.samp2 <- rbind(boot.nas2, boot.ben2)
  
  # do regression
  ## endline only
  if(grepl("_y1", var)){
    lm.boot2 <- lm(boot.samp2[,var]~tr_f+state, data=boot.samp2)
    
    non.coef[i] <- summary(lm.boot2)$coefficients[2,1]
    part.coef[i] <- summary(lm.boot2)$coefficients[3,1]
  }
  ## controlling-fr
  else if(!grepl("_y1", var) & strat.fun(paste0(var, "_y0"), thedf=panel.df)=="Controlling-for: true.fun"){
    lm.boot2 <- lm(boot.samp2[,paste0(var, "_y1")]~tr_f+state+boot.samp2[,paste0(var, "_y0")], data=boot.samp2)
    
    non.coef[i] <- summary(lm.boot2)$coefficients[2,1]
    part.coef[i] <- summary(lm.boot2)$coefficients[3,1]
  }
  ## differencing
  else if(!grepl("_y1", var) & strat.fun(paste0(var, "_y0"), thedf=panel.df)=="Difference: true.fun1"){
    lm.boot2 <- lm(boot.samp2[,var]~tr_f+state, data=boot.samp2)
    
    non.coef[i] <- summary(lm.boot2)$coefficients[2,1]
    part.coef[i] <- summary(lm.boot2)$coefficients[3,1]
  }
  
  }
  
  ll_non <- quantile(non.coef,0.025)
  ul_non <- quantile(non.coef,0.975)
  ll_part <- quantile(part.coef,0.025)
  ul_part <- quantile(part.coef,0.975)
  
  #return(cbind(boot.coef, non.coef, part.coef))
  return(cbind(ll_non,ul_non, 
               ll_part, ul_part))
  
}
#system.time(indBoot.fun(var="attitude_cw"))
#system.time(indBoot.fun(var="in_cw"))
#system.time(indBoot.fun(var="pgp_amount_y1"))


# apply function to ind.vars and add to ind2.coefs as columns ll_non/part and ul_non/part
set.seed(2353)
system.time(ind.coefs[,c("ll_non", "ul_non", "ll_part", "ul_part")] <- t(sapply(ind.vars, indBoot.fun)))

# make the cols in terms of sd
ind.coefs[,c("size_non", "size_ll_non", "size_ul_non",
             "size_part", "size_ll_part", "size_ul_part")] <- ind.coefs[,c("coef_non", "ll_non", "ul_non",
                                                                            "coef_part", "ll_part", "ul_part")]/ind.coefs[,"sd"]


save(ind.coefs, file="ind.coefs.Rdata")
```
```{r}
load("ind.coefs.Rdata")
```


