---
title: 'ObsDat coefficient plots: bstrap coefs'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
load("../a_clean/a_obsDat_clean.rda")

library(tidyr)
library(dplyr)
library(broom)
#library(HSPSUtils)

# function to sample groups after dplyr::group_by
sample_n_groups = function(tbl, size, replace = TRUE, weight = NULL) {
  # regroup when done
  grps = tbl %>% groups %>% lapply(as.character) %>% unlist
  # check length of groups non-zero
  keep = tbl %>% summarise() %>% ungroup() %>% sample_n(size, replace, weight)
  keep$new_site <- paste0(keep$site, rownames(keep))
  # keep only selected groups, regroup because joins change count.
  # regrouping may be unnecessary but joins do something funky to grouping variable
  tbl %>% inner_join(keep, by=grps) %>% group_by(.dots = grps)
}
```

# Plan

Cluster bootstrap.  SAMPLE SITES WITHIN STATES!!!  SAMPLE WITHIN TR AND CO.

1. Calc coefficients
2. Boostrap SEs
3. Save


## Markets

### Case resampling

case resample bootstrapping. The thing I know best, though slower (and safer from assumptions!) than residual bootstrap.

```{r, eval=F}
set.seed(1234)

# the lm to get the coefs
#fit.star<-lm(pastoralists_index_rank~treatment*time + site, data=markets)
fit.star<-lm(pastoralists_index_rank~treatment*time, data=markets)

R<-500 # Number of Repetitions
h<-matrix(NA, R, 1)
for (i in 1:R){
  # sample sites within states
  nas_samp1 <- markets[markets$State %in% "nasarawa" & markets$treatment %in% 1,] %>% group_by(site) %>%
    sample_n_groups(size=6) %>%
    as.data.frame()
  nas_samp0 <- markets[markets$State %in% "nasarawa" & markets$treatment %in% 0,] %>% group_by(site) %>%
    sample_n_groups(size=3) %>%
    as.data.frame()
  ben_samp1 <- markets[markets$State %in% "benue" & markets$treatment %in% 1,] %>% group_by(site) %>%
    sample_n_groups(size=4) %>%
    as.data.frame()
  ben_samp0 <- markets[markets$site %in% "sabon gida agan",]
  ben_samp0$new_site <- "sabon gida agan"
  markets1 <- rbind(nas_samp1, nas_samp0, ben_samp1, ben_samp0)
 
  #b<-lm(pastoralists_index_rank~treatment*time + new_site, data=markets1)$coef["treatment:time"]
  b<-lm(pastoralists_index_rank~treatment*time, data=markets1)$coef["treatment:time"]
  h[i,] <- b
}
c1_treat1_ci_case<-quantile(h[,1],c(0.025,0.975))
c1_coefs <- fit.star$coefficients['treatment:time']

# vs canned
estimatr::lm_robust(pastoralists_index_rank ~ treatment*time + site, data=markets, cluster = site, se="CR2")
```

#### Now repeat it for all Obs outcomes.

Start by getting the coefs in a df

```{r}
# get coefs and SDs so coefplot can be effect size
#marketVars <- names(markets)[c(grepl("index", names(markets)))]
#outcomes <- names(markets)[grepl("(market|farm|past)", names(markets))] # already made in loaded .rda

#get coefficient from ols and SD from data
markCoefs <- matrix(NA, nrow=length(outcomes), ncol=3)
for(i in 1:length(outcomes))
{
  #thecoef <- lm(markets[,outcomes[i]]~treatment*time + site + State, data=markets)$coefficients["treatment:time"]
  thecoef <- lm(markets[,outcomes[i]]~treatment*time, data=markets)$coefficients["treatment:time"]
  markCoefs[i,1] <- outcomes[i]
  markCoefs[i,2] <- thecoef
  markCoefs[i,3] <- sd(markets[,outcomes[i]], na.rm=T)
  
}
markCoefs <- as.data.frame(markCoefs)
names(markCoefs) <- c("var", "coef", "sd")
markCoefs[,2:3] <- sapply(markCoefs[,2:3], function(x) {as.numeric(as.character(x))})

```

Now bootstrap the CIs

```{r, eval=F}
set.seed(1234)

bsCIs.fun <- function(var, reps)
{
  R <- reps
  h <- matrix(NA, R, 1)
  for(i in 1:R)
  {
    # sample sites within states
    nas_samp1 <- markets[markets$State %in% "nasarawa" & markets$treatment %in% 1,] %>% group_by(site) %>%
      sample_n_groups(size=6) %>%
      as.data.frame()
    nas_samp0 <- markets[markets$State %in% "nasarawa" & markets$treatment %in% 0,] %>% group_by(site) %>%
      sample_n_groups(size=3) %>%
      as.data.frame()
  ben_samp1 <- markets[markets$State %in% "benue" & markets$treatment %in% 1,] %>% group_by(site) %>%
    sample_n_groups(size=4) %>%
    as.data.frame()
  ben_samp0 <- markets[markets$site %in% "sabon gida agan",]
  ben_samp0$new_site <- "sabon gida agan"
  markets1 <- rbind(nas_samp1, nas_samp0, ben_samp1, ben_samp0)
  
  #b<-lm(markets1[,var]~treatment*time + new_site, data=markets1)$coef["treatment:time"]
  b<-lm(markets1[,var]~treatment*time, data=markets1)$coef["treatment:time"]
  h[i,] <- b
  }
  # get bootstrap CIs from distribution of coefs
  bs_CIs<-quantile(h[,1],c(0.025,0.975))
  #c1_coefs <- thelm$coefficients['treatment:time']
  
  return(bs_CIs)
}
system.time(
for(i in 1:length(outcomes))
{
  CIs <- bsCIs.fun(var=outcomes[i], reps=1000)
  markCoefs[i, c("ll", "ul")] <- bsCIs.fun(var=outcomes[i], reps=1000)
}
)
```

Save.

```{r, eval=F}
#save(markCoefs, file="marketCoefs.rda") #with site and state FEs (should be more precise but biased)
save(markCoefs, file="marketCoefs1.rda") # without FEs
```

Don't run that time-consuming code repeatedly, just load the output.

```{r}
#load("marketCoefs.rda")
load("marketCoefs1.rda")
```


## Events

### Case resampling

case resample bootstrapping. The thing I know best, though slower (and safer from assumptions!) than residual bootstrap.

```{r, eval=F}
set.seed(1234)

# the lm to get the coefs
#fit.star<-lm(outgroup_index_rank~treatment*time + site, data=events)
fit.star<-lm(outgroup_index_rank~treatment*time, data=events)

R<-500 # Number of Repetitions
h<-matrix(NA, R, 1)
for (i in 1:R){
  # sample sites within states
  nas_samp1 <- events[events$State %in% "nasarawa" & events$treatment %in% 1,] %>% group_by(site) %>%
    sample_n_groups(size=5) %>%
    as.data.frame()
  nas_samp0 <- events[events$State %in% "nasarawa" & events$treatment %in% 0,] %>% group_by(site) %>%
    sample_n_groups(size=3) %>%
    as.data.frame()
  ben_samp1 <- events[events$State %in% "benue" & events$treatment %in% 1,] %>% group_by(site) %>%
    sample_n_groups(size=4) %>%
    as.data.frame()
  ben_samp0 <- events[events$site %in% "sabon gida agan",]
  ben_samp0$new_site <- "sabon gida agan"
  events1 <- rbind(nas_samp1, nas_samp0, ben_samp1, ben_samp0)
 
  #b<-lm(outgroup_index_rank~treatment*time + new_site, data=events1)$coef["treatment:time"]
  b<-lm(outgroup_index_rank~treatment*time, data=events1)$coef["treatment:time"]
  h[i,] <- b
}
c1_treat1_ci_case<-quantile(h[,1],c(0.025,0.975))
c1_coefs <- fit.star$coefficients['treatment:time']

# vs canned
#estimatr::lm_robust(pastoralists_index_rank ~ treatment*time + site, data=events, cluster = site, se="CR2")
estimatr::lm_robust(pastoralists_index_rank ~ treatment*time, data=events, cluster = site, se="CR2")
```

#### Now repeat it for all Obs outcomes.

Start by getting the coefs in a df

```{r}
# get coefs
outgroupVars

#get coefficient from ols
eventCoefs <- matrix(NA, nrow=length(outgroupVars), ncol=3)
for(i in 1:length(outgroupVars))
{
  #thecoef <- lm(events[,outgroupVars[i]]~treatment*time + site + State, data=events)$coefficients["treatment:time"]
  thecoef <- lm(events[,outgroupVars[i]]~treatment*time, data=events)$coefficients["treatment:time"]
  eventCoefs[i,1] <- outgroupVars[i]
  eventCoefs[i,2] <- thecoef
  eventCoefs[i,3] <- sd(events[,outgroupVars[i]], na.rm=T)
  
}
eventCoefs <- as.data.frame(eventCoefs)
names(eventCoefs) <- c("var", "coef", "sd")
eventCoefs[,2:3] <- sapply(eventCoefs[,2:3], function(x) {as.numeric(as.character(x))})

```

Now bootstrap the CIs

```{r}
set.seed(1234)

bsCIs.fun <- function(var, reps)
{
  R <- reps
  h <- matrix(NA, R, 1)
  for(i in 1:R)
  {
    # sample sites within states
    nas_samp1 <- events[events$State %in% "nasarawa" & events$treatment %in% 1,] %>% group_by(site) %>%
      sample_n_groups(size=6) %>%
      as.data.frame()
    nas_samp0 <- events[events$State %in% "nasarawa" & events$treatment %in% 0,] %>% group_by(site) %>%
      sample_n_groups(size=3) %>%
      as.data.frame()
  ben_samp1 <- events[events$State %in% "benue" & events$treatment %in% 1,] %>% group_by(site) %>%
    sample_n_groups(size=4) %>%
    as.data.frame()
  ben_samp0 <- events[events$site %in% "sabon gida agan",]
  ben_samp0$new_site <- "sabon gida agan"
  events1 <- rbind(nas_samp1, nas_samp0, ben_samp1, ben_samp0)
  
  #b<-lm(events1[,var]~treatment*time + new_site, data=events1)$coef["treatment:time"]
  b<-lm(events1[,var]~treatment*time + new_site, data=events1)$coef["treatment:time"]
  h[i,] <- b
  }
  # get bootstrap CIs from distribution of coefs
  bs_CIs<-quantile(h[,1],c(0.025,0.975))
  #c1_coefs <- thelm$coefficients['treatment:time']
  
  return(bs_CIs)
}
system.time(
for(i in 1:length(outgroupVars))
{
  CIs <- bsCIs.fun(var=outgroupVars[i], reps=1000)
  eventCoefs[i, c("ll", "ul")] <- bsCIs.fun(var=outgroupVars[i], reps=1000)
}
)
```

Save.

```{r, eval=F}
#save(eventCoefs, file="eventCoefs.rda") # with site/state FEs
save(eventCoefs, file="eventCoefs1.rda") # without site/state FEs
```

Load it in.

```{r}
load("eventCoefs1.rda")
```
