---
title: "ecpn_diff-in-diff plots: data and function"
output:
  word_document: default
  html_document: default
---

note: if want to convert to pdf:

dev.copy(pdf,file="endComm_plot_nas.pdf")
dev.off()

pdf(file="endComm_plot_nas.pdf", bg="transparent", width=5, height=5)
endComm_plot_nas
dev.off()


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(dplyr)
library(tidyr)
library(ggplot2)

load("../../c_creating_dataframes/f-aggregateComms_ap.Rdata")
load("../../c_creating_dataframes/rand_df.Rdata")
load("../../b_creating_outcomes/f2-panelData.Rdata")
load("../../../obs_dat/b_analysis/eventsMedian.Rdata")
load("../../../obs_dat/b_analysis/marketMedian.Rdata")

# clean environment
rm(list=ls(pattern="Var|var|.fun|Fun|Col|Index|Indice|Stand|fmla|outcomes"))

#until I figure out insecurity, vio, list, reverse scale it.
#ag.df$in_cw_base <- abs(ag.df$in_cw_base+1)
#ag.df$in_cw_end <- abs(ag.df$in_cw_end+1)
#panel.df$in_cw_y0 <- abs(panel.df$in_cw_y0+1)
#panel.df$in_cw_y1 <- abs(panel.df$in_cw_y1+1)

#ag.df$vio_cw_base <- abs(ag.df$vio_cw_base-1)
#ag.df$vio_cw_end <- abs(ag.df$vio_cw_end-1)
#panel.df$vio_cw_y0 <- abs(panel.df$vio_cw_y0-1)
#panel.df$vio_cw_y1 <- abs(panel.df$vio_cw_y1-1)


#ag.df$list_exp_base <- ag.df$list_exp_base*-1
#ag.df$list_exp_end <- ag.df$list_exp_end*-1
```


# Make plot data

Isolate vars.

```{r}
# comm
ag.vars <- c("attitude_cw", "in_cw", 'contactOnly_cw',
                  'rMean', "end_exp",
                  "pgp_donate_end", "pgp_amount_end")
# individual
ind.vars <- c('attitude_cw', "in_cw", 'contactOnly_cw',
              'pgp_amount_y1', 'pgp_donate_y1')
# both (placebo)
pl.vars <- "vio_cw"

# add additive index
ag.vars <- c(ag.vars, setdiff(gsub("_cw", "_index", ag.vars), ag.vars))
ind.vars <- c(ind.vars, setdiff(gsub("_cw", "_index", ind.vars), ind.vars))
stopifnot(setdiff(ag.vars,names(ag.df))==0)
stopifnot(setdiff(ind.vars,names(panel.df))==0)
```

Ag.df plot data
- mean, sd
- also could want to plot SEs.  
- for SE with clusters, need effective sample size, which needs ICC.

```{r}
#Aggregate Plot df
base <- ag.df[,c(paste0(ag.vars[!grepl("pgp", ag.vars)], "_base"), "treatment", "state", "psu")]
names(base) <- sub("_base", "", names(base))
base$survey <- "Baseline"
end <- ag.df[,c(paste0(ag.vars[!grepl("pgp", ag.vars)], "_end"), "treatment", "state", "psu")]
names(end) <- sub("_end", "", names(end))
end$survey <- "Endline"
plot.df <- rbind(base,end)
rm(base, end)

# get ICCs with dplyr
plot2.df <- plot.df %>% dplyr::group_by(survey) %>% 
  dplyr::summarize_all(funs(ICC::ICCbare(psu,.))) %>%
  as.data.frame() # warnings for non-numerics
names(plot2.df) <- paste0(names(plot2.df), "_icc")

# get mean and sd with dplyr
plot.df$state <- as.character(plot.df$state) # save me trouble with dplyr later
plot.df$psu <- as.numeric(as.character(plot.df$psu))
plot1.df<-plot.df %>% 
  dplyr::group_by(treatment,survey) %>%
  dplyr::summarise_all(list(~mean(.), ~sd(.))) %>% # warnings because cannot sumarise non-numeric
  as.data.frame()

# combine mean/sd df with ICC df
plot.df <- cbind(plot1.df, plot2.df)
plot.df$Treatment<-ifelse(plot.df$treatment %in% 1, "ECPN", "Non-ECPN")
#plot.df$State <- ifelse(plot.df$state %in% "nas", "Nas", "Ben")
#plot.df$plotID <- interaction(plot.df$Treatment, plot.df$State)
rm(plot1.df, plot2.df)

# need to add SEs; need to calc effective sample size; need to remove state, psu, survey, from these
sdVars <-  names(plot.df)[grepl("_sd", names(plot.df))]
sdVars <- sdVars[!sdVars %in% c("state_sd", "psu_sd")]
seVars <- sub("_sd", "_se", sdVars)
iccVars <- sub("_sd", "_icc", sdVars)
essVars <- sub("_sd", "_ess", sdVars)
plot.df[,essVars] <- (2*15)/(1+plot.df[,iccVars]*(2-1)) 

# icc is negative for a couple things...making effective sample size larger than actual...
for(i in 1:length(iccVars))
{
  plot.df[,essVars[i]] <- ifelse(plot.df[,essVars[i]] > 30, 30, plot.df[,essVars[i]])
}
plot.df[,seVars] <- plot.df[,sdVars]/sqrt(plot.df[,essVars])
```

Individual-level (Tr-Co) plot data

```{r}
#Panel Plot df
base1 <- panel.df[,c(paste0(ind.vars[!grepl("pgp", ind.vars)], "_y0"), "treatment", "state", "community")]
names(base1) <- sub("_y0", "", names(base1))
base1$survey <- "Baseline"
end1 <- panel.df[,c(paste0(ind.vars[!grepl("pgp", ind.vars)], "_y1"), "treatment", "state", "community")]
names(end1) <- sub("_y1", "", names(end1))
end1$survey <- "Endline"
plot.df1 <- rbind(base1,end1)
plot.df1$state <- as.character(plot.df1$state) # save me trouble with dplyr later
plot.df1$community <- as.character(plot.df1$community)

plot.df1<-plot.df1 %>% 
  dplyr::group_by(treatment,survey) %>% 
  dplyr::summarise_all(funs(mean(., na.rm = TRUE), sd(., na.rm=T))) %>% # warnings because cannot sumarise non-numeric
  as.data.frame()

sumVars <- intersect(names(base1), ind.vars)
iccVars1 <- paste0(intersect(names(base1), gsub("_icc", "", iccVars)), "_icc")
for(i in 1:length(sumVars))
{
  plot.df1[plot.df1$survey %in% "Baseline",iccVars1[i]] <- ICC::ICCbare(base1$community,base1[,sumVars[i]])
  plot.df1[plot.df1$survey %in% "Endline",iccVars1[i]] <- ICC::ICCbare(end1$community,end1[,sumVars[i]])
}
plot.df1$Treatment<-ifelse(plot.df1$treatment %in% 1, "ECPN", "Non-ECPN")

# need to add SEs; need to calc effective sample size; need to remove state, psu, survey, from these
sdVars1 <-  names(plot.df1)[grepl("_sd", names(plot.df1))]
sdVars1 <- sdVars1[!sdVars1 %in% c("state_sd", "community_sd")]
seVars1 <- sub("_sd", "_se", sdVars1)
iccVars <- sub("_sd", "_icc", sdVars1)
essVars1 <- sub("_sd", "_ess", sdVars1)
avgSize <- mean(table(base1$community)) # diff sized clusters...using the average
lengthComm <- length(table(base1$community)) # number of clusters is 29 -- no loko pastoralists.
plot.df1[,essVars1] <- (avgSize*lengthComm)/(1+plot.df1[,iccVars1]*(avgSize-1)) 
plot.df1[,seVars1] <- plot.df1[,sdVars1]/sqrt(plot.df1[,essVars1])
```

Individual Part-Non-Co plot data.

```{r}
# Part-non-control Plot df
base2 <- panel.df[,c(paste0(ind.vars[!grepl("pgp", ind.vars)], "_y0"), "treatment", "state", "committee")]
names(base2) <- sub("_y0", "", names(base2))
base2$survey <- "Baseline"
end2 <- panel.df[,c(paste0(ind.vars[!grepl("pgp", ind.vars)], "_y1"), "treatment", "state", "committee")]
names(end2) <- sub("_y1", "", names(end2))
end2$survey <- "Endline"
plot.df2 <- rbind(base2,end2)
plot.df2$Treatment <- interaction(plot.df2$treatment, plot.df2$committee)
levels(plot.df2$Treatment) <- c("Control", "Non-Part", NA, "Part")
plot.df2$Treatment <- ordered(plot.df2$Treatment, levels=c("Part", "Non-Part", "Control"))

plot.df2$state <- as.character(plot.df2$state) # save me trouble with dplyr later
plot.df2<-plot.df2 %>% 
  dplyr::group_by(Treatment,survey) %>%  # chris: could add state here to differentiate nas from ben
  dplyr::summarise_all(funs(mean(., na.rm = TRUE), sd(., na.rm=T))) %>% # warnings because cannot sumarise non-numeric
  as.data.frame()

for(i in 1:length(sumVars))
{
  plot.df2[plot.df2$survey %in% "Baseline",iccVars1[i]] <- ICC::ICCbare(base1$community,base1[,sumVars[i]])
  plot.df2[plot.df2$survey %in% "Endline",iccVars1[i]] <- ICC::ICCbare(end1$community,end1[,sumVars[i]])
}
# need to add SEs; need to calc effective sample size; need to remove state, psu, survey, from these
plot.df2[,essVars1] <- (avgSize*lengthComm)/(1+plot.df2[,iccVars1]*(avgSize-1)) 
plot.df2[,seVars1] <- plot.df2[,sdVars1]/sqrt(plot.df2[,essVars1])

rm(list=ls(pattern="(se|sd|ess|icc)Vars"))
rm(list=ls(pattern="base|end|avgSize|lengthComm"))
```

##########
# Plot functions - ggplot showing each group before and after.
##########

```{r}
# Fixing colors
grps <-c("ECPN","Non-ECPN","Part", "Non-Part", "Control")
color.codes<-as.character(c("#FC8D59", "#00BFC4", "#FC8D59", "dark red", "#00BFC4"))
#ECPN = "#FC8D59", Non-ECPN = "#00BFC4", Part="FC8D59", Non-Part="green", Control="#00BFC4")
#plot.df$colors <- c("#00BFC4","#00BFC4","#FC8D59","#FC8D59")
#plot.df1$colors <- c("#FC8D59","#FC8D59","#00BFC4","#00BFC4")
#plot.df2$colors <- c("#FC8D59","#FC8D59", "green", "green", "#FFFFBF","#FFFFBF")

# The main Plot function chris: still need to make SE errorbars same color as lines...
# gg line plot
plot.fun<-function(var, thedf, time, title, xlab, ylab, ymin, ymax){
  ggplot(data=thedf, aes(x=thedf[[time]], y=thedf[[paste0(var, "_mean")]], group=Treatment)) +
  geom_line(aes(color=Treatment))+
  geom_point(aes(color=Treatment))+
  scale_colour_manual(values=setNames(color.codes, grps)) +
  coord_cartesian(ylim = c(ymin, ymax)) +
  #geom_errorbar(aes(ymin = thedf[[paste0(var, "_mean")]] - thedf[[paste0(var, "_se")]], 
   #                ymax= thedf[[paste0(var, "_mean")]] + thedf[[paste0(var, "_se")]],
  #                 color=Treatment), 
  #      width=.2, position=position_dodge(0.03)) + 
  ggtitle(title) +
  theme_bw() +
  theme(panel.grid.major = element_blank()) +
  theme(plot.title = element_text(size=18)) +
  xlab(xlab) +
  ylab(ylab)
}
```


# Save

```{r}
save.image("didPlots_dfs.Rdata")

```