---
title: "ecpn_diff-in-diff plots: data and function"
output:
  word_document: default
  html_document: default
---

note: if want to convert to pdf:

dev.copy(pdf,file="endComm_plot_nas.pdf")
dev.off()

pdf(file="endComm_plot_nas.pdf", bg="transparent", width=5, height=5)
endComm_plot_nas
dev.off()


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(dplyr)
library(tidyr)
library(ggplot2)

load("../../c_creating_dataframes/f-aggregateComms_ap.Rdata")
load("../../c_creating_dataframes/rand_df.Rdata")
load("../../b_creating_outcomes/f2-panelData.Rdata")
load("../../../obs_dat/b_analysis/eventsMedian.Rdata")
load("../../../obs_dat/b_analysis/marketMedian.Rdata")

# clean environment
rm(list=ls(pattern="Var|var|.fun|Fun|Col|Index|Indice|Stand|fmla|outcomes"))

#reverse scaled in earlier code.
#ag.df$in_cw_base <- abs(ag.df$in_cw_base+1)
#ag.df$in_cw_end <- abs(ag.df$in_cw_end+1)
#panel.df$in_cw_y0 <- abs(panel.df$in_cw_y0+1)
#panel.df$in_cw_y1 <- abs(panel.df$in_cw_y1+1)

#ag.df$vio_cw_base <- abs(ag.df$vio_cw_base-1)
#ag.df$vio_cw_end <- abs(ag.df$vio_cw_end-1)
#panel.df$vio_cw_y0 <- abs(panel.df$vio_cw_y0-1)
#panel.df$vio_cw_y1 <- abs(panel.df$vio_cw_y1-1)


#ag.df$list_exp_base <- ag.df$list_exp_base*-1
#ag.df$list_exp_end <- ag.df$list_exp_end*-1
```


# Make plot data

Isolate vars.

```{r}
# comm
ag.vars <- c("attitude_cw", "in_cw", 'contactOnly_cw',
                  'rMean', "end_exp",
                  "pgp_donate_end", "pgp_amount_end")
# individual
ind.vars <- c('attitude_cw', "in_cw", 'contactOnly_cw',
              'pgp_amount_y1', 'pgp_donate_y1')
# both (placebo)
pl.vars <- "vio_cw"

# add additive index
ag.vars <- c(ag.vars, setdiff(gsub("_cw", "_index", ag.vars), ag.vars))
ind.vars <- c(ind.vars, setdiff(gsub("_cw", "_index", ind.vars), ind.vars))
stopifnot(setdiff(ag.vars,names(ag.df))==0)
stopifnot(setdiff(ind.vars,names(panel.df))==0)
```

Make df and plot function.

```{r}
#Aggregate Plot df - comm level
base <- ag.df[,c(paste0(ag.vars[!grepl("pgp", ag.vars)], "_base"), "treatment", "state", "psu", "comm")]
names(base) <- sub("_base", "", names(base))
base$survey <- "Baseline"
end <- ag.df[,c(paste0(ag.vars[!grepl("pgp", ag.vars)], "_end"), "treatment", "state", "psu", "comm")]
names(end) <- sub("_end", "", names(end))
end$survey <- "Endline"
plot.df <- rbind(base,end)
plot.df$comm <- gsub("\\.", "", plot.df$comm)

# get mean and sd at site-level with dplyr
plot.df$state <- as.character(plot.df$state) # save me trouble with dplyr later
plot.df$psu <- as.numeric(as.character(plot.df$psu))
plot1.df<-plot.df %>% 
  dplyr::group_by(psu,survey) %>%  # chris: could add state here to differentiate nas from ben
  dplyr::summarise_all(list(~mean(.), ~sd(.))) %>% # warnings because cannot sumarise non-numeric
  as.data.frame()

plot.df$Treatment<-ifelse(plot.df$treatment %in% 1, "ECPN", "Non-ECPN")
plot1.df$Treatment<-ifelse(plot1.df$treatment_mean %in% 1, "ECPN", "Non-ECPN")
names(plot1.df) <- gsub("_mean", "", names(plot1.df))


# Individual Plot df
base1 <- panel.df[,c(paste0(ind.vars[!grepl("pgp", ind.vars)], "_y0"), "treatment", "state", "community", "id_num")]
names(base1) <- sub("_y0", "", names(base1))
base1$survey <- "Baseline"
end1 <- panel.df[,c(paste0(ind.vars[!grepl("pgp", ind.vars)], "_y1"), "treatment", "state", "community", "id_num")]
names(end1) <- sub("_y1", "", names(end1))
end1$survey <- "Endline"
plot.df1 <- rbind(base1,end1)
plot.df1$state <- as.character(plot.df1$state) # save me trouble with dplyr later
plot.df1$community <- as.character(plot.df1$community)


# Panel Plot df
base2 <- panel.df[,c(paste0(ind.vars[!grepl("pgp", ind.vars)], "_y0"), "treatment", "state", "committee", "community", "id_num")]
names(base2) <- sub("_y0", "", names(base2))
base2$survey <- "Baseline"
end2 <- panel.df[,c(paste0(ind.vars[!grepl("pgp", ind.vars)], "_y1"), "treatment", "state", "committee", "community", "id_num")]
names(end2) <- sub("_y1", "", names(end2))
end2$survey <- "Endline"
plot.df2 <- rbind(base2,end2)
plot.df2$Treatment <- interaction(plot.df2$treatment, plot.df2$committee)
levels(plot.df2$Treatment) <- c("Control", "Non-Part", NA, "Part")
plot.df2$Treatment <- ordered(plot.df2$Treatment, levels=c("Part", "Non-Part", "Control"))
plot.df2$state <- as.character(plot.df2$state) # save me trouble with dplyr later
plot.df2$community <- as.character(plot.df2$community)

plot2.df<-plot.df2 %>% 
  dplyr::group_by(community,survey,Treatment) %>%
  dplyr::summarise_all(list(~mean(.))) %>% # warnings because cannot sumarise non-numeric
  as.data.frame()
plot2.df$thegroup <- interaction(plot2.df$community, plot2.df$Treatment)

# Fixing colors
grps <-c("ECPN","Non-ECPN","Part", "Non-Part", "Control")
color.codes<-as.character(c("#FC8D59", "#00BFC4", "#FC8D59", "dark red", "#00BFC4"))
#ECPN = "#FC8D59", Non-ECPN = "#00BFC4", Part="FC8D59", Non-Part="green", Control="#00BFC4")
#plot.df$colors <- c("#00BFC4","#00BFC4","#FC8D59","#FC8D59")
#plot.df1$colors <- c("#FC8D59","#FC8D59","#00BFC4","#00BFC4")
#plot.df2$colors <- c("#FC8D59","#FC8D59", "green", "green", "#FFFFBF","#FFFFBF")

# The main Plot function chris: still need to make SE errorbars same color as lines...
# gg line plot
plot.fun<-function(var, group, thedf, time, title, xlab, ylab, ymin, ymax){
  ggplot(data=thedf, aes(x=thedf[[time]], y=thedf[[var]], group=thedf[[group]])) +
  geom_line(aes(color=Treatment))+
  geom_point(aes(color=Treatment))+
  scale_colour_manual(values=setNames(color.codes, grps)) +
  coord_cartesian(ylim = c(ymin, ymax)) +
  #geom_errorbar(aes(ymin = thedf[[paste0(var, "_mean")]] - thedf[[paste0(var, "_se")]], 
   #                ymax= thedf[[paste0(var, "_mean")]] + thedf[[paste0(var, "_se")]],
  #                 color=Treatment), 
  #      width=.2, position=position_dodge(0.03)) + 
  ggtitle(title) +
  theme_bw() +
  theme(panel.grid.major = element_blank()) +
  theme(plot.title = element_text(size=18)) +
  xlab(xlab) +
  ylab(ylab)
}
```
```{r, eval=F}
#test
plot.fun(var='attitude_cw', group='comm', thedf=plot.df, time='survey', title="Trust - Community", 
         xlab="Survey", ylab="Average Attitudinal Index Score",
         ymin=-0.1, ymax=1.1)
```

Plot.df is ag.df at community-level.

Plot1.df is ag.df at site-level.

Plot.df1 is panel.df at individual-level, collapsing TR and CO

Plot.df2 is panel.df at individual-level, separating Part, Nonpart, Co.

<!--Neither of these below are done. Don't need them. -->
Plot.df3 is panel.df at community-level.

Plot.df4 is panel.df at site-level.


## Trust Index

ECPN sites improed more on Outgroup Index than control sites.

```{r, eval=F}
(attitudeComm.plot_disag <- plot.fun(var='attitude_cw', group='psu', thedf=plot1.df, time='survey', title="Trust - Community", 
         xlab="Survey", ylab="Average Attitudinal Index Score",
         ymin=-0.1, ymax=1.1))
```

```{r}
(attitudeComm.plot <- plot.fun(var='attitude_cw', group='comm', thedf=plot.df, time='survey', title="Community-level attitude change", 
         xlab="Survey", ylab="Average Attitudinal Index Score",
         ymin=-0.1, ymax=1.1))


png(file="attitudeComm.plot_disag.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
attitudeComm.plot
dev.off()
```

Part vs Non vs Con.  Part is blue and improves.  Non-part is green and gets a bit worse.  Control is red and gets much worse.

```{r}
(attitudePan.plot <- plot.fun(var='attitude_cw', group='thegroup', thedf=plot2.df, time='survey', title="Individual-level attitude change",
         xlab="Survey", ylab="Average Attitudinal Index Score",
         ymin=-0.1, ymax=1.1))

png(file="attitudePan_plot_disag.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
attitudePan.plot
dev.off()
```

## Intergroup Contact Index

ECPN sites decreased less on contact index than control sites.

```{r}
(conComm.plot <- plot.fun(var='contactOnly_cw', group='comm',
                          thedf=plot.df, time='survey',
                          title="Community-level contact change",
                          xlab="Survey", 
                          ylab="Average Intergroup Contact Index Score",
                          ymin=-0.1, ymax=1.1))

png(file="conComm_plot_disag.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
conComm.plot
dev.off()
```


## Perceptions of Security Index

ECPN sites improved more on the security index than control sites.

```{r}
(inComm.plot <- plot.fun(var='in_cw', group='comm',
                         thedf=plot.df, time='survey', title="Community-level insecurity perceptions change", 
         xlab="Survey", ylab="Average Perceptions of Insecurity Index Score",
         ymin=-1.1, ymax=0.1))

png(file="inComm_plot_disag.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
inComm.plot
dev.off()
```

