---
title: "e-makeIndices"
author: "Christopher Grady"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(estimatr)
library(dplyr)
rm(list=ls())
load("../a_cleaning/c_dataCombine.Rdata")
#load()
```

# Decisions

- range or SD scale variables before putting in index?  Things I read say SD, but range is more intuitive for presenting results.

# Functions

<!--Note that inverse covariance weighting and factor analysis stuff has been moved to the "f" files.  IC weighting shouldn't combine these two data sets.  Weights should be dataset specific. -->

Need to do something systematic about these count vars.
(1) code these things into categories: 0s+3 quantiles?
(2) *rank order these things so that ties are same value*
(3) something else?

Here is a function to code into categories, if I choose to do that.  This works for individual variables and can lapply it.

```{r}
#test <- df

# chris: should have had it ignore vars with a max of 1 with an "if" statement. Right now, just not applying it to those vars.
# this removes 0s and then make those their own category.
countFun <- function(var, cats)
{
  thing <- quantile(var[!var %in% 0], na.rm=T, prob=0:cats/cats)
  var_count <- cut(var, thing, include.lowest = T, labels=F)
  newvar <- as.vector(ifelse(var %in% 0, var, var_count))
  newvar <- reshape::rescaler(newvar, type="range")
  return(newvar)
  
}
#test$newvar <- countFun(var=test$clash_details_group.violence_when, cats=3)
#table(df$clash_details_group.violence_when)
#table(test$newvar)

#test$newvar <- countFun(var=test$clash_details_group.violence_when1, cats=3)
#table(df$clash_details_group.violence_when1)
#table(test$newvar)

```

# Outcomes

Primary Outcomes:
    - Intergroup Trust (direct trust questions, bogardus, endorsement experiment)
    - Bargaining == shared resources, dispute resolution?
    - Conflict == two indices
        - insecurity: how much fear from violence prevented people from working, going out at night, getting water, etc.
        - violence_effect: how much people were physically affected by violence, among people who knew bout violence.
    - note: do some type of mediation from trust --> bargaining --> conflict?

Secondary Outcomes:
    - Knowledge about violent conflict
    - Public Goods Game
    - Intergroup Contact other than ECPN (direct Q, markets/social events, and hypothetical with randomization experiment)

Potential Mediators:
    - Reduced threat/anxiety
    - Ingroup Expansion (superordinate identity? Social Distance?)
    - empathy?
    - Potential Benefit
    - List Experiment (Intergroup Affect)
        - note: for "intergroup contact" paper, this may be a primary outcome.

Spillover Outcomes:
    - Trust other groups (ethnic, religious).


# Make Indices & Fixing Variables in the indices

First just making indices by adding things together.  Doing inverse covariance weighting in the next files (the "f" files) after separating the randomly selected people and the panel people.  Could also do factor analysis at that time.

#########################################
# Primary Outcomes
########################################

Primary Outcomes:
    - Intergroup Trust (direct questions, endorsement experiment)
    - Bargaining == shared resources, dispute resolution?
    - Conflict == two indices
        - insecurity: how much fear from violence prevented people from working, going out at night, getting water, etc.
        - violence_effect: how much people were physically affected by violence, among people who knew bout violence.
    - note: do some type of mediation from trust --> bargaining --> conflict?


# Trust

- Main: Direct questions for Index
    - trust_x:	From 1-5, how much do you trust people from X GROUP in your area?
    - trust_area:	People in this area can be trusted
- Additional Outcomes as Robustness Check (not to add to index?): 
    - Bogardus Social Distance Scale
    - Endorsement experiment

*Direct Trust*

```{r}
trustVars <- names(df)[grepl("trust_(x|area)", names(df))]

check.fun <- function(index,vars)
{
  t1 <- summary(df[,index])
  t2 <- psych::alpha(df[,vars])
  return(list(t1,t2))
}


df[,trustVars] <- reshape::rescaler(df[,trustVars],type="range")
df$trust_index <- rowMeans(df[,trustVars],na.rm=T)
check.fun('trust_index', trustVars)

#lm(trust_index~treatment*survey+state, data=df)
```

*Social Distance*

```{r}
distVars <- names(df)[grepl("comfort_group", names(df))]
df[,distVars] <- reshape::rescaler(df[,distVars],type="range")
df$dist_index <- rowMeans(df[,distVars],na.rm=T)
check.fun('dist_index', distVars)

#lm(dist_index~treatment*survey+state, data=df)
```

*Endorsement Experiment*

Not an index, just one question.


*Big Index of all Direct Survey Questions*

```{r}
allTrustVars <- c(trustVars,distVars)
df$allTrust_index <- rowMeans(df[allTrustVars],na.rm=T)
check.fun('allTrust_index', allTrustVars)

#lm(allTrust_index~treatment*survey+state, data=df)
```


# Bargaining == shared resources, dispute resolution?

- Main: Shared Resource Index. Less sharing of resources (less people trying to use same plot of land)
    - share_farmland|pastureland|market
- Additional outcomes: dispute resolution index.
    - Where sharing, does it cause disputes/tension?

*Shared Resources*

Bargaining would mean less land resource sharing.

```{r}
# higher scores == more sharing land resources == bad
shareVars <- names(df)[grepl("^share_(farmland|pasture)$", names(df))]
df[,shareVars] <- reshape::rescaler(df[,shareVars],type="range")
df$share_index <- rowMeans(df[,shareVars],na.rm=T)
check.fun('share_index', shareVars)

#lm(share_index~treatment*survey+state, data=df)
#lm(share_farmland~treatment*survey+state, data=df)
#lm(share_pasture~treatment*survey+state, data=df)
```

*Dispute Resolution*

want: when land resources are shared, are they causing disputes?
want: are the disputes resolved?

want: combined index.  Higher scores if disputes are not happening or if they are resolved peacefully?
want: combined index. higher scores if land not shared.  If land is shared, higher score if not causing disputes.

want: fully combined index. higher scores if land not shared.  If land is shared, higher score if not causing disputes.  If causing disputes, higher scores if disputes always resolved peacefully.


```{r}
# when land resources are shared, are they causing disputes? # higher scores == less disputes == good
dispVars <- names(df)[grepl("(farmland|pasture)_(dispute$|tension$)", names(df))]
summary(df[,dispVars])
df$disp_index <- rowMeans(df[,dispVars],na.rm=T)
check.fun('disp_index', dispVars)

#table(df2$share_farmland_dispute)
#table(end$share_farmland_dispute)


#lm(disp_index~treatment*survey+state, data=df)

###########################

# when they occur, are the disputes resolved? higher scores == more resolved == good.
resolveVars <- names(df)[grepl("(farmland|pasture)_disputes_resolved|resolve_|persist", names(df))]
summary(df[,resolveVars])
df[,resolveVars] <- reshape::rescaler(df[,resolveVars],type="range")
##dispute_persist: coded so high is good (never persist)
##farmland/pasture disputes resolved coded so high is good (always resolved)
##resolve_peace coded so that high is good (strongly agree resolved peacefully)
df$resolve_index <- rowMeans(df[,resolveVars],na.rm=T)
check.fun('resolve_index', resolveVars)

table(df1$farmland_disputes_resolved)
table(base$farmland_disputes_resolved)

#lm(resolve_index~treatment*survey+state, data=df)

```


**fully combined Bargaining index**

Bargaining Index: higher scores if land not shared.  If land is shared, higher score if not causing disputes.  If causing disputes, higher scores if disputes always resolved peacefully.

```{r}
# Bargaining Index!
## higher scores == more sharing land resources == bad
## higher scores == less dispute == good.
## higher scores == more resolved == good.
df$barg_index_farm <- ifelse(df$share_farmland %in% 0, 1, 
                        ifelse(df$share_farmland_dispute %in% 1, 1,
                               ifelse(!(df$share_farmland_dispute %in% 1), df$farmland_disputes_resolved, NA)))
df$barg_index_past <- ifelse(df$share_pasture %in% 0, 1, 
                        ifelse(df$share_pasture_dispute %in% 1, 1,
                               ifelse(!(df$share_pasture_dispute %in% 1), df$pasture_disputes_resolved, NA)))

# index
bargVars <- names(df)[grepl("barg_index", names(df))]
summary(df[,bargVars])
df$barg_index <- rowMeans(df[,bargVars],na.rm=T)
check.fun('barg_index', bargVars)

#lm(barg_index~treatment*survey*farm_pastor+state, data=df)
```


# Conflict 

How much fear from violence prevented people from working, going out at night, getting water, etc.  Formerly called "Security" because NGOs.

## Insecurity Group

higher scores are _bad_ here.  Need to make them GOOD.

"In any clash that occurred in the last year, were you or anyone in your family negatively affected by an attack caused by X group? 

Yes, my work/business was interrupted/closed
Yes, I was forced to leave my home/migrate
Yes, my property was damaged
Yes, a family member was injured
Yes, a family member was killed
"

And also the insecurity index.

```{r}
#violence_effect is not recoded yet
table(df$violence_effect)
df$vio1_bus <- ifelse(grepl("business", df$violence_effect), 1, 0)
df$vio2_home <- ifelse(grepl("home", df$violence_effect), 1, 0)
df$vio3_prop <- ifelse(grepl("property", df$violence_effect), 1, 0)
df$vio4_inj <- ifelse(grepl("injured", df$violence_effect), 1, 0)
df$vio5_kill <- ifelse(grepl("killed", df$violence_effect), 1, 0)
df$violence_effect_num <- rowMeans(df[,grepl("^vio[0-9]_", names(df))], na.rm=T)
vioExpVars <- names(df)[grepl("^vio[0-9]_", names(df))]
df$vioNothing <- ifelse(grepl("^no$", df$violence_effect) | is.na(df$violence_effect), 1, 0)

#table(df$vio5_kill, df$survey, df$state) # deaths go down in both states, but go down a lot more in Nassarawa.
#table(df$vio4_inj, df$survey, df$state) # injuries go down in both states, but go down a lot more in Nassarawa.
##lm(vio5_kill~treatment*survey*farm_pastor+state, data=df)
##lm(vio4_inj~treatment*survey*farm_pastor+state, data=df)
##lm(vioNothing~treatment*survey*farm_pastor+state, data=df)

# is this just because treatment people were more aware?
### yes, it was somewhat. All TR is less likely to be killed, pastoralists are less likely to be injured but farmers are more likely, and pastoralists are more likely to say "no" but farmers are more likely.
#test <- df[df$clash_group.violence %in% 1,]
##lm(vio5_kill~treatment*survey*farm_pastor+state, data=test)
##lm(vio4_inj~treatment*survey*farm_pastor+state, data=test)
##lm(vioNothing~treatment*survey*farm_pastor+state, data=test)



# physical insecurity/conflict effect
inVars <- names(df)[grepl("avoid|insecurity", names(df))] # also add "violence_work_effect" and "violence_effect_num"?
df$insecurity_group.work_days <- reshape::rescaler(dense_rank(df$insecurity_group.work_days), type="range")
## make "days could not work" 0 if respondent said working was not prevented.
df[df$insecurity_group.working %in% 0, "insecurity_group.work_days"] <- 0
## index can either use binary "affect work yes/no" or continuous "how many days work affected", but not both. Going with binary because other vars in index are binary.
#inVars <- inVars[!inVars %in% "insecurity_group.work_days"]
inVars <- inVars[!inVars %in% "insecurity_group.working"]
##make index
df$in_index <- rowMeans(df[,inVars], na.rm=T)
#psych::alpha(df[,inVars]) #0.9
#lm(in_index~treatment*survey+state, data=df)


# all together-- actually meaningless because "vio_effect" vars only asked if know about violence.  TR group was more likely to know about violence.  Need to look at this only for people who knew about violence?  But that's weird about the insecurity group.
conVioEffVars <- c(vioExpVars,inVars)
df$conVioEff_index <- rowMeans(df[,conVioEffVars], na.rm=T)
#psych::alpha(df[,conVioEffVars])
```

######################
# Secondary Outcomes
#####################

Secondary Outcomes:
    - Knowledge about violent conflict
    - Public Goods Game
    - Intergroup Contact other than ECPN (direct Q, markets/social events, and hypothetical with randomization experiment)

# Knowledge/Awareness

Want a variable measuring respondents' awareness of conflict events.  The actual amount of conflict events for each site will be different.  How to know actual amount of conflict?  Median?  Or this just becomes a binary yes/no to conflict within the past one year.


NOTE: higher scores are BAD here for everything except "violence_when", where high values are GOOD (mean longer since violence).  Need to reverse.

```{r clash}
# want: measure of respondents' awareness of conflict events
awareVars <- names(df)[grepl("clash_group.violence$", names(df))] # just one variable now.
summary(df[,awareVars])
#lm(clash_group.violence~treatment*survey*farm_pastor+state, data=df)


# old clashVars: report more or less violence overall.
clashVars <- names(df)[grepl("clash", names(df))][-c(1:2)] # for the index, can only use things on both baseline & endline. No burned/injured.

# the "violence_when" q is coded so that high scores (13 months/1) are GOOD.  Need to reverse so that high scores are BAD.
df$clash_details_group.violence_when <- abs(df$clash_details_group.violence_when-max(df$clash_details_group.violence_when, na.rm=T)) 

# handle the countvars by making it ranks - baseline and endline separately
df[df$survey %in% 0,clashVars[c(1,2,4)]] <- sapply(df[df$survey %in% 0,clashVars[c(1,2,4)]], dense_rank)
df[df$survey %in% 0,clashVars] <- sapply(df[df$survey %in% 0,clashVars], reshape::rescaler, type="range")

##endline
df[df$survey %in% 1,clashVars[c(1,2,4)]] <- sapply(df[df$survey %in% 1,clashVars[c(1,2,4)]], dense_rank)
df[df$survey %in% 1,clashVars] <- sapply(df[df$survey %in% 1,clashVars], reshape::rescaler, type="range")
#chris: what to do with people tied at 0?
summary(df[,clashVars])


# when people are not aware of violence, other vars should be NA. Otherwise just a "vio awareness index"
#df[c(1:5, 150:155),clashVars] # correct

# when people say there was no violence, need to make the other vars 0, not NA.
df[df$clash_group.violence %in% 0, clashVars[c(1,2,4)]] <- 0

# drop 3 because it's the screening question that determines if other questions get asked
df$clash_index <- rowMeans(df[,clashVars[c(1,2,4)]],na.rm=T)
#psych::alpha(df[,clashVars[c(1,2,4)]], na.rm=T) # great index

```

# Public Goods Game (PGG/PGP)

Want variables for if donated and how much donated

```{r}
# donate yes/no
df$pgp_donate <- ifelse(df$pgp_amount>0, 1, 0)
# amount donated already as pgp_amount
```

# Intergroup Contact other than ECPN (direct Q, markets/social events, and hypothetical with percent/randomization experiment)

## Contact Direct Survey Questions.

```{r}
# the vars
contactVars <- names(df)[grepl("(contact.*num|other|contact.*pos|contact_market)", names(df))]
summary(df[,contactVars])

#chris: note that these (num of contacts) has a ton of NA for when people don't have contact.  Need to use "x_at_market" and "contact_nonmarket" so the num of contacts is just 0 if people have no contact, not NA.  
## Use number of contacts if they say they have contact, otherwise use "yes/no if they had contact".
## Only "contact_pos" and "contact_market_pos" should be left NA if they are NA.
df[contactVars[c(1:4,7)]][is.na(df[contactVars[c(1:4,7)]])] <- 0


```

**Alternative coding for contact (robustness check)**

Collapse into two categories: none, once or more.  Has to be coded first because the main index recodes the variables.

```{r}
# categories
df[,paste0(contactVars[c(1:4,7)], "_cats")] <- NA
df[,paste0(contactVars[1], "_cats")] <- df[,contactVars[1]] ## already binary
## baseline
df[df$survey %in% 0,paste0(contactVars[c(2:4,7)], "_cats")] <- lapply(df[df$survey %in% 0,contactVars[c(2:4,7)]], countFun, cats=1)
## endline
df[df$survey %in% 1,paste0(contactVars[c(2:4,7)], "_cats")] <- lapply(df[df$survey %in% 1,contactVars[c(2:4,7)]], countFun, cats=1)

# check
#summary(df[,paste0(contactVars[c(2:4,7)], "_cats")])

# originally did not disaggregate baseline and endline
#df[,contactVars[c(2:4,7)]] <- lapply(df[,contactVars[c(2:4,7)]], countFun, cats=2)
#df[,contactVars[-c(2:4,7)]] <- lapply(df[,contactVars[-c(2:4,7)]], reshape::rescaler, type='range')

# just the contact number vars
df$contactOnly_cats_index <- rowMeans(df[,paste0(contactVars[c(1:4,7)], "_cats")], na.rm=T)
#psych::alpha(df[,paste0(contactVars[c(1:4,7)], "_cats")]) # 0.79

```


```{r contact}
# Count data, needs to be put into categories or ranks
# ranks
df[df$survey %in% 0,contactVars[c(2:4,7)]] <- sapply(df[df$survey %in% 0,contactVars[c(2:4,7)]], dense_rank)
df[df$survey %in% 0,contactVars] <- sapply(df[df$survey %in% 0,contactVars], reshape::rescaler, type='range')
##endline
df[df$survey %in% 1,contactVars[c(2:4,7)]] <- sapply(df[df$survey %in% 1,contactVars[c(2:4,7)]], dense_rank)
df[df$survey %in% 1,contactVars] <- sapply(df[df$survey %in% 1,contactVars], reshape::rescaler, type='range')

# all the vars
df$contact_index <- rowMeans(df[,contactVars], na.rm=T)
#psych::alpha(df[,contactVars]) # 0.81

# just the contact number vars
df$contactOnly_index <- rowMeans(df[,contactVars[c(1:4,7)]], na.rm=T)
#psych::alpha(df[,contactVars][c(2:4,7)]) # 0.79

```

#### Desc Stat

Look at num contacts when contact_nonmarket is yes.  Look at contact_market when x_at_market is yes.  How often 0 anyway?

```{r}
summary(df[df$x_at_market %in% 1,contactVars[c(2:4,7)]])
summary(df[df$contact_nonmarket %in% 1,contactVars[c(2:4,7)]])

table(df[,contactVars[7]], df$x_at_market) # 384 "no" ppl for contact_market when say x is at market.
table(df[,contactVars[2]], df$contact_nonmarket, exclude=c())
table(df[,contactVars[4]], df$contact_nonmarket, exclude=c()) # basically no one says no to social contact when they say yes to contact nonmarket

```

## Hypothetical contact in percent/randomizaiton experiment

rand_exp1a	select_one yes_no_dk	Think about groups that you might join in your leisure time.  Would you join a group that had 5% X Group members?
rand_exp1b	select_one yes_no_dk	Think about the community you live in.  Would you live in a community that had 5% X Group members?

High values good.

Want: Measure of how willing the respondent is to interact with members of other group in hypothetical situations.  Want to know if treatment group becomes more willing from baseline to endline.

### Percent Experiment Pt1

See if relationship between % outgroup and saying "yes" changes.  Are respondents less willing to join groups as the % of outgroup members in the group increases?

Need lm(randOutcome ~ randCondition) at baseline and endline for each community.  

```{r}
df$rand_outcomeA <- rowSums(df[,grepl("rand_exp[0-9]a$", names(df))], na.rm=T)
df$rand_outcomeB <- rowSums(df[,grepl("rand_exp[0-9]b$", names(df))], na.rm=T)
df$rand_condition <- ifelse(!is.na(df$group5p.rand_exp1a) | !is.na(df$group5p.rand_exp1b), 5, 
                                     ifelse(!is.na(df$group25p.rand_exp2a) | !is.na(df$group25p.rand_exp2b), 25,
                                            ifelse(!is.na(df$group50p.rand_exp3a) | !is.na(df$group50p.rand_exp3b), 50,
                                                   ifelse(!is.na(df$group75p.rand_exp4a) | !is.na(df$group75p.rand_exp4b), 75, NA)))) # using both Qs in case someone refused one.

# make an average rand_outcome for "join group" and "live in community"
df$rand_outcome <- rowMeans(df[,grepl("rand_outcome", names(df))], na.rm=T)
df[,c("rand_outcomeA", "rand_outcomeB")] <- NULL

# showing that rand_outcomeA and B are basically the same outcome.
#df[1:10,c("rand_outcomeA", "rand_outcomeB", "rand_outcome", "rand_condition", names(df)[grepl("rand_exp[0-9]a$", names(df))])]
#prop.table(table(df$rand_outcomeB, df$gender),2)

#cor(df$rand_outcomeA, df$rand_outcomeB)
#summary(lm(rand_outcomeA ~ gender + farm_pastor + treatment + as.numeric(age), df)) # predicted by same things
#summary(lm(rand_outcomeB ~ gender + farm_pastor + treatment + as.numeric(age), df))
```

Each community needs to be assigned the value of lm(randOutcome ~ randCondition) for their community at baseline/endline.  Going to try to group_by(community, survey), run the lm model, and assign the coef to the entire group.

```{r}
# chris: only works if nothing is loaded except the packages and data of this .rmd?
df <- df %>% dplyr::group_by(community, survey) %>%
  mutate(rand_lm = coef(lm(rand_outcome ~ rand_condition))[2]) %>%
  as.data.frame(.)

stopifnot(coef(lm(rand_outcome ~ rand_condition, data=df[df$survey %in% 0 & df$community %in% "50.pastoralists",]))[2] ==
            mean(df$rand_lm[df$survey %in% 0 & df$community %in% "50.pastoralists"], na.rm=T))
stopifnot(coef(lm(rand_outcome ~ rand_condition, data=df[df$survey %in% 1 & df$community %in% "22.farmers",]))[2] ==
            mean(df$rand_lm[df$survey %in% 1 & df$community %in% "22.farmers"], na.rm=T))
```

Note: Need to make sure it aggregates properly in aggregation file.

Looking at it descriptively, treatment areas just say "yes" more to every category, from 5% to 75%, but especially 25% and 50%.  Can look at that at community-level with vars for: (1) increase at 5%, (2) increase at 25%, (3) increase at 50%, (4) increase at 75%, and (5) average increase.  Can then ask: did Treatment group increase more at every level, on average, than Control group?  That leads to "percent experiment pt2".

### Percent Experiment pt2

Instead of asking "did the relationship between % outgroup and saying yes change from baseline to endline?" Let's ask "Did more people say yes in the treatment group than the control group, across all categories?"  

The reason for this: in Treatment, "yes" was higher for every % outgroup, which means the _relationship_ between X & Y did not change, but looks like a treatment effect.  Just doesn't work because the 5% outgroup condition is supposed to be a calibrate/everyone says yes condition, but it didn't work.

**In aggregation file, the "rand_outcome" column can be made into a DiD outcome like all the others.  It will be the % of each community who said "yes" to the percent experiment at that time point, across all experimental conditions.**  In aggregation file, I also code the % who said yes in each experimental condition so we can make that plot.

## Direct Observation of Behavior

In the "obsDat" folder.  Can be added to comm-level after aggregation.




##############################
# Potential Mediators
##############################

Potential Mediators:
    - Reduced threat
    - Ingroup Expansion (superordinate identity? Social Distance?)
    - Potential Benefit
    - List Experiment (Intergroup Affect)

Spillover Outcomes:
    - Trust other groups (ethnic, religious).

## Threat

High numbers are BAD. Need to make them GOOD.

```{r}
# Set vars
threatVars <- names(df)[grepl("threat_group.threat", names(df))]
df[,threatVars] <- reshape::rescaler(df[,threatVars],type="range")

# Reverse code things that are not yet reversed -- all of them
df[,c(threatVars)] <- df[,threatVars]*-1

# Make Index about Psychological Threat
summary(df[,threatVars])
df$threat_index <- rowMeans(df[,threatVars],na.rm=T)
#psych::alpha(df[,threatVars]) # 0.59, not great, Jim.
```

## Ingroup Expansion

## Social Cohesion Group

Note there are multiple concepts.

- General/abstract things in sc1, and concrete/hypothetical things in sc2.
- some empathy things (next code chunk)
- some ingroup expansion things (here).

```{r}
cohesVars <- names(df)[grepl("social_cohesion_group", names(df))]
df[,cohesVars] <- reshape::rescaler(df[,cohesVars],type="range")
summary(df[,cohesVars])
df$cohes_index <- rowMeans(df[,cohesVars], na.rm=T)
#psych::alpha(df[,cohesVars]) # 0.75

# sc1 - abstract
cohesVars1 <- cohesVars[1:5]
df$cohes_index1 <- rowMeans(df[,cohesVars1], na.rm=T)
#psych::alpha(df[,cohesVars1]) # 0.77

# sc2 - concrete
cohesVars2 <- cohesVars[6:10]
df$cohes_index2 <- rowMeans(df[,cohesVars2], na.rm=T)
#psych::alpha(df[,cohesVars2]) # 0.76

# empathy (chunk below)

# expand
expandVars <- cohesVars[1:8]
df$expand_index <- rowMeans(df[,expandVars], na.rm=T)
#psych::alpha(df[expandVars]) # 0.74
```


## empathy

Empathy == (helping other group in trouble) & Perspective-taking (who is responsible for violence)

```{r}
empVars <- c("social_cohesion_group2.misfortune_x", "social_cohesion_group2.misfortune_your")
perspVars <- "threat_group.x_responsible"

df[,empVars] <- reshape::rescaler(df[,empVars],type="range")
df[,perspVars] <- reshape::rescaler(df[,perspVars],type="range")

summary(df[,empVars])
df$emp_index <- rowMeans(df[,empVars], na.rm=T)
df$persp_index <- df[,perspVars]
df$empPersp_index <- rowMeans(df[,c(empVars, perspVars)])

#alpha
#psych::alpha(df[,c(empVars, perspVars)])
```

## Potential Benefit

## Econ Benefit Group

```{r}
table(df$econ_benefit_group.benefit_econ)
beneVars <- names(df)[grepl("(econ|qip)", names(df))][-4]
df[,beneVars] <- reshape::rescaler(df[,beneVars],type="range")
summary(df[,beneVars])

# all
#table(df$econ_benefit_group.benefit_econ, df$econ_benefit_group.more_benefit, exclude=c()) # if agreed they benefit materially
#table(df$econ_benefit_group.benefit_econ, df$econ_benefit_group.more_benefit_disagree, exclude=c()) # if disagreed they benefit
df$bene_index <- rowMeans(df[,beneVars],na.rm=T)

# perceptions only
beneVarsPerc <- beneVars[1:3]
df$bene_index_perc <- rowMeans(df[,beneVarsPerc],na.rm=T)

# awareness/use only
beneVarsReal <- beneVars[4:7]
df$bene_index_real <- rowMeans(df[,beneVarsReal],na.rm=T)

# best question only
beneVar <- beneVars[1]
df$bene_index1 <- df[,beneVar]
```

## List Experiment (Intergroup Affect)
        - note: for "intergroup contact" paper, this may be a primary outcome.

# Spillover Outcomes:

## Trust other groups (ethnic, religious).

Outgroup & X Group

```{r}
outVars <- names(df)[grepl("(comf|outgroup)", names(df))]
df[,outVars] <- reshape::rescaler(df[,outVars],type="range")
summary(df[,outVars])

df$out_index <- rowMeans(df[,outVars],na.rm=T)
psych::alpha(df[,outVars]) # 0.89


# X specifically
xVars <- names(df)[grepl("(comf|trust_x)", names(df))]
summary(df[,xVars])

df$x_index <- rowMeans(df[,xVars],na.rm=T)
psych::alpha(df[,xVars]) # 0.89

# other groups specifically
otherVars <- setdiff(outVars,xVars)
summary(df[,otherVars])

df$other_index <- rowMeans(df[,otherVars],na.rm=T)
psych::alpha(df[,otherVars]) # 0.89

```













**************************

# Stuff from Policy Paper






## Dispute Resolution Group

high numbers are GOOD.  fewer disputes, better dispute resolution.  Sharing resources also included here.

This one is hard.  'Resolve' is what we want, but it gives higher scores if tension/disputes are resolved peacefully.  Resolving peacefully can only happen if disputes occur, so people with no disputes score lower on this than they should.  To fix that, I am making the variables so that no disputes is equivalent to always peacefully resolved disputes.  Then making the index by putting these together for each resource (markets, farmland, pastures).  Then add in the "disputes generally resolved peacefully" var and the "disputes generally persist after attempts to resolve them" var.

If people report not sharing a resource, they get NA for dispute/resolving.  That seems right, but the "no disputes" scoring low is definitely wrong.

```{r}
# more sharing resources, fewer disputes, & better resolved disputes (this big index does not make sense. sharing farmland opens up qs about disputes.)
shareVars <- names(df)[grepl("^share_[a-z]*$", names(df))]
numDisVars <- names(df)[grepl("(dispute$|tension$)", names(df))]
resolveVars <- names(df)[grepl("(resolve[^s]|persist)", names(df))]

# if NO disputes (1=no), then give max for dispute resolution.
df$farmland_disputes_resolved <- ifelse(df$share_farmland_dispute %in% 1 & is.na(df$farmland_disputes_resolved), max(df$farmland_disputes_resolved, na.rm=T),  df$farmland_disputes_resolved)
df$pasture_disputes_resolved <- ifelse(df$share_pasture_dispute %in% 1 & is.na(df$pasture_disputes_resolved), max(df$pasture_disputes_resolved, na.rm=T),  df$pasture_disputes_resolved)
df$market_disputes_resolved <- ifelse(df$share_market_dispute %in% 1 & is.na(df$market_disputes_resolved), max(df$market_disputes_resolved, na.rm=T),  df$market_disputes_resolved)

disVars <- c(shareVars, numDisVars, resolveVars)
df[,disVars] <- reshape::rescaler(df[,disVars],type="range")
#summary(df[,disVars])
df$dis_index <- rowMeans(df[,disVars], na.rm=T)
#psych::alpha(df[,disVars]) # won't give an alpha? Something wrong with this as an index, perfect correlations.  Shared should not be a part of it.


################################################
# Individual parts of dispute resolution.
################################################

# better resolved
df$resolve_index <- rowMeans(df[,resolveVars], na.rm=T)
#summary(df[,resolveVars])
#psych::alpha(df[,resolveVars]) #0.48

# fewer disputes
df$numDis_index <- rowMeans(df[,numDisVars], na.rm=T)
#summary(df[,numDisVars])
#psych::alpha(df[,numDisVars]) #0.78

# shared resources
df$share_index <- rowMeans(df[,shareVars], na.rm=T)
#psych::alpha(df[,shareVars]) #0.39

```

### Dispute Actors

This is the section of the PAP under "dispute resolution"....though it should have been the disputes over shared resources, immediately above.

There are too many actors in this to make any sense of it.

```{r}
disActorVars <- names(df)[grepl("dispute_resolution_group", names(df))]

df[,disActorVars] <- reshape::rescaler(df[,disActorVars],type="range")
#summary(df[,disActorVars])
df$disActor_index <- rowMeans(df[,disActorVars], na.rm=T)
#psych::alpha(df[,disActorVars]) #0.82

# I don't want to code all of these.
## local gov
## rel leaders
## sec officials
## state gov
## trad leader
## women
## youth
```

## Violence Group

We want to use this as a placebo, but field team thinks it might be affected by program.  So...I guess we are not using it as a placebo?  Nah, it's a placebo to check SDB.

```{r}
vioVars <- names(end)[grepl("violence_group", names(end))]
df[,vioVars] <- reshape::rescaler(df[,vioVars],type="range")

summary(df[,vioVars])
df$vio_index <- rowMeans(df[,vioVars], na.rm=T)
#psych::alpha(df[,vioVars]) # 0.83

```


Chris: Add this one?

peace_commit:	You would personally commit to peace with X group, even if members of X group used violence against your group.



********************************

**Added later when figuring out what academic paper is about**.  Reframing paper around intergroup bargaining

Need measurements of:
(1) trust
(2) intergroup affect/animosity
(3) threat
(4) empathy
(5) ingroup expansion/intergroup cohesion
(6) perceptions of economic benefit

## Intergroup Affect/Animosity

comfort_group:	With regards to someone from X group, would you feel comfortable:
field:	...if they worked in your field?
watch_animals:	…paying them to watch your animals?
trade_goods:	…trading goods with them?
share_meal:	…sharing a meal with them?
marry:	…with a close relative marrying a person from X group?

contact_pos:	Overall, would you say your interactions with X group are:

list_exp1b: "I’m going to read you a list of items that anger or upset some people.  I’d like you to tell me how many of these things upset you.  Please don’t tell me which items upset you, just how many of them upset you.

When your football team loses a match
Increases in the price of gasoline
Lack of rainfall
When you have to interact with a member of X group in the market

Remember, don’t tell me which items upset you, just how many.
"

end_exp1a:	Imagine that there is a proposal by a Farmer’s Cooperative Society for action to enhance access to clean water in rural areas.  Though expensive, the proposal aims to bring fresh, clean water to hundreds of areas without access to it, including this one.  If this were proposed, how would you feel about it?
end_exp1b:	Imagine that there is a proposal by MACBAN for action to enhance access to clean water in rural areas.  Though expensive, the proposal aims to bring fresh, clean water to hundreds of areas without access to it, including this one.  If this were proposed, how would you feel about it?
end_exp1c:	Imagine that there is a proposal for action to enhance access to clean water in rural areas.  Though expensive, the proposal aims to bring fresh, clean water to hundreds of areas without access to it, including this one.  If this were proposed, how would you feel about it?



## Threat - done above

x_threat:	You see X group as a threat to your community
x_influence:	You think X group have too much influence on your community
x_values:	You think that people from X group have different morals than people from your group


Add "x_responsible:	Some people say X group is responsible for most of the violence in this community, while others say that both groups are responsible for the violence here.  Which is closer to your view?



## Empathy

??

misfortune_x:	Suppose something unfortunate happened to someone from X group in this community, such as a serious illness or the death of a parent. How likely is it that some people in the community from your group would get together to help them?
misfortune_your: Suppose something unfortunate happened to someone from your group in this community, such as a serious illness or the death of a parent. How likely is it that some people in the community from X group would get together to help them?


## Ingroup expansion

help_neighbors:	People in this area are willing to help their neighbors across ethnic and religious lines
**trust_area:	People in this area can be trusted** **this is used in trust index**
get_along:	People in this area generally do not get along together
values:	People in this area do not share the same morals
work_together:	People in this area see the benefits of working together to achieve common goals

x_values:	You think that people from X group have different morals than people from your group

contribute_your:	What proportion of your group in this area contribute time or money toward common development goals, such as building a levy or repairing a road?
contribute_x:	What proportion of X group in this area contribute time or money toward common development goals, such as building a levy or repairing a road?
water_prob:	If there was a water supply problem in this community, how likely is it that people from your group and people from X group would cooperate to try to solve the problem?


## Perceptions Economic Benefit

econ_benefit_group:	Please tell me how strongly you agree/disagree with each of the following statements:
benefit_econ:	You currently benefit economically from cooperating with members of X GROUP. Do you…
more_benefit:	You would benefit economically more than you currently do if there was peace between your communities and X group. Do you… 
more_benefit_disagree:	You would benefit economically if there were peace between your community and X group.  Do you… 



# Excluded

Survey Experiments: not an index, not useful at individual level.

Different actors success in dispute resolution.

# make usernames same on y0 and y1

```{r}
levels(df$username)[levels(df$username) %in% "f.gbeyi"] <- "f.gbenyi"
levels(df$username)[levels(df$username) %in% "f.onaja"] <- "f.onoja"
levels(df$username)[levels(df$username) %in% "l.awule"] <- "l.aule"
```



# Save

```{r}
save.image(file="d-additiveIndices.Rdata")

```

Next step is to separate preselected & randomly selected, aggregate randomly selected.