---
title: "Scale variables and make additive indices"
author: "Christopher Grady"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(estimatr)
library(dplyr)
rm(list=ls())
load("../a_cleaning/c_dataCombine.Rdata")
#load()

# make usernames same on y0 and y1
levels(df$username)[levels(df$username) %in% "f.gbeyi"] <- "f.gbenyi"
levels(df$username)[levels(df$username) %in% "f.onaja"] <- "f.onoja"
levels(df$username)[levels(df$username) %in% "l.awule"] <- "l.aule"
```

# Goal

- Scale variables (many count vars)
- make additive indices since it's just rowMean of scaled vars

# Decisions

- range or SD scale variables before putting in index? SD for index, though range is more intuitive if presenting results for individual questions. Doesn't make much difference for estimating TR effects.

# Functions

<!--Note that inverse covariance weighting and factor analysis stuff has been moved to the "f" files.  IC weighting shouldn't combine these two data sets.  Weights should be dataset specific. -->

Need to do something systematic about these count vars.
(1) code these things into categories: 0s+3 quantiles?
(2) *rank order these things so that ties are same value*
(3) something else?

Here is a function to code into categories, if I choose to do that.  This works for individual variables and can lapply it.

```{r}
#test <- df

# chris: should have had it ignore vars with a max of 1 with an "if" statement. Right now, just not applying it to those vars.
# this removes 0s and then make those their own category.
countFun <- function(var, cats)
{
  thing <- quantile(var[!var %in% 0], na.rm=T, prob=0:cats/cats)
  var_count <- cut(var, thing, include.lowest = T, labels=F)
  newvar <- as.vector(ifelse(var %in% 0, var, var_count))
  newvar <- reshape::rescaler(newvar, type="range")
  return(newvar)
  
}
#test$newvar <- countFun(var=test$clash_details_group.violence_when, cats=3)
#table(df$clash_details_group.violence_when)
#table(test$newvar)

#test$newvar <- countFun(var=test$clash_details_group.violence_when1, cats=3)
#table(df$clash_details_group.violence_when1)
#table(test$newvar)

```

# Outcomes

Primary Outcomes
- Attitudes
    - index: direct trust questions + bogardus
    - endorsement experiment
- Contact
    - index: contact in many situations
    - randomization experiment (percent experiment)
- Perceptions of Insecurity
    - index: fear doing things in many situations
- Public Goods Game
    - % donated, amount donated

Placebo
- attitudes towards violence

Other outcomes
- Bargaining == shared resources, dispute resolution?
    - note: do some type of mediation from trust --> bargaining --> conflict?
- Knowledge about violent conflict

Potential Mediators:
    - Reduced threat/anxiety?
    - Ingroup Expansion (superordinate identity?)
    - empathy?
    - Perceived Potential Benefit?

Spillover Outcomes:
    - Trust other groups (ethnic, religious)?


# Make Indices & Fixing Variables in the indices

First just making indices by adding things together.  Doing inverse covariance weighting in the next files (the "f" files) after separating the randomly selected people and the panel people.  Could also do factor analysis at that time.

#########################################
# Primary Outcomes
########################################

# Attitudes

- Direct questions for Index
    - trust_x:	From 1-5, how much do you trust people from X GROUP in your area?
    - trust_area:	People in this area can be trusted
    - Bogardus Social Distance Scale
- Endorsement experiment

*Direct Trust*

```{r}
trustVars <- names(df)[grepl("trust_(x|area)", names(df))]

check.fun <- function(index,vars)
{
  t1 <- summary(df[,index])
  t2 <- psych::alpha(df[,vars])
  return(list(t1,t2))
}

df[,trustVars] <- reshape::rescaler(df[,trustVars],type="range")
```

*Social Distance*

```{r}
distVars <- names(df)[grepl("comfort_group", names(df))]
df[,distVars] <- reshape::rescaler(df[,distVars],type="range")
```

*Index of Attitudes Direct Survey Questions (Trust, Bogardus)*

```{r}
attitudeVars <- c(trustVars,distVars)
df$attitude_index <- rowMeans(df[attitudeVars],na.rm=T)
check.fun('attitude_index', attitudeVars)
```

*Endorsement Experiment*

Not an index, just one question. Nothing to do here.

*************

# Intergroup Contact other than ECPN

direct Q, markets/social events, and hypothetical with percent/randomization experiment)

## Contact Direct Survey Questions.

```{r}
# the vars
contactVars <- names(df)[grepl("(contact.*num|other|contact.*pos|contact_market)", names(df))]
summary(df[,contactVars])

#chris: note that these (num of contacts) has a ton of NA for when people don't have contact.  Need to use "x_at_market" and "contact_nonmarket" so the num of contacts is just 0 if people have no contact, not NA.  
## Use number of contacts if they say they have contact, otherwise use "yes/no if they had contact".
## Only "contact_pos" and "contact_market_pos" should be left NA if they are NA. Those are not actual contact counts.
df[contactVars[c(1:4,7)]][is.na(df[contactVars[c(1:4,7)]])] <- 0

```

*Make the contact index.  Counts skewed to use dense_rank.*

But first, raw and categories versions as robustness checks for appendix.

Counts: Collapse into two categories: none, once or more.

```{r}
# categories
df[,paste0(contactVars[c(1:4,7)], "_cats")] <- NA
df[,paste0(contactVars[1], "_cats")] <- df[,contactVars[1]] ## already binary
## baseline
df[df$survey %in% 0,paste0(contactVars[c(2:4,7)], "_cats")] <- lapply(df[df$survey %in% 0,contactVars[c(2:4,7)]], countFun, cats=1)
## endline
df[df$survey %in% 1,paste0(contactVars[c(2:4,7)], "_cats")] <- lapply(df[df$survey %in% 1,contactVars[c(2:4,7)]], countFun, cats=1)

# check
#summary(df[,paste0(contactVars[c(2:4,7)], "_cats")])

# just the contact number vars
df$contactOnly_cats_index <- rowMeans(df[,paste0(contactVars[c(1:4,7)], "_cats")], na.rm=T)
#psych::alpha(df[,paste0(contactVars[c(1:4,7)], "_cats")]) # 0.79

```

Raw: using the numbers people gave us, slightly truncating extreme outliers that might be data entry errors.

```{r}
summary(df[,contactVars[c(1:4,7)]])
df[df[contactVars[7]]>100,contactVars[7]] <- c(101,103,102)
df[df[contactVars[3]]>100,contactVars[3]] <- 101
df[,paste0(contactVars[c(1:4,7)], "_raw")] <- df[,contactVars[c(1:4,7)]]
df$contactOnly_raw_index <- rowMeans(df[,contactVars[c(1:4,7)]], na.rm=T)

```

Ranked.

```{r contact}
# Count data skewed, needs to be ranked w/in base/end
# ranks
df[df$survey %in% 0,contactVars[c(2:4,7)]] <- sapply(df[df$survey %in% 0,contactVars[c(2:4,7)]], dense_rank)
df[df$survey %in% 0,contactVars] <- sapply(df[df$survey %in% 0,contactVars], reshape::rescaler, type='range')
##endline
df[df$survey %in% 1,contactVars[c(2:4,7)]] <- sapply(df[df$survey %in% 1,contactVars[c(2:4,7)]], dense_rank)
df[df$survey %in% 1,contactVars] <- sapply(df[df$survey %in% 1,contactVars], reshape::rescaler, type='range')

# index (just the contact number vars)
df$contactOnly_index <- rowMeans(df[,contactVars[c(1:4,7)]], na.rm=T)
#psych::alpha(df[,contactVars][c(2:4,7)]) # 0.79

```


## Hypothetical contact in percent/randomizaiton experiment

rand_exp1a	select_one yes_no_dk	Think about groups that you might join in your leisure time.  Would you join a group that had 5% X Group members?
rand_exp1b	select_one yes_no_dk	Think about the community you live in.  Would you live in a community that had 5% X Group members?

High values good.

Want: Measure of how willing the respondent is to interact with members of other group in hypothetical situations.  Want to know if treatment group becomes more willing from baseline to endline.

### Percent Experiment Pt1

See if relationship between % outgroup and saying "yes" changes.  Are respondents less willing to join groups as the % of outgroup members in the group increases?

Need lm(randOutcome ~ randCondition) at baseline and endline for each community.  

```{r}
df$rand_outcomeA <- rowSums(df[,grepl("rand_exp[0-9]a$", names(df))], na.rm=T)
df$rand_outcomeB <- rowSums(df[,grepl("rand_exp[0-9]b$", names(df))], na.rm=T)
df$rand_condition <- ifelse(!is.na(df$group5p.rand_exp1a) | !is.na(df$group5p.rand_exp1b), 5, 
                                     ifelse(!is.na(df$group25p.rand_exp2a) | !is.na(df$group25p.rand_exp2b), 25,
                                            ifelse(!is.na(df$group50p.rand_exp3a) | !is.na(df$group50p.rand_exp3b), 50,
                                                   ifelse(!is.na(df$group75p.rand_exp4a) | !is.na(df$group75p.rand_exp4b), 75, NA)))) # using both Qs in case someone refused one.

# make an average rand_outcome for "join group" and "live in community"
df$rand_outcome <- rowMeans(df[,grepl("rand_outcome", names(df))], na.rm=T)
df[,c("rand_outcomeA", "rand_outcomeB")] <- NULL

# showing that rand_outcomeA and B are basically the same outcome.
#df[1:10,c("rand_outcomeA", "rand_outcomeB", "rand_outcome", "rand_condition", names(df)[grepl("rand_exp[0-9]a$", names(df))])]
#prop.table(table(df$rand_outcomeB, df$gender),2)

#cor(df$rand_outcomeA, df$rand_outcomeB)
#summary(lm(rand_outcomeA ~ gender + farm_pastor + treatment + as.numeric(age), df)) # predicted by same things
#summary(lm(rand_outcomeB ~ gender + farm_pastor + treatment + as.numeric(age), df))
```

Each community needs to be assigned the value of lm(randOutcome ~ randCondition) for their community at baseline/endline.  Going to try to group_by(community, survey), run the lm model, and assign the coef to the entire group.

```{r}
# chris: only works if nothing is loaded except the packages and data of this .rmd?
df <- df %>% dplyr::group_by(community, survey) %>%
  mutate(rand_lm = coef(lm(rand_outcome ~ rand_condition))[2]) %>%
  as.data.frame(.)

stopifnot(coef(lm(rand_outcome ~ rand_condition, data=df[df$survey %in% 0 & df$community %in% "50.pastoralists",]))[2] ==
            mean(df$rand_lm[df$survey %in% 0 & df$community %in% "50.pastoralists"], na.rm=T))
stopifnot(coef(lm(rand_outcome ~ rand_condition, data=df[df$survey %in% 1 & df$community %in% "22.farmers",]))[2] ==
            mean(df$rand_lm[df$survey %in% 1 & df$community %in% "22.farmers"], na.rm=T))
```

Note: Need to make sure it aggregates properly in aggregation file.

Looking at it descriptively, treatment areas just say "yes" more to every category, from 5% to 75%, but especially 25% and 50%.  Can look at that at community-level with vars for: (1) increase at 5%, (2) increase at 25%, (3) increase at 50%, (4) increase at 75%, and (5) average increase.  Can then ask: did Treatment group increase more at every level, on average, than Control group?  That leads to "percent experiment pt2".

### Percent Experiment pt2

Instead of asking "did the relationship between % outgroup and saying yes change from baseline to endline?" Let's ask "Did more people say yes in the treatment group than the control group, across all categories?"  

The reason for this: in Treatment, "yes" was higher for every % outgroup, which means the _relationship_ between X & Y did not change, but looks like a treatment effect.  Just doesn't work because the 5% outgroup condition is supposed to be a calibrate/everyone says yes condition, but it didn't work.

**In aggregation file, the "rand_outcome" column can be made into a DiD outcome like all the others.  It will be the % of each community who said "yes" to the percent experiment at that time point, across all experimental conditions.**  In aggregation file, I also code the % who said yes in each experimental condition so we can make that plot.

## Direct Observation of Behavior

In the "obsDat" folder.


# Perceptions of Insecurity from conflict 

How much fear from violence prevented people from working, going out at night, getting water, etc.

## Insecurity Group

higher scores are _bad_ here.  Need to make them GOOD.

The insecurity index.

```{r}
# physical insecurity/conflict effect
inVars <- names(df)[grepl("avoid|insecurity", names(df))] # also add "violence_work_effect" and "violence_effect_num"?
df$insecurity_group.work_days <- reshape::rescaler(dense_rank(df$insecurity_group.work_days), type="range")
## make "days could not work" 0 if respondent said working was not prevented.
df[df$insecurity_group.working %in% 0, "insecurity_group.work_days"] <- 0
## index can either use binary "affect work yes/no" or continuous "how many days work affected", but not both. Going with binary because other vars in index are binary.
#inVars <- inVars[!inVars %in% "insecurity_group.work_days"]
inVars <- inVars[!inVars %in% "insecurity_group.working"]
##make index
df$in_index <- rowMeans(df[,inVars], na.rm=T)
#psych::alpha(df[,inVars]) #0.9
```


# Public Goods Game (PGG/PGP)

Want variables for if donated and how much donated

```{r}
# donate yes/no
df$pgp_donate <- ifelse(df$pgp_amount>0, 1, 0)
# amount donated already as pgp_amount
```


## Violence Group

We want to use this as a placebo, but field team thinks it might be affected by program.  So...I guess we are not using it as a placebo?  Nah, it's a placebo to check SDB.

Edit: "peace_commit" question was not part of violence attitudes index, but it could have been:	You would personally commit to peace with X group, even if members of X group used violence against your group.
    - add this? Decided against adding it so the placebo is just the stuff I apriori wanted as a placebo.

```{r}
vioVars <- names(end)[grepl("violence_group", names(end))]
df[,vioVars] <- reshape::rescaler(df[,vioVars],type="range")

summary(df[,vioVars])
df$vio_index <- rowMeans(df[,vioVars], na.rm=T)
#psych::alpha(df[,vioVars]) # 0.83

```




*****************************



######################
# Secondary Outcomes
#####################

# Bargaining == shared resources, dispute resolution?

- Main: Shared Resource Index. Less sharing of resources (less people trying to use same plot of land)
    - share_farmland|pastureland|market
- Additional outcomes: dispute resolution index.
    - Where sharing, does it cause disputes/tension?

*Shared Resources*

Bargaining would mean less land resource sharing.

```{r}
# higher scores == more sharing land resources == bad
shareVars <- names(df)[grepl("^share_(farmland|pasture)$", names(df))]
df[,shareVars] <- reshape::rescaler(df[,shareVars],type="range")
df$share_index <- rowMeans(df[,shareVars],na.rm=T)
check.fun('share_index', shareVars)

#lm(share_index~treatment*survey+state, data=df)
#lm(share_farmland~treatment*survey+state, data=df)
#lm(share_pasture~treatment*survey+state, data=df)
```

*Dispute Resolution*

want: when land resources are shared, are they causing disputes?
want: are the disputes resolved?

want: combined index.  Higher scores if disputes are not happening or if they are resolved peacefully?
want: combined index. higher scores if land not shared.  If land is shared, higher score if not causing disputes.

want: fully combined index. higher scores if land not shared.  If land is shared, higher score if not causing disputes.  If causing disputes, higher scores if disputes always resolved peacefully.


```{r}
# when land resources are shared, are they causing disputes? # higher scores == less disputes == good
dispVars <- names(df)[grepl("(farmland|pasture)_(dispute$|tension$)", names(df))]
summary(df[,dispVars])
df$disp_index <- rowMeans(df[,dispVars],na.rm=T)
check.fun('disp_index', dispVars)

#table(df2$share_farmland_dispute)
#table(end$share_farmland_dispute)


#lm(disp_index~treatment*survey+state, data=df)

###########################

# when they occur, are the disputes resolved? higher scores == more resolved == good.
resolveVars <- names(df)[grepl("(farmland|pasture)_disputes_resolved|resolve_|persist", names(df))]
summary(df[,resolveVars])
df[,resolveVars] <- reshape::rescaler(df[,resolveVars],type="range")
##dispute_persist: coded so high is good (never persist)
##farmland/pasture disputes resolved coded so high is good (always resolved)
##resolve_peace coded so that high is good (strongly agree resolved peacefully)
df$resolve_index <- rowMeans(df[,resolveVars],na.rm=T)
check.fun('resolve_index', resolveVars)

table(df1$farmland_disputes_resolved)
table(base$farmland_disputes_resolved)

#lm(resolve_index~treatment*survey+state, data=df)

```


**fully combined Bargaining index**

Bargaining Index: higher scores if land not shared.  If land is shared, higher score if not causing disputes.  If causing disputes, higher scores if disputes always resolved peacefully.

```{r}
# Bargaining Index!
## higher scores == more sharing land resources == bad
## higher scores == less dispute == good.
## higher scores == more resolved == good.
df$barg_index_farm <- ifelse(df$share_farmland %in% 0, 1, 
                        ifelse(df$share_farmland_dispute %in% 1, 1,
                               ifelse(!(df$share_farmland_dispute %in% 1), df$farmland_disputes_resolved, NA)))
df$barg_index_past <- ifelse(df$share_pasture %in% 0, 1, 
                        ifelse(df$share_pasture_dispute %in% 1, 1,
                               ifelse(!(df$share_pasture_dispute %in% 1), df$pasture_disputes_resolved, NA)))

# index
bargVars <- names(df)[grepl("barg_index", names(df))]
summary(df[,bargVars])
df$barg_index <- rowMeans(df[,bargVars],na.rm=T)
check.fun('barg_index', bargVars)

#lm(barg_index~treatment*survey*farm_pastor+state, data=df)
```

# Knowledge/Awareness

Want a variable measuring respondents' awareness of conflict events.  The actual amount of conflict events for each site will be different.  How to know actual amount of conflict?  Median?  Or this just becomes a binary yes/no to conflict within the past one year.


NOTE: higher scores are BAD here for everything except "violence_when", where high values are GOOD (mean longer since violence).  Need to reverse.

```{r clash}
# want: measure of respondents' awareness of conflict events
awareVars <- names(df)[grepl("clash_group.violence$", names(df))] # just one variable now.
summary(df[,awareVars])
#lm(clash_group.violence~treatment*survey*farm_pastor+state, data=df)


# old clashVars: report more or less violence overall.
clashVars <- names(df)[grepl("clash", names(df))][-c(1:2)] # for the index, can only use things on both baseline & endline. No burned/injured.

# the "violence_when" q is coded so that high scores (13 months/1) are GOOD.  Need to reverse so that high scores are BAD.
df$clash_details_group.violence_when <- abs(df$clash_details_group.violence_when-max(df$clash_details_group.violence_when, na.rm=T)) 

# handle the countvars by making it ranks - baseline and endline separately
df[df$survey %in% 0,clashVars[c(1,2,4)]] <- sapply(df[df$survey %in% 0,clashVars[c(1,2,4)]], dense_rank)
df[df$survey %in% 0,clashVars] <- sapply(df[df$survey %in% 0,clashVars], reshape::rescaler, type="range")

##endline
df[df$survey %in% 1,clashVars[c(1,2,4)]] <- sapply(df[df$survey %in% 1,clashVars[c(1,2,4)]], dense_rank)
df[df$survey %in% 1,clashVars] <- sapply(df[df$survey %in% 1,clashVars], reshape::rescaler, type="range")
#chris: what to do with people tied at 0?
summary(df[,clashVars])


# when people are not aware of violence, other vars should be NA. Otherwise just a "vio awareness index"
#df[c(1:5, 150:155),clashVars] # correct

# when people say there was no violence, need to make the other vars 0, not NA.
df[df$clash_group.violence %in% 0, clashVars[c(1,2,4)]] <- 0

# drop 3 because it's the screening question that determines if other questions get asked
df$clash_index <- rowMeans(df[,clashVars[c(1,2,4)]],na.rm=T)
#psych::alpha(df[,clashVars[c(1,2,4)]], na.rm=T) # great index

```

"In any clash that occurred in the last year, were you or anyone in your family negatively affected by an attack caused by X group? 

Yes, my work/business was interrupted/closed
Yes, I was forced to leave my home/migrate
Yes, my property was damaged
Yes, a family member was injured
Yes, a family member was killed
"

```{r}
#violence_effect is not recoded yet
table(df$violence_effect)
df$vio1_bus <- ifelse(grepl("business", df$violence_effect), 1, 0)
df$vio2_home <- ifelse(grepl("home", df$violence_effect), 1, 0)
df$vio3_prop <- ifelse(grepl("property", df$violence_effect), 1, 0)
df$vio4_inj <- ifelse(grepl("injured", df$violence_effect), 1, 0)
df$vio5_kill <- ifelse(grepl("killed", df$violence_effect), 1, 0)
df$violence_effect_num <- rowMeans(df[,grepl("^vio[0-9]_", names(df))], na.rm=T)
vioExpVars <- names(df)[grepl("^vio[0-9]_", names(df))]
df$vioNothing <- ifelse(grepl("^no$", df$violence_effect) | is.na(df$violence_effect), 1, 0)

#table(df$vio5_kill, df$survey, df$state) # deaths go down in both states, but go down a lot more in Nassarawa.
#table(df$vio4_inj, df$survey, df$state) # injuries go down in both states, but go down a lot more in Nassarawa.
##lm(vio5_kill~treatment*survey*farm_pastor+state, data=df)
##lm(vio4_inj~treatment*survey*farm_pastor+state, data=df)
##lm(vioNothing~treatment*survey*farm_pastor+state, data=df)

# is this just because treatment people were more aware?
### yes, it was somewhat. All TR is less likely to be killed, pastoralists are less likely to be injured but farmers are more likely, and pastoralists are more likely to say "no" but farmers are more likely.
#test <- df[df$clash_group.violence %in% 1,]
##lm(vio5_kill~treatment*survey*farm_pastor+state, data=test)
##lm(vio4_inj~treatment*survey*farm_pastor+state, data=test)
##lm(vioNothing~treatment*survey*farm_pastor+state, data=test)


```


##############################
# Potential Mediators
##############################

Potential Mediators:
    - Reduced threat
    - Ingroup Expansion (superordinate identity?)
    - Potential Benefit
    - List Experiment (Intergroup Affect)

Spillover Outcomes:
    - Trust other groups (ethnic, religious).

## Threat

High numbers are BAD. Need to make them GOOD.

```{r}
# Set vars
threatVars <- names(df)[grepl("threat_group.threat", names(df))]
df[,threatVars] <- reshape::rescaler(df[,threatVars],type="range")

# Reverse code things that are not yet reversed -- all of them
df[,c(threatVars)] <- df[,threatVars]*-1

# Make Index about Psychological Threat
summary(df[,threatVars])
df$threat_index <- rowMeans(df[,threatVars],na.rm=T)
#psych::alpha(df[,threatVars]) # 0.59, not great, Jim.
```

## Ingroup Expansion

## Social Cohesion Group

Note there are multiple concepts.

- General/abstract things in sc1, and concrete/hypothetical things in sc2.
- some empathy things (next code chunk)
- some ingroup expansion things (here).

```{r}
cohesVars <- names(df)[grepl("social_cohesion_group", names(df))]
df[,cohesVars] <- reshape::rescaler(df[,cohesVars],type="range")
summary(df[,cohesVars])
df$cohes_index <- rowMeans(df[,cohesVars], na.rm=T)
#psych::alpha(df[,cohesVars]) # 0.75

# sc1 - abstract
cohesVars1 <- cohesVars[1:5]
df$cohes_index1 <- rowMeans(df[,cohesVars1], na.rm=T)
#psych::alpha(df[,cohesVars1]) # 0.77

# sc2 - concrete
cohesVars2 <- cohesVars[6:10]
df$cohes_index2 <- rowMeans(df[,cohesVars2], na.rm=T)
#psych::alpha(df[,cohesVars2]) # 0.76

# empathy (chunk below)

# expand
expandVars <- cohesVars[1:8]
df$expand_index <- rowMeans(df[,expandVars], na.rm=T)
#psych::alpha(df[expandVars]) # 0.74
```


## empathy

Empathy == (helping other group in trouble) & Perspective-taking (who is responsible for violence)

```{r}
empVars <- c("social_cohesion_group2.misfortune_x", "social_cohesion_group2.misfortune_your")
perspVars <- "threat_group.x_responsible"

df[,empVars] <- reshape::rescaler(df[,empVars],type="range")
df[,perspVars] <- reshape::rescaler(df[,perspVars],type="range")

summary(df[,empVars])
df$emp_index <- rowMeans(df[,empVars], na.rm=T)
df$persp_index <- df[,perspVars]
df$empPersp_index <- rowMeans(df[,c(empVars, perspVars)])

#alpha
#psych::alpha(df[,c(empVars, perspVars)])
```

## Potential Benefit

## Econ Benefit Group

```{r}
table(df$econ_benefit_group.benefit_econ)
beneVars <- names(df)[grepl("(econ|qip)", names(df))][-4]
df[,beneVars] <- reshape::rescaler(df[,beneVars],type="range")
summary(df[,beneVars])

# all
#table(df$econ_benefit_group.benefit_econ, df$econ_benefit_group.more_benefit, exclude=c()) # if agreed they benefit materially
#table(df$econ_benefit_group.benefit_econ, df$econ_benefit_group.more_benefit_disagree, exclude=c()) # if disagreed they benefit
df$bene_index <- rowMeans(df[,beneVars],na.rm=T)

# perceptions only
beneVarsPerc <- beneVars[1:3]
df$bene_index_perc <- rowMeans(df[,beneVarsPerc],na.rm=T)

# awareness/use only
beneVarsReal <- beneVars[4:7]
df$bene_index_real <- rowMeans(df[,beneVarsReal],na.rm=T)

# best question only
beneVar <- beneVars[1]
df$bene_index1 <- df[,beneVar]
```

## List Experiment

Failed experiment.

# Spillover Outcomes:

## Trust other groups (ethnic, religious).

Outgroup & X Group

```{r}
outVars <- names(df)[grepl("(comf|outgroup)", names(df))]
df[,outVars] <- reshape::rescaler(df[,outVars],type="range")
summary(df[,outVars])

df$out_index <- rowMeans(df[,outVars],na.rm=T)
psych::alpha(df[,outVars]) # 0.89


# X specifically
xVars <- names(df)[grepl("(comf|trust_x)", names(df))]
summary(df[,xVars])

df$x_index <- rowMeans(df[,xVars],na.rm=T)
psych::alpha(df[,xVars]) # 0.89

# other groups specifically
otherVars <- setdiff(outVars,xVars)
summary(df[,otherVars])

df$other_index <- rowMeans(df[,otherVars],na.rm=T)
psych::alpha(df[,otherVars]) # 0.89

```













**************************

# Stuff from Policy Paper

## Dispute Resolution Group

high numbers are GOOD.  fewer disputes, better dispute resolution.  Sharing resources also included here.

This one is hard.  'Resolve' is what we want, but it gives higher scores if tension/disputes are resolved peacefully.  Resolving peacefully can only happen if disputes occur, so people with no disputes score lower on this than they should.  To fix that, I am making the variables so that no disputes is equivalent to always peacefully resolved disputes.  Then making the index by putting these together for each resource (markets, farmland, pastures).  Then add in the "disputes generally resolved peacefully" var and the "disputes generally persist after attempts to resolve them" var.

If people report not sharing a resource, they get NA for dispute/resolving.  That seems right, but the "no disputes" scoring low is definitely wrong.

```{r}
# more sharing resources, fewer disputes, & better resolved disputes (this big index does not make sense. sharing farmland opens up qs about disputes.)
shareVars <- names(df)[grepl("^share_[a-z]*$", names(df))]
numDisVars <- names(df)[grepl("(dispute$|tension$)", names(df))]
resolveVars <- names(df)[grepl("(resolve[^s]|persist)", names(df))]

# if NO disputes (1=no), then give max for dispute resolution.
df$farmland_disputes_resolved <- ifelse(df$share_farmland_dispute %in% 1 & is.na(df$farmland_disputes_resolved), max(df$farmland_disputes_resolved, na.rm=T),  df$farmland_disputes_resolved)
df$pasture_disputes_resolved <- ifelse(df$share_pasture_dispute %in% 1 & is.na(df$pasture_disputes_resolved), max(df$pasture_disputes_resolved, na.rm=T),  df$pasture_disputes_resolved)
df$market_disputes_resolved <- ifelse(df$share_market_dispute %in% 1 & is.na(df$market_disputes_resolved), max(df$market_disputes_resolved, na.rm=T),  df$market_disputes_resolved)

disVars <- c(shareVars, numDisVars, resolveVars)
df[,disVars] <- reshape::rescaler(df[,disVars],type="range")
#summary(df[,disVars])
df$dis_index <- rowMeans(df[,disVars], na.rm=T)
#psych::alpha(df[,disVars]) # won't give an alpha? Something wrong with this as an index, perfect correlations.  Shared should not be a part of it.


################################################
# Individual parts of dispute resolution.
################################################

# better resolved
df$resolve_index <- rowMeans(df[,resolveVars], na.rm=T)
#summary(df[,resolveVars])
#psych::alpha(df[,resolveVars]) #0.48

# fewer disputes
df$numDis_index <- rowMeans(df[,numDisVars], na.rm=T)
#summary(df[,numDisVars])
#psych::alpha(df[,numDisVars]) #0.78

# shared resources
df$share_index <- rowMeans(df[,shareVars], na.rm=T)
#psych::alpha(df[,shareVars]) #0.39

```

### Dispute Actors

This is the section of the PAP under "dispute resolution"....though it should have been the disputes over shared resources, immediately above.

There are too many actors in this to make any sense of it.

```{r}
disActorVars <- names(df)[grepl("dispute_resolution_group", names(df))]

df[,disActorVars] <- reshape::rescaler(df[,disActorVars],type="range")
#summary(df[,disActorVars])
df$disActor_index <- rowMeans(df[,disActorVars], na.rm=T)
#psych::alpha(df[,disActorVars]) #0.82

# I don't want to code all of these.
## local gov
## rel leaders
## sec officials
## state gov
## trad leader
## women
## youth
```


***************

# Save

```{r}
save.image(file="d-additiveIndices.Rdata")

```

Next step is to separate preselected & randomly selected, aggregate randomly selected.