---
title: "f-aggregateComms"
author: "cdgrady21"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
load("d-additiveIndices.Rdata")
library(plyr)
library(dplyr)
library(estimatr)
library(psych)
```

chris: note: the "violence_effect_num" variable that is the mean of the "vio[1-9]_" variables should probably be combined into an index with ICW, not just the mean.  Same for Insecurty/Conflict.


# Functions

From Cyrus Samii for IC weighting and factor analysis.

```{r}
## from cyrus samii IC weighting

# Function to standardize columns of a matrix
# where you designate a standardization group
# (e.g., the control group in an experiment)
# with "sgroup", a logical vector.

matStand <- function(x, sgroup = rep(TRUE, nrow(x))){
  for(j in 1:ncol(x)){
    x[,j] <- (x[,j] - mean(x[sgroup,j]))/sd(x[sgroup,j]) # chris: demeans outcome, but by control group mean, not x group mean?  Then divides by control group sd, which I get.  But why demean by control group mean even for tr group members?
  }
  return(x)
}

# Function that takes in data in matrix format and returns
# (i) IC weights and (ii) ICW index.
# Weights can be incorporated using the "wgts" argument.
# The "revcols" argument takes a vector indicating which columns,
# if any, should have values reversed (that is, standardized 
# values are multiplied by -1) prior to construction of the index. 

icwIndex <- function(	xmat,
                      wgts=rep(1, nrow(xmat)),
                      revcols = NULL,
                      sgroup = rep(TRUE, nrow(xmat))){
  X <- matStand(xmat, sgroup)
  if(length(revcols)>0){
    X[,revcols] <-  -1*X[,revcols]
  }
  i.vec <- as.matrix(rep(1,ncol(xmat)))
  Sx <- cov.wt(X, wt=wgts)[[1]]
  weights <- solve(t(i.vec)%*%solve(Sx)%*%i.vec)%*%t(i.vec)%*%solve(Sx)
  index <- t(solve(t(i.vec)%*%solve(Sx)%*%i.vec)%*%t(i.vec)%*%solve(Sx)%*%t(X))
  return(list(weights = weights, index = index))
}

# Factor analysis function (R base does not have one. factanal() is MLE, which we don't want.) 
#source("http://www.stat.sc.edu/~habing/courses/530/fact.txt")
```


# Separate into baseline and endline

```{r}
# first make rand.df to mess with
rand.df <- df

# then make var to indicate control group for ICW
rand.df$control <- ifelse(rand.df$treatment == 1, 0, 1)

# want separate baseline & endline indices
rand.df1 <- rand.df[rand.df$survey %in% 0,]
rand.df2 <- rand.df[rand.df$survey %in% 1,]

# removing panel people/preselected from endline, since not randomly selected
rand.df2 <- rand.df2[!rand.df2$pre_selected %in% 'pre',]

```


# Factors

chris: not yet done.  Really hard to do because some questions designed to be NA for some respondents (comfort watching animals).  Fill with overal mean.  Other problem: diff number of factors baseline/endline?

Put every question into a factor analysis?  Put every _index into a factor analysis?

```{r, eval=F}
lambda <- fact(x,method="iter",maxfactors=1, niter=130)$loadings
sigma <- cor(x)
# This Thompson's method.
z.fac <- matStand(x)%*%solve(sigma)%*%lambda
```

R-bloggers version.

```{r, eval=F}
# Make list of all vars to include in factor
allVars <- ls()[grepl("Vars", ls(), ignore.case=FALSE)]
allVars <- paste(allVars, collapse=",")
rand.df1_f <- rand.df1[,c(allTrustVars,awareVars,bargVars,beneVarsPerc,
                          cohesVars,inVars,
                          contactVars,conVioEffVars,dispVars,
                          disVars,numDisVars,outVars,resolveVars,shareVars,
                          threatVars,vioExpVars,vioVars)]
rand.df2_f <- rand.df2[,c(allTrustVars,awareVars,bargVars,beneVarsPerc,
                          cohesVars,inVars,
                          contactVars,conVioEffVars,dispVars,
                          disVars,numDisVars,outVars,resolveVars,shareVars,
                          threatVars,vioExpVars,vioVars)]
remCols <- names(rand.df1_f)[grepl(".(1|2)", names(rand.df1_f))]
rand.df1_f[,remCols] <- NULL
rand.df2_f[,remCols] <- NULL
#which(is.na(rand.df1_f), arr.ind=TRUE)

#Replace NA with mean for column
rand.df1_f <- zoo::na.aggregate(rand.df1_f)
rand.df2_f <- zoo::na.aggregate(rand.df2_f)

#Create the correlation matrix
rand.df1_f_cor <- cor(rand.df1_f)
rand.df2_f_cor <- cor(rand.df2_f)

# Determine Number of Factors to Extract
library(nFactors)
ev1 <- eigen(rand.df1_f_cor) # get eigenvalues
ap1 <- parallel(subject=nrow(rand.df1_f),var=ncol(rand.df1_f),
  rep=100,cent=.05)
nS1 <- nScree(x=ev1$values, aparallel=ap1$eigen$qevpea)
plotnScree(nS1)

ev2 <- eigen(rand.df2_f_cor) # get eigenvalues
ap2 <- parallel(subject=nrow(rand.df2_f),var=ncol(rand.df2_f),
  rep=100,cent=.05)
nS2 <- nScree(x=ev2$values, aparallel=ap2$eigen$qevpea)
plotnScree(nS2)

#Factor analysis of the data
factors_df1 <- fa(r = rand.df1_f_cor, nfactors = 4)
factors_df2 <- fa(r = rand.df2_f_cor, nfactors = 4)

#Getting the factor loadings and model analysis
factors_df1
factors_df2
```



# Inverse Covariance Weighted Indices

Testing.

```{r, eval=F}
# cannot have any NAs.
#x <- na.omit(rand.df[,xVars])
#cor(x)
# should replace NA with mean for the column?? doing so with na.aggregate.
x <- rand.df[,xVars]
x <- zoo::na.aggregate(x)
out_cw <- icwIndex(x)
cor(x)
out_cw$weights
rand.df$x_cw <- as.vector(out_cw$index)

cor(na.omit(rand.df[,c("x_cw", "x_index")])) # super highly correlated.


# Now, only using control group for ICW
x <- rand.df[,xVars]
x <- zoo::na.aggregate(x)
out_cw <- icwIndex(xmat=x, sgroup=as.logical(rand.df[,'control']))
cor(x)
out_cw$weights
rand.df$x_cw <- as.vector(out_cw$index)

cor(na.omit(rand.df[,c("x_cw", "x_index")])) # super highly correlated.
```

Functions

```{r}
# both tr and co
ic.fun1 <- function(vars, thedf)
{
  x <- thedf[,vars]
  x <- zoo::na.aggregate(x)
  out_cw <- icwIndex(x)
  print(cor(x))
  print(out_cw$weights)
  return(as.vector(out_cw$index))
}


# just co
ic.fun <- function(vars, thedf)
{
  x <- thedf[,vars]
  x <- zoo::na.aggregate(x)
  out_cw <- icwIndex(xmat=x, sgroup=as.logical(thedf[,'control']))
  print(cor(x))
  print(out_cw$weights)
  return(as.vector(out_cw$index))
}
```

Doing.

```{r}
# should loop but feeling braindead
# Baseline
rand.df1$trust_cw <- ic.fun(trustVars, rand.df1)
rand.df1$dist_cw <- ic.fun(distVars, rand.df1)
rand.df1$allTrust_cw <- ic.fun(allTrustVars, rand.df1)
rand.df1$x_cw <- ic.fun(xVars, rand.df1)
rand.df1$out_cw <- ic.fun(outVars, rand.df1)
rand.df1$other_cw <- ic.fun(otherVars, rand.df1)
#rand.df1$aware_cw <- ic.fun(awareVars, rand.df1) # just one variable
rand.df1$clash_cw <- ic.fun(clashVars, rand.df1)
rand.df1$contact_cw <- ic.fun(contactVars, rand.df1)
rand.df1$contactOnly_cw <- ic.fun(contactVars[c(1:4,7)], rand.df1)
rand.df1$contactOnly_cats_cw <- ic.fun(paste0(contactVars[c(1:4,7)], "_cats"), rand.df1)
rand.df1$bene_cw <- ic.fun(beneVarsPerc, rand.df1)
rand.df1$threat_cw <- ic.fun(threatVars, rand.df1)
rand.df1$in_cw <- ic.fun(inVars, rand.df1)
rand.df1$cohes_cw <- ic.fun(cohesVars, rand.df1)
rand.df1$cohes1_cw <- ic.fun(cohesVars1, rand.df1)
rand.df1$cohes2_cw <- ic.fun(cohesVars2, rand.df1)
rand.df1$dis_cw <- ic.fun(disVars, rand.df1)
rand.df1$share_cw <- ic.fun(shareVars, rand.df1)
rand.df1$numDis_cw <- ic.fun(numDisVars, rand.df1)
rand.df1$resolve_cw <- ic.fun(resolveVars, rand.df1)
rand.df1$barg_cw <- ic.fun(bargVars, rand.df1)
rand.df1$disActor_cw <- ic.fun(disActorVars, rand.df1)
rand.df1$vio_cw <- ic.fun(vioVars, rand.df1)
rand.df1$vioExp_cw <- ic.fun(vioExpVars, rand.df1)
rand.df1$persp_cw <- rand.df1$persp_index
rand.df1$emp_cw <- ic.fun(empVars, rand.df1)
rand.df1$expand_cw <- ic.fun(expandVars, rand.df1)

# Endline
rand.df2$trust_cw <- ic.fun(trustVars, rand.df2)
rand.df2$dist_cw <- ic.fun(distVars, rand.df2)
rand.df2$allTrust_cw <- ic.fun(allTrustVars, rand.df2)
rand.df2$x_cw <- ic.fun(xVars, rand.df2)
rand.df2$out_cw <- ic.fun(outVars, rand.df2)
rand.df2$other_cw <- ic.fun(otherVars, rand.df2)
#rand.df2$aware_cw <- ic.fun(awareVars, rand.df2) # only one var
rand.df2$clash_cw <- ic.fun(clashVars, rand.df2)
rand.df2$contact_cw <- ic.fun(contactVars, rand.df2)
rand.df2$contactOnly_cw <- ic.fun(contactVars[c(1:4,7)], rand.df2)
rand.df2$contactOnly_cats_cw <- ic.fun(paste0(contactVars[c(1:4,7)], "_cats"), rand.df2)
rand.df2$bene_cw <- ic.fun(beneVarsPerc, rand.df2)
rand.df2$threat_cw <- ic.fun(threatVars, rand.df2)
rand.df2$in_cw <- ic.fun(inVars, rand.df2)
rand.df2$cohes_cw <- ic.fun(cohesVars, rand.df2)
rand.df2$cohes1_cw <- ic.fun(cohesVars1, rand.df2)
rand.df2$cohes2_cw <- ic.fun(cohesVars2, rand.df2)
rand.df2$dis_cw <- ic.fun(disVars, rand.df2)
rand.df2$share_cw <- ic.fun(shareVars, rand.df2)
rand.df2$numDis_cw <- ic.fun(numDisVars, rand.df2)
rand.df2$resolve_cw <- ic.fun(resolveVars, rand.df2)
rand.df2$barg_cw <- ic.fun(bargVars, rand.df2)
rand.df2$disActor_cw <- ic.fun(disActorVars, rand.df2)
rand.df2$vio_cw <- ic.fun(vioVars, rand.df2)
rand.df2$vioExp_cw <- ic.fun(vioExpVars, rand.df2)
rand.df2$persp_cw <- rand.df2$persp_index
rand.df2$emp_cw <- ic.fun(empVars, rand.df2)
rand.df2$expand_cw <- ic.fun(expandVars, rand.df2)

# Now scale as 0-1 so that we can easily discuss them as % increase/decrease for MC report. # not necessary until aggregated.
#icVars <- names(rand.df1)[grepl("_cw", names(rand.df1))]
#rand.df1[,icVars] <- reshape::rescaler(rand.df1[,icVars],type="range")
#rand.df2[,icVars] <- reshape::rescaler(rand.df2[,icVars],type="range")

# rebind
rand.df <- rbind(rand.df1, rand.df2)
```


# Rand Experiment

Needs to be done before aggregating.  Done in e-makeIndices_ap.Rmd file.



# Save

```{r}
save(rand.df, file="rand_df.Rdata")

```


