---
title: "f2-panelPpl"
author: "Christopher Grady"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
load("d-additiveIndices.Rdata")
id <- read.csv("identified_preSurvey.csv") # must be matched by name with the new "pre" data
load('preselected_list.Rda')
library(estimatr)
```

<!--Chris note: Initially I did the IC weighting on the pre.df by itself and the merge.df by itself.  But this meant the weights were calculated for panel people alone at endline, but for all baseline people.  Now I am making a df of ONLY panel people at baseline and endline.  Then doing the IC weighting on that dataset with the same people for two diff time points.  Different weights at different time points, only using panel people to calc those weights. -->

# Make Panel df by match preselected people from baseline to endline

First (1) remove random ppl from endline df for a list of preselected at endline and (2) remove endline people from big df for a list of possible matches at baseline.

Note: "id$z$" is for assigned as full participants (1) and partial participants (2).  "id$full$" is 1 for assigned as full, 0 otherwise.  id$part$ is same but for partial participants.

```{r}
pre.df <- df[df$pre_selected %in% 'pre',]
stopifnot(setdiff(pre.df$id_num, pre$ID.Number)==2004) # should only be missing 2004, since that was a comm_leader

# fix part variable in id
id$part[id$part %in% 0] <- 1
id$part[is.na(id$part)] <- 0
id$name <- trimws(tolower(id$name))


merge.df <- df[df$survey %in% 0,]
```

Merge respondents information from pre and id into pre.df (endline responses)

```{r}
# first get info from pre and id files
pre.df <- merge(pre.df, pre[,c("baseName", 'ID.Number')], by.x="id_num", by.y="ID.Number") # this should drop id_num 2004
id <- id[!(id$name %in% "james iortyom" & id$gender %in% "female"),] # need to drop the female james iortyom from id
pre.df <- merge(pre.df, id[,c("name", "z", "part", "full")], by.x="baseName", by.y="name", all.x=TRUE)


#Check that people who were on project committees were supposed to be part of the project committees.
table(pre.df$committee_group.committee, pre.df$full, exclude=c()) # err, the ID list was really not accurate?
table(pre.df$forum_group.forum, pre.df$part, exclude=c()) # ID list not even close

table(pre.df$z, pre.df$committee_group.committee, exclude=c()) # 1 means supposed to do committee, 2 means supposed to do forum
table(pre.df$z, pre.df$forum_group.forum, exclude=c()) # 1 means supposed to do committee, 2 means supposed to do forum

# if "yes" to anything, yes.
pre.df$forum <- ifelse(pre.df$forum_group.forum %in% 1 | pre.df$part %in% 1, 1, 0)
pre.df$committee <- ifelse(pre.df$committee_group.committee %in% 1 | pre.df$full %in% 1, 1, 0)
```

Connect endline (pre.df) to baseline people (merge.df)

```{r}
# by baseline name
merge.df$name.1 <- trimws(tolower(merge.df$name.1))
#setdiff(names(pre.df),names(df))

# make baseline colnames _y0 and endline colnames _y1
pre.df$name.1 <- NULL
newNames <- names(pre.df)[names(pre.df) %in% names(merge.df)]
newNames2 <- names(merge.df)[names(merge.df) %in% names(pre.df)] # need to do it for merge.df also so they in right order
names(pre.df)[names(pre.df) %in% newNames] <- paste0(newNames, "_y1")
names(merge.df)[names(merge.df) %in% newNames2] <- paste0(newNames2, "_y0")

# merge only within community
merge.df$merger <- paste0(merge.df$name.1, "-", merge.df$psu_y0)
pre.df$merger <- paste0(pre.df$baseName, "-", pre.df$psu_y1)

panel.df <- merge(merge.df, pre.df, by.x="merger", by.y="merger") 

# remove obs when people had same name at baseline.  we cannot be sure which person from baseline we surveyed
#sort(table(panel.df$merger))
panel.df <- panel.df[!(panel.df$merger %in% "james iortyom-21" & panel.df$gender_y0 %in% "female"),]# we know we only have the male james iortyom, but merging merged both the baseline female and the baseline male with the endline male
panel.df <- panel.df[!(panel.df$merger %in% "aishatu ibrahim-5" | panel.df$merger %in% "hadiza abu-22" | panel.df$merger %in% "mohammed sani-35"),]
stopifnot(max(table(panel.df$merger))==1)
rm(merge.df); rm(pre.df); rm(pre); rm(id)
```

Make control indicator for ICW weighting

```{r}
panel.df$control <- ifelse(panel.df$treatment_y0 == 1, 0,1)

```



# Inverse Covariance Weighted Indices, Factors

### Functions

From Cyrus Samii for IC weighting and factor analysis.

```{r}
load(file="index_fun.Rda")
```


Make the set of vars at baseline and set of vars at endline.

<!-- Chris note: probably could have separated panel.df into baseline and endline, then calc'd ICW indices, then recombined.  Not sure if that's easier.-->

```{r}
# gotta be a better way to do this than going individually...think I am close with varList and the do.call function, but not getting it.
varList <- ls(pattern="Vars")
thing1 <- do.call("list",mget(varList))

#for(i in 1:length(varList)){
#  paste0(varList[i], "_y0") <- c(paste0(thing1[[varList[i]]], "_y0"))
#}
#paste0(varList[[1]], "_y0") <- paste0(thing1[[varList[1]]], "_y0")

# crappy way below in testing since I abandoned the good way for time

```

Testing.

```{r, eval=F}

# cannot have any NAs.
#x <- na.omit(panel.df[,xVars])
#cor(x)
# should replace NA with mean for the column.
x <- panel.df[,paste0(xVars, "_y0")]
x <- zoo::na.aggregate(x)
out_cw <- icwIndex(x)
cor(x)
out_cw$weights
panel.df$x_cw_y0 <- as.vector(out_cw$index)

cor(na.omit(panel.df[,c("x_cw_y0", "x_index_y0")])) # super highly correlated.


# Control group only
x <- panel.df[,paste0(xVars, "_y0")]
x <- zoo::na.aggregate(x)
out_cw <- icwIndex(xmat=x, sgroup=as.logical(panel.df[,'control']))
cor(x)
out_cw$weights
panel.df$x_cw_y0 <- as.vector(out_cw$index)

cor(na.omit(panel.df[,c("x_cw_y0", "x_index_y0")])) # super highly correlated.


```

Functions.

```{r}
# both tr and co
ic.fun1 <- function(vars,thedf)
{
  x <- thedf[,vars]
  x <- zoo::na.aggregate(x)
  out_cw <- icwIndex(x)
  print(cor(x))
  print(out_cw$weights)
  return(as.vector(out_cw$index))
}

# control only
ic.fun <- function(vars,thedf)
{
  x <- thedf[,vars]
  x <- zoo::na.aggregate(x)
  out_cw <- icwIndex(xmat=x, sgroup=as.logical(thedf[,'control']))
  print(cor(x))
  print(out_cw$weights)
  return(as.vector(out_cw$index))
}

```

Doing.

```{r}
# outcomes at baseline -- should loop but feeling braindead
panel.df$trust_cw_y0 <- ic.fun(vars=paste0(trustVars, "_y0"),thedf=panel.df)
panel.df$dist_cw_y0 <- ic.fun(vars=paste0(distVars, "_y0"),thedf=panel.df) # dist
panel.df$attitude_cw_y0 <- ic.fun(vars=paste0(attitudeVars, "_y0"),thedf=panel.df) # allTrust
panel.df$other_cw_y0 <- ic.fun(vars=paste0(otherVars, "_y0"),thedf=panel.df) # others
panel.df$threat_cw_y0 <- ic.fun(vars=paste0(threatVars, "_y0"),thedf=panel.df) #threat
panel.df$in_cw_y0 <- ic.fun(vars=paste0(inVars, "_y0"),thedf=panel.df) # in
panel.df$barg_cw_y0 <- ic.fun(vars=paste0(bargVars, "_y0"),thedf=panel.df) # bargain
panel.df$vioExp_cw_y0 <- ic.fun(vars=paste0(vioExpVars, "_y0"),thedf=panel.df) # vioExp
panel.df$persp_cw_y0 <- panel.df$persp_index_y0
panel.df$emp_cw_y0 <- ic.fun(vars=paste0(empVars, "_y0"), thedf=panel.df)
panel.df$expand_cw_y0 <- ic.fun(vars=paste0(expandVars, "_y0"), thedf=panel.df)

panel.df$x_cw_y0 <- ic.fun(vars=paste0(xVars, "_y0"),thedf=panel.df)
panel.df$out_cw_y0 <- ic.fun(vars=paste0(outVars, "_y0"),thedf=panel.df)
panel.df$clash_cw_y0 <- ic.fun(vars=paste0(clashVars[c(1,2,4)], "_y0"),thedf=panel.df)
panel.df$contact_cw_y0 <- ic.fun(vars=paste0(contactVars, "_y0"),thedf=panel.df)
panel.df$contactOnly_cw_y0 <- ic.fun(vars=paste0(contactVars[c(1:4,7)], "_y0"),thedf=panel.df)
panel.df$contactOnly_cats_cw_y0 <- ic.fun(vars=paste0(contactVars[c(1:4,7)], "_cats_y0"),thedf=panel.df)
panel.df$contactOnly_raw_cw_y0 <- ic.fun(vars=paste0(contactVars[c(1:4,7)], "_raw_y0"),thedf=panel.df)

panel.df$bene_cw_y0 <- ic.fun(vars=paste0(beneVarsPerc, "_y0"),thedf=panel.df)
panel.df$cohes_cw_y0 <- ic.fun(vars=paste0(cohesVars, "_y0"),thedf=panel.df)
panel.df$cohes1_cw_y0 <- ic.fun(vars=paste0(cohesVars1, "_y0"),thedf=panel.df)
panel.df$cohes2_cw_y0 <- ic.fun(vars=paste0(cohesVars2, "_y0"),thedf=panel.df)
panel.df$dis_cw_y0 <- ic.fun(vars=paste0(disVars, "_y0"),thedf=panel.df)
panel.df$share_cw_y0 <- ic.fun(vars=paste0(shareVars, "_y0"),thedf=panel.df)
panel.df$numDis_cw_y0 <- ic.fun(vars=paste0(numDisVars, "_y0"),thedf=panel.df)
panel.df$resolve_cw_y0 <- ic.fun(vars=paste0(resolveVars, "_y0"),thedf=panel.df)
panel.df$disActor_cw_y0 <- ic.fun(vars=paste0(disActorVars, "_y0"),thedf=panel.df)
panel.df$vio_cw_y0 <- ic.fun(vars=paste0(vioVars, "_y0"),thedf=panel.df)

# outcomes at endline
panel.df$trust_cw_y1 <- ic.fun(vars=paste0(trustVars, "_y1"),thedf=panel.df)
panel.df$dist_cw_y1 <- ic.fun(vars=paste0(distVars, "_y1"),thedf=panel.df) # dist
panel.df$attitude_cw_y1 <- ic.fun(vars=paste0(attitudeVars, "_y1"),thedf=panel.df) # allTrust
panel.df$other_cw_y1 <- ic.fun(vars=paste0(otherVars, "_y1"),thedf=panel.df) # others
panel.df$threat_cw_y1 <- ic.fun(vars=paste0(threatVars, "_y1"),thedf=panel.df) #threat
panel.df$in_cw_y1 <- ic.fun(vars=paste0(inVars, "_y1"),thedf=panel.df) # in
panel.df$barg_cw_y1 <- ic.fun(vars=paste0(bargVars, "_y1"),thedf=panel.df) # bargain
panel.df$vioExp_cw_y1 <- ic.fun(vars=paste0(vioExpVars, "_y1"),thedf=panel.df) # vioExp
panel.df$persp_cw_y1 <- panel.df$persp_index_y1
panel.df$emp_cw_y1 <- ic.fun(vars=paste0(empVars, "_y1"), thedf=panel.df)
panel.df$expand_cw_y1 <- ic.fun(vars=paste0(expandVars, "_y1"), thedf=panel.df)

panel.df$x_cw_y1 <- ic.fun(vars=paste0(xVars, "_y1"),thedf=panel.df)
panel.df$out_cw_y1 <- ic.fun(vars=paste0(outVars, "_y1"),thedf=panel.df)
panel.df$clash_cw_y1 <- ic.fun(vars=paste0(clashVars[c(1,2,4)], "_y1"),thedf=panel.df)
panel.df$contact_cw_y1 <- ic.fun(vars=paste0(contactVars, "_y1"),thedf=panel.df)
panel.df$contactOnly_cw_y1 <- ic.fun(vars=paste0(contactVars[c(1:4,7)], "_y1"),thedf=panel.df)
panel.df$contactOnly_cats_cw_y1 <- ic.fun(vars=paste0(contactVars[c(1:4,7)], "_cats_y1"),thedf=panel.df)
panel.df$contactOnly_raw_cw_y1 <- ic.fun(vars=paste0(contactVars[c(1:4,7)], "_raw_y1"),thedf=panel.df)

panel.df$bene_cw_y1 <- ic.fun(vars=paste0(beneVarsPerc, "_y1"),thedf=panel.df)
panel.df$cohes_cw_y1 <- ic.fun(vars=paste0(cohesVars, "_y1"),thedf=panel.df)
panel.df$cohes1_cw_y1 <- ic.fun(vars=paste0(cohesVars1, "_y1"),thedf=panel.df)
panel.df$cohes2_cw_y1 <- ic.fun(vars=paste0(cohesVars2, "_y1"),thedf=panel.df)
panel.df$dis_cw_y1 <- ic.fun(vars=paste0(disVars, "_y1"),thedf=panel.df)
panel.df$share_cw_y1 <- ic.fun(vars=paste0(shareVars, "_y1"),thedf=panel.df)
panel.df$numDis_cw_y1 <- ic.fun(vars=paste0(numDisVars, "_y1"),thedf=panel.df)
panel.df$resolve_cw_y1 <- ic.fun(vars=paste0(resolveVars, "_y1"),thedf=panel.df)
panel.df$disActor_cw_y1 <- ic.fun(vars=paste0(disActorVars, "_y1"),thedf=panel.df)
panel.df$vio_cw_y1 <- ic.fun(vars=paste0(vioVars, "_y1"),thedf=panel.df)


# Now scale as 0-1 so that we can easily discuss them as % increase/decrease for MC report.
## Also makes them comparable (without rescale, high score at endline would look much higher than high score at baseline, or vice versa).
icVars <- names(panel.df)[grepl("_cw", names(panel.df))]
panel.df[,icVars] <- reshape::rescaler(panel.df[,icVars],type="range")

# cor(na.omit(panel.df[,c("resolve_cw", "resolve_index")])) # 0.84 correlated.
```

***********

# Make DiD outcomes

panel.df$var_y1 - panel.df$var_y0

```{r}
# Try to remove _y1 and _y0 from things that are only needed once
panel.df$psu <- as.factor(as.character(panel.df$psu_y1))
panel.df$state <- as.factor(as.character(panel.df$state_y1))
panel.df$community <- as.factor(as.character(panel.df$community_y1))
panel.df$treatment <- as.factor(as.character(panel.df$treatment_y1))
panel.df$id_num <- as.factor(as.character(panel.df$id_num_y1))
panel.df$farm_pastor <- as.factor(as.character(panel.df$farm_pastor_y1))
panel.df$qip_aware <- panel.df$qip_aware_y1
panel.df$qip_ben <- panel.df$qip_ben_y1
panel.df$qip_group.borehole_use <- panel.df$qip_group.borehole_use_y1
panel.df$qip_group.borehole_aware <- panel.df$qip_group.borehole_aware_y1
panel.df[, grepl("(psu|state|community|treatment|id_num|farm_pastor|qip_ben|qip_aware|qip_group.borehole_use|qip_group.borehole_aware)_(y0|y1)", names(panel.df))] <- NULL


# make things numeric because R thinks age is a character
#thing <- sapply(panel.df[,grepl("(_y0|_y1)", names(panel.df))], class)
#thing[thing=="factor"]; thing[thing=="character"]
needNum <- c("age_y0", "age_y1")
panel.df[,needNum] <- sapply(panel.df[,needNum], as.numeric)

thing <- sapply(panel.df[,grepl("_y1", names(panel.df))], class)
newY1 <- names(thing)[thing=="numeric"]
thing0 <- sapply(panel.df[,grepl("_y0", names(panel.df))], class)
newY0 <- names(thing0)[thing0=="numeric"]

panel.df[,sub("_y1$", "", newY1)] <- panel.df[,newY1] - panel.df[,newY0]

# test that worked right
panel.df$test <- panel.df$cohes_index_y1 - panel.df$cohes_index_y0
stopifnot(panel.df$test==panel.df$cohes_index)
panel.df$test <- NULL

# pgp is only at endline, so remove pgp base vars
panel.df[,names(panel.df)[grepl("(pgp_.*_y0|pgp_[[:alpha:]]*$)", names(panel.df))]] <- NULL 


```


## Survey Exps (Added later 8-23-2018 when I realized these could maybe be analyzed in panel.df)

Haven't quite figured out how to analyze this in a way that makes sense.

The Survey Exps are Special.

could do svy experiments by grouping co, nonpart, and participants together and looking at the: (1) average change from 3-4 items on the list, (2) change in correlation between % outgroup and "yes" answers on rand exp, and (3) change in the support decrease in the endorsement exp.

### List Exp

Remember, list experiment is still coded with high numbers being BAD.

We want the average change going 3-4 item for each experimental group in 2015 compared to the average change going 3-4 item of each group in 2018.  What is the "treatment effect" in 2015, and it is smaller in 2018?  Is it smaller for participant group than for control group?

Need new variable that just says "list_exp_y0" with their score at baseline, and a variable that says "list_exp_cond_y0" for their condition at baseline.  Predict score with condition.

```{r}
#table(panel.df$list_exp1a); table(panel.df$list_exp1b) # can ignore these, since these are individual level change among people who were asked the same experimental condition.

panel.df$list_outcome_y0 <- rowSums(panel.df[,grepl("list_exp1[a-z]_y0$", names(panel.df))], na.rm=T)
panel.df$list_outcome_y1 <- rowSums(panel.df[,grepl("list_exp1[a-z]_y1$", names(panel.df))], na.rm=T)
panel.df$list_condition_y0 <- ifelse(!is.na(panel.df$list_exp1a_y0), 0, 
                                     ifelse(!is.na(panel.df$list_exp1b_y0), 1, NA))
panel.df$list_condition_y1 <- ifelse(!is.na(panel.df$list_exp1a_y1), 0, 
                                     ifelse(!is.na(panel.df$list_exp1b_y1), 1, NA))

# Negative effect like in ag.df?
mosaic::mean(panel.df$list_exp1a_y0, na.rm=T)
mosaic::mean(panel.df$list_exp1b_y0, na.rm=T)
summary(mosaic::mean(panel.df$list_exp1b_y0~panel.df$community, na.rm=T) - mosaic::mean(panel.df$list_exp1a_y0~panel.df$community, na.rm=T))
mosaic::mean(panel.df$list_exp1a_y0~panel.df$treatment, na.rm=T)
mosaic::mean(panel.df$list_exp1b_y0~panel.df$treatment, na.rm=T)


mosaic::mean(panel.df$list_exp1a_y1, na.rm=T)
mosaic::mean(panel.df$list_exp1b_y1, na.rm=T)
summary(mosaic::mean(panel.df$list_exp1b_y1~panel.df$community, na.rm=T) - mosaic::mean(panel.df$list_exp1a_y1~panel.df$community, na.rm=T))
mosaic::mean(panel.df$list_exp1a_y1~panel.df$treatment, na.rm=T)
mosaic::mean(panel.df$list_exp1b_y1~panel.df$treatment, na.rm=T)

# Quick look -- in both surveys the treatment group was less affected by an additional item.  No effect here.
#estimatr::lm_robust(list_outcome_y0~list_condition_y0*treatment, data=panel.df, clusters=community)
#estimatr::lm_robust(list_outcome_y1~list_condition_y1*treatment, data=panel.df)

```


### Rand Experiment

We mainly want to look at average change from baseline to endline.

We also want to look at the change in correlation between % outgroup and "yes" answers.

```{r}
panel.df$rand_outcomeA_y0 <- rowSums(panel.df[,grepl("rand_exp[0-9]a_y0$", names(panel.df))], na.rm=T)
panel.df$rand_outcomeA_y1 <- rowSums(panel.df[,grepl("rand_exp[0-9]a_y1$", names(panel.df))], na.rm=T)

panel.df$rand_outcomeB_y0 <- rowSums(panel.df[,grepl("rand_exp[0-9]b_y0$", names(panel.df))], na.rm=T)
panel.df$rand_outcomeB_y1 <- rowSums(panel.df[,grepl("rand_exp[0-9]b_y1$", names(panel.df))], na.rm=T)

panel.df$rand_condition_y0 <- ifelse(!is.na(panel.df$group5p.rand_exp1a_y0), 5, 
                                     ifelse(!is.na(panel.df$group25p.rand_exp2a_y0), 25,
                                            ifelse(!is.na(panel.df$group50p.rand_exp3a_y0), 50,
                                                   ifelse(!is.na(panel.df$group75p.rand_exp4a_y0), 75, NA))))
panel.df$rand_condition_y1 <- ifelse(!is.na(panel.df$group5p.rand_exp1a_y1), 5, 
                                     ifelse(!is.na(panel.df$group25p.rand_exp2a_y1), 25,
                                            ifelse(!is.na(panel.df$group50p.rand_exp3a_y1), 50,
                                                   ifelse(!is.na(panel.df$group75p.rand_exp4a_y1), 75, NA))))

# make an average rand_outcome for "join group" and "live in community"
panel.df$rand_outcome_y0 <- rowMeans(panel.df[,grepl("rand_outcome[A-B]_y0$", names(panel.df))], na.rm=T)
panel.df$rand_outcome_y1 <- rowMeans(panel.df[,grepl("rand_outcome[A-B]_y1$", names(panel.df))], na.rm=T)

panel.df[,c("rand_outcomeA_y0", "rand_outcomeB_y0", "rand_outcomeA_y1", "rand_outcomeB_y1")] <- NULL

# describe relationship -- average prop "yes" at each %outgroup
mosaic::mean(panel.df$rand_outcome_y0~panel.df$treatment, na.rm=T)
mosaic::mean(panel.df$rand_outcome_y0~panel.df$committee, na.rm=T)# no diff by participant/nonpart at baseline
mosaic::mean(panel.df$rand_outcome_y1~panel.df$treatment, na.rm=T)
mosaic::mean(panel.df$rand_outcome_y1~panel.df$committee, na.rm=T)# big diff by part/nonpart at endline
### not due to systematic diffs in condition
mosaic::mean(panel.df$rand_condition_y0~panel.df$treatment, na.rm=T)
mosaic::mean(panel.df$rand_condition_y1~panel.df$treatment, na.rm=T)


# Quick look -- % outgroup actually has no effect on the treatment group at y1, but it does at y0!  AND their baseline is higher.
#estimatr::lm_robust(rand_outcome_y0 ~ rand_condition_y0*treatment, panel.df)
#estimatr::lm_robust(rand_outcome_y1 ~ rand_condition_y1*treatment, panel.df)

```


### Endorsement Exp

We want to look at the change in the "support decrease" when the outgroup endorses the policy.

outcome_y1 will be each respondent's response at endline.  outcome_y0 will be each respondent's response at baseline.

condition_y1 will be 0 (generic) or 1 (endorse) at endline.  condition_y0 will be 

lm(outcome)

```{r}
# get one column that has their outcome/response
panel.df$end_outcome_y0 <- rowSums(panel.df[,grepl("end_exp1[a-z]_y0$", names(panel.df))], na.rm=T)
panel.df$end_outcome_y1 <- rowSums(panel.df[,grepl("end_exp1[a-z]_y1$", names(panel.df))], na.rm=T)

# condition at baseline: 1c is generic, 1a is pastoralists TR, 1b is farmers TR.
panel.df$end_condition_y0 <- ifelse(!is.na(panel.df$end_exp1a_y0), 1, 
                                     ifelse(!is.na(panel.df$end_exp1b_y0), 1, 
                                            ifelse(!is.na(panel.df$end_exp1c_y0), 0, NA)))
panel.df$end_condition_y1 <- ifelse(!is.na(panel.df$end_exp1a_y1), 1, 
                                     ifelse(!is.na(panel.df$end_exp1b_y1), 1, 
                                            ifelse(!is.na(panel.df$end_exp1c_y1), 0, NA)))

```

```{r, eval=F}
# Quick look -- endorsement affects treatment more at baseline, less at endline.  Possible negative effect?
estimatr::lm_robust(end_outcome_y0~end_condition_y0*treatment+state, data=panel.df)
estimatr::lm_robust(end_outcome_y1~end_condition_y1*treatment+state, data=panel.df)

estimatr::lm_robust(end_outcome_y0~end_condition_y0*treatment+state, data=panel.df, subset = panel.df$farm_pastor %in% "farmers")
estimatr::lm_robust(end_outcome_y1~end_condition_y1*treatment+state, data=panel.df, subset = panel.df$farm_pastor %in% "pastoralists")


# Farmers
# this shows that farmers in treatment were more affected by outgroup endorsement than farmers in control, at y0
mean(panel.df[panel.df$treatment %in% 0 & panel.df$farm_pastor %in% 'farmers' & panel.df$end_condition_y0 %in% 0 ,'end_outcome_y0'])
mean(panel.df[panel.df$treatment %in% 0 & panel.df$farm_pastor %in% 'farmers' & panel.df$end_condition_y0 %in% 1 ,'end_outcome_y0'])
mean(panel.df[panel.df$treatment %in% 1 & panel.df$farm_pastor %in% 'farmers' & panel.df$end_condition_y0 %in% 0 ,'end_outcome_y0'])
mean(panel.df[panel.df$treatment %in% 1 & panel.df$farm_pastor %in% 'farmers' & panel.df$end_condition_y0 %in% 1 ,'end_outcome_y0'])

# farmers in control and treatment were VERY affected by the endorsement at y1.  So, sort of a treatment effect by maintaining y0 in tr.
mean(panel.df[panel.df$treatment %in% 0 & panel.df$farm_pastor %in% 'farmers' & panel.df$end_condition_y1 %in% 0 ,'end_outcome_y1'])
mean(panel.df[panel.df$treatment %in% 0 & panel.df$farm_pastor %in% 'farmers' & panel.df$end_condition_y1 %in% 1 ,'end_outcome_y1'])
mean(panel.df[panel.df$treatment %in% 1 & panel.df$farm_pastor %in% 'farmers' & panel.df$end_condition_y1 %in% 0 ,'end_outcome_y1'])
mean(panel.df[panel.df$treatment %in% 1 & panel.df$farm_pastor %in% 'farmers' & panel.df$end_condition_y1 %in% 1 ,'end_outcome_y1'])

# Pastoralists
# this shows that pastoralists in treatment were slightly less affected by outgroup endorsement than pastoralists in control, at y0
mean(panel.df[panel.df$treatment %in% 0 & panel.df$farm_pastor %in% 'pastoralists' & panel.df$end_condition_y0 %in% 0 ,'end_outcome_y0'])
mean(panel.df[panel.df$treatment %in% 0 & panel.df$farm_pastor %in% 'pastoralists' & panel.df$end_condition_y0 %in% 1 ,'end_outcome_y0'])
mean(panel.df[panel.df$treatment %in% 1 & panel.df$farm_pastor %in% 'pastoralists' & panel.df$end_condition_y0 %in% 0 ,'end_outcome_y0'])
mean(panel.df[panel.df$treatment %in% 1 & panel.df$farm_pastor %in% 'pastoralists' & panel.df$end_condition_y0 %in% 1 ,'end_outcome_y0'])

# pastoralists in control and treatment were equally unaffected by the endorsement at y1.  So, no tr effect.
mean(panel.df[panel.df$treatment %in% 0 & panel.df$farm_pastor %in% 'pastoralists' & panel.df$end_condition_y1 %in% 0 ,'end_outcome_y1'])
mean(panel.df[panel.df$treatment %in% 0 & panel.df$farm_pastor %in% 'pastoralists' & panel.df$end_condition_y1 %in% 1 ,'end_outcome_y1'])
mean(panel.df[panel.df$treatment %in% 1 & panel.df$farm_pastor %in% 'pastoralists' & panel.df$end_condition_y1 %in% 0 ,'end_outcome_y1'])
mean(panel.df[panel.df$treatment %in% 1 & panel.df$farm_pastor %in% 'pastoralists' & panel.df$end_condition_y1 %in% 1 ,'end_outcome_y1'])

```




# Covariance adjustment

Predict each individual's _change_ on outcomes with their demographic characteristics.  <!-- For things that change, like age, education, income, etc...predict with endline measure? -->

### Testing

residualize and then mean-deviate by state block?

```{r, eval=F}

# need to loop a covar adjustment over all the outcome variables.
#occupation_y1/0, religion_y1/0 = too correlated with farm_pastor community.
# should I use all of these, like survey duration enumerator?
# should I use the values at y0 and y1 as well as the change in those values 
## add residual as a column in the df
covars <- c('age_y1', 'ethnic2_y1', 'radio_y0', 'radio_y1',
            'gender_y1', 'income_month_y0', 'income_month_y1',
            'username_y0', 'username_y1', 'duration_y0', 'duration_y1'
            )

#tr resid
panel.df$treatment <- as.numeric(as.character(panel.df$treatment))
tr_fmla<-reformulate(covars, response='treatment')
tr.lm <- lm(tr_fmla,panel.df) # with other controls

lm.tr_resid<-resid(tr.lm)
panel.df[names(lm.tr_resid),"tr_resid"]<-lm.tr_resid
stopifnot(panel.df[8,"tr_resid"]==lm.tr_resid["8"])

# x_index resid
x_fmla<-reformulate(covars, response='x_index')
x.lm <- lm(x_fmla,panel.df) # with other controls

lm.x_index_resid<-resid(x.lm)
panel.df[names(lm.x_index_resid),"x_index_resid"]<-lm.x_index_resid
stopifnot(panel.df[8,"x_index_resid"]==lm.x_index_resid["8"])



# check
##non adjusted
lm_robust(x_index~treatment, data=panel.df, clusters=community)

# as controls
new_fmla <- reformulate(c('treatment', covars), response="x_index")
(lm.con <- lm_robust(new_fmla, data=panel.df, clusters=community))
test1 <- lm.con$coefficients['treatment']

#covar adjusted
(lm.adj <- lm_robust(x_index_resid~tr_resid, data=panel.df, clusters=community))
test2 <- lm.adj$coefficients['tr_resid']
stopifnot(round(test1,8)==round(test2,8)) # R's weird rounding

# mean-deviate by state
# ave is buggy and gives all NA
#panel.df$x_index_residMD<- panel.df$x_index_resid - stats::ave(panel.df$x_index_resid,panel.df$state, na.rm=TRUE)

# dplyr
test <- panel.df %>%
  dplyr::group_by(state) %>%
  mutate(x_index_resid_MD = x_index_resid - mean(x_index_resid, na.rm=T),
         tr_resid_MD = tr_resid - mean(tr_resid, na.rm=T)) %>%
  as.data.frame(ungroup(.))

# with state as covar
lm_robust(x_index_resid~tr_resid + state, data=test, clusters=community)

# state MD
lm_robust(x_index_resid_MD~tr_resid_MD, data=test, clusters=community)


##########################################################################
adj.fun <- function(var)
{
  the_fmla <- reformulate (covars, response=var)
  the_lm <- lm(the_fmla, panel.df)
  the_resids <- resid(the_lm)
  panel.df[names(the_resids), paste0(var,"_resid")] <- the_resids
  stopifnot(panel.df[19,paste0(var,"_resid")]==the_resids['19'])
  
  grmeans <- as.data.frame(tapply(panel.df[,paste0(var,"_resid")], panel.df$state, mean, na.rm=T))
  names(grmeans) <- "grmean"
  panel.df[,paste0(var, "_grmeans")] <- grmeans$grmean[match(panel.df$state, rownames(grmeans))]
  panel.df[,paste0(var,"_resid", "_MD")] <- panel.df[,paste0(var,"_resid")] - panel.df[,paste0(var,"_grmeans")]
  
  panel.df[paste0(var, "_grmeans")] <- NULL
  
  return(panel.df)
  
  # damn ave function is buggy
  #panel.df[,paste0(var,"_resid","_MD")] <- panel.df[,paste0(var,"_resid")] - ave(panel.df[,paste0(var,"_resid")], panel.df$state, na.rm=T)
  
  # dplyr does not play nice within functions
  #new.df <- panel.df %>%
  #  dplyr::group_by(state) %>%
  #  mutate(.[,paste0(var,"_resid","_MD")] <- .[,paste0(var,"_resid")] - mean(.[,paste0(var,"_resid")], na.rm=T)) %>%
  #  as.data.frame(ungroup(.))
  #return(new.df)
  
}


```

### Still Testing

Maybe mean-deviate everything by state before residualizing? What I really want is the equivalent of lm(outcome ~ treatment * (cov1+cov2))

```{r, eval=F}
# fewer so this is simpler.
covars <- c('age_y1', 'radio_y0', 'radio_y1', 'duration_y1'
            )

library(dplyr)
panel.df <- panel.df %>% dplyr::group_by(state) %>%
  mutate(tr_MD = as.numeric(treatment) - mean(as.numeric(treatment), na.rm=T),
         age_MD = age_y1 - mean(age_y1, na.rm=T),
         radio_y0_MD = radio_y0 - mean(radio_y0, na.rm=T),
         radio_y1_MD = radio_y1 - mean(radio_y1, na.rm=T),
         duration_MD = duration_y1 - mean(duration_y1, na.rm=T),
         x_index_MD = x_index - mean(x_index, na.rm=T)) %>%
  as.data.frame(ungroup(.))

lm.x_index_MD_resid <- resid(lm(x_index_MD ~ age_MD + radio_y0_MD + radio_y1_MD + duration_MD, data=panel.df))
lm.tr_MD_resid <- resid(lm(tr_MD ~ age_MD + radio_y0_MD + radio_y1_MD + duration_MD, data=panel.df))
panel.df[names(lm.x_index_MD_resid),"x_index_MD_resid"]<-lm.x_index_MD_resid
panel.df[names(lm.tr_MD_resid),"tr_MD_resid"]<-lm.tr_MD_resid

# test
estimatr::lm_robust(x_index_MD_resid ~ tr_MD_resid, data=panel.df, clusters=community)
# What is the equivalent normal model?
#This is what I want it to be, I think
estimatr::lm_robust(x_index ~ treatment*(state+age_y1+radio_y0+radio_y1+duration_y1), data=panel.df, clusters=community)
# It is not the one above, so maybe it is this?
estimatr::lm_robust(x_index ~ treatment+state*(age_y1+radio_y0+radio_y1+duration_y1), data=panel.df, clusters=community)

# argh, I just want the rosenbaum version of the Lin covar adjustment
lm_robust(x_index ~ treatment * (state+age_y1+radio_y0+radio_y1+duration_y1), data=panel.df, clusters=community)

```

## Systematize for all outcomes

Just using state as a covariate when I residualize.

Need to sapply a function that does this.

```{r}
covars <- c('age_y1', 'ethnic2_y1', 'radio_y0', 'radio_y1',
            'gender_y1', 'income_month_y0', 'income_month_y1',
            'username_y0', 'username_y1', 'duration_y0', 'duration_y1',
            "state"
            )

#tr resid
panel.df$treatment <- as.numeric(as.character(panel.df$treatment))
tr_fmla<-reformulate(covars, response='treatment')
tr.lm <- lm(tr_fmla,panel.df) # with other controls

lm.tr_resid<-resid(tr.lm)
panel.df[names(lm.tr_resid),"tr_resid"]<-lm.tr_resid
stopifnot(panel.df[8,"tr_resid"]==lm.tr_resid["8"])

#function to resid the other vars.
#####################################################
adj.fun <- function(var)
{
  the_fmla <- reformulate (covars, response=var)
  the_lm <- lm(the_fmla, panel.df)
  the_resids <- resid(the_lm)
  panel.df[names(the_resids), paste0(var,"_resid")] <- the_resids
  stopifnot(panel.df[8,paste0(var,"_resid")]==the_resids['8'])
  
  return(panel.df[,paste0(var,"_resid")])
}


```

Test function.

```{r, eval=F}
panel.df$test <- adj.fun("x_index")

test <- panel.df[is.na(panel.df$test),]
test[1:5,c("x_index", "treatment", "test", covars)]

#
new_fmla<-reformulate(c("treatment", covars), response='x_index')
(lm.test1 <- lm_robust(new_fmla, data=test, clusters=community))
test1 <- lm.test1$coefficients['treatment']

(lm.test2 <- lm_robust(x_index_resid~tr_resid, data=test, clusters=community))
test2 <- lm.test2$coefficients['tr_resid']
stopifnot(round(test1,8)==round(test2,8))

```

Use function to make _resid versions of all vars.

```{r}
outcomes <- c(names(panel.df)[grepl("index$", names(panel.df))], names(panel.df)[grepl("cw$", names(panel.df))],
              'pgp_amount_y1', 'pgp_donate_y1', 'pgp_meanDist_y1',
              "bene_index_perc")
# outcome resids...sapply not working
#panel.df[,paste0(outcomes, "_resid")] <- sapply(panel.df[,outcomes], adj.fun)

panel.df[,paste0(outcomes, "_resid")] <- NA
for(i in 1:ncol(panel.df[,paste0(outcomes, "_resid")]))
{
  panel.df[,paste0(outcomes, "_resid")[i]] <- adj.fun(paste0(outcomes)[i])
}

# test
# as controls
new_fmla <- reformulate(c('treatment', covars), response="out_index")
lm.con <- lm_robust(new_fmla, data=panel.df, clusters=community)
test1 <- lm.con$coefficients['treatment']

#covar adjusted
(lm.adj <- lm_robust(out_index_resid~tr_resid, data=panel.df, clusters=community))
test2 <- lm.adj$coefficients['tr_resid']
stopifnot(round(test1,8)==round(test2,8)) # R's weird rounding


```

## Possible better way

Lin method.

```{r, eval=F}
# Lin method
## need to do some kind of LASSO to predict which covariates matter
lm_robust(x_index ~ treatment * (state+age_y1+radio_y0+radio_y1+duration_y1), data=panel.df, clusters=community)

# How to do some Rosenbaum version of that?  
```


# moved here later - reversing variables when LOW is good

Used to be in setup of panelAnalysis.Rmd

```{r}
# need to reverse some cols so that HIGH is GOOD for all variables.  For these variables right now, HIGH is BAD.  This makes HIGH GOOD.
## inVars and so all in_index things were reversed in the e-makeIndices file.
revCols <- c("clash_index","clash_cw", "clash_cw_y0", "clash_cw_y1",
             "threat_index", "threat_cw", "threat_cw_y0", "threat_cw_y1",
             "in_index", "in_cw", "in_cw_y0", "in_cw_y1"#,
             #"list_exp", "list_exp_y0", "list_exp_y1"
             )
panel.df[,revCols] <- panel.df[,revCols]*-1

## How I was doing it in future rmd files.
#revCols <- c("clash_index", "threatIn_index", "threat_index", "in_index",
#             "clash_cw", "threatIn_cw", "threat_cw", "in_cw"
#             )
#revCols_agg <- c(revCols, paste0(revCols, "_base"), paste0(revCols, "_end"), paste0(revCols, "_resid"))
#ag.df[,revCols_agg] <- ag.df[,revCols_agg]*-1

#revCols_ind <- c(revCols, paste0(revCols, "_y0"), paste0(revCols, "_y1"), paste0(revCols, "_resid"))
#panel.df[,revCols_ind] <- panel.df[,revCols_ind]*-1
#rm(list=ls(pattern="revCols"))


```



# ADDED LATER - all_index with Inverse Covariance Weighting

What if we combined all the outcomes in ag.df using inverse covariance weighting?  Does that make sense?

Slightly difference than NPC.  NPC does not weight them, though it will account for their interdependence because really correlated things will be correlated in the null distribution, making extreme values on both less rare than if they were independent.

Not sure how NPC and icw results should be interpreted differently...they should really tell the same story.

```{r}
allIndices <- c("x_cw", "cohes_cw", "pgp_amount_y1",
                "pgp_donate_y1", "contactOnly_cw", "in_cw",
                "resolve_cw")
allIndices1 <- c("x_cw", "cohes_cw", "pgp_amount_y1",
                "pgp_donate_y1", "contactOnly_cw") # we did not list hypotheses about insecurity or dispute resolution at panel level.



ic2.fun <- function(vars)
{
  x <- panel.df[,vars]
  x <- zoo::na.aggregate(x)
  out_cw <- icwIndex(x)
  print(cor(x))
  print(out_cw$weights)
  return(as.vector(out_cw$index))
}

panel.df$all_cw <- ic2.fun(allIndices)
panel.df$all1_cw <- ic2.fun(allIndices1)

# no pgg
panel.df$all2_cw <- ic2.fun(allIndices[-c(3,4)])
panel.df$all3_cw <- ic2.fun(allIndices1[-c(3,4)])
```




# Save

To use for analysis in next file.

```{r}
rm(list=ls(pattern="(^new|thing|^need|^test|new_fmla$|lm)"))
rm(list=ls(pattern="(base|end|^df)"))
rm(i)
save.image(file="f2-panelData.Rdata")

```




# ADDED LATER - checking things

```{r}
weirdAge <- panel.df[abs(panel.df$age)>20, c('age_y0', 'age_y1', 'treatment', 'committee')]
table(weirdAge$treatment)
table(weirdAge$committee)
```















# OLD OLD OLD

# And for their value at baseline

back when I was doing the IC weighting on individual datasets.

```{r, eval=F, include=F}
merge.df$x_cw <- ic.fun(vars=xVars, thedf=merge.df)
merge.df$out_cw <- ic.fun(vars=outVars, thedf=merge.df)
merge.df$clash_cw <- ic.fun(vars=clashVars[c(1,2,4)], thedf=merge.df)
merge.df$contact_cw <- ic.fun(vars=contactVars, thedf=merge.df)
merge.df$contactOnly_cw <- ic.fun(vars=contactVars[c(1:4,7)], thedf=merge.df)
merge.df$bene_cw <- ic.fun(vars=beneVarsPerc, thedf=merge.df)
merge.df$threatIn_cw <- ic.fun(vars=threatInVars, thedf=merge.df)
merge.df$threat_cw <- ic.fun(vars=threatVars, thedf=merge.df)
merge.df$in_cw <- ic.fun(vars=inVars, thedf=merge.df)
merge.df$cohes_cw <- ic.fun(vars=cohesVars, thedf=merge.df)
merge.df$cohes1_cw <- ic.fun(vars=cohesVars1, thedf=merge.df)
merge.df$cohes2_cw <- ic.fun(vars=cohesVars2, thedf=merge.df)
merge.df$dis_cw <- ic.fun(vars=disVars, thedf=merge.df)
merge.df$share_cw <- ic.fun(vars=shareVars, thedf=merge.df)
merge.df$numDis_cw <- ic.fun(vars=numDisVars, thedf=merge.df)
merge.df$resolve_cw <- ic.fun(vars=resolveVars, thedf=merge.df)
merge.df$disActor_cw <- ic.fun(vars=disActorVars,thedf=merge.df)
merge.df$vio_cw <- ic.fun(vars=vioVars, thedf=merge.df)
```