---
title: "ecpn_coefplot"
author: "cdgrady21"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())

library(plyr)
library(dplyr)
library(tidyr)

load('ag.coefs.Rdata')
load('ind.coefs.Rdata')
#load('ind2.coefs.Rdata')

#load('ag.coefs_orig.Rdata')
#load('ind.coefs_orig.Rdata')
#load('ind2.coefs_orig.Rdata')

## add obs data to coefs
load("../../obsDat/analysis/marketMedian.Rdata")
load("../../obsDat/analysis/eventsMedian.Rdata")

marks <- as.data.frame(markMed.thing[c("pastoralists_index", "farmers_index"),])
marks$sd <- NA
marks["pastoralists_index","sd"] <- sd(markets$pastoralists_index, na.rm=T)
marks["farmers_index","sd"] <- sd(markets$farmers_index, na.rm=T)

evs <- as.data.frame(eventsMed.thing[c("attend_total", "eat_total"),])
evs$sd <- NA
evs["attend_total","sd"] <- sd(events$attend_total, na.rm=T)
evs["eat_total","sd"] <- sd(events$eat_total, na.rm=T)

markEvs <- rbind(marks,evs)
markEvs[,c("ll", "ul")] <- markEvs[,c("lower", "upper")]; markEvs[,c("lower", "upper")] <- NULL
addNames <- setdiff(names(ag.coefs), names(markEvs))
markEvs[,addNames] <- NA
markEvs$var <- rownames(markEvs)
markEvs$size <- markEvs$coef/markEvs$sd
markEvs[,c("ll_size", "ul_size")] <- markEvs[,c("ll", "ul")]/markEvs$sd
markEvs <- markEvs[c(names(ag.coefs))]

ag.coefs <- rbind(ag.coefs, markEvs)

```

<!--Note: have made all of these into png, but works with pdf.  just add width=7, height=4 -->

# Make a combined coefplot

Cbind ag.coefs and ind.coefs together.

```{r}
# need to add the outcomes that we don't use at the individual-level (the survey exps, obsDat)
ind.coefs <- add_row(ind.coefs, var=setdiff(ag.coefs$var, ind.coefs$var)[!grepl("pgp", setdiff(ag.coefs$var, ind.coefs$var))])
#names(ind.coefs) <- paste0(names(ind.coefs), "_ind")
thecoefs <- cbind(ag.coefs, ind.coefs[,2:length(ind.coefs)])

```

Set the plot df

```{r}
# order by size
thecoefs <- thecoefs[order(thecoefs$size),]
varNames<-thecoefs$var
res<-t(thecoefs[,c("size", "ll_size", "ul_size",
                   "size_ind", "size_ll_ind", "size_ul_ind",
                   "size_part", "size_ll_part", "size_ul_part",
                   "size_non", "size_ll_non", "size_ul_non")]) # drop sd, varnames
colnames(res)<-varNames

# chris: renaming the outcomes, need to change code when outcome order changes.
orignames <- colnames(res)

newlabs <- c("Markets-pastoralists",
              "Perceptions of security",
                  "Contact",
                  "Outgroup affect",
             "Bargaining",
             "PGG Donate",
             "Empathy",
             "Percent exp",
              "Endorsement exp",
             "Events-attend",
             "Perceived benefit",
             "Ingroup expansion",
             "Percent exp1",
             "Markets-farmers",
             "Events-eat",
             "Threat",
             "PGG amount",
              "List exp",
             "Clash awareness"
             )
newlabs <- rev(newlabs)
cbind(newlabs,orignames) # check
colnames(res) <- newlabs

MainOuts <- res[,c("Contact", "List exp", "Percent exp1", "Percent exp", "Endorsement exp", "Outgroup affect", "PGG amount", "Perceptions of security")]
MarkEvents <- res[,c("Markets-pastoralists", "Markets-farmers", "Events-attend", "Events-eat")]
MainMechs <- res[,c("Empathy", "Threat", "Ingroup expansion", "Perceived benefit", "Bargaining")]


res1 <- res[,colnames(res) %in% intersect(colnames(res), colnames(MainOuts))]
res2 <- res[,colnames(res) %in% intersect(colnames(res), colnames(MarkEvents))]
res3 <- res[,colnames(res) %in% intersect(colnames(res), colnames(MainMechs))]
```


# MAKE DIFFERENT COEFPLOTS

### Intergroup Affect Outcomes

Survey self-reports (allTrustVars) and endorsement experiment.

```{r}
affect_outcomes <- c("Endorsement exp", "Outgroup affect")
affect_outcomes <- rev(affect_outcomes)
res1 <- res1[,affect_outcomes] # change order away from effect size and towards outcome type

lablen <- nchar(colnames(res1))
#ub<-rep(max(ind_un["ul",]),ncol(ind)) # if want to change bounds for aesthetics
#lb<-rep(-0.05,ncol(ind))
#ind<-rbind(res,ub,lb)

png(file="ecpn_coefplots_MainOuts-cats.png")

par(mar=c(3,10,2,2),oma=c(0,0,0,0),mgp=c(1.5,.5,0),mfrow=c(1,1))
maxmods <- ncol(res1)
newmods <- c(1,2.25,3.5,4.75,5.25,5.75,6.25,7.5)

## Community and individual on same
plot(range(as.vector(res1[c("ll_size","ul_size"),]),na.rm=TRUE),c(0.5,maxmods),type="n",
     axes=FALSE,ylab="",xlab="Est. Effect Size and 95% CI",
     main="Main outcomes: Community and Individual-level")
axis(1)
abline(v=0,col="gray",lwd=.5)
points(res1["size",],newmods,pch=19)
segments(res1["ll_size",],newmods, res1["ul_size",],newmods)
axis(2,at=newmods,labels=dimnames(res1)[[2]],las=2)
# adding in the panel
points(res1["size_ind",],(newmods)-.3,pch=1)
segments(res1["size_ll_ind",],(newmods)-.3,
         res1["size_ul_ind",],(newmods)-.3,lty=2)
legend("bottomleft",legend=c("Community Data","Individual Data"),
       pch=c(19,1),lty=c(1,2),bty="n", cex=0.75)
dev.off()

```



************************

Make the coefplot with all outcomes.

```{r}
main_outcomes <- c("Outgroup affect", "Endorsement exp", "Contact", "Percent exp", "Markets-pastoralists", "Markets-farmers", "Events-attend", "Events-eat", "Perceptions of security")
main_outcomes <- rev(main_outcomes)
res_main <- res[,main_outcomes] # change order away from effect size and towards outcome type

lablen <- nchar(colnames(res_main))
#ub<-rep(max(ind_un["ul",]),ncol(ind)) # if want to change bounds for aesthetics
#lb<-rep(-0.05,ncol(ind))
#ind<-rbind(res,ub,lb)

png(file="ecpn_coefplots_MainOuts-cats.png")

par(mar=c(3,10,2,2),oma=c(0,0,0,0),mgp=c(1.5,.5,0),mfrow=c(1,1))
maxmods <- ncol(res_main)
newmods <- c(1.0, 2.25,3.0,3.75,4.5,5.25,6.0, 7.0,7.75)

## Community and individual on same
plot(range(as.vector(res_main[c("ll_size","ul_size"),]),na.rm=TRUE),c(0.5,maxmods),type="n",
     axes=FALSE,ylab="",xlab="Est. Effect Size and 95% CI",
     main="Main outcomes: Community and Individual-level")
axis(1)
abline(v=0,col="gray",lwd=.5)
points(res_main["size",],newmods,pch=19)
segments(res_main["ll_size",],newmods, res_main["ul_size",],newmods)
axis(2,at=newmods,labels=dimnames(res_main)[[2]],las=2)
# adding in the panel
points(res_main["size_ind",],(newmods)-.3,pch=1)
segments(res_main["size_ll_ind",],(newmods)-.3,
         res_main["size_ul_ind",],(newmods)-.3,lty=2)
legend("topright",legend=c("Community Data","Individual Data"),
       pch=c(19,1),lty=c(1,2),bty="n", cex=0.75)
dev.off()

```

Now just the survey outcomes

```{r}
survey_outcomes <- c("Outgroup affect", "Endorsement exp", "Contact", 
                   "Percent exp", "Perceptions of security", "PGG amount",
                   "PGG Donate")
survey_outcomes <- rev(survey_outcomes)
res_survey <- res[,survey_outcomes] # change order away from effect size and towards outcome type

lablen <- nchar(colnames(res_survey))
#ub<-rep(max(ind_un["ul",]),ncol(ind)) # if want to change bounds for aesthetics
#lb<-rep(-0.05,ncol(ind))
#ind<-rbind(res,ub,lb)

png(file="ecpn_coefplots_SurveyOuts-cats.png")

par(mar=c(3,10,4,2),oma=c(0,0,0,0),mgp=c(1.5,.5,0),mfrow=c(1,1))
maxmods <- ncol(res_survey)
newmods <- c(1.0,1.75, 3.0, 4.25,5.0, 6.25,7.0)

## Community and individual on same
plot(range(as.vector(res_survey[c("ll_size","ul_size"),]),na.rm=TRUE),c(0.5,maxmods),type="n",
     axes=FALSE,ylab="",xlab="Est. Effect Size and 95% CI",
     main="Main outcomes: Community and Individual-level")
axis(1)
abline(v=0,col="gray",lwd=.5)
points(res_survey["size",],newmods,pch=19)
segments(res_survey["ll_size",],newmods, res_survey["ul_size",],newmods)
axis(2,at=newmods,labels=dimnames(res_survey)[[2]],las=2)
# adding in the panel
points(res_survey["size_ind",],(newmods)-.3,pch=1)
segments(res_survey["size_ll_ind",],(newmods)-.3,
         res_survey["size_ul_ind",],(newmods)-.3,lty=2)
legend("topleft",legend=c("Community Data","Individual Data"),
       pch=c(19,1),lty=c(1,2),bty="n", cex=0.75)
dev.off()

```


Now for the panel

Dark spots are Committee/Full Participant vs control, Open spots are the non-participants vs control.

```{r}
res1_p <- res1[,c("Perceptions of security", "Contact", "Outgroup affect")]
lablen <- nchar(colnames(res1_p))
#ub<-rep(max(ind_un["ul",]),ncol(ind)) # if want to change bounds for aesthetics
#lb<-rep(-0.05,ncol(ind))
#ind<-rbind(res,ub,lb)

png(file="ecpn_coefplots_MainOuts_panel-cats.png")

par(mar=c(3,10,1.5,2),oma=c(8,0,8,0),mgp=c(1.5,.5,0),mfrow=c(1,1))
maxmods <- ncol(res1_p)
newmods <- c(1,1.75,2.5)

## panel
plot(range(as.vector(res1_p[c("size_ll_non","size_ul_part"),]),na.rm=TRUE),c(0.5,maxmods),type="n",
     axes=FALSE,ylab="",xlab="Est. Effect Size and 95% CI",
     main="Main outcomes: Individual-level")
axis(1)
abline(v=0,col="gray",lwd=.5)
points(res1_p["size_part",],newmods,pch=19)
segments(res1_p["size_ll_part",],newmods, res1_p["size_ul_part",],newmods)
axis(2,at=newmods,labels=dimnames(res1_p)[[2]],las=2)
# adding in the nonparts
points(res1_p["size_non",],(newmods)-.2,pch=1)
segments(res1_p["size_ll_non",],(newmods)-.2,
         res1_p["size_ul_non",],(newmods)-.2,lty=2)
legend("topright",legend=c("Participants","Nonparticipants"),
       pch=c(19,1),lty=c(1,2),bty="n", cex=0.9)
dev.off()

```





*****************

Market/Events Outcomes

```{r}
mark_outcomes <- c("Markets-pastoralists", "Markets-farmers", "Events-attend", "Events-eat")
mark_outcomes <- rev(mark_outcomes)
res2 <- res2[,mark_outcomes] # change order away from effect size and towards outcome type
colnames(res2) <- c("Events: eat", "Events: attend", "Markets: farmers", "Markets: pastoralists")

lablen <- nchar(colnames(res2))
#ub<-rep(max(ind_un["ul",]),ncol(ind)) # if want to change bounds for aesthetics
#lb<-rep(-0.05,ncol(ind))
#ind<-rbind(res,ub,lb)

png(file="ecpn_coefplots_markEvents.png")

par(mar=c(6,9,2,1),oma=c(6,0,6,0),mgp=c(1.5,.5,0),mfrow=c(1,1))
maxmods <- ncol(res2)

## Community and individual on same
plot(c(-0.25,0.8),c(0.5,maxmods),type="n",
     axes=FALSE,ylab="",xlab="Est. Median Effect Size and 95% CI",
     main="Markets and social observations")
axis(1)
abline(v=0,col="gray",lwd=.5)
points(res2["size",],1:maxmods,pch=19)
segments(res2["ll_size",],1:maxmods, res2["ul_size",],1:maxmods)
axis(2,at=1:maxmods,labels=dimnames(res2)[[2]],las=2)
#legend("bottomright",legend=c("Community Data","Individual Data"),
#       pch=c(19,1),lty=c(1,2),bty="n", cex=0.75)
dev.off()

```



# Make mechanism coefplot

```{r}
main_mechs <- c("Empathy", "Threat", "Ingroup expansion", "Perceived benefit")
main_mechs <- rev(main_mechs)
res3 <- res3[,main_mechs] # change order away from effect size and towards outcome type

png(file="ecpn_coefplots_Mechs.png")

par(mar=c(3,10,2,2),oma=c(0,0,0,0),mgp=c(1.5,.5,0),mfrow=c(1,1))
maxmods <- ncol(res3)

## Community and individual on same
plot(range(as.vector(res3[c("ll_size","ul_size"),]),na.rm=TRUE),c(0.5,maxmods),type="n",
     axes=FALSE,ylab="",xlab="Est. Effect Size and 95% CI",
     main="Main mechanisms: Community and Individual-level")
axis(1)
abline(v=0,col="gray",lwd=.5)
points(res3["size",],1:maxmods,pch=19)
segments(res3["ll_size",],1:maxmods, res3["ul_size",],1:maxmods)
axis(2,at=1:maxmods,labels=dimnames(res3)[[2]],las=2)
# adding in the panel
points(res3["size_ind",],(1:maxmods)-.3,pch=1)
segments(res3["size_ll_ind",],(1:maxmods)-.3,
         res3["size_ul_ind",],(1:maxmods)-.3,lty=2)
legend("bottomleft",legend=c("Community Data","Individual Data"),
       pch=c(19,1),lty=c(1,2),bty="n", cex=0.75)
dev.off()



```


# Make mechanisms for panel only

Dark spots are Committee/Full Participant vs control, Open spots are the non-participants vs control.

```{r}
#ub<-rep(max(ind_un["ul",]),ncol(ind)) # if want to change bounds for aesthetics
#lb<-rep(-0.05,ncol(ind))
#ind<-rbind(res,ub,lb)

png(file="ecpn_coefplots_mechs_panel.png")

par(mar=c(3,10,2,2),oma=c(0,0,0,0),mgp=c(1.5,.5,0),mfrow=c(1,1))
maxmods <- ncol(res3)
newmods <- c(1.5,2.25,3,3.75)

## panel
plot(range(as.vector(res3[c("size_ll_non","size_ul_non"),]),na.rm=TRUE),c(0.5,maxmods),type="n",
     axes=FALSE,ylab="",xlab="Est. Effect Size and 95% CI",
     main="Main mechanisms: Individual-level")
axis(1)
abline(v=0,col="gray",lwd=.5)
points(res3["size_part",],newmods,pch=19)
segments(res3["size_ll_part",],newmods, res3["size_ul_part",],newmods)
axis(2,at=newmods,labels=dimnames(res3)[[2]],las=2)
# adding in the nonparts
points(res3["size_non",],(newmods)-.3,pch=1)
segments(res3["size_ll_non",],(newmods)-.3,
         res3["size_ul_non",],(newmods)-.3,lty=2)
legend("bottomleft",legend=c("Participants","Nonparticipants"),
       pch=c(19,1),lty=c(1,2),bty="n", cex=0.75)
dev.off()

```


**********************

# Make the ag.df coefplot only

Set the plot df

```{r}
res_agdf <- res1[1:3,]
```

Make the coefplot

```{r}
lablen <- nchar(colnames(res_agdf))
#ub<-rep(max(ind_un["ul",]),ncol(ind)) # if want to change bounds for aesthetics
#lb<-rep(-0.05,ncol(ind))
#ind<-rbind(res,ub,lb)

png(file="ecpn_coefplots_agdf.png")

par(mar=c(3,10,2,2),oma=c(0,0,0,0),mgp=c(1.5,.5,0),mfrow=c(1,1))
maxmods <- ncol(res1)

## ag.df
plot(range(as.vector(res1[c("ll","ul"),]),na.rm=TRUE),c(0.5,maxmods),type="n",
     axes=FALSE,ylab="",xlab="Est. Effect Size and 95% CI",
     main="Effects of ECPN in Community-Level Data")
axis(1)
abline(v=0,col="gray",lwd=.5)
points(res1["size",],1:maxmods,pch=19)
segments(res1["ll",],1:maxmods, res1["ul",],1:maxmods)
axis(2,at=1:maxmods,labels=dimnames(res1)[[2]],las=2)
dev.off()

```


# Make the panel.df coefplot only

Set the plot df

```{r}
# order by size
pan.coefs <- ind.coefs[order(ind.coefs$size_part),]
varNames<-pan.coefs$var
pan.res<-t(pan.coefs[,c("size_non", "size_ll_non", "size_ul_non",
                        "size_part", "size_ll_part", "size_ul_part")])
colnames(pan.res)<-varNames
pan.res <- pan.res[,1:9] # drop svy exps

orignames <- colnames(pan.res)
newlabs <- c("Intergroup Contact",
             "Outgroup Trust",
             "Perceptions of Security",
             "Intergroup Cohesion",
             "PGG Donate",
             "Dispute Resolution",
             "Shared Resources",
             "Clash History",
             "PGG Amount"
             )

newlabs <- rev(newlabs)
cbind(newlabs,orignames) # check
colnames(pan.res) <- newlabs

pan.notHyps <- pan.res[,c("Shared Resources", "Clash History")]
pan.res1 <- pan.res[,!colnames(pan.res) %in% intersect(colnames(pan.res), colnames(pan.notHyps))]
pan.res2 <- pan.res[,colnames(pan.res) %in% intersect(colnames(pan.res), colnames(pan.notHyps))]
```


Dark spots are Committee/Full Participant vs control, Open spots are the non-participants vs control.

```{r}
lablen <- nchar(colnames(pan.res1))
#ub<-rep(max(ind_un["ul",]),ncol(ind)) # if want to change bounds for aesthetics
#lb<-rep(-0.05,ncol(ind))
#ind<-rbind(res,ub,lb)

png(file="ecpn_coefplots_panOrdered.png")

par(mar=c(3,10,2,2),oma=c(0,0,0,0),mgp=c(1.5,.5,0),mfrow=c(1,1))
maxmods <- ncol(pan.res1)

## Community and individual on same
plot(round(range(as.vector(pan.res1[c("size_ll_part","size_ul_part"),]),na.rm=TRUE)),c(0.5,maxmods),type="n",
     axes=FALSE,ylab="",xlab="Est. Effect Size and 95% CI",
     main="Effects of ECPN on Participants and Nonparticipants")
axis(1)
abline(v=0,col="gray",lwd=.5)
points(pan.res1["size_part",],1:maxmods,pch=19)
segments(pan.res1["size_ll_part",],1:maxmods, pan.res1["size_ul_part",],1:maxmods)
axis(2,at=1:maxmods,labels=dimnames(pan.res1)[[2]],las=2)
# adding in the non-participants
points(pan.res1["size_non",],(1:maxmods)-.3,pch=1)
segments(pan.res1["size_ll_non",],(1:maxmods)-.3,
         pan.res1["size_ul_non",],(1:maxmods)-.3,lty=2)
legend("topleft",legend=c("Participants","Non-participants"),
       pch=c(19,1),lty=c(1,2),bty="n", cex=0.75)
dev.off()

```


# Old

```{r, eval=F, include=F}
# ag.coefs
# for use with original diff-in-diff estimation strategy
newlabs_orig <- c("Perceptions of Security",
             "Comfort with Other Group",
             "Intergroup Contact",
             "Public Goods Game - Donation",
             "Endorsement Experiment",
             "Random Experiment",
             "Cohesion with Other Group",
             "Random Experiment1",
             "Dispute Resolution",
             "List Experiment",
             "Public Goods Game - Amount",
             "Clash History",
             "Shared Resources"
             )
# for use with lm(end~tr+base) strategy
newlabs <- c("Public Goods Game - Donation",
                  "Comfort with Other Group",
                  "Endorsement Experiment",
             "Random Experiment",
             "Perceptions of Insecurity",
             "Clash History",
              "Cohesion with Other Group",
             "Intergroup Contact",
             "Dispute Resolution",
             "Random Experiment1",
              "List Experiment",
              "Shared Resources",
              "Public Goods Game - Amount"
             )


# panel
# for use with original diff-in-diff estimation strategy
newlabs_orig <- c("Intergroup Contact",
             "Comfort with Other Group",
             "Cohesion with Other Group",
             "Perceptions of Insecurity",
             "Public Goods Game - Donation",
             "Dispute Resolution",
             "Clash History",
             "Shared Resources",
             "Public Goods Game - Amount"
             )
# for use with lm(end~tr+base) strategy.
newlabs <- c("Public Goods Game - Donation",
             "Comfort with Other Group",
             "Intergroup Contact",
             "Clash History",
             "Cohesion with Other Group",
             "Dispute Resolution",
             "Shared Resources",
             "Perceptions of Insecurity",
             "Public Goods Game - Amount"
             )

```