---
title: "ecpn_diff-in-diff plots"
output:
  word_document: default
  html_document: default
---

note: if want to convert to pdf:

dev.copy(pdf,file="endComm_plot_nas.pdf")
dev.off()

pdf(file="endComm_plot_nas.pdf", bg="transparent", width=5, height=5)
endComm_plot_nas
dev.off()


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(plyr)
library(dplyr)
library(tidyr)
library(ggplot2)

load("../c_creating_dataframes/f-aggregateComms_ap.Rdata")
load("../c_creating_dataframes/rand_df.Rdata")
load("../b_creating_outcomes/f2-panelData.Rdata")
load("../../obsDat/analysis/eventsMedian.Rdata")
load("../../obsDat/analysis/marketMedian.Rdata")

#until I figure out insecurity, vio, list, reverse scale it.
ag.df$in_cw_base <- abs(ag.df$in_cw_base+1)
ag.df$in_cw_end <- abs(ag.df$in_cw_end+1)
panel.df$in_cw_y0 <- abs(panel.df$in_cw_y0+1)
panel.df$in_cw_y1 <- abs(panel.df$in_cw_y1+1)

ag.df$vio_cw_base <- abs(ag.df$vio_cw_base-1)
ag.df$vio_cw_end <- abs(ag.df$vio_cw_end-1)
panel.df$vio_cw_y0 <- abs(panel.df$vio_cw_y0-1)
panel.df$vio_cw_y1 <- abs(panel.df$vio_cw_y1-1)


ag.df$list_exp_base <- ag.df$list_exp_base*-1
ag.df$list_exp_end <- ag.df$list_exp_end*-1
```


# Make plot data

Isolate vars.

```{r}
#The vars to plot.
ag.vars <- c('allTrust_cw', 'contactOnly_cw', "in_cw",
             'pgp_amount_end', 'pgp_donate_end',
             'threat_cw', 'bene_cw', 'clash_cw', "barg_cw",
             'list_exp', 'rand_lm', 'rMean', 'end_exp',
             'vio_cw')

## individual
ind.vars <- c('allTrust_cw', 'contactOnly_cw', "in_cw",
              'pgp_amount_y1', 'pgp_donate_y1',
              'threat_cw', 'bene_cw', 'clash_cw', "barg_cw",
              "vio_cw")

# add additive index
ag.vars <- c(ag.vars, setdiff(gsub("_cw", "_index", ag.vars), ag.vars))
ind.vars <- c(ind.vars, setdiff(gsub("_cw", "_index", ind.vars), ind.vars))
stopifnot(setdiff(ag.vars,names(ag.df))==0)
stopifnot(setdiff(ind.vars,names(panel.df))==0)
```

Ag.df plot data

```{r}
#Aggregate Plot df
base <- ag.df[,c(paste0(ag.vars[!grepl("pgp", ag.vars)], "_base"), "treatment", "state", "psu")]
names(base) <- sub("_base", "", names(base))
base$survey <- "Baseline"
end <- ag.df[,c(paste0(ag.vars[!grepl("pgp", ag.vars)], "_end"), "treatment", "state", "psu")]
names(end) <- sub("_end", "", names(end))
end$survey <- "Endline"
plot.df <- rbind(base,end)

# get ICCs with dplyr
plot2.df <- plot.df %>% dplyr::group_by(survey) %>% 
  dplyr::summarize_all(funs(ICC::ICCbare(psu,.))) %>%
  as.data.frame() # warnings for non-numerics
names(plot2.df) <- paste0(names(plot2.df), "_icc")


# get mean and sd with dplyr
plot.df$state <- as.character(plot.df$state) # save me trouble with dplyr later
plot.df$psu <- as.numeric(as.character(plot.df$psu))
plot1.df<-plot.df %>% 
  dplyr::group_by(treatment,survey) %>%
  dplyr::summarise_all(list(~mean(.), ~sd(.))) %>% # warnings because cannot sumarise non-numeric
  as.data.frame()

# combine
plot.df <- cbind(plot1.df, plot2.df)
plot.df$Treatment<-ifelse(plot.df$treatment %in% 1, "ECPN", "Non-ECPN")
#plot.df$State <- ifelse(plot.df$state %in% "nas", "Nas", "Ben")
#plot.df$plotID <- interaction(plot.df$Treatment, plot.df$State)

# need to add SEs; need to calc effective sample size; need to remove state, psu, survey, from these
sdVars <-  names(plot.df)[grepl("_sd", names(plot.df))]
sdVars <- sdVars[!sdVars %in% c("state_sd", "psu_sd")]
seVars <- sub("_sd", "_se", sdVars)
iccVars <- sub("_sd", "_icc", sdVars)
essVars <- sub("_sd", "_ess", sdVars)
plot.df[,essVars] <- (2*15)/(1+plot.df[,iccVars]*(2-1)) 

# icc is negative for a couple things...making effective sample size larger than actual...
for(i in 1:length(iccVars))
{
  plot.df[,essVars[i]] <- ifelse(plot.df[,essVars[i]] > 30, 30, plot.df[,essVars[i]])
}
plot.df[,seVars] <- plot.df[,sdVars]/sqrt(plot.df[,essVars])
```

Individual-level (Tr-Co) plot data

```{r}
#Panel Plot df
base1 <- panel.df[,c(paste0(ind.vars[!grepl("pgp", ind.vars)], "_y0"), "treatment", "state", "community")]
names(base1) <- sub("_y0", "", names(base1))
base1$survey <- "Baseline"
end1 <- panel.df[,c(paste0(ind.vars[!grepl("pgp", ind.vars)], "_y1"), "treatment", "state", "community")]
names(end1) <- sub("_y1", "", names(end1))
end1$survey <- "Endline"
plot.df1 <- rbind(base1,end1)
plot.df1$state <- as.character(plot.df1$state) # save me trouble with dplyr later
plot.df1$community <- as.character(plot.df1$community)

plot.df1<-plot.df1 %>% 
  dplyr::group_by(treatment,survey) %>%  # chris: could add state here to differentiate nas from ben
  dplyr::summarise_all(funs(mean(., na.rm = TRUE), sd(., na.rm=T))) %>% # warnings because cannot sumarise non-numeric
  as.data.frame()

sumVars <- names(base1)[1:8]
iccVars1 <- iccVars[c(1:7,11)]
for(i in 1:length(sumVars))
{
  plot.df1[plot.df1$survey %in% "Baseline",iccVars1[i]] <- ICC::ICCbare(base1$community,base1[,sumVars[i]])
  plot.df1[plot.df1$survey %in% "Endline",iccVars1[i]] <- ICC::ICCbare(end1$community,end1[,sumVars[i]])
}
plot.df1$Treatment<-ifelse(plot.df1$treatment %in% 1, "ECPN", "Non-ECPN")

# need to add SEs; need to calc effective sample size; need to remove state, psu, survey, from these
sdVars1 <-  names(plot.df1)[grepl("_sd", names(plot.df1))]
sdVars1 <- sdVars1[!sdVars1 %in% c("state_sd", "community_sd")]
seVars1 <- sub("_sd", "_se", sdVars1)
iccVars <- sub("_sd", "_icc", sdVars1)
essVars1 <- sub("_sd", "_ess", sdVars1)
avgSize <- mean(table(base1$community)) # diff sized clusters...using the average
lengthComm <- length(table(base1$community)) # number of clusters is 29 -- no loko pastoralists.
plot.df1[,essVars1] <- (avgSize*lengthComm)/(1+plot.df1[,iccVars1]*(avgSize-1)) 
plot.df1[,seVars1] <- plot.df1[,sdVars1]/sqrt(plot.df1[,essVars1])
```

Individual Part-Non-Co plot data.

```{r}
# Part-non-control Plot df
base2 <- panel.df[,c(paste0(ind.vars[!grepl("pgp", ind.vars)], "_y0"), "treatment", "state", "committee")]
names(base2) <- sub("_y0", "", names(base2))
base2$survey <- "Baseline"
end2 <- panel.df[,c(paste0(ind.vars[!grepl("pgp", ind.vars)], "_y1"), "treatment", "state", "committee")]
names(end2) <- sub("_y1", "", names(end2))
end2$survey <- "Endline"
plot.df2 <- rbind(base2,end2)
plot.df2$Treatment <- interaction(plot.df2$treatment, plot.df2$committee)
levels(plot.df2$Treatment) <- c("Control", "Non-Part", NA, "Part")
plot.df2$Treatment <- ordered(plot.df2$Treatment, levels=c("Part", "Non-Part", "Control"))

plot.df2$state <- as.character(plot.df2$state) # save me trouble with dplyr later
plot.df2<-plot.df2 %>% 
  dplyr::group_by(Treatment,survey) %>%  # chris: could add state here to differentiate nas from ben
  dplyr::summarise_all(funs(mean(., na.rm = TRUE), sd(., na.rm=T))) %>% # warnings because cannot sumarise non-numeric
  as.data.frame()

for(i in 1:length(sumVars))
{
  plot.df2[plot.df2$survey %in% "Baseline",iccVars1[i]] <- ICC::ICCbare(base1$community,base1[,sumVars[i]])
  plot.df2[plot.df2$survey %in% "Endline",iccVars1[i]] <- ICC::ICCbare(end1$community,end1[,sumVars[i]])
}
# need to add SEs; need to calc effective sample size; need to remove state, psu, survey, from these
plot.df2[,essVars1] <- (avgSize*lengthComm)/(1+plot.df2[,iccVars1]*(avgSize-1)) 
plot.df2[,seVars1] <- plot.df2[,sdVars1]/sqrt(plot.df2[,essVars1])

#rm(pattern="(se|sd|ess|icc)Vars") #chris: regex inside pattern not work?
```

##########
# Plot functions - ggplot showing each group before and after.
##########

```{r}
# Fixing colors
grps <-c("ECPN","Non-ECPN","Part", "Non-Part", "Control")
color.codes<-as.character(c("#FC8D59", "#00BFC4", "#FC8D59", "dark red", "#00BFC4"))
#ECPN = "#FC8D59", Non-ECPN = "#00BFC4", Part="FC8D59", Non-Part="green", Control="#00BFC4")
#plot.df$colors <- c("#00BFC4","#00BFC4","#FC8D59","#FC8D59")
#plot.df1$colors <- c("#FC8D59","#FC8D59","#00BFC4","#00BFC4")
#plot.df2$colors <- c("#FC8D59","#FC8D59", "green", "green", "#FFFFBF","#FFFFBF")

# The main Plot function chris: still need to make SE errorbars same color as lines...
# gg line plot
plot.fun<-function(var, thedf, time, title, xlab, ylab, ymin, ymax){
  ggplot(data=thedf, aes(x=thedf[[time]], y=thedf[[paste0(var, "_mean")]], group=Treatment)) +
  geom_line(aes(color=Treatment))+
  geom_point(aes(color=Treatment))+
  scale_colour_manual(values=setNames(color.codes, grps)) +
  coord_cartesian(ylim = c(ymin, ymax)) +
  #geom_errorbar(aes(ymin = thedf[[paste0(var, "_mean")]] - thedf[[paste0(var, "_se")]], 
   #                ymax= thedf[[paste0(var, "_mean")]] + thedf[[paste0(var, "_se")]],
  #                 color=Treatment), 
  #      width=.2, position=position_dodge(0.03)) + 
  ggtitle(title) +
  theme_bw() +
  theme(panel.grid.major = element_blank()) +
  theme(plot.title = element_text(size=18)) +
  xlab(xlab) +
  ylab(ylab)
}
```

## Trust Index

ECPN sites improed more on Outgroup Index than control sites.

```{r}
(affectComm.plot <- plot.fun(var='allTrust_cw', thedf=plot.df, time='survey', title="Affect - Community", 
         xlab="Survey", ylab="Average Affect Index Score",
         ymin=0.3, ymax=0.7))

png(file="affectComm_plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
affectComm.plot
dev.off()
```

Part vs Non vs Con.  Part is blue and improves.  Non-part is green and gets a bit worse.  Control is red and gets much worse.

```{r}
(affectPan.plot <- plot.fun(var='allTrust_cw', thedf=plot.df2, time='survey', title="Affect - Panel",
         xlab="Survey", ylab="Average Affect Index Score",
         ymin=0.3, ymax=0.7))

png(file="affectPan_plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
affectPan.plot
dev.off()

# why using these ugly colors instead of red green blue? have since fixed.
#ggplot_build(outPan.plot)$data
#ggplot_build(outComm.plot)$data
```

```{r, eval=F, include=F}
# looking at indices on the same scale. Tell the same story: up for all, up more for treatment and participants.

(outComm.plot <- plot.fun(var='x_index', thedf=plot.df, time='survey', title="Outgroup Attitudes - Community", 
         xlab="Survey", ylab="Average Outgroup Index Score",
         ymin=0, ymax=0.5))

(outInd.plot <- plot.fun(var='x_index', thedf=plot.df1, time='survey', title="Outgroup Attitudes - Individual",
         xlab="Survey", ylab="Average Outgroup Index Score",
         ymin=-0.35, ymax=0.35))

(outPan.plot <- plot.fun(var='x_index', thedf=plot.df2, time='survey', title="Outgroup Attitudes - Panel",
         xlab="Survey", ylab="Average Outgroup Index Score",
         ymin=0.3, ymax=0.7))
```


## Intergroup Contact Index

ECPN sites decreased less on contact index than control sites.

```{r}
(conComm.plot <- plot.fun(var='contactOnly_cw', thedf=plot.df, time='survey', title="Intergroup Contact - Community", 
         xlab="Survey", ylab="Average Intergroup Contact Index Score",
         ymin=0.3, ymax=0.7))

png(file="conComm_plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
conComm.plot
dev.off()
```

Part improves, Non-part and Control both get worse at identical rate.

```{r}
(conPan.plot <- plot.fun(var='contactOnly_cw', thedf=plot.df2, time='survey', title="Intergroup Contact - Panel",
         xlab="Survey", ylab="Average Intergroup Contact Index Score",
         ymin=0, ymax=0.7))

png(file="conPan_plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
conPan.plot
dev.off()

```


```{r, eval=F}
# index not cw
(conComm.plot <- plot.fun(var='contactOnly_index', thedf=plot.df, time='survey', title="Contact Index - Community", 
         xlab="Survey", ylab="Average Contact Index Score",
         ymin=0.3, ymax=0.7))

(conPan.plot <- plot.fun(var='contactOnly_index', thedf=plot.df2, time='survey', title="Contact Index - Panel",
         xlab="Survey", ylab="Average Contact Index Score",
         ymin=0.3, ymax=0.7))


```

## Perceptions of Security Index

ECPN sites improved more on the security index than control sites.

```{r}
(inComm.plot <- plot.fun(var='in_cw', thedf=plot.df, time='survey', title="Perceptions of Physical Security - Community", 
         xlab="Survey", ylab="Average Perceptions of Physical Security Index Score",
         ymin=0.3, ymax=0.7))

png(file="inComm_plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
inComm.plot
dev.off()
```

Control gets much worse, part gets a little worse and non-part gets a little better.

```{r}
(inPan.plot <- plot.fun(var='in_cw', thedf=plot.df2, time='survey', title="Perceptions of Physical Security - Panel",
         xlab="Survey", ylab="Average Perceptions of Physical Security Index Score",
         ymin=0.3, ymax=0.7))

png(file="inPan_plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
inPan.plot
dev.off()
```


## Placebo plot

Communities: Treatment gets _more_ accepting of violence, Control gets less accepting.  If there was SDB, we would expect the opposite.

```{r}
(vioComm.plot <- plot.fun(var='vio_cw', thedf=plot.df, time='survey', title="Attitudes towards Violence - Community", 
         xlab="Survey", ylab="Average Violence Index Score",
         ymin=0.1, ymax=0.6))

png(file="vioComm_plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
vioComm.plot
dev.off()
```

Panel: All groups become less violence-accepting at ~the same rate.

```{r}
(vioPan.plot <- plot.fun(var='vio_cw', thedf=plot.df2, time='survey', title="Attitudes towards Violence - Individual",
         xlab="Survey", ylab="Average Attitudes towards Violence Index Score",
         ymin=0.1, ymax=0.6))

png(file="vioPan_plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
vioPan.plot
dev.off()
```


**************************
After this point, less important plots.



**************************





## List Experiment

High values are bad here.

ECPN sites decreased less than control sites on list experiment.  A measure of prejudice where high values mean a greater proportion of people expressing anger at "interacting with the outgroup in the market."

<!--Lots of places have negative prejudice at endline (fewer angry with 4 item list than 3 item list).-->

```{r}
(listComm.plot <- plot.fun(var='list_exp', thedf=plot.df, time='survey', title="List Experiment", 
         xlab="Survey", ylab="Average Difference Between 3 Item and 4 Item List",
         ymin=-0.35, ymax=0.35))

png(file="listComm_plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
listComm.plot
dev.off()

```


## Percent Experiment

ECPN sites and control sites stayed the same on the percent experiment.  This percent experiment is a measure of prejudice where lower scores indicate less willingness to join a group/live in a community as the percentage of outgroup members in the community increase from 5/25/50/75 percent.

```{r}
(randComm.plot <- plot.fun(var='rand_lm', thedf=plot.df, time='survey', title="Percent Experiment", 
         xlab="Survey", ylab="Average Change in Relationship Between % Outgroup Members and Joining Group/Living in Community",
         ymin=-0.004, ymax=0.004))

```

Making a better graph by showing the 75% to 5% drop for TR and Co at baseline and endline (4 lines, each with 4 points).

```{r}
rand.df$tr2 <- ifelse(rand.df$treatment %in% 1, "Treatment", "Control")
rand.df$treatmentSurvey <- interaction(rand.df$tr2, rand.df$survey)
rand.df$tr2 <- NULL
rand.df <- rand.df[!is.na(rand.df$rand_condition),] # remove ppl who refused to answer, so we don't get an NA category

plot2.df <- rand.df %>% 
  select(treatment,survey,treatmentSurvey, community, rand_outcome, rand_condition) %>%
  dplyr::group_by(treatmentSurvey, rand_condition) %>%
  dplyr::summarise(randOut=mean(rand_outcome, na.rm=T)) %>%
  as.data.frame()
levels(plot2.df$treatmentSurvey) <- c("Co-Base", "Tr-Base", "Co-End", "Tr-End")
plot2.df$SurveyGroup <- ordered(plot2.df$treatmentSurvey, 
                                    levels = c("Tr-Base", "Tr-End", "Co-Base", "Co-End"))

(randComm.plot2 <- ggplot(data=plot2.df, aes(x=factor(rand_condition), y=randOut, group=SurveyGroup)) +
  geom_line(aes(color=SurveyGroup))+
  geom_point(aes(color=SurveyGroup))+
  geom_text(aes(x=2.6, y=0.60, label="Tr-End"), color="firebrick4", size=3.5) + 
  geom_text(aes(x=2.6, y=0.505, label="Co-End"), color="deepskyblue4", size=3.5) +
  geom_text(aes(x=2.6, y=0.455, label="Tr-Base"), color="firebrick2", size=3.5) + 
  geom_text(aes(x=2.6, y=0.395, label="Co-Base"), color="deepskyblue", size=3.5) + 
  coord_cartesian(ylim = c(min(plot2.df['randOut'])-0.1, max(plot2.df['randOut'])+0.1)) +
  ggtitle("Percent Experiment") +
  theme_bw() +
  theme(panel.grid.major = element_blank()) +
  theme(plot.title = element_text(size=18)) +
  xlab("Percentage Outgroup Members") +
  ylab("Percentage Subjects Willing to Join/Live") + 
  scale_color_manual(values=c("firebrick2", "firebrick4", "deepskyblue", "deepskyblue4"), guide=F))

png(file="randComm_plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
randComm.plot2
dev.off()

```


Maybe it's better to show the difference between baseline and endline at each proportion outgroup. So lines for Tr and Co at each % outgroup members.

```{r}
plot3.df <- rand.df %>% 
  select(treatment,survey, community, rand_outcome, rand_condition) %>%
  dplyr::group_by(treatment, rand_condition) %>%
  dplyr::summarise(randOut_end=mean(rand_outcome[survey %in% 1], na.rm=T), 
                   randOut_base=mean(rand_outcome[survey %in% 0]),
                   randOut=randOut_end-randOut_base) %>%
  as.data.frame()
plot3.df$Treatment <- ifelse(plot3.df$treatment %in% 1, "Treatment", "Control")
plot3.df$Treatment <- ordered(plot3.df$Treatment, levels=c("Treatment", "Control"))

(randComm.plot3 <- ggplot(data=plot3.df, aes(x=factor(rand_condition), y=randOut, group=Treatment)) +
  geom_line(aes(color=Treatment))+
  geom_point(aes(color=Treatment))+
  coord_cartesian(ylim = c(min(plot3.df['randOut'])-0.05, max(plot3.df['randOut'])+0.05)) +
  ggtitle("Percent Experiment") +
  theme_bw() +
  theme(panel.grid.major = element_blank()) +
  theme(plot.title = element_text(size=18)) +
  xlab("Percentage Outgroup Members") +
  ylab("Percentage Subjects Willing to Join/Live"))
```

Nevermind, that's not better.

### Percent Experiment -- Panel/Ind Data

```{r}
panel.df$tr_f <- droplevels(interaction(panel.df$treatment, panel.df$committee))
panel.df$tr2 <- ifelse(panel.df$tr_f %in% "1.1", "Part", 
                       ifelse(panel.df$tr_f %in% "1.0", "Non", 
                              ifelse(panel.df$tr_f %in% "0.0", "Control", NA)))

## need to remake dataset to have TR2, SVY, COND, OUTCOME
rand_ind.df1 <- panel.df[,c("tr2", "rand_condition_y0", "rand_condition_y1", "rand_outcome_y0", "rand_outcome_y1", "id_num")]
rand_baseline <- panel.df[,c("tr2", "rand_condition_y0", "rand_outcome_y0")]
names(rand_baseline) <- gsub("_y0", "", names(rand_baseline))
rand_baseline$survey <- "base"
rand_endline <- panel.df[,c("tr2", "rand_condition_y1", "rand_outcome_y1")]
names(rand_endline) <- gsub("_y1", "", names(rand_endline))
rand_endline$survey <- "end"
rand_ind.df <- rbind(rand_baseline, rand_endline)
rand_ind.df$treatmentSurvey <- interaction(rand_ind.df$tr2, rand_ind.df$survey)

rand_ind.df2 <- rand_ind.df %>% dplyr::group_by(treatmentSurvey, rand_condition) %>%
  dplyr::summarise(randOut=mean(rand_outcome, na.rm=T)) %>%
  as.data.frame()
levels(rand_ind.df2$treatmentSurvey) <- c("Co-Base", "Non-Base", "Part-Base", "Co-End", "Non-End", "Part-End")
rand_ind.df2$SurveyGroup <- ordered(rand_ind.df2$treatmentSurvey, 
                                    levels = c("Part-Base", "Part-End", "Non-Base", "Non-End", "Co-Base", "Co-End"))

(randPan.plot <- ggplot(data=rand_ind.df2, aes(x=factor(rand_condition), y=randOut, group=SurveyGroup)) +
  geom_line(aes(color=SurveyGroup))+
  geom_point(aes(color=SurveyGroup))+
  geom_text(aes(x=4.3, y=0.55, label="Part-End"), color="firebrick4", size=3.5) + 
  geom_text(aes(x=4.3, y=0.34, label="Co-End"), color="deepskyblue4", size=3.5) +
  geom_text(aes(x=4.3, y=0.31, label="Part-Base"), color="firebrick2", size=3.5) + 
  geom_text(aes(x=4.3, y=0.45, label="Co-Base"), color="deepskyblue", size=3.5) + 
  geom_text(aes(x=4.3, y=0.405, label="Non-Base"), color="palegreen2", size=3.5) + 
  geom_text(aes(x=4.3, y=0.61, label="Non-End"), color="palegreen4", size=3.5) + 
  coord_cartesian(ylim = c(min(rand_ind.df2['randOut'])-0.05, max(rand_ind.df2['randOut'])+0.05)) +
  ggtitle("Percent Experiment") +
  theme_bw() +
  theme(panel.grid.major = element_blank()) +
  theme(plot.title = element_text(size=18)) +
  xlab("Percentage Outgroup Members") +
  ylab("Percentage Subjects Willing to Join/Live") + 
  scale_color_manual(values=c("firebrick2", "firebrick4", "palegreen2", "palegreen4", "deepskyblue", "deepskyblue4" ), guide=F))

png(file="randPan_plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
randPan.plot
dev.off()

```

Again, maybe it's better to show the _difference_ between baseline and endline at each proportion outgroup. So lines for Part, Non, and Co at each % outgroup members.

```{r}
rand_ind.df3 <- rand_ind.df %>% dplyr::group_by(tr2, rand_condition) %>%
  dplyr::summarise(randOut_end=mean(rand_outcome[survey %in% "end"], na.rm=T),
                   randOut_base=mean(rand_outcome[survey %in% "base"], na.rm=T),
                   randOut=randOut_end - randOut_base) %>%
  as.data.frame()

rand_ind.df3$Treatment <- rand_ind.df3$tr2
#plot3.df$Treatment <- ordered(plot3.df$Treatment, levels=c("Treatment", "Control"))

(randPan.plot3 <- ggplot(data=rand_ind.df3, aes(x=factor(rand_condition), y=randOut, group=Treatment)) +
  geom_line(aes(color=Treatment))+
  geom_point(aes(color=Treatment))+
  coord_cartesian(ylim = c(min(rand_ind.df3['randOut'])-0.05, max(rand_ind.df3['randOut'])+0.05)) +
  ggtitle("Percent Experiment") +
  theme_bw() +
  theme(panel.grid.major = element_blank()) +
  theme(plot.title = element_text(size=18)) +
  xlab("Percentage Outgroup Members") +
  ylab("Percentage Subjects Willing to Join/Live"))
```




## Endorsement Experiment

ECPN sites decreased less than control sites on the endorsement experiment.  This endorsement experiment is a measure of prejudice where respondents are asked their support for a public policy.  Half are asked their support when the policy is endorsed by the outgroup.  The greater the decrease in support due to the outgroup endorsement, the higher the prejudice.

Both groups have mildly negative response to outgroup endorsement at baseline.  Both groups have more negative response at endline, but control response changes the most negatively.

```{r}
(endComm.plot <- plot.fun(var='end_exp', thedf=plot.df, time='survey', title="Endorsement Experiment", 
         xlab="Survey", ylab="Average Change in Support for Policy Endorsed by Outgroup",
         ymin=-0.6, ymax=0))

png(file="endComm_plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
endComm.plot
dev.off()
```

Individual-level graph. chris: here.

```{r}
# need a plot with the relationship at baseline for Part, Non, and C, then the relationship at endline for Part, Non, and Co.  
## Probably need the relationsip for each TR group in each community to do any analysis.
## aggregating all the TR-Endorse, TR-Generic, CO-Endorse, CO-Generic
endInd_df <- panel.df[,c("tr2", "end_condition_y0", "end_condition_y1",
                         "end_outcome_y0", "end_outcome_y1", "state", "farm_pastor", "community")]

test <- endInd_df %>% dplyr::group_by(community, tr2) %>%
  dplyr::summarise_all(mean,na.rm=T)
lm(end_outcome_y0~end_condition_y0*tr2, data=test)
lm(end_outcome_y1~end_condition_y1*tr2, data=test)

# ignoring communities
part <- endInd_df[endInd_df$tr2 %in% "Part",]
non <- endInd_df[endInd_df$tr2 %in% "Non",]
con <- endInd_df[endInd_df$tr2 %in% "Control",]

part_baseline <- coefficients(lm(end_outcome_y0~end_condition_y0, data=part))[2]
part_endline <- coefficients(lm(end_outcome_y1~end_condition_y1, data=part))[2]

non_baseline <- coefficients(lm(end_outcome_y0~end_condition_y0, data=non))[2]
non_endline <- coefficients(lm(end_outcome_y1~end_condition_y1, data=non))[2]

con_baseline <- coefficients(lm(end_outcome_y0~end_condition_y0, data=con))[2]
con_endline <- coefficients(lm(end_outcome_y1~end_condition_y1, data=con))[2]




(endInd.plot <- plot.fun(var='end_exp', thedf=plot.df1, time='survey', title="Endorsement Experiment", 
         xlab="Survey", ylab="Average Change in Support for Policy Endorsed by Outgroup",
         ymin=-0.6, ymax=0.2))


```


## Public Goods Game

Not a before after plot, since this was just at endline.  Barplot for donate at all and donate amount.

```{r}
# want a plot that shows Tr/Co on X-axis with bars for each outcome (donate at all, donate amount), and Y-axis is percent for donate at all (0-1) & amount for donate amount (0-1000)

## Make a df with obs that are comm-outcome, vars for community and value amount
pgg.df <- ag.df %>% select(pgp_donate_end, pgp_amount_end, treatment)
pgg.df <- reshape2::melt(pgg.df, id="treatment")
pgg.df <- pgg.df %>% dplyr::group_by(treatment,variable) %>% 
  summarise(Value=mean(value)) %>%
  as.data.frame()

#putting outcomes on same scale
pgg.df[pgg.df$variable %in% "pgp_amount_end", 'Value'] <- pgg.df[pgg.df$variable %in% "pgp_amount_end", 'Value']/1000
colnames(pgg.df)[colnames(pgg.df)=="variable"] <- "Outcome"
levels(pgg.df$Outcome) <- c("Made Donation", "Donation Amount")
pgg.df$Treatment <- as.factor(ifelse(pgg.df$treatment %in% 1, "ECPN", "Non-ECPN"))
pgg.df$Treatment <- ordered(pgg.df$Treatment, levels = c("ECPN", "Non-ECPN"))

(pggComm.plot <- ggplot(data=pgg.df, aes(x=Outcome, y=Value, fill=Treatment)) +
  geom_bar(stat="identity", position="dodge")+
  scale_fill_manual(values=setNames(color.codes, grps)) +
  ggtitle("Public Goods Game") +
  theme_bw() +
  theme(panel.grid.major = element_blank()) +
  theme(plot.title = element_text(size=18)) +
  xlab("PGG Outcome") +
  #ylab("Percent Donating") +
  scale_y_continuous(
    "Percent Donating", 
    sec.axis = sec_axis(~ . * 1000, name = "Donation Amount")))

png(file="pggComm_plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
pggComm.plot
dev.off()

# Individual


# Panel
## Make a df with obs that are comm-outcome, vars for community and value amount
panel.df$tr2 <- droplevels(interaction(panel.df$treatment, panel.df$committee))
pgg.df2 <- panel.df %>% select(pgp_donate_y1, pgp_amount_y1, tr2)
pgg.df2 <- reshape2::melt(pgg.df2, id="tr2")
pgg.df2 <- pgg.df2 %>% dplyr::group_by(tr2,variable) %>% 
  summarise(Value=mean(value)) %>%
  as.data.frame()

##putting outcomes on same scale
pgg.df2[pgg.df2$variable %in% "pgp_amount_y1", 'Value'] <- pgg.df2[pgg.df2$variable %in% "pgp_amount_y1", 'Value']/1000
colnames(pgg.df2)[colnames(pgg.df2)=="variable"] <- "Outcome"
levels(pgg.df2$Outcome) <- c("Made Donation", "Donation Amount")
pgg.df2$tr2 <- as.factor(as.character(pgg.df2$tr2))
levels(pgg.df2$tr2) <- c("Control", "Non-Part", "Part")
pgg.df2$tr2 <- ordered(pgg.df2$tr2, levels = c("Part", "Non-Part", "Control"))
pgg.df2$Treatment <- pgg.df2$tr2

## Plot
(pggPan.plot <- ggplot(data=pgg.df2, aes(x=Outcome, y=Value, fill=Treatment)) +
  geom_bar(stat="identity", position="dodge")+
  scale_fill_manual(values=setNames(color.codes, grps)) +
  ggtitle("Public Goods Game") +
  theme_bw() +
  theme(panel.grid.major = element_blank()) +
  theme(plot.title = element_text(size=18)) +
  xlab("PGG Outcome") +
  #ylab("Percent Donating") +
  scale_y_continuous(
    "Percent Donating", 
    sec.axis = sec_axis(~ . * 1000, name = "Donation Amount")))

png(file="pggPan_plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
pggPan.plot
dev.off()
```


# Density Plots

```{r}
load("nullPs.Rdata")
load("GlobP_un.Rdata")
load("thep.Rdata")

load("p_nullPs.Rdata")
load("theGlobP_approx.Rdata")
load("p_thep_approx.Rdata")

```

Community

```{r}
png(file="nullDist_plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))

plot(density(nullPs),
     main="Null Distribution of p-values: Community Data")
abline(v=GlobP_un)

dev.off()

# the corrected p
thep

```

Panel

```{r}
png(file="p_nullDist_plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))

plot(density(p_nullPs),
     main="Null Distribution of p-values: Panel Data")
abline(v=theGlobP_approx)

dev.off()

# the corrected p
p_thep_approx
```

# Save plots

For use later.

```{r}
thing <- grep(".plot",names(.GlobalEnv),value=TRUE)
#Pattern1_list<-do.call("list",mget(thing)) # show the graph of all objects


save(endComm.plot,   randComm.plot,  conComm.plot,   outInd.plot,    shareInd.plot,  clashComm.plot, resComm.plot, 
     outComm.plot,   listComm.plot,  inInd.plot,     clashInd.plot,  inComm.plot,    cohComm.plot,   cohInd.plot, 
     resInd.plot, shareComm.plot, conInd.plot, randComm.plot2, randComm.plot3, pggComm.plot, 
     clashPan.plot, resPan.plot, inPan.plot, sharePan.plot, conPan.plot, outPan.plot, cohPan.plot, pggPan.plot,
     file='ecpn_plots.Rdata') # must be easier way to save objects that match a pattern...

```


```{r, eval=F, include=F}
# save plot.dfs for rebecca ot see
plot.df_share <- plot.df[,1:15]
plot.df1_share <- plot.df1[,1:12]
plot.df2_share <- plot.df2[,1:12]
pgg.df
pgg.df2

save(plot.df_share, plot.df1_share, plot.df2_share,pgg.df, pgg.df2,
     file='z-did_plot_dfs_share.Rdata')

```