---
title: "g-aggAnalysis for academic paper"
output:
  word_document:
    toc: yes
  pdf_document:
    number_sections: yes
    toc: yes
  html_document:
    df_print: paged
    toc: yes
---

<!--Chris: notes

Want to replace all lm() with lm_lin() but lm_lin() does not allow me to vary treatment in a function.-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(76465)
rm(list=ls())
load("../c_creating_dataframes/f-aggregateComms_ap.Rdata")
load("../c_creating_dataframes/rand_df.Rdata")
#load("f-aggregateData_together.Rdata")
#load("rand_df_together.Rdata")

library(NPC)
library(dplyr)
library(mosaic)
library(estimatr)
library(robustbase)
library(quantreg)
library(sandwich)
library(clubSandwich)
library(lmtest)
library(coin)

#author: "cdgrady21"
#date: '`r format(Sys.Date(), "%B %d, %Y")`'


#True p-value function.  Don't need covariate adjustment to absorb error.  True p's Especially necessary with community level analysis, because we have a small number of clusters.  Treatment assigned at PSU level.

# Differencing
true.fun1 <- function(var, tr, nsims=3000, dat=ag.df)
{
  if(grepl("resid", var)){
    thelm <- lm(dat[,var]~dat[,tr], data=dat)
    thecoef <-coef(thelm)[2]
    
    rand.coef = rep(NA,nsims)
    for(i in 1:nsims){
      rand.nas <- sample(unique(dat$psu[dat$state %in% "nas"]), size=6)
      rand.ben <- sample(unique(dat$psu[dat$state %in% "ben"]), size=4)
      rand <- c(as.character(rand.nas), as.character(rand.ben))
      rand.samp <- dat
      rand.samp$treatment <- ifelse(rand.samp$psu %in% rand, 1, 0)
      tr.lm <- lm(tr_fmla,rand.samp)
      lm.tr_resid<-resid(tr.lm)
      rand.samp[names(lm.tr_resid),"tr_resid"]<-lm.tr_resid
      
      lm.null <- lm(rand.samp[,var]~rand.samp[,tr], data=rand.samp)
      rand.coef[i] <- summary(lm.null)$coefficients[2,1]
    }
  }
  else if(tr=="treatment"){
    thelm <- lm(dat[,var]~dat[,tr]+state, data=dat)
    thecoef <-coef(thelm)[2]
    
    rand.coef = rep(NA,nsims)
    for(i in 1:nsims){
      rand.nas <- sample(unique(dat$psu[dat$state %in% "nas"]), size=6)
      rand.ben <- sample(unique(dat$psu[dat$state %in% "ben"]), size=4)
      rand <- c(as.character(rand.nas), as.character(rand.ben))
      rand.samp <- dat
      rand.samp[,tr] <- ifelse(rand.samp$psu %in% rand, 1, 0)
     
      lm.null <- lm(rand.samp[,var]~rand.samp[,tr]+state, data=rand.samp)
      rand.coef[i] <- summary(lm.null)$coefficients[2,1]
      }
  }
  else{
    thelm <- lm(dat[,var]~dat[,tr]+state, data=dat)
    thecoef <-coef(thelm)[2]
    
    rand.coef = rep(NA,nsims)
    for(i in 1:nsims){
      rand.samp <- dat %>% dplyr::group_by(state) %>% # for indices predicting indices, just shuffle within state.
        mutate(newtr = shuffle(.data[[tr]])) %>%
        as.data.frame(.)
      
      lm.null <- lm(rand.samp[,var]~rand.samp[,'newtr']+state, data=rand.samp)
      rand.coef[i] <- summary(lm.null)$coefficients[2,1]
    }
  }
  thep <- mean(rand.coef>thecoef)
  thedf <- data.frame(coef=thecoef,truep=thep)
  rownames(thedf) <- paste0(var, "~",tr)
  return(thedf)
}
#true.fun(var='x_index', tr='treatment')
#true.fun(var='x_cw', tr='treatment')
#true.fun(var='cohes_cw', tr='bene_cw')
#true.fun(var='x_cw_resid', tr='tr_resid') # doing this with resids #1 doesn't make sense to me, #2 doesn't change results, and #3 takes a long time.
## would make sense if there was a confounder, but this is a randomized experiment so should not have confounders. Could maybe use error reduction.


######## Controlling For
true.fun <- function(var, tr, nsims=3000, dat=ag.df)
{
  if(grepl("resid", var)){
    thelm <- lm(dat[,var]~dat[,tr], data=dat)
    thecoef <-coef(thelm)[2]
    
    rand.coef = rep(NA,nsims)
    for(i in 1:nsims){
      rand.nas <- sample(unique(dat$psu[dat$state %in% "nas"]), size=6)
      rand.ben <- sample(unique(dat$psu[dat$state %in% "ben"]), size=4)
      rand <- c(as.character(rand.nas), as.character(rand.ben))
      rand.samp <- dat
      rand.samp$treatment <- ifelse(rand.samp$psu %in% rand, 1, 0)
      tr.lm <- lm(tr_fmla,rand.samp)
      lm.tr_resid<-resid(tr.lm)
      rand.samp[names(lm.tr_resid),"tr_resid"]<-lm.tr_resid
      
      lm.null <- lm(rand.samp[,var]~rand.samp[,tr], data=rand.samp)
      rand.coef[i] <- summary(lm.null)$coefficients[2,1]
    }
  }
  else if(tr=="treatment" & (grepl("end", var) | grepl("y1", var))){
    thelm <- lm(dat[,var]~dat[,tr]+state, data=dat)
    thecoef <-coef(thelm)[2]
    
    rand.coef = rep(NA,nsims)
    for(i in 1:nsims){
      rand.nas <- sample(unique(dat$psu[dat$state %in% "nas"]), size=6)
      rand.ben <- sample(unique(dat$psu[dat$state %in% "ben"]), size=4)
      rand <- c(as.character(rand.nas), as.character(rand.ben))
      rand.samp <- dat
      rand.samp[,tr] <- ifelse(rand.samp$psu %in% rand, 1, 0)
     
      lm.null <- lm(rand.samp[,var]~rand.samp[,tr]+state, data=rand.samp)
      rand.coef[i] <- summary(lm.null)$coefficients[2,1]
      }
  }
  else if(tr=="treatment" & !(grepl("end", var) | grepl("y1", var))){
    thelm <- lm(dat[,paste0(var,"_end")]~dat[,tr]+dat[,paste0(var,"_base")]+state, data=dat)
    thecoef <-coef(thelm)[2]
    
    rand.coef = rep(NA,nsims)
    for(i in 1:nsims){
      rand.nas <- sample(unique(dat$psu[dat$state %in% "nas"]), size=6)
      rand.ben <- sample(unique(dat$psu[dat$state %in% "ben"]), size=4)
      rand <- c(as.character(rand.nas), as.character(rand.ben))
      rand.samp <- dat
      rand.samp[,tr] <- ifelse(rand.samp$psu %in% rand, 1, 0)
     
      lm.null <- lm(rand.samp[,paste0(var,"_end")]~rand.samp[,tr]+dat[,paste0(var,"_base")]+state, data=rand.samp)
      rand.coef[i] <- summary(lm.null)$coefficients[2,1]
      }
  }
  else if(grepl("end", var) | grepl("y1", var)){
    thelm <- lm(dat[,var]~dat[,tr]+state, data=dat)
    thecoef <-coef(thelm)[2]
    
    rand.coef = rep(NA,nsims)
    for(i in 1:nsims){
      rand.samp <- dat %>% dplyr::group_by(state) %>% # for indices predicting indices, just shuffle within state.
        mutate(newtr = shuffle(.data[[tr]])) %>%
        as.data.frame(.)
      
      lm.null <- lm(rand.samp[,var]~rand.samp[,'newtr']+state, data=rand.samp)
      rand.coef[i] <- summary(lm.null)$coefficients[2,1]
    }
  }
  else if(!grepl("end", var) | grepl("y1", var)){
    thelm <- lm(dat[,paste0(var,"_end")]~dat[,tr]+dat[,paste0(var,"_base")]+state, data=dat)
    thecoef <-coef(thelm)[2]
    
    rand.coef = rep(NA,nsims)
    for(i in 1:nsims){
      rand.samp <- dat %>% dplyr::group_by(state) %>% # for indices predicting indices, just shuffle within state.
        mutate(newtr = shuffle(.data[[tr]])) %>%
        as.data.frame(.)
      
      lm.null <- lm(rand.samp[,paste0(var,"_end")]~rand.samp[,'newtr']+dat[,paste0(var,"_base")]+state, data=rand.samp)
      rand.coef[i] <- summary(lm.null)$coefficients[2,1]
    }
  }
  
  thep <- mean(rand.coef>thecoef)
  thedf <- data.frame(coef=thecoef,truep=thep)
  rownames(thedf) <- paste0(var, "~",tr)
  return(thedf)
}
#true.fun(var='x_index', tr='treatment')
#true.fun(var='x_cw', tr='treatment')
#true.fun(var='cohes_cw', tr='bene_cw')
#true.fun(var='x_cw_resid', tr='tr_resid') # doing this with resids #1 doesn't make sense, #2 doesn't change results, and #3 takes a long time.
## would make sense if there was a confounder, but this is a randomized experiment so should not have confounders.
#true.fun(var="pgp_amount_end", tr="treatment")
#true.fun('pgp_donate_end', 'bene_cw')
#true.fun('rMean', 'treatment')
#true.fun1('rMean', 'treatment')



# Which function to use?
strat.fun <- function(var){
  thesd <- sd(ag.df[[var]])*.2
  thediff <- abs(mosaic::mean(ag.df[[var]]~ag.df$treatment)[1]-mosaic::mean(ag.df[[var]]~ag.df$treatment)[2])
  thebal <- thediff-thesd
  if(thebal<0){
    return("Controlling-for: true.fun")
  }
  if(thebal>=0){
    return("Difference: true.fun1")
  }
  else(return("Fail"))
}
#strat.fun("x_cw_base")

```
```{r, eval=F, include=F}
# I prefer the SD method, but could also use lin hypothesis test or an equivalence test.
## issue with these: we are super low powered, so no baseline differences will be stat sig.  And equivalence test will always say "not same, not diff"

# Hypothesis test
(x1_test <- lm_lin(x_cw_base~treatment, covariates= ~state, data=ag.df, clusters=psu))

# equivalence
TOSTtwo(m1=mean(ag.df$x_cw_base[ag.df$treatment %in% 0]), m2=mean(ag.df$x_cw_base[ag.df$treatment %in% 1]), 
        sd1=sd(ag.df$x_cw_base[ag.df$treatment %in% 0]), sd2=sd(ag.df$x_cw_base[ag.df$treatment %in% 1]), 
        n1=length(unique(ag.df$comm[ag.df$treatment %in% 0])), n2=length(unique(ag.df$comm[ag.df$treatment %in% 1])),
        low_eqbound_d=-0.1, high_eqbound_d=0.1, alpha = 0.05)

TOSTtwo(m1=mean(ag.df$contactOnly_cw_base[ag.df$treatment %in% 0]), m2=mean(ag.df$contactOnly_cw_base[ag.df$treatment %in% 1]), 
        sd1=sd(ag.df$contactOnly_cw_base[ag.df$treatment %in% 0]), sd2=sd(ag.df$contactOnly_cw_base[ag.df$treatment %in% 1]), 
        n1=length(unique(ag.df$comm[ag.df$treatment %in% 0])), n2=length(unique(ag.df$comm[ag.df$treatment %in% 1])),
        low_eqbound_d=-0.01, high_eqbound_d=0.01, alpha = 0.05)
```

# Subsets

Look at farmers and pastoralists separately.

```{r}
farmers <- ag.df[grepl(".farmers", ag.df$comm),]
pastors <- ag.df[grepl(".pastor", ag.df$comm),]
```

Look at states separately.

```{r}
nas <- ag.df[ag.df$state %in% "nas",]
ben <- ag.df[ag.df$state %in% "ben",]

```


# Hypotheses

Theory of Change: Intergroup contact improves intergroup attitudes, especially trust, which allows groups to bargain and reduce conflict.

Primary Outcomes:
    - Intergroup affect (direct questions on trust/social distance, endorsement experiment)
    - Intergroup Contact other than ECPN (direct Q, markets/social events, and hypothetical with randomization experiment)
    - Insecurity (how much fear from violence prevented people from working, going out at night, getting water, etc.)

Secondary Outcomes:
    - Knowledge about violent conflict
    - Public Goods Game

Potential Mediators:
    - Reduced threat
    - Empathy
    - Ingroup Expansion
    - Potential Benefit

Placebo: Violence

# Variable list

- trust/distance: trustVars, distVars, 
- bargaining: bargVars, 
- Insecurity: vioExpVars, inVars, conVioEffVars, 
- Awareness: awareVars and/or clashVars, 
- Coordination: pgp_donate, pgp_amount, 
- Contact: contactOnly, randExp/percExp, market/social observation
- Threat: threatVars
- Ingroup expansion: cohesVars1
- Empathy: cohes2vars OR empVars and perspVars
- benefit: beneVar OR beneVarsReal (endline only)
- Affect: list experiment, endorsement experiment

# Testing Outcomes

We will use the differencing strategy when treatment and control are not balanced at baseline.  We will use the controlling-for strategy when treatment and control are balanced at baseline.  We say the groups are balanced if they are within 0.2 SDs of eachother at baseline.

true.fun1 is with differencing. true.fun is controlling-for. strat.fun tells us which to use.


************

# Intergroup Trust

**allTrust**: `r paste(allTrustVars, collapse=", ")`

```{r}
# select
strat.fun("allTrust_cw_base")

# true pvals
(trust1 <- true.fun('allTrust_cw', 'treatment'))
trust_ind <- true.fun('allTrust_index', 'treatment')

# group
(trust1_farm <- true.fun('allTrust_cw', 'treatment', dat=farmers))
(trust1_past <- true.fun('allTrust_cw', 'treatment', dat=pastors))

# state
lm_robust(allTrust_cw ~ treatment, clusters = psu, data = nas)
lm_robust(allTrust_cw ~ treatment, clusters = psu, data = ben)

# both
lm_robust(allTrust_cw ~ treatment * state, clusters=psu, data=farmers)
lm_robust(allTrust_cw ~ treatment * state, clusters=psu, data=pastors)
```

The coefficient of `r round(trust1$coef,5)` is  `r round(trust1$coef/sd(ag.df$allTrust_cw),3)` standard deviations.

**trust only**: `r paste(trustVars, collapse=", ")`

```{r}
# select
strat.fun("trust_cw_base")

# true pvals
#(trust2 <- true.fun('trust_cw', 'treatment'))
(trust2 <- true.fun1('trust_cw', 'treatment'))
#true.fun("outgroup_atts_group.trust_x", 'treatment') # one 
#true.fun("social_cohesion_group.trust_area", 'treatment')
```

The coefficient of `r round(trust2$coef,5)` is  `r round(trust2$coef/sd(ag.df$trust_cw),3)` standard deviations.


**social distance**: `r paste(distVars, collapse=", ")`

```{r}
# select
strat.fun("dist_cw_base")

# true pvals
#(dist1 <- true.fun('dist_cw', 'treatment'))
(dist1 <- true.fun1('dist_cw', 'treatment'))

# strat.fun("dist_index_base")
#(dist1 <- true.fun1('dist_index', 'treatment'))

#true.fun1("comfort_group.field", 'treatment') # no effect
#true.fun1("comfort_group.marry", 'treatment')
#true.fun1("comfort_group.share_meal", 'treatment')
#true.fun1("comfort_group.trade_goods", 'treatment')
#true.fun1("comfort_group.watch_animals", 'treatment') # no effect

#summary(ag.df[,c("comfort_group.field_base", "comfort_group.field_end", "comfort_group.field",
#         "comfort_group.watch_animals_base", "comfort_group.watch_animals_end", "comfort_group.watch_animals",
#         "comfort_group.share_meal_base", "comfort_group.share_meal_end", "comfort_group.share_meal")])
```

The coefficient of `r round(dist1$coef,5)` is  `r round(dist1$coef/sd(ag.df$dist_cw),3)` standard deviations.


**allOutgroup**: `r paste(xVars, collapse=", ")`

```{r}
# select
strat.fun("x_cw_base")

# true pvals
(x1 <- true.fun('x_cw', 'treatment'))
```

The coefficient of `r round(x1$coef,5)` is  `r round(x1$coef/sd(ag.df$x_cw),3)` standard deviations.

```{r,eval=F}
# look at trust alone
strat.fun("outgroup_atts_group.trust_x_base")
true.fun("outgroup_atts_group.trust_x", "treatment")

strat.fun("social_cohesion_group.trust_area_base")
true.fun("social_cohesion_group.trust_area", "treatment")

# other trust
strat.fun("outgroup_atts_group.trust_ethnic_base")
true.fun("outgroup_atts_group.trust_ethnic", "treatment")

strat.fun("outgroup_atts_group.trust_rel_base")
true.fun1("outgroup_atts_group.trust_rel", "treatment")

# Means
mosaic::mean(ag.df$social_cohesion_group.trust_area_base~ag.df$treatment)
mosaic::mean(ag.df$social_cohesion_group.trust_area_end~ag.df$treatment)

mosaic::mean(ag.df$outgroup_atts_group.trust_x_base~ag.df$treatment)
mosaic::mean(ag.df$outgroup_atts_group.trust_x_end~ag.df$treatment)

mosaic::mean(ag.df$outgroup_atts_group.trust_ethnic_base~ag.df$treatment)
mosaic::mean(ag.df$outgroup_atts_group.trust_ethnic_end~ag.df$treatment)

mosaic::mean(ag.df$outgroup_atts_group.trust_rel_base~ag.df$treatment)
mosaic::mean(ag.df$outgroup_atts_group.trust_rel_end~ag.df$treatment)
```


## Insecurity/Violence Effects

```{r}
# select
strat.fun("in_cw_base")

# true pvals
(in1 <- true.fun1('in_cw', 'treatment'))
in_ind <- true.fun1('in_index', 'treatment')

# select
strat.fun("vioExp_cw_base")

# true pvals
(vioExp1 <- true.fun('vioExp_cw', 'treatment'))


# both state/group
lm_robust(in_cw ~ treatment * state, clusters=psu, data=farmers)
lm_robust(in_cw ~ treatment * state, clusters=psu, data=pastors)
```

## Awareness

```{r}
# select
strat.fun("clash_cw_base")

# true pvals
(clash1 <- true.fun1('clash_cw', 'treatment'))

#aware
strat.fun("clash_group.violence_base")

# true pvals
(aware1 <- true.fun1('clash_group.violence', 'treatment'))

```

TR knows more about clashes.


## Contact

Intergroup interaction variables: `r paste(contactVars[c(1:4,7)], collapse=", ")`

```{r con}
strat.fun("contactOnly_cw_base")
(con1 <- true.fun1('contactOnly_cw', 'treatment'))
strat.fun("contactOnly_index_base")
con_ind <- true.fun1('contactOnly_index', 'treatment')


# both state/group
lm_robust(contactOnly_cw ~ treatment * state, clusters=psu, data=farmers)
lm_robust(contactOnly_cw ~ treatment * state, clusters=psu, data=pastors)
```

The coefficient of `r round(con1$coef,5)` is  `r round(con1$coef/sd(ag.df$contactOnly_cw),3)` standard deviations.

**Robustness check** with alternative measure

```{r, eval=F}
strat.fun("contactOnly_cats_cw_base")
(con1.1 <- true.fun1('contactOnly_cats_cw', 'treatment'))
strat.fun("contactOnly_cats_index_base")
con_ind.1 <- true.fun1('contactOnly_cats_index', 'treatment')

```

## PGP -- Group Coordination

### Donation Amount

```{r}
(pgp1 <- true.fun('pgp_amount_end', 'treatment'))
```

Treatment sites donated less.

### Donate yes/no

```{r}
(pgp2 <- true.fun('pgp_donate_end', 'treatment'))
```


## Bargaining

```{r}
# select
strat.fun("barg_cw_base")

# true pvals
(barg <- true.fun('barg_cw', 'treatment'))
```


## Affect

# Survey Experiments

These all relate to outgroup affect and would probably go somewhere in the outgroup affect category if we didn't include them on their own.

## List Exp

Here we look to see if treatment places changed more positively than control places on the list experiment.  Is the difference between the 3 item and the 4 item question SMALLER at endline than at baseline?

To make "list_exp", we: (1) calculate the 4 item mean and the 3 item mean for each community at baseline and endline, (2) calculate the difference between the 4 item mean and the 3 item mean for each community at baseline and endline, (3) subtract that difference at endline from that difference at baseline.  Higher values good (fewer items "upset or anger" average treatment community members at endline than at baseline, relative to control).

```{r list}
strat.fun("list_exp_base")
(list1 <- true.fun('list_exp', 'treatment'))
```

The coefficient of `r round(list1$coef,5)` is  `r round(list1$coef/sd(ag.df$list_exp),3)` standard deviations.

## Rand Exp

Note: this is not a "Randomized Response" experiment, which, similar to a list exp, tries to get honest responses from respondents.  This is an experiment that asks respondents if they would join a group or join a community with **5%/25%/50%/75%** outgroup members.  Higher values means more people say "Yes".  

Each community is assigned their relationship between Outgroup % and "Yes" (how much less likely they are to say "Yes" as outgroup % increases) at baseline and endline.  rand_lm is that relationship at endline - that relationship at baseline.  Higher values good.

```{r rand}
strat.fun("rand_lm_base")
(rand1 <- true.fun1('rand_lm', 'treatment'))
```

There is no difference between treatment and control communities in their willingness to join groups/communities with increasing numbers of outgroup members.

### Rand Exp 2

The analysis of the linear relationship between % outgroup and willingness to join/live fails if the treatment influences _all_ categories, including the lowest 5% category.  To determine if there was a wholesale increase at every category, we can instead analyze the percentage of respondents who say "yes" in treatment comms vs. control comms, blocked by percentage outgroup members and clustered at PSU.

```{r}
strat.fun("rMean_base")
(rand2 <- true.fun1('rMean', 'treatment'))
```

## Endorsement Experiment

```{r end}
strat.fun("end_exp_base")
(end1 <- true.fun('end_exp', 'treatment'))
```

The coefficient of `r round(end1$coef,5)` is  `r round(end1$coef/sd(ag.df$end_exp),3)` standard deviations.


# Placebo

**atts towards violence**: `r paste(vioVars, collapse=", ")`

```{r}
# violence
strat.fun("vio_cw_base")
vio1 <- true.fun1("vio_cw", "treatment")
#true.fun("vio_cw", "treatment")
#true.fun1("vio_index", "treatment")
#true.fun("vio_index", "treatment")
```

No effect.  If there was social desirability bias to tell enumerators what they wanted to hear in TR comms but not CO comms, would probably see it here.


******

# Mechanisms

Things that ECPN could work through.  If ECPN improves them,  Do they correlate with attitudes/contact/security?

## Threat

Variables: `r threatVars`

```{r con}
strat.fun("threat_cw_base")
(threat1 <- true.fun('threat_cw', 'treatment'))
#true.fun("threat_group.threat_dis_group.x_threat", 'treatment')

true.fun('allTrust_cw', 'threat_cw')
true.fun('contactOnly_cw', 'threat_cw')
true.fun('in_cw', 'threat_cw')
```

Nothing.  Cannot work through reduced feelings of threat because ECPN does not correlate with feelings of threat.  The coefficient of `r round(threat1$coef,5)` is  `r round(threat1$coef/sd(ag.df$threat_cw),3)` standard deviations.

Threat is negatively correlated with intergroup affect, though.


## Empathy/Perspective-Taking

```{r}
# select
strat.fun("emp_cw_base")

# true pvals
(emp1 <- true.fun1('emp_cw', 'treatment'))
# true.fun1('emp_index', 'treatment') # confirm with index

# empathy and outcomes
(emp_trust <- true.fun('allTrust_cw', 'emp_cw'))
(emp_contact <- true.fun('contactOnly_cw', 'emp_cw'))
(emp_in <- true.fun('in_cw', 'emp_cw'))



# select
strat.fun("persp_cw_base")

# true pvals persp
(persp1 <- true.fun1('persp_cw', 'treatment'))
#true.fun1('persp_cw', 'treatment') # diff coef because _cw is standardized 0-1
#true.fun1('threat_group.x_responsible', 'treatment') #check to make sure identical

# persp and outcomes
(persp_trust <- true.fun('allTrust_cw', 'persp_cw'))
(persp_contact <- true.fun('contactOnly_cw', 'persp_cw'))
(persp_in <- true.fun('in_cw', 'persp_cw'))

```

ECPN maybe increases empathy increases, by these measures (Below 0.10 pvalue).  Empathy correlates with intergroup attitudes; some correlation with security.

ECPN does not cause perspective-taking, but again only one question.  Perspective-taking does correlated with intergroup attitudes, contact, and somewhat security (p<.10).


## Ingroup Expansion

Variables: `r cohesVars1`

```{r con}
strat.fun("expand_cw_base")
(expan1 <- true.fun('expand_cw', 'treatment'))

# expansion and outcomes
(expand_trust <- true.fun('allTrust_cw', 'expand_cw'))
(expand_contact <- true.fun('contactOnly_cw', 'expand_cw'))
(expand_in <- true.fun('in_cw', 'expand_cw'))
```

Nope, ECPN does not increase this.  But change here correlates with intergroup attitudes.


## Benefit

Variables: `r beneVars`

```{r con}
strat.fun("econ_benefit_group.benefit_econ_base")
(bene1 <- true.fun('econ_benefit_group.benefit_econ', 'treatment'))


strat.fun("bene_cw_base")
(bene2 <- true.fun('bene_cw', 'treatment'))

```

Not more likely to say currently benefitting!

```{r, eval=F}
(bene2 <- true.fun1('x_cw', 'bene_cw'))
(bene3 <- true.fun1('cohes_cw', 'bene_cw'))
```




# Save 

For combining pvals across levels of analysis.

```{r save1, eval=F}
combP <- GlobP_un
save(ag.df, combP, file="g-aggAnal.Rdata")

```

For referencing these values

```{r save2}
save.image("g-aggAnalComplete.Rdata")
```

For appendices.  chris: need to add con1.1 for alternative contact coding.

```{r save3}
save(trust_ind, in_ind, con_ind,
     vio1,
     threat1, emp1, persp1, expan1,
     file="z_appendices_ag.Rdata")

```
************

# Testing

```{r, include=F, eval=F}
lm(contactOnly_cw~treatment, ag.df)
lm(contactOnly_cw_end~treatment+contactOnly_cw_base, ag.df)

lm(x_cw~treatment, ag.df)
lm(x_cw_end~treatment+x_cw_base, ag.df)


mean(ag.df$contactOnly_cw[ag.df$treatment %in% 1])
mean(ag.df$contactOnly_cw[ag.df$treatment %in% 0])

mean(ag.df$contactOnly_cw_end[ag.df$treatment %in% 1])-mean(ag.df$contactOnly_cw_base[ag.df$treatment %in% 1])

mean(ag.df$contactOnly_cw_end[ag.df$treatment %in% 0])-mean(ag.df$contactOnly_cw_base[ag.df$treatment %in% 0])

# predict change vs predict end with base examples
set.seed(264398)
size <- 1000
tau<- 0.01
co_base <- 0.5
tr_base <- 0

testfun <- function(size, tau, co_base, tr_base){
  tr <- c(rep(0,size), rep(1,size))
  base <- c(rnorm(size,co_base,1), rnorm(size,tr_base,1))
  t1_noise <- c(rnorm(size,0,0.5), rnorm(size,tau,0.5))
  end <- base+t1_noise
  delt <- end-base
  test <- data.frame(tr=tr,base=base,end=end,delt=delt)
  
  # Method 1 -- predict the change
  sum1 <- summary(lm(delt~tr,test))$coefficients
  m1_coef <- sum1['tr',1]
  m1_p <- sum1['tr',4]
  #c(m1_coef,m1_p)
  
  # Method 2 -- predict t1
  sum2 <- summary(lm(end~tr+base,test))$coefficients
  m2_coef <- sum2['tr',1]
  m2_p <- sum2['tr',4]
  #c(m2_coef,m2_p)
  
  newdf <- data.frame(m1_coef=m1_coef,m1_p=m1_p,m2_coef=m2_coef,m2_p=m2_p)
  
  return(newdf)
  #plot(density(m1_null$tr))
  #plot(density(m2_null$tr))
}

testdf <- do(2000)*testfun(size=1000,tau=0.2,co_base=0,tr_base=0)
testdf$v1_2_diff <- testdf$m1_coef-testdf$m2_coef
summary(testdf$v1_2_diff)
(v1a=summary(testdf$m1_coef))
(v2a=summary(testdf$m2_coef))


v1b=summary(testdf$m1_coef)
v2b=summary(testdf$m2_coef)

testdf$v1_2_p <- testdf$m1_p-testdf$m2_p
summary(testdf$v1_2_p)
summary(testdf$m1_p)
summary(testdf$m2_p)

##########

# DAVE SIMULATIONS ABOUT DIFFERENCING VS CONTROLLING FOR
b1 = b2 = double(1000) # store betas
p1 = p2 = double(1000) # store p-values
for (i in 1:1000) {
    ## make fakedata
    size <- 1000
    tau<- 0.01
    co_base <- 0.5
    tr_base <- 0
    tr <- c(rep(0,size), rep(1,size))
    base <- c(rnorm(size,co_base,1), rnorm(size,tr_base,1))
    t1_noise <- c(rnorm(size,0,0.5), rnorm(size,tau,0.5))
    end <- base+t1_noise
    delt <- end-base
    test <- data.frame(tr=tr,base=base,end=end,delt=delt)

    sum1 = summary(lm(delt~tr,test))$coefficients
    sum2 = summary(lm(end~tr+base,test))$coefficients

    b1[i] = sum1[2, 1]
    p1[i] = sum1[2, 4]
    b2[i] = sum2[2, 1]
    p2[i] = sum2[2, 4]
}

summary(b1)
summary(b2)
summary(b1-b2)
summary(p1)
summary(p2)

plot(density(b1))
lines(density(b2), col = "red")

plot(density(p1))
lines(density(p2), col = "red")

#######











# normal
summary(lm(contactOnly_cw_end~treatment+state+contactOnly_cw_base, ag.df))

# Lin
lm_lin(contactOnly_cw_end ~ treatment, covariates=~state+contactOnly_cw_base, data=ag.df)

# Lin manual
summary(lm(contactOnly_cw_end~treatment*(state+contactOnly_cw_base), ag.df))

# Lin manual robust
ag.df$con_base_md <- ag.df$contactOnly_cw_base - mean(ag.df$contactOnly_cw_base)
ag.df$state_md <- ifelse(ag.df$state %in% "nas", 1, 0)
ag.df$state_md <- ag.df$state_md - mean(ag.df$state_md)
lm_robust(contactOnly_cw_end~treatment*(state_md+con_base_md), ag.df)


# Lin method changes treatment slope?  is it the interaction?
lm_robust(contactOnly_cw_end~treatment+state+contactOnly_cw_base, ag.df)
lm_robust(contactOnly_cw_end~treatment*(state+contactOnly_cw_base), ag.df)

lm_robust(contactOnly_cw_end~treatment+state_md+con_base_md, ag.df)
lm_robust(contactOnly_cw_end~treatment*(state_md+con_base_md), ag.df)

lm_lin(contactOnly_cw_end ~ treatment, covariates=~state+contactOnly_cw_base, data=ag.df)

# Chris note: Need to mean-deviate covariates if going to use interaction terms, otherwise the covariate and its interaction terms are wildly collinear!
```

```{r, eval=F, include=F}
# combined coef for MC report
b1 <- x1$coef/sd(ag.df$x_cw)
b2 <- cohes$coef/sd(ag.df$cohes_cw)
b3 <- pgp1$coef/sd(ag.df$pgp_amount_end)
b4 <- pgp2$coef/sd(ag.df$pgp_donate_end)
b5 <- con1$coef/sd(ag.df$contactOnly_cw)
b6 <- in1$coef/sd(ag.df$in_cw)
b7 <- res1$coef/sd(ag.df$resolve_cw)
allB <- b1+b2+b3+b4+b5+b6+b7

```

```{r, eval=F, include=F}
# my own fisher prod fun, but it's so bad and slow.
# Fisher Product Function
f_prod.fun <- function(ps)
{
  log_ps <- rep(NA,length(ps)) # take natural log of each p
  for(i in 1:length(ps)){
    log_ps[i] <- log(ps[i])
  }
  chiP <- sum(log_ps)*-2 # sum the logged ps, multiply sum by 2
  df <- length(ps)*2
  newp = pchisq(chiP, df, lower.tail = FALSE)
  return(data.frame(chi=chiP, globalp=newp, df=df))
}
system.time(do(1000)*f_prod.fun(fakePs))
badPs <- rep(0.5,4)
f_prod.fun(badPs)
```
