---
title: "ecpn_coefplot_coefs"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
set.seed(357436)

library(plyr)
library(dplyr)
library(tidyr)

load("../d_analysis/g-aggAnalComplete.Rdata")
load("../d_analysis/g2-panelAnalComplete.Rdata")
#rm("thedf")

# Setup Wanted Vars

# coef name list
## aggregate
ag.vars <- c('allTrust_cw', 'contactOnly_cw', "in_cw", 'pgp_amount_end', 'pgp_donate_end',
                               'threat_cw', 'cohes1_cw', 'cohes2_cw',
                               'bene_cw', 'clash_cw', "barg_cw",
             'list_exp', 'rand_lm', 'rMean', 'end_exp')
setdiff(ag.vars, names(ag.df))




## individual
ind.vars <- c('allTrust_cw', 'contactOnly_cw', "in_cw", 'pgp_amount_y1', 'pgp_donate_y1',
                               'threat_cw', 'cohes1_cw', 'cohes2_cw',
                               'bene_cw', 'clash_cw', "barg_cw")
setdiff(ind.vars, names(panel.df))


#Standardize outcomes to effect size, instead of raw.  Since want standardized effect size in coefplot.
## done when made indices
#ag.df[,ag.vars] <- scale(ag.df[,ag.vars])
#panel.df[,ind.vars] <- scale(panel.df[,ind.vars])


# make multi-DF strat.fun
strat.fun <- function(var,thedf){
  thesd <- sd(thedf[[var]])*.2
  thediff <- abs(mosaic::mean(thedf[[var]]~thedf[['treatment']])[1]-mosaic::mean(thedf[[var]]~thedf[["treatment"]])[2])
  thebal <- thediff-thesd
  if(thebal<0){
    return("Controlling-for: true.fun")
  }
  if(thebal>=0){
    return("Difference: true.fun1")
  }
  else(return("Fail"))
}
#strat.fun("x_cw_base", ag.df)
#strat.fun("x_cw_y0", panel.df)
```

## Effect Sizes

Functions to get coefficient from OLS and SD of each variable

```{r}
ag_coef <- c(trust1[[1]], con1[[1]], in1[[1]],
               pgp1[[1]], pgp2[[1]],
               threat1[[1]], expan1[[1]],
               cohes2_1[[1]], bene2[[1]],
               clash1[[1]], barg[[1]],
               list1[[1]], rand1[[1]],
               rand2[[1]], end1[[1]])

# get SD of _base 
ag_SD <- c(sd(ag.df$allTrust_cw_base), sd(ag.df$contactOnly_cw_base), sd(ag.df$in_cw_base),
              sd(ag.df$pgp_amount_end), sd(ag.df$pgp_donate_end),
              sd(ag.df$threat_cw_base), sd(ag.df$cohes1_cw_base),
              sd(ag.df$cohes2_cw_base), sd(ag.df$bene_cw_base),
              sd(ag.df$clash_cw_base), sd(ag.df$barg_cw_base),
              sd(ag.df$list_exp_base), sd(ag.df$rand_lm),
              sd(ag.df$rMean), sd(ag.df$end_exp_base)
              )

pan_coef <- c(p_trustp1[[1]], p_contactp1[[1]], p_inp1[[1]],
               p_pgpp1[[1]], p_pgpp2[[1]],
               p_threatp1[[1]], p_expanp1[[1]],
               p_cohes2p1[[1]], p_benep1[[1]],
               p_clashp1[[1]], p_bargp1[[1]]
                 )

pan_SD <- c(sd(panel.df$allTrust_cw_y0), sd(panel.df$contactOnly_cw_y0), sd(panel.df$in_cw_y0),
              sd(panel.df$pgp_amount_y1), sd(panel.df$pgp_donate_y1),
              sd(panel.df$threat_cw_y0), sd(panel.df$cohes1_cw_y0),
              sd(panel.df$cohes2_cw_y0), sd(panel.df$bene_cw_y0),
              sd(panel.df$clash_cw_y0), sd(panel.df$barg_cw_y0))

coef.fun <- function(var,thedf)
{
  
  # pgp - panel
  if(grepl("y1", var)){
  the_fmla <- reformulate(paste0("tr_f+state"), response=var)
  the_lm <- lm(the_fmla, data=thedf)
  thesd  <- sd(thedf[,var], na.rm=T)
  size_non <- coef(the_lm)['tr_f1.0']#/thesd
  size_part <- coef(the_lm)['tr_f1.1']#/thesd
  
  return(c(size_non, size_part))
  }
  
  # pgp - ag
  else if(grepl("end", var)){
  the_fmla <- reformulate(paste0("treatment+state"), response=var)
  the_lm <- lm(the_fmla, data=thedf)
  thesd  <- sd(thedf[,var], na.rm=T)
  size <- coef(the_lm)['treatment']#/thesd
  
  return(size)
  }
  
  # panel.df, controlling for
  else if(all(names(thedf)[1:5] %in% names(panel.df)[1:5]) &  strat.fun(paste0(var, "_y0"), thedf=panel.df)=="Controlling-for: true.fun"){
  the_fmla <- reformulate(paste0("tr_f+state+",var, "_y0"), response=paste0(var, "_y1"))
  the_lm <- lm(the_fmla, data=thedf)
  thesd  <- sd(thedf[,paste0(var, "_y0")], na.rm=T)
  size_non <- coef(the_lm)['tr_f1.0']#/thesd
  size_part <- coef(the_lm)['tr_f1.1']#/thesd
  
  return(c(size_non, size_part))
  }
  
  # panel.df, differencing/pgg
  else if(all(names(thedf)[1:5] %in% names(panel.df)[1:5]) &  strat.fun(paste0(var, "_y0"), thedf=panel.df)=="Difference: true.fun1"){
  the_fmla <- reformulate(paste0("tr_f+state"), response=var)
  the_lm <- lm(the_fmla, data=thedf)
  thesd  <- sd(thedf[,var], na.rm=T)
  size_non <- coef(the_lm)['tr_f1.0']#/thesd
  size_part <- coef(the_lm)['tr_f1.1']#/thesd
  
  return(c(size_non, size_part))
  }
  
  # ag.df, controlling for
  else if(all(names(thedf)[1:5] %in% names(ag.df)[1:5]) &  strat.fun(paste0(var, "_base"), thedf=ag.df)=="Controlling-for: true.fun"){
  the_fmla <- reformulate(paste0("treatment+state+",var, "_base"), response=paste0(var, "_end"))
  the_lm <- lm(the_fmla, data=thedf)
  thesd  <- sd(thedf[,paste0(var, "_base")], na.rm=T)
  size <- coef(the_lm)['treatment']#/thesd
  
  return(size)
  }
  
  # ag.df, differencing/pgg
  else if(all(names(thedf)[1:5] %in% names(ag.df)[1:5]) &  strat.fun(paste0(var, "_base"), thedf=ag.df)=="Difference: true.fun1"){
  the_fmla <- reformulate(paste0("treatment+state"), response=var)
  the_lm <- lm(the_fmla, data=thedf)
  thesd  <- sd(thedf[,var], na.rm=T)
  size <- coef(the_lm)['treatment']#/thesd
  
  return(size)
  }
  
  # unknown things
  else(paste("FAIL"))
}

#coef.fun("x_cw", panel.df)
#coef.fun("x_cw", ag.df)
#coef.fun("pgp_amount_y1", panel.df)
#coef.fun("pgp_amount_end", ag.df)
```

Aggregate df

```{r}
#get coefficient from ols
ag.coefs <- matrix(NA, nrow=length(ag.vars), ncol=3)
for(i in 1:length(ag.vars))
{
  ag.coefs[i,1] <- ag.vars[i]
  ag.coefs[i,2] <- ag_coef[i]
  ag.coefs[i,3] <- ag_SD[i]
  
}
ag.coefs <- as.data.frame(ag.coefs)
names(ag.coefs) <- c("var", "coef", "sd")

# make numeric
ag.coefs[,2:3] <- sapply(ag.coefs[,2:3], function(x) {as.numeric(as.character(x))})

```

Panel - tr_n

```{r}
# get coefficients from ols
ind.coefs <- matrix(NA, nrow=length(ind.vars), ncol=3)
for(i in 1:length(ind.vars))
{
  ind.coefs[i,1] <- ind.vars[i]
  ind.coefs[i,2] <- pan_coef[i]
  ind.coefs[i,3] <- pan_SD[i]
  
}

ind.coefs <- as.data.frame(ind.coefs)
names(ind.coefs) <- c("var", "coef_ind", "sd")

# make numeric
ind.coefs[,2:3] <- sapply(ind.coefs[,2:3], function(x) {as.numeric(as.character(x))})

```

Panel - tr_f

```{r}
# get coefficients from ols
ind.coefs2 <- matrix(NA, nrow=length(ind.vars), ncol=4)
for(i in 1:length(ind.vars))
{
  ind.coefs2[i,1] <- ind.vars[i]
  ind.coefs2[i,2:3] <- coef.fun(paste0(ind.vars)[i], panel.df)
  ind.coefs2[i,4] <- pan_SD[i]
}

ind.coefs2 <- as.data.frame(ind.coefs2)
names(ind.coefs2) <- c("var", "coef_non", "coef_part", "sd")

# make numeric
ind.coefs2[,2:4] <- sapply(ind.coefs2[,2:4], function(x) {as.numeric(as.character(x))})

ind.coefs <- cbind(ind.coefs, ind.coefs2[,c("coef_non", "coef_part")])
```

## Bootstrap Conf Intervals


### Aggregate DF: Bootstrap standardized outcomes.

Need to resample the way we sampled (sample 9 sites in Nas, sample 6 sites in Ben).  Then do lm(outcome~treatment) newly for each resample to make a distribution, then take 2.5th quartile and 97.5th quartile from that distribution.  Do that for every variable in ag.vars and add it to ag.coefs as ll and ul.


```{r}
# function to resample and lm 1,000 times, then take 0.025 and 0.975 quantiles.
agBoot.fun <- function(var)
{
  boot.coef <- rep(NA,1000)
  for(i in 1:1000)
  {
    # sample PSUs within state
  boot.nas <- ag.df[ag.df$state %in% "nas",] %>% group_by(psu) %>%
    nest() %>%
    sample_n(size=9, replace=T) %>%
    unnest() %>% as.data.frame(.)
  boot.ben <- ag.df[ag.df$state %in% "ben",] %>% group_by(psu) %>%
    nest() %>%
    sample_n(size=6, replace=T) %>%
    unnest() %>% as.data.frame(.)
  boot.samp <- rbind(boot.nas, boot.ben)
  
  # do regression
  ## pgg
  if(grepl("_end", var)){
    lm.boot <- lm(boot.samp[,var]~treatment+state, data=boot.samp)
    boot.coef[i] <- summary(lm.boot)$coefficients[2,1]
    }
  ## differecing
  else if(!grepl("_end", var) & strat.fun(paste0(var, "_base"), thedf=ag.df)=="Difference: true.fun1"){
    lm.boot <- lm(boot.samp[,var]~treatment+state, data=boot.samp)
    boot.coef[i] <- summary(lm.boot)$coefficients[2,1]
    }
  
  ## controlling-for
  else if(!grepl("_end", var) & strat.fun(paste0(var, "_base"), thedf=ag.df)=="Controlling-for: true.fun"){
    lm.boot <- lm(boot.samp[,paste0(var, "_end")]~treatment+state+boot.samp[,paste0(var, "_base")], data=boot.samp)
    boot.coef[i] <- summary(lm.boot)$coefficients[2,1]
    }
  }
  
  #mn <- mean(boot.coef)
  #med <- median(boot.coef)
  ll <- quantile(boot.coef,0.025)
  ul <- quantile(boot.coef,0.975)
  
  #return(cbind(mn,med,ll,ul))
  return(cbind(ll,ul))
  
}
#agBoot.fun(var="x_cw")
#agBoot.fun(var="in_cw")
#agBoot.fun(var="pgp_amount_end")
agBoot.fun(var="contactOnly_cw")


# apply function to ag.vars and add to ag.coefs as columns ll and ul
set.seed(867564)
system.time(ag.coefs[,c("ll", "ul")] <- t(sapply(ag.vars, agBoot.fun)))

# make the cols in terms of sd
ag.coefs[,c("size", "ll_size", "ul_size")] <- ag.coefs[,c(2,4:5)]/ag.coefs[,3]

save(ag.coefs, file="ag.coefs.Rdata")
```



### Participant - Nonparticipant - Control Comparison


Linear effect (tr_n) and effects for each group (tr_f).

Also want a plot showing full participants and nonparticipants vs control.

Need to resample the way we sampled (sample ~10 individuals within each comm).  Then do lm(outcome~treatment) newly for each resample to make a distribution, then take 2.5th quartile and 97.5th quartile from that distribution.  Do that for every variable in ind.vars and add it to ind.coefs as ll and ul.


```{r}
# will need to do sep regs for part-control and non-control to get SEs.
## the one-model SEs will give me the wrong SEs for participants, since it will be participants vs Non, instead of participants vs control.
require(purrr)

indBoot.fun <- function(var)
{
  boot.coef <- rep(NA,1000)
  non.coef <- rep(NA,1000)
  part.coef <- rep(NA,1000)
  for(i in 1:1000)
  {
    # Resample communities
  boot.nas2 <- panel.df[panel.df$state %in% "nas",] %>% group_by(psu) %>%
    nest() %>%
    sample_n(size=9, replace=T) %>%
    unnest() %>%
    as.data.frame(.)
  boot.ben2 <- panel.df[panel.df$state %in% "ben",] %>% group_by(psu) %>%
    nest() %>%
    sample_n(size=6, replace=T) %>%
    unnest() %>%
    as.data.frame(.)
  boot.samp2 <- rbind(boot.nas2, boot.ben2)
  
  # do regression
  ## endline only
  if(grepl("_y1", var)){
    lm.boot <- lm(boot.samp2[,var]~tr_n+state, data=boot.samp2)
    lm.boot2 <- lm(boot.samp2[,var]~tr_f+state, data=boot.samp2)
    
    boot.coef[i] <- summary(lm.boot)$coefficients[2,1]
    non.coef[i] <- summary(lm.boot2)$coefficients[2,1]
    part.coef[i] <- summary(lm.boot2)$coefficients[3,1]
  }
  ## controlling-fr
  else if(!grepl("_y1", var) & strat.fun(paste0(var, "_y0"), thedf=panel.df)=="Controlling-for: true.fun"){
    lm.boot <- lm(boot.samp2[,paste0(var, "_y1")]~tr_n+state+boot.samp2[,paste0(var, "_y0")], data=boot.samp2)
    lm.boot2 <- lm(boot.samp2[,paste0(var, "_y1")]~tr_f+state+boot.samp2[,paste0(var, "_y0")], data=boot.samp2)
    
    boot.coef[i] <- summary(lm.boot)$coefficients[2,1]
    non.coef[i] <- summary(lm.boot2)$coefficients[2,1]
    part.coef[i] <- summary(lm.boot2)$coefficients[3,1]
  }
  ## differencing
  else if(!grepl("_y1", var) & strat.fun(paste0(var, "_y0"), thedf=panel.df)=="Difference: true.fun1"){
    lm.boot <- lm(boot.samp2[,var]~tr_n+state, data=boot.samp2)
    lm.boot2 <- lm(boot.samp2[,var]~tr_f+state, data=boot.samp2)
    
    boot.coef[i] <- summary(lm.boot)$coefficients[2,1]
    non.coef[i] <- summary(lm.boot2)$coefficients[2,1]
    part.coef[i] <- summary(lm.boot2)$coefficients[3,1]
  }
  
  }
  
  ll_ind <- quantile(boot.coef,0.025)
  ul_ind <- quantile(boot.coef,0.975)
  ll_non <- quantile(non.coef,0.025)
  ul_non <- quantile(non.coef,0.975)
  ll_part <- quantile(part.coef,0.025)
  ul_part <- quantile(part.coef,0.975)
  
  #return(cbind(boot.coef, non.coef, part.coef))
  return(cbind(ll_ind, ul_ind, 
               ll_non,ul_non, 
               ll_part, ul_part))
  
}
#system.time(indBoot.fun(var="x_cw"))
#system.time(indBoot.fun(var="in_cw"))
#system.time(indBoot.fun(var="pgp_amount_y1"))


# apply function to ind.vars and add to ind2.coefs as columns ll_non/part and ul_non/part
set.seed(2353)
system.time(ind.coefs[,c("ll_ind", "ul_ind", "ll_non", "ul_non", "ll_part", "ul_part")] <- t(sapply(ind.vars, indBoot.fun)))

# make the cols in terms of sd
ind.coefs[,c("size_ind", "size_ll_ind", "size_ul_ind",
             "size_non", "size_ll_non", "size_ul_non",
             "size_part", "size_ll_part", "size_ul_part")] <- ind.coefs[,c("coef_ind", "ll_ind", "ul_ind",
                                                                            "coef_non", "ll_non", "ul_non",
                                                                            "coef_part", "ll_part", "ul_part")]/ind.coefs[,"sd"]


save(ind.coefs, file="ind.coefs.Rdata")
```


