---
title: "d_obsDat_figs"
author: "Christopher Grady"
date: "September 7, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
load("../clean/a_obsDat_clean.rda")
library(dplyr)
library(ggplot2)
library(estimatr)

```

# Overview

Plots to help visualize the market/event observation data

# Markets

## Make plots DFs

```{r}
markets.df <- markets[, c("State", "site", "treatment", "time", 
                          "month_num", "date",
                         names(markets)[grepl("farm|past", names(markets))])]

# at site-level and month-level
markets.df1 <- markets.df %>% 
  dplyr::group_by(site,month_num) %>%
  dplyr::summarise_all(funs(mean(., na.rm = TRUE))) %>%
  as.data.frame()
#for now fix this way; later don't summarise_all this column
markets.df1$treatment <- as.factor(as.character(markets.df1$treatment))


#################

# at tr/co-level and month-level
markets.df2 <- markets.df %>% 
  dplyr::group_by(treatment,month_num) %>%
  dplyr::summarise_all(funs(mean(., na.rm = TRUE))) %>%
  as.data.frame()
markets.df2$treatment <- as.factor(as.character(markets.df2$treatment))

#########

# at site-level & t1/t2-level
markets.df1b <- markets.df %>% 
  dplyr::group_by(site,time) %>%
  dplyr::summarise_all(funs(mean(., na.rm = TRUE))) %>%
  as.data.frame()
markets.df1b$treatment <- as.factor(as.character(markets.df1b$treatment))

########

# at tr/co-level & t1/t2-level
markets.df2b <- markets.df %>% 
  dplyr::group_by(treatment,time) %>%
  dplyr::summarise_all(funs(mean(., na.rm = TRUE))) %>%
  as.data.frame()
markets.df2b$treatment <- as.factor(as.character(markets.df2b$treatment))
```

## Plots

### Plot function

```{r}
plot.fun<-function(outcome, thedf, time, grp, title, xlab, ylab, ymin, ymax){
  ggplot(data=thedf, aes(x=thedf[[time]], y=thedf[[outcome]], group=grp)) +
  geom_line(aes(color=treatment))+
  geom_point(aes(color=treatment))+
  coord_cartesian(ylim = c(ymin, ymax)) +
  geom_vline(xintercept=8) +
  ggtitle(title) +
  theme_bw() +
  theme(panel.grid.major = element_blank()) +
  theme(plot.title = element_text(size=18)) +
  xlab(xlab) +
  ylab(ylab)
}

## manual plot to be functionized
### markets.df1 == site-level, month-level
### markets.df2b == tr/co-level, t1/t2-level.
ggplot(data=markets.df2b, aes(x=markets.df2b[['time']], y=markets.df2b[['pastoralists_index_rank']], group=treatment)) +
  geom_line(aes(color=treatment))+
  geom_point(aes(color=treatment))+
  geom_vline(xintercept=8)+
  #coord_cartesian(ylim = c(ymin, ymax)) +
  ggtitle("title") +
  theme_bw() +
  theme(panel.grid.major = element_blank()) +
  theme(plot.title = element_text(size=18)) +
  xlab("xlab") +
  ylab("ylab")


plot.fun(outcome='pastoralists_index_rank', thedf=markets.df2,
         time='month_num',
         grp='treatment', title="Past Index by Month in TR and CO", 
         xlab="Month", ylab="Index",
         ymin=0, ymax=35)


```






# Events


## Plot 1

Show each community's value on outcomes for each month.

Need a function that:
- shows each unit with "outcome amount" on the Y-axis and "time" on the X-axis.
- lets me vary the outcome, dataset (events/markets), time variable (time or month_num), and unit (TR & CO collapsed together or separated out).
- adds a vertical line after month 6 to represent the break in observations.

## Make Plot dataframes.

First, fix things in main df.

```{r}
#events$treatment <- as.character(events$treatment)

quantile(events$attend_total, seq(0,1,0.1))
#chris: short-term solution to cap it at 550?
```

Make new plot dataframes

```{r}
events.df <- events[, c("State", "site", "treatment", "time", "month_num", "date",
                         "attend_total", "attend_farm", "attend_past",
                         "eat_total", "eat_farm", "eat_past",
                         "farmers_index", "pastoralists_index")]

# at site-level and month-level
events.df1 <- events.df %>% 
  dplyr::group_by(site,month_num) %>%
  dplyr::summarise_all(funs(mean(., na.rm = TRUE))) %>%
  as.data.frame()
#for now fix this way; later don't summarise_all this column
events.df1$treatment <- as.factor(as.character(events.df1$treatment))

## sort by site and month_num
events.df1 <- events.df1[order(events.df1$site, events.df1$month_num),]
#events[order(events$site, events$month_num), c("site", "month_num", "attend_total", "Observer.Name")]
## chris: agudu 15,16,17 are where the numbers don't make sense.

#################

# at tr/co-level and month-level
events.df2 <- events.df %>% 
  dplyr::group_by(treatment,month_num) %>%
  dplyr::summarise_all(funs(mean(., na.rm = TRUE))) %>%
  as.data.frame()

events.df2$treatment <- as.factor(as.character(events.df2$treatment))

#########

# at site-level & t1/t2-level
events.df1b <- events.df %>% 
  dplyr::group_by(site,time) %>%
  dplyr::summarise_all(funs(mean(., na.rm = TRUE))) %>%
  as.data.frame()
events.df1b$treatment <- as.factor(as.character(events.df1b$treatment))




########

# at tr/co-level & t1/t2-level
events.df2b <- events.df %>% 
  dplyr::group_by(treatment,time) %>%
  dplyr::summarise_all(funs(mean(., na.rm = TRUE))) %>%
  as.data.frame()
events.df2b$treatment <- as.factor(as.character(events.df2b$treatment))




```

Plot function.  Allows changing:
- the data frame
- the outcome variable
- the time variable (time vs month_num)
- grp (site vs treatment)
- title, labels, min/max


```{r}
plot.fun<-function(outcome, thedf, time, grp, title, xlab, ylab, ymin, ymax){
  ggplot(data=thedf, aes(x=thedf[[time]], y=thedf[[outcome]], group=grp)) +
  geom_line(aes(color=treatment))+
  geom_point(aes(color=treatment))+
  coord_cartesian(ylim = c(ymin, ymax)) +
  geom_vline(xintercept=8) +
  ggtitle(title) +
  theme_bw() +
  theme(panel.grid.major = element_blank()) +
  theme(plot.title = element_text(size=18)) +
  xlab(xlab) +
  ylab(ylab)
}

ggplot(data=events.df2, aes(x=events.df2[['month_num']], y=events.df2[['pastoralists_index']], group=treatment)) +
  geom_line(aes(color=treatment))+
  geom_point(aes(color=treatment))+
  geom_vline(xintercept=8)+
  #coord_cartesian(ylim = c(ymin, ymax)) +
  ggtitle("title") +
  theme_bw() +
  theme(panel.grid.major = element_blank()) +
  theme(plot.title = element_text(size=18)) +
  xlab("xlab") +
  ylab("ylab")

# at TR-level
plot.fun(outcome='pastoralists_index', thedf=events.df2, time='month_num',
         grp='treatment', title="Attend T1-T2", 
         xlab="Month", ylab="Attendance",
         ymin=0.3, ymax=0.7)

# at site-level
plot.fun(outcome='attend_total', thedf=events.df1, time='time',
         grp="site", title="Attend T1-T2", 
         xlab="Time", ylab="Attendance",
         ymin=0.3, ymax=0.7)



```


# Plot 2

Collapse all TR sites into TR and all CO sites into CO.

## make plot data: plan 

Mean/median for Tr & Co at Base & End.
- first need every community to get a baseline value and endline value (mean for community at baseline/endline?)?
- or just take every observation for CO at Base, then the mean of all the obs?
- leave sites disaggregated and plot before/after for each?

## Make new plot dataframes

```{r}
events.df <- events[, c("State", "site", "treatment", "time", "month_num", "date",
                         "attend_total", "attend_farm", "attend_past",
                         "eat_total", "eat_farm", "eat_past",
                         "farmers_index", "pastoralists_index")]

# at site-level
events.df1 <- events.df %>% 
  dplyr::group_by(site,month_num) %>%
  dplyr::summarise_all(funs(mean(., na.rm = TRUE))) %>%
  as.data.frame()
#for now fix this way; later don't summarise_all this column
events.df1$treatment <- as.factor(as.character(events.df1$treatment))

## sort by site and month_num
events.df1 <- events.df1[order(events.df1$site, events.df1$month_num),]
#events[order(events$site, events$month_num), c("site", "month_num", "attend_total")]

#################

# at tr/co-level
events.df2 <- events.df %>% 
  dplyr::group_by(treatment,month_num) %>%
  dplyr::summarise_all(funs(mean(., na.rm = TRUE))) %>%
  as.data.frame()

events.df2$treatment <- as.factor(as.character(events.df2$treatment))

```



