---
title: "obsDat"
output:
  pdf_document:
    keep_tex: yes
    number_sections: yes
    toc: yes
  word_document:
    toc: yes
  html_document:
    df_print: paged
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
load("../a_clean/a_obsDat_clean.rda")
library(dplyr)
library(estimatr)

```

chris: does not run after splitting from a_obsDat_clean; some object names have changed.

# Overview

This is an analysis of the market and event observational data.  The outcomes are the raw number of people attending the market/event or engaging in some behavior at the market/event.  The outcomes are non-normal and skewed.  As a result of this skew, outcomes are rank rescaled or analyzed using quantile regression or robust regression.

We want to know if treatment communities improved more than control communities over time.  We can do this in two ways: (1) code observations as 0 or 1 on a "time" variable, where 0 is early/baseline and 1 is late/endline; (2) code observations by month using a "month number" variable that is 1 for the first month of observation, 2 for the second, month, 3 for the third month, etc.

# Markets

## Mean changes (community fixed effects)

Do treatment communities increase on these market variables more than control communities from "before" time to "after" time?  The coefficient is how much more the treatment communities changed than the control communities on average.  A coef of 100 means treatment communities increased 100 more than control communities from 0-1.  This can be because for multiple reasons: (1) the control communities did not change and the treatment communities changed 100, (2) the control communities changed 100 and the treatment communities changed 200, (3) the control communities changed -100 and the treatment communities stayed the same, etc...

The coefficient is the average effect _within_ community.  This is a community fixed effect.  This prevents us from thinking the program had a positive effect just because we observed more high value treatment communities in the "after" stage than in the "before" stage.  Or from thinking the program had a negative effect just because we observed more low value treatment communities in the "after" stage than in the "before" stage.

The outcomes are rank-scaled to fix strong right skew.  They are rank-scaled in two different ways for robustness.

```{r, echo=F, include=F}
# Before/After 
# run regression for all outcomes
marks.fun <- function(var)
{
  fmla1 <- reformulate(c("treatment*time+site+State"), response=var)
  lm1 <- lm_robust(fmla1, data=markets, clusters=site)
  thecoef <- coefficients(lm1)['treatment:time']
  thep <- summary(lm1)$coefficients['treatment:time',4]
  return(c(thecoef,thep))
  
}
#marks.fun(var="market_stalls_total_rank")

## combined rank
mark.thing <- t(sapply(rankOutcomes,marks.fun))
colnames(mark.thing) <- c("coef", "p")

## Separate rank
#mark.thing2 <- t(sapply(rankOutcomesSep,marks.fun))
#colnames(mark.thing2) <- c("coef", "p")
#mark.thing2
```
```{r}
mark.thing
```
```{r, eval=F, include=F}
# rebecca wants effect sizes; variable is rank
summary(markets$pastoralist_women_sell_fura_rank); sd(markets$pastoralist_women_sell_fura_rank, na.rm=T)
summary(markets$pastoralist_women_sell_fura); sd(markets$pastoralist_women_sell_fura, na.rm=T)

marks.fun(var="pastoralist_women_sell_fura_rank")[1]/sd(markets$pastoralist_women_sell_fura_rank, na.rm=T)
marks.fun(var="pastoralist_sellers_rank")[1]/sd(markets$pastoralist_sellers_rank, na.rm=T)

#thing <- mosaic::do(500)*lm(pastoralist_women_sell_fura_rank~sample(treatment)*time+site+State, markets)
#mean(thing[["treatment.time"]]>=13)
```

### Median changes (within site correction)

It looks like the median treatment group sites also increased relative to the median control group site.

```{r, eval=T}
# run median regression for all outcomes
library(quantreg)

marksMed.fun <- function(var)
{
  fmla <- reformulate(c("treatment*time+site"), response=var)
  lm1<-rq(fmla, data=markets, tau=0.5)
  thecoef <- coefficients(lm1)['treatment:time']
  lb <- summary(lm1)$coefficients['treatment:time',"lower bd"]
  ub <- summary(lm1)$coefficients['treatment:time',"upper bd"]
  return(c(thecoef,lb, ub))
}

markMed.thing <- t(sapply(outcomes,marksMed.fun))
colnames(markMed.thing) <- c("coef", "lower", "upper")
markMed.thing
```

## Summary

The data mildly suggest a positive relationship between ECPN and more market interaction.  It looks like TR pastoralists, as we move from baseline to endline, were more likely to be in the markets than CO pastoralists.  This is important because the market is almost always in the farming community, so this represents pastoralists entering the farming community.  

The evidence is not especially strong.  The p-values are below 0.10, but now below 0.05.  But these results should be interpreted in conjunction with the "Contact" results from the main analysis, which corroborates the idea that contact plummeted far more in control than in Treatment.  We should also keep in mind that these data are very messy.




### Save stuff

```{r}
save(markets,markMed.thing, file="marketMedian.Rdata")
```

************************

# Events

The same analyses as the _Markets_ data: (i) a before-after analysis, and (ii) a panel analysis.

## Mean Changes

Do treatment communities increase on these event variables more than control communities from "before" time to "after" time?  Do treatment communities increase on the event variables more as time goes on?

The interpretation is the same as for the market data.  The coefficient is how much more the treatment communities changed than the control communities on average.  A coef of 100 means treatment communities increased 100 more than control communities from 0-1.  This can be because for multiple reasons: (1) the control communities did not change and the treatment communities changed 100, (2) the control communities changed 100 and the treatment communities changed 200, (3) the control communities changed -100 and the treatment communities stayed the same, etc...

The coefficient is the average effect _within_ community.  This is a community fixed effect.  This prevents us from thinking the program had a positive effect just because we observed more high value treatment communities in the "after" stage than in the "before" stage.  Or from thinking the program had a negative effect just because we observed more low value treatment communities in the "after" stage than in the "before" stage.


First we look at the data from the before-after perspective.

```{r, echo=F, include=F}
#events$tr_time <- interaction(events$treatment, events$time)
#library(mosaic)
#mosaic::mean(events$Number.of.People..in.atttenddance~events$tr_time)
#mosaic::mean(events$Number.of.People.who.eat.or.drink~events$tr_time, na.rm=T)

# before/after
events.fun <- function(var)
{
  fmla <- reformulate(c("treatment*time+site+State+Host.Community"), response=var)
  lm1 <- lm(fmla, data=events)
  thecoef <- coefficients(lm1)['treatment:time']
  thep <- summary(lm1)$coefficients['treatment:time',4]
  return(c(thecoef,thep))
  
}
#events.fun('Number.of.People..in.atttenddance_rank')

event.thing <- t(sapply(rankEventOutcomes,events.fun))
colnames(event.thing) <- c("coef", "p")
```
```{r}
event.thing
```

### Median changes (within site correction)

It looks like the median treatment group sites also increased relative to the median control group site.

```{r, eval=T}
# run median regression for all outcomes
library(quantreg)

# have to drop sites without at least 2 obs per time point
(thetab <- as.matrix(table(events$Community.Name, events$time)))
sigh <- data.frame(comm = rownames(thetab), bef = thetab[,1], end = thetab[,2])
dropsies <- na.omit(ifelse(sigh$bef < 2 | sigh$end < 2, as.character(sigh$comm), NA))
events2 <- droplevels(events[!events$Community.Name %in% dropsies,])

eventsMed.fun <- function(var)
{
  fmla <- reformulate(c("treatment*time"), response=var)
  lm1<-rq(fmla, data=events2, tau=0.5)
  thecoef <- coefficients(lm1)['treatment:time']
  lb <- summary(lm1)$coefficients['treatment:time',"lower bd"]
  ub <- summary(lm1)$coefficients['treatment:time',"upper bd"]
  return(c(thecoef,lb, ub))
}
eventsMed.fun(var="attend_past")

eventsMed.thing <- t(sapply(eventOutcomes,eventsMed.fun))
colnames(eventsMed.thing) <- c("coef", "lower", "upper")
eventsMed.thing
```


## Summary

It looks like ECPN had no effect on event attendance.  The data weakly suggest that more pastoralists showed up to and took food at farming events, but fewer farmers showed up to and took food at pastoralists events.  

#### Save stuff

```{r}
save(events, eventsMed.thing, file="eventsMedian.Rdata")
```


# Overall Summary

Some evidence that ECPN increased attendance to markets by pastoralists.  The data show an increase in pastoralist buyers and sellers in treatment markets, relative to control.  The effect is because the number of pastoralists in control markets drops whereas the number of pastoralists in treatment remains about the same.  The evidence is not especially strong on its own, but corroborates the main analysis results about intergroup contact.

There is no difference between treatment and control in the social event data.


<!--
# Old wrong stuff

And this checks the effect if we use the panel nature of the data.  Insead of 0-1, we now have 1 in the first month and 17 in the last month with other months in between.

```{r, echo=F, include=F}
####################
# Panel
marks.funP <- function(var)
{
  fmla1 <- reformulate(c("treatment*month_num+site+State"), response=var)
  lm1 <- lm_robust(fmla1, data=markets, clusters=site)
  thecoef <- coefficients(lm1)['treatment:month_num']
  thep <- summary(lm1)$coefficients['treatment:month_num',4]
  return(c(thecoef,thep))
  
}
#marks.fun("market_stalls_total")

#mark.thing <- t(sapply(outcomes,marks.fun))
mark.thingP <- t(sapply(rankOutcomes,marks.funP))
colnames(mark.thingP) <- c("coef", "p")
```
```{r}
mark.thingP
```

**Events**

Now we look at the data from a panel perspective.

```{r, echo=F, include=F}

####################
# Panel
marks.funP <- function(var)
{
  fmla1 <- reformulate(c("treatment*month_num+site+State"), response=var)
  lm1 <- lm_robust(fmla1, data=events, clusters=site)
  thecoef <- coefficients(lm1)['treatment:month_num']
  thep <- summary(lm1)$coefficients['treatment:month_num',4]
  return(c(thecoef,thep))
  
}
#marks.fun(var='attend_total')

#mark.thing <- t(sapply(outcomes,marks.fun))
event.thingP <- t(sapply(rankEventOutcomes,marks.funP))
colnames(event.thingP) <- c("coef", "p")
```
```{r}
event.thingP

```

```{r, eval=F, include=F}
# events function separate for farmers and pastoralists?
Fevents.fun <- function(var)
{
  fmla <- reformulate(c("treatment*time+site+State"), response=var)
  #lm1<-robustbase::lmrob(fmla, data=events, control = robustbase::lmrob.control(setting="KS2014", max.it = 500))
  lm1 <- lm(fmla, data=events[events$Host.Community %in% 'farmer',])
  thecoef <- coefficients(lm1)['treatment:time']
  thep <- summary(lm1)$coefficients['treatment:time',4]
  return(c(thecoef,thep))
  
}
#Fevents.fun('Number.of.People..in.atttenddance_rank', 'farmer')

Fevent.thing <- t(sapply(rankEventOutcomes,Fevents.fun))
colnames(Fevent.thing) <- c("coef", "p")
Fevent.thing

Pevents.fun <- function(var)
{
  fmla <- reformulate(c("treatment*time+site+State"), response=var)
  #lm1<-robustbase::lmrob(fmla, data=events, control = robustbase::lmrob.control(setting="KS2014", max.it = 500))
  lm1 <- lm(fmla, data=events[events$Host.Community %in% 'pastoralist',])
  thecoef <- coefficients(lm1)['treatment:time']
  thep <- summary(lm1)$coefficients['treatment:time',4]
  return(c(thecoef,thep))
  
}

Pevent.thing <- t(sapply(rankEventOutcomes,Pevents.fun))
colnames(Pevent.thing) <- c("coef", "p")
Pevent.thing

```

-->