---
title: "d_obsDat_figs"
author: "Christopher Grady"
output: html_document
---

chris 8-6-2023: we use these plots to answer reviewer #1s question asking if the overall trend could be explained by collapse in a single control community.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
load("../a_clean/a_obsDat_clean.rda")
library(dplyr)
library(ggplot2)
library(estimatr)

```

# Overview

Plots to help visualize the market/event observation data

# Markets

## Make plots DFs

```{r}
markets.df <- markets[, c("State", "site", "treatment", "time", 
                          "month_num", "date",
                         names(markets)[grepl("farm|past", names(markets))])]

#only want overall index outcomes
markets.df <- markets.df[, c("State", "site", "treatment", "time", 
                          "month_num", "date",
                          names(markets)[grepl("index", names(markets))])]

# at site-level and month-level
markets.df1 <- markets.df %>% 
  dplyr::group_by(site,month_num) %>%
  dplyr::summarise_all(funs(mean(., na.rm = TRUE))) %>%
  as.data.frame()
#for now fix this way; later don't summarise_all this column
markets.df1$treatment <- as.factor(as.character(markets.df1$treatment))


#################

# at tr/co-level and month-level
markets.df2 <- markets.df %>% 
  dplyr::group_by(treatment,month_num) %>%
  dplyr::summarise_all(funs(mean(., na.rm = TRUE))) %>%
  as.data.frame()
markets.df2$treatment <- as.factor(as.character(markets.df2$treatment))

#########

# at site-level & t1/t2-level
markets.df1b <- markets.df %>% 
  dplyr::group_by(site,time) %>%
  dplyr::summarise_all(funs(mean(., na.rm = TRUE))) %>%
  as.data.frame()
markets.df1b$treatment <- as.factor(as.character(markets.df1b$treatment))

########

# at tr/co-level & t1/t2-level
markets.df2b <- markets.df %>% 
  dplyr::group_by(treatment,time) %>%
  dplyr::summarise_all(funs(mean(., na.rm = TRUE))) %>%
  as.data.frame()
markets.df2b$treatment <- as.factor(as.character(markets.df2b$treatment))

# colors
grps <-c("1", "0")
color.codes<-as.character(c("#FC8D59", "#00BFC4"))
```

## Plots

### Plot function

```{r}
#var='pastoralists_index_rank'; thedf=markets.df1; time1='month_num'; group1='treatment'; title="Past Index by Month in TR and CO";xlab="Month";ylab="Index";ymin=0; ymax=35

plot.fun<-function(var, thedf, time1, group1, title, xlab, ylab, ymin=0){
  ggplot(data=thedf, aes(x=thedf[[time1]], y=thedf[[var]], group=thedf[[group1]])) +
  geom_line(aes(color=treatment))+
  geom_point(aes(color=treatment))+
  coord_cartesian(ylim = c(ymin, max(thedf[[var]]))) +
  geom_vline(xintercept=max(thedf[[time1]]/2)) +
  scale_colour_manual(values=setNames(color.codes, grps)) +
  ggtitle(title) +
  theme_bw() +
  theme(panel.grid.major = element_blank()) +
  theme(plot.title = element_text(size=18)) +
  xlab(xlab) +
  ylab(ylab) +
  scale_x_continuous(breaks = seq(min(thedf[[time1]]), max(thedf[[time1]]), by = 1))
}

```

# Pastoralists Index

### markets.df1 == site-level, month
```{r}
market_pasts_siteMonth.plot <-
  plot.fun(var='pastoralists_index_rank', thedf=markets.df1,
         time1='month_num',
         group1='site', title="Pastoralist index (site-level, month)", 
         xlab="Month", ylab="Index")

png(file="market_pasts_siteMonth.plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
market_pasts_siteMonth.plot
dev.off()
```

```{r}
plot.fun(var='pastoralists_index_raw', thedf=markets.df1,
         time1='month_num',
         group1='site', title="Past Index by Month in TR and CO", 
         xlab="Month", ylab="Index",
         ymin=0)
```

### markets.df1b == site-level & t1/t2-time
```{r}
market_pasts_siteTime.plot <-
  plot.fun(var='pastoralists_index_rank', thedf=markets.df1b,
         time1='time',
         group1='site', title="Pastoralist index (site-level, base-end)", 
         xlab="Baseline to Endline", ylab="Index")

png(file="market_pasts_siteTime.plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
market_pasts_siteTime.plot
dev.off()
```

```{r}
plot.fun(var='pastoralists_index_raw', thedf=markets.df1b,
         time1='time',
         group1='site', title="Past Index by Month in TR and CO", 
         xlab="Month", ylab="Index",
         ymin=0)
```

### markets.df2 == tr/co-level and month-level.
```{r}
market_pasts_TrMonth.plot <-
  plot.fun(var='pastoralists_index_rank', thedf=markets.df2,
         time1='month_num',
         group1='treatment', title="Pastoralist index (TR-level, month)", 
         xlab="Month", ylab="Index")

png(file="market_pasts_TrMonth.plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
market_pasts_TrMonth.plot
dev.off()
```

```{r}
plot.fun(var='pastoralists_index_raw', thedf=markets.df2,
         time1='month_num',
         group1='treatment', title="Past Index by Month in TR and CO", 
         xlab="Month", ylab="Index",
         ymin=0)
```

### markets.df2b == tr/co-level, t1/t2-level.
```{r}
market_pasts_TrTime.plot <-
  plot.fun(var='pastoralists_index_rank', thedf=markets.df2b,
         time1='time',
         group1='treatment', title="Pastoralist index (TR-level, base-end)", 
         xlab="Baseline to Endline", ylab="Index")

png(file="market_pasts_TrTime.plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
market_pasts_TrTime.plot
dev.off()
```

```{r}
plot.fun(var='pastoralists_index_raw', thedf=markets.df2b,
         time1='time',
         group1='treatment', title="Past Index by Month in TR and CO", 
         xlab="Month", ylab="Index",
         ymin=0)
```


## Farmers Index

### markets.df1 == site-level, month
```{r}
market_farms_siteMonth.plot <-
  plot.fun(var='farmers_index_rank', thedf=markets.df1,
         time1='month_num',
         group1='site', title="Farmer index (site-level, month)", 
         xlab="Month", ylab="Index")

png(file="market_farms_siteMonth.plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
market_farms_siteMonth.plot
dev.off()
```


### markets.df1b == site-level & t1/t2-time
```{r}
market_farms_siteTime.plot <-
  plot.fun(var='farmers_index_rank', thedf=markets.df1b,
         time1='time',
         group1='site', title="Farmer index (site-level, base-end)", 
         xlab="Baseline to Endline", ylab="Index")

png(file="market_farms_siteTime.plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
market_farms_siteTime.plot
dev.off()
```


### markets.df2 == tr/co-level and month-level.
```{r}
market_farms_TrMonth.plot <-
  plot.fun(var='farmers_index_rank', thedf=markets.df2,
         time1='month_num',
         group1='treatment', title="Farmer index (TR-level, month)", 
         xlab="Month", ylab="Index")

png(file="market_farms_TrMonth.plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
market_farms_TrMonth.plot
dev.off()
```


### markets.df2b == tr/co-level, t1/t2-level.
```{r}
market_farms_TrTime.plot <-
  plot.fun(var='farmers_index_rank', thedf=markets.df2b,
         time1='time',
         group1='treatment', title="Farmer index (TR-level, base-end)", 
         xlab="Baseline to Endline", ylab="Index")

png(file="market_farms_TrTime.plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
market_farms_TrTime.plot
dev.off()
```


*********************

# Events

## Make Plot dataframes.

First, fix things in main df.

```{r}
#events$treatment <- as.character(events$treatment)

quantile(events$outgroupPerc_index_rank, seq(0,1,0.1),na.rm=T)
```

Make new plot dataframes

```{r}
events.df <- events[, c("State", "site", 
                        "treatment", "time", 
                        "month_num", "date",
                        "outgroupPerc_index",
                        "outgroupPerc_index_rank",
                        "attend_outgroup_presPerc_rank",
                        "eat_outgroup_eatPerc_rank")]

# at site-level and month-level
events.df1 <- events.df %>% 
  dplyr::group_by(site,month_num) %>%
  dplyr::summarise_all(funs(mean(., na.rm = TRUE))) %>%
  as.data.frame()
#for now fix this way; later don't summarise_all this column
events.df1$treatment <- as.factor(as.character(events.df1$treatment))

## sort by site and month_num
events.df1 <- events.df1[order(events.df1$site, events.df1$month_num),]
#events[order(events$site, events$month_num), c("site", "month_num", "attend_total", "Observer.Name")]
## chris: agudu 15,16,17 have weirdly big for total attendance. It's okay, we use rank outcomes because of this skew.

#################

# at tr/co-level and month-level
events.df2 <- events.df %>% 
  dplyr::group_by(treatment,month_num) %>%
  dplyr::summarise_all(funs(mean(., na.rm = TRUE))) %>%
  as.data.frame()

events.df2$treatment <- as.factor(as.character(events.df2$treatment))

#########

# at site-level & t1/t2-level
events.df1b <- events.df %>% 
  dplyr::group_by(site,time) %>%
  dplyr::summarise_all(funs(mean(., na.rm = TRUE))) %>%
  as.data.frame()
events.df1b$treatment <- as.factor(as.character(events.df1b$treatment))

########

# at tr/co-level & t1/t2-level
events.df2b <- events.df %>% 
  dplyr::group_by(treatment,time) %>%
  dplyr::summarise_all(funs(mean(., na.rm = TRUE))) %>%
  as.data.frame()
events.df2b$treatment <- as.factor(as.character(events.df2b$treatment))

```

# Outgroup index

### events.df1 == site-level, month
```{r}
events_outgroup_siteMonth.plot <-
  plot.fun(var='outgroupPerc_index_rank', thedf=events.df1,
         time1='month_num',
         group1='site', title="Outgroup index (site-level, month)", 
         xlab="Month", ylab="Index")

png(file="events_outgroup_siteMonth.plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
events_outgroup_siteMonth.plot
dev.off()
```


### markets.df1b == site-level & t1/t2-time
```{r}
events_outgroup_siteTime.plot <-
  plot.fun(var='outgroupPerc_index_rank', thedf=events.df1b,
         time1='time',
         group1='site', title="Outgroup index (site-level, base-end)", 
         xlab="Baseline to Endline", ylab="Index")

png(file="events_outgroup_siteTime.plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
events_outgroup_siteTime.plot
dev.off()
```


### markets.df2 == tr/co-level and month-level.
```{r}
event_outgroup_TrMonth.plot <-
  plot.fun(var='outgroupPerc_index_rank', thedf=events.df2,
         time1='month_num',
         group1='treatment', title="Outgroup index (TR-level, month)", 
         xlab="Month", ylab="Index")

png(file="event_outgroup_TrMonth.plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
event_outgroup_TrMonth.plot
dev.off()
```


### markets.df2b == tr/co-level, t1/t2-level.
```{r}
event_outgroup_TrTime.plot <-
  plot.fun(var='outgroupPerc_index_rank', thedf=events.df2b,
         time1='time',
         group1='treatment', title="Outgroup index (TR-level, base-end)", 
         xlab="Baseline to Endline", ylab="Index")

png(file="event_outgroup_TrTime.plot.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
event_outgroup_TrTime.plot
dev.off()
```
