---
title: "g2-panelAnalysis"
output:
  word_document:
    toc: yes
  pdf_document:
    number_sections: yes
    toc: yes
  html_document:
    df_print: paged
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(7867564)
rm(list=ls())
load("../b_creating_outcomes/f2-panelData.Rdata")

#library(NPC) # archived
library(estimatr)
library(mosaic)
library(coin)
library(robustbase)

#True p-value function.
load("true_fun_ind.rda")

#true.fun(var='x_cw', tr='treatment')
#true.fun(var='cohes_cw_resid', tr='tr_resid') # Could be useful if confounders
#true.fun(var='cohes_cw', tr='bene_cw')
#true.fun(var="pgp_amount_y1", tr='treatment')
#true.fun(var="pgp_amount_y1", tr='bene_cw')

#com.fun(var="x_cw", nsims=1000)
#com.fun1(var="x_cw", nsims=1000)

#strat.fun("cohes_cw_y0")
#strat.fun("x_cw_y0")
```


# Committee vs Non-committee vs. Control

```{r}
# make treatment variables
panel.df$tr_f <- droplevels(interaction(panel.df$treatment, panel.df$committee))
panel.df$tr_n <- as.numeric(panel.df$tr_f)
```

# Make a table of all outcomes with coefs and pvalues for the diff ways of making indices and estimating models.

- Rows as outcomes; columns for CW-Cont, CW-diff, Ind-Cont, Ind-diff; each column shows coef & pvalue.

- index: inverse-covariance weights ("cw") or additive ("ind")
- model: controlling-for ("cont") or differencing ("diff")

```{r}
# matrices sooooo fast
#system.time(replicate(10000, data.frame(thecoef=c(NA, NA), truep=c(NA, NA))))
#system.time(replicate(10000, matrix(NA, nrow=2, ncol=2, dimnames=list(NULL, c("thecoef", "truep")))))

#chris: doesnt work with pgp
analysis.fun <- function(var,nsims)
{
  if(paste0(var, "_cw_y1") %in% names(panel.df))
  {
    var_cw_cont <- comp.fun(paste0(var, "_cw"), nsims)
    var_ind_cont <- comp.fun(paste0(var, "_index"), nsims)
    var_cw_diff <- comp.fun1(paste0(var, "_cw"), nsims)
    var_ind_diff <- comp.fun1(paste0(var, "_index"), nsims)
    
    which1 <- strat.fun(paste0(var, "_cw_y0"))
    thebase <- ifelse(grepl("Contr", which1), "cw_cont", "cw_diff")
  }
  else if(grepl("pgp", var))
  {
    var_cw_cont <- comp.fun1(var, nsims)
    var_ind_cont <- matrix(NA, nrow=2, ncol=2, dimnames=list(NULL, c("thecoef", "truep")))
    var_cw_diff <- matrix(NA, nrow=2, ncol=2, dimnames=list(NULL, c("thecoef", "truep")))
    var_ind_diff <- matrix(NA, nrow=2, ncol=2, dimnames=list(NULL, c("thecoef", "truep")))
    which1 <- NA
    thebase <- NA
  }
  else
  {
    var_cw_cont <- comp.fun(var, nsims)
    var_ind_cont <- matrix(NA, nrow=2, ncol=2, dimnames=list(NULL, c("thecoef", "truep")))
    var_cw_diff <- comp.fun1(var, nsims)
    var_ind_diff <- matrix(NA, nrow=2, ncol=2, dimnames=list(NULL, c("thecoef", "truep")))
    
    which1 <- strat.fun(var)
    thebase <- ifelse(grepl("Contr", which1), "cw_cont", "cw_diff")
  }
  
  var_tab <- rbind(var_cw_cont, var_ind_cont, var_cw_diff, var_ind_diff)
  var_tab <- cbind (var_tab, c(rep("cw_cont", 2), 
                               rep("ind_cont",2), 
                               rep("cw_diff",2), 
                               rep("ind_diff",2)))
  var_tab[4] <- thebase
  colnames(var_tab)[3:4] <- c("version", "base")
  var_tab[4] <- ifelse(var_tab[[4]] == var_tab[[3]], 1, 0)
  
  return(var_tab)
}

#(trust_tab <- analysis.fun(var='attitude', nsims=100))
#(in_tab <- analysis.fun('in', nsims=100))
#(con_tab <- analysis.fun('contactOnly', nsims=100))
#(pgp_tab <- analysis.fun(var='pgp_amount_y1', nsims=100))

```

loop over outcomes.  note: rmean and end_exp don't have index & cw versions. Can still do true.fun1 and true.fun, but cannot do icw and index.

Note: takes awhile to run (like 10 minutes) so ran once and now loading.

```{r, eval=F}
# loop over all outcomes
outcome_list <- c("attitude", "in", 'contactOnly',
                  #'rand_outcome', "end_exp", # dont make sense at ind-level
                  "pgp_donate_y1", "pgp_amount_y1")
newList_ind <- vector(mode="list", length=length(outcome_list))
for(i in 1:length(outcome_list))
{
  newList_ind[[i]] <- analysis.fun(outcome_list[i], nsims=3000)
}
save(newList_ind, file="list_of_coefs_and_ps_ind.Rda")
```
```{r}
load("list_of_coefs_and_ps_ind.Rda")
```


Now do it for raw vs binary category vs ranked contact outcomes.

```{r, eval=F}
#table(panel.df$contactOnly_raw_cw)
#table(panel.df$contactOnly_cats_cw)
#table(panel.df$contactOnly_cw)

nsims=3000
var_cw_cont <- comp.fun(paste0("contactOnly", "_cw"), nsims)
var_cats_cont <- comp.fun(paste0("contactOnly_cats", "_cw"), nsims)
var_raw_cont <- comp.fun(paste0("contactOnly_raw", "_cw"), nsims)

var_cw_diff <- comp.fun1(paste0("contactOnly", "_cw"), nsims)
var_cats_diff <- comp.fun1(paste0("contactOnly_cats", "_cw"), nsims)
var_raw_diff <- comp.fun1(paste0("contactOnly_raw", "_cw"), nsims)

var_tab_ind <- rbind(var_cw_cont, var_cats_cont, var_raw_cont, 
                 var_cw_diff, var_cats_diff, var_raw_diff)
save(var_tab_ind, file="list_of_rank_bin_raw_ind.Rda")
```
```{r}
load("list_of_rank_bin_raw_ind.Rda")
```

# Placebos

```{r, eval=F}
# loop over all placebo outcomes
placebo_list <- c("vio", 
                  "violence_group.criminals",
                  "violence_group.defend_group",
                  "violence_group.defend_religion",
                  "violence_group.government", 
                  "violence_group.maintain_culture",
                  "violence_group.retaliate",
                  'outgroup_atts_group.trust_rel',
                  "radio")
#analysis.fun(var=placebo_list[1], nsims=100)
#analysis.fun(var=placebo_list[9],nsims=100)

placeboList_ind <- vector(mode="list", length=length(placebo_list))
for(i in 1:length(placebo_list))
{
  placeboList_ind[[i]] <- analysis.fun(placebo_list[i], nsims=3000)
}
save(placeboList_ind, file="pl_list_of_coefs_and_ps_ind.Rda")
```
```{r}
load("pl_list_of_coefs_and_ps_ind.Rda")
```

# NPC

Now NPC (NPC now defunct, not on CRAN, i am using an old version.)

```{r, eval=F}
npc <- NPC::NPC(panel.df, tr.var = "treatment", tr.label = 1, 
                    clust.var = "psu", block.var = "state", 
                    y.vars = c("attitude_cw", "in_cw", 'contactOnly_cw'), 
                alternative = "greater", test.statistic = "StudentsT",n.perms=10000, seed=952022,
             print.steps=FALSE)
(p_combP <- npc$p.values['NPC']) # cumulative
npc # all of them

```
