---
title: "ecpn_diff-in-diff plots"
output:
  word_document: default
  html_document: default
---

note: if want to convert to pdf:

dev.copy(pdf,file="endComm_plot_nas.pdf")
dev.off()

pdf(file="endComm.plot_nas2.pdf", bg="transparent", width=7.8, height=6)
endComm_plot_nas
dev.off()

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(plyr)
library(dplyr)
library(tidyr)
library(ggplot2)

load("../c_creating_dataframes/f-aggregateComms_ap.Rdata")
load("../c_creating_dataframes/rand_df.Rdata")
load("../b_creating_outcomes/f2-panelData.Rdata")
load("../../obsDat/analysis/eventsMedian.Rdata")
load("../../obsDat/analysis/marketMedian.Rdata")

#until I figure out insecurity, reverse it.
ag.df$in_cw_base <- abs(ag.df$in_cw_base+1)
ag.df$in_cw_end <- abs(ag.df$in_cw_end+1)
panel.df$in_cw_y0 <- abs(panel.df$in_cw_y0+1)
panel.df$in_cw_y1 <- abs(panel.df$in_cw_y1+1)

ag.df$list_exp_base <- ag.df$list_exp_base*-1
ag.df$list_exp_end <- ag.df$list_exp_end*-1

### violence is coded so high is "desirable" instead of high is "like violence more".  Making high=="like violence more"
ag.df$vio_cw_base <- abs(ag.df$vio_cw_base-1)
ag.df$vio_cw_end <- abs(ag.df$vio_cw_end-1)
panel.df$vio_cw_y0 <- abs(panel.df$vio_cw_y0-1)
panel.df$vio_cw_y1 <- abs(panel.df$vio_cw_y1-1)
```

Make plot data

```{r}
#The vars to plot.
ag.vars <- c('allTrust_cw', 'contactOnly_cw', "in_cw",
             'pgp_amount_end', 'pgp_donate_end',
             'threat_cw','bene_cw', 'clash_cw', "barg_cw",
             'list_exp', 'rand_lm', 'rMean', 'end_exp',
             'vio_cw')

## individual
ind.vars <- c('allTrust_cw', 'contactOnly_cw', "in_cw",
              'pgp_amount_y1', 'pgp_donate_y1',
              'threat_cw','bene_cw', 'clash_cw', "barg_cw",
              'vio_cw')

# add additive index
ag.vars <- c(ag.vars, setdiff(gsub("_cw", "_index", ag.vars), ag.vars))
ind.vars <- c(ind.vars, setdiff(gsub("_cw", "_index", ind.vars), ind.vars))
stopifnot(setdiff(ag.vars,names(ag.df))==0)
stopifnot(setdiff(ind.vars,names(panel.df))==0)
```

Community-level data

```{r}
#Aggregate Plot df
base <- ag.df[,c(paste0(ag.vars[!grepl("pgp", ag.vars)], "_base"), "treatment", "state", "psu")]
names(base) <- sub("_base", "", names(base))
base$survey <- "Baseline"
end <- ag.df[,c(paste0(ag.vars[!grepl("pgp", ag.vars)], "_end"), "treatment", "state", "psu")]
names(end) <- sub("_end", "", names(end))
end$survey <- "Endline"
plot.df <- rbind(base,end)

# get mean and sd with dplyr
plot.df$state <- as.character(plot.df$state) # save me trouble with dplyr later
plot.df$psu <- as.numeric(as.character(plot.df$psu))
plot.df<-plot.df %>% 
  dplyr::group_by(treatment,survey,state) %>%
  dplyr::summarise_all(list(~mean(.), ~sd(.))) %>% # warnings because cannot sumarise non-numeric
  as.data.frame()

plot.df$Treatment<-ifelse(plot.df$treatment %in% 1, "ECPN", "Non-ECPN")
plot.df$State <- ifelse(plot.df$state %in% "nas", "Nas", "Ben")
#plot.df$plotID <- interaction(plot.df$Treatment, plot.df$State)
```

Now do same for individual-level data.

```{r}
#Panel Plot df
base1 <- panel.df[,c(paste0(ind.vars[!grepl("pgp", ind.vars)], "_y0"), "treatment", "state", "community")]
names(base1) <- sub("_y0", "", names(base1))
base1$survey <- "Baseline"
end1 <- panel.df[,c(paste0(ind.vars[!grepl("pgp", ind.vars)], "_y1"), "treatment", "state", "community")]
names(end1) <- sub("_y1", "", names(end1))
end1$survey <- "Endline"
plot.df1 <- rbind(base1,end1)

plot.df1$state <- as.character(plot.df1$state) # save me trouble with dplyr later
plot.df1$community <- as.character(plot.df1$community)

plot.df1<-plot.df1 %>% 
  dplyr::group_by(treatment,survey,state) %>%
  dplyr::summarise_all(funs(mean(., na.rm = TRUE), sd(., na.rm=T))) %>% # warnings because cannot sumarise non-numeric (like community)
  as.data.frame()

plot.df1$Treatment<-ifelse(plot.df1$treatment %in% 1, "ECPN", "Non-ECPN")
```

Now do same for individual-level data, separating Part-Non-Con

```{r}
# Part-non-control Plot df
base2 <- panel.df[,c(paste0(ind.vars[!grepl("pgp", ind.vars)], "_y0"), "treatment", "state", "committee")]
names(base2) <- sub("_y0", "", names(base2))
base2$survey <- "Baseline"
end2 <- panel.df[,c(paste0(ind.vars[!grepl("pgp", ind.vars)], "_y1"), "treatment", "state", "committee")]
names(end2) <- sub("_y1", "", names(end2))
end2$survey <- "Endline"
plot.df2 <- rbind(base2,end2)
plot.df2$Treatment <- interaction(plot.df2$treatment, plot.df2$committee)
levels(plot.df2$Treatment) <- c("Control", "Non-Part", NA, "Part")
plot.df2$Treatment <- ordered(plot.df2$Treatment, levels=c("Part", "Non-Part", "Control"))

plot.df2$state <- as.character(plot.df2$state) # save me trouble with dplyr later
plot.df2<-plot.df2 %>% 
  dplyr::group_by(Treatment,survey,state) %>%  # chris: could add state here to differentiate nas from ben
  dplyr::summarise_all(funs(mean(., na.rm = TRUE), sd(., na.rm=T))) %>% # warnings because cannot sumarise non-numeric
  as.data.frame()

#rm(pattern="(se|sd|ess|icc)Vars") #chris: regex inside pattern not work?
```


Plot functions - ggplot showing each group before and after.

```{r}
# Fixing colors
grps <-c("ECPN","Non-ECPN","Part", "Non-Part", "Control")
color.codes<-as.character(c("#FC8D59", "#00BFC4", "#FC8D59", "dark red", "#00BFC4"))
#ECPN = "#FC8D59", Non-ECPN = "#00BFC4", Part="FC8D59", Non-Part="green", Control="#00BFC4")
#plot.df$colors <- c("#00BFC4","#00BFC4","#FC8D59","#FC8D59")
#plot.df1$colors <- c("#FC8D59","#FC8D59","#00BFC4","#00BFC4")
#plot.df2$colors <- c("#FC8D59","#FC8D59", "green", "green", "#FFFFBF","#FFFFBF")

# The main Plot function chris: still need to make SE errorbars same color as lines...
# gg line plot
plot.fun<-function(var, thedf, time, title, xlab, ylab, ymin, ymax){
  ggplot(data=thedf, aes(x=thedf[[time]], y=thedf[[paste0(var, "_mean")]], group=Treatment)) +
  geom_line(aes(color=Treatment))+
  geom_point(aes(color=Treatment))+
  scale_colour_manual(values=setNames(color.codes, grps)) +
  coord_cartesian(ylim = c(ymin, ymax)) +
  #geom_errorbar(aes(ymin = thedf[[paste0(var, "_mean")]] - thedf[[paste0(var, "_se")]], 
   #                ymax= thedf[[paste0(var, "_mean")]] + thedf[[paste0(var, "_se")]],
  #                 color=Treatment), 
  #      width=.2, position=position_dodge(0.03)) + 
  ggtitle(title) +
  theme_bw() +
  theme(panel.grid.major = element_blank()) +
  theme(plot.title = element_text(size=18)) +
  xlab(xlab) +
  ylab(ylab)
}

# test

```

## Trust Index

ECPN sites in both states improed more on Affect Index than control sites.

Using index instead of ICW changes very little.

```{r}
# nas
(affectComm.plot_nas <- plot.fun(var='allTrust_cw', thedf=plot.df[plot.df$state %in% "nas",], time='survey', title="Affect - Nassarawa Communities", 
         xlab="Survey", ylab="Average Affect Index Score",
         ymin=0.1, ymax=0.8))

png(file="affectComm_plot_nas.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
affectComm.plot_nas
dev.off()


# ben
(affectComm.plot_ben <- plot.fun(var='allTrust_cw', thedf=plot.df[plot.df$state %in% "ben",], time='survey', title="Affect - Benue Communities", 
         xlab="Survey", ylab="Average Affect Index Score",
         ymin=0.1, ymax=0.8))

png(file="affectComm_plot_ben.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
affectComm.plot_ben
dev.off()
```

Part vs Non vs Con.

```{r}
# nas
(affectPan.plot_nas <- plot.fun(var='allTrust_cw', thedf=plot.df2[plot.df2$state %in% "nas",], time='survey', title="Affect - Nassarawa Individuals",
         xlab="Survey", ylab="Average Affect Index Score",
         ymin=0.4, ymax=0.8))

png(file="affectPan_plot_nas.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
affectPan.plot_nas
dev.off()


# ben
(affectPan.plot_ben <- plot.fun(var='allTrust_cw', thedf=plot.df2[plot.df2$state %in% "ben",], time='survey', title="Affect - Benue Individuals",
         xlab="Survey", ylab="Average Affect Index Score",
         ymin=0.4, ymax=0.8))

png(file="affectPan_plot_ben.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
affectPan.plot_ben
dev.off()
# why using these ugly colors instead of red green blue? have since fixed.
#ggplot_build(outPan.plot)$data
#ggplot_build(outComm.plot)$data
```


## Intergroup Contact Index

ECPN in Nas improve more than non-ECPN.  ECPN in Benue decrease less than non-ECPN.

Using index instead of ICW brings all these lines closer together.

```{r}
# nas
(conComm.plot_nas <- plot.fun(var='contactOnly_cw', thedf=plot.df[plot.df$state %in% "nas",], time='survey', title="Intergroup Contact - Nassarawa Communities", 
         xlab="Survey", ylab="Average Intergroup Contact Index Score",
         ymin=0, ymax=0.6))

png(file="conComm_plot_nas.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
conComm.plot_nas
dev.off()

# ben
(conComm.plot_ben <- plot.fun(var='contactOnly_cw', thedf=plot.df[plot.df$state %in% "ben",], time='survey', title="Intergroup Contact - Benue Communities", 
         xlab="Survey", ylab="Average Intergroup Contact Index Score",
         ymin=0, ymax=0.6))

png(file="conComm_plot_ben.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
conComm.plot_ben
dev.off()
```

In Nas: participants improve the most, non-participants and controls both improve at the same rate.  In Ben: participants stay flat, nonparticipants decrease a bit, and controls decrease the most.

```{r}
# nas
(conPan.plot_nas <- plot.fun(var='contactOnly_cw', thedf=plot.df2[plot.df2$state %in% "nas",], time='survey', title="Intergroup Contact - Nassarawa Individuals",
         xlab="Survey", ylab="Average Intergroup Contact Index Score",
         ymin=0, ymax=0.4))

png(file="conPan_plot_nas.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
conPan.plot_nas
dev.off()

# benue
(conPan.plot_ben <- plot.fun(var='contactOnly_cw', thedf=plot.df2[plot.df2$state %in% "ben",], time='survey', title="Intergroup Contact - Benue Individuals",
         xlab="Survey", ylab="Average Intergroup Contact Index Score",
         ymin=0, ymax=0.4))

png(file="conPan_plot_ben.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
conPan.plot_ben
dev.off()

```

Floor and ceiling:  I think not.  

```{r, eval=F}
ceil <- plot.df[plot.df$state %in% "nas", c("contactOnly_cw_mean", "state", "survey")]
ceil <- round(max(ceil$contactOnly_cw_mean),1)
sum(ag.df$contactOnly_cw_end>ceil) #/30

floor <- plot.df[plot.df$state %in% "ben", c("contactOnly_cw_mean", "state", "survey")]
floor <- round(min(floor$contactOnly_cw_mean),2)
sum(ag.df$contactOnly_cw_end<floor) # /30
```

## Perceptions of Security Index

In Nas: Insecurity decreases in ECPN sites more than in non-ECPN, which stay about the same.  In Ben: both decrease insecurity, but ECPN sites drop a bit more.

Using additive index instead of ICW, basically same but more muted differences.

```{r}
# nas
(inComm.plot_nas <- plot.fun(var='in_cw', thedf=plot.df[plot.df$state %in% "nas",], time='survey', title="Perceptions of Physical Security - Nassarawa Communities", 
         xlab="Survey", ylab="Average Perceptions of Physical Security Index Score",
         ymin=0, ymax=1))

png(file="inComm_plot_nas.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
inComm.plot_nas
dev.off()

# ben
(inComm.plot_ben <- plot.fun(var='in_cw', thedf=plot.df[plot.df$state %in% "ben",], time='survey', title="Perceptions of Physical Security - Benue Communities", 
         xlab="Survey", ylab="Average Perceptions of Physical Security Index Score",
         ymin=0, ymax=1))

png(file="inComm_plot_ben.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
inComm.plot_ben
dev.off()
```

In Nas: insecurity decreases for all respondents in TR sites, but stays about the same in CO sites.  In Ben: insecurity decreases for everyone, but most for Participants in TR sites.  Nonpart/Co decrease at about same rate.

```{r}
# nas
(inPan.plot_nas <- plot.fun(var='in_cw', thedf=plot.df2[plot.df2$state %in% "nas",], time='survey', title="Perceptions of Insecurity - Nassarawa Individuals",
         xlab="Survey", ylab="Average Perceptions of Insecurity Index Score",
         ymin=0.2, ymax=0.7))

png(file="inPan_plot_nas.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
inPan.plot_nas
dev.off()

# ben
(inPan.plot_ben <- plot.fun(var='in_cw', thedf=plot.df2[plot.df2$state %in% "ben",], time='survey', title="Perceptions of Insecurity - Benue Individuals",
         xlab="Survey", ylab="Average Perceptions of Insecurity Index Score",
         ymin=0.2, ymax=0.7))

png(file="inPan_plot_ben.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
inPan.plot_ben
dev.off()
```


## Violence Placebo

In Nas: Violence accepting goes up a bit in TR, down a bit in CO.  In Ben: Tr stays exactly the same, Co becomes more accepting of violence.

Additive index: scale is reversed, did not look at it.

```{r}
# nas
(vioComm.plot_nas <- plot.fun(var='vio_cw', thedf=plot.df[plot.df$state %in% "nas",], time='survey', title="Attitudes towards Violence - Nassarawa Communities", 
         xlab="Survey", ylab="Average Attitudes towards Violence Index Score",
         ymin=0, ymax=1))

png(file="vioComm_plot_nas.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
vioComm.plot_nas
dev.off()

# ben
(vioComm.plot_ben <- plot.fun(var='vio_cw', thedf=plot.df[plot.df$state %in% "ben",], time='survey', title="Attitudes towards Violence - Benue Communities", 
         xlab="Survey", ylab="Average Attitudes towards Violence Index Score",
         ymin=0, ymax=1))

png(file="vioComm_plot_ben.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
vioComm.plot_ben
dev.off()
```

In Nas: Every group becomes less accepting of violence, with Control changing the most.  In Ben: violence acceptance decreases for everyone, but it decreases for Part/Nonpart a bit more than for Control.

```{r}
# nas
(vioPan.plot_nas <- plot.fun(var='vio_cw', thedf=plot.df2[plot.df2$state %in% "nas",], time='survey', title="Attitudes towards Violence - Nassarawa Individuals",
         xlab="Survey", ylab="Average Attitudes towards Violence Index Score",
         ymin=0.1, ymax=0.6))

png(file="vioPan_plot_nas.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
vioPan.plot_nas
dev.off()

# ben
(vioPan.plot_ben <- plot.fun(var='vio_cw', thedf=plot.df2[plot.df2$state %in% "ben",], time='survey', title="Attitudes towards Violence - Benue Individuals",
         xlab="Survey", ylab="Average Attitudes towards Violence Index Score",
         ymin=0.1, ymax=0.6))

png(file="vioPan_plot_ben.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
vioPan.plot_ben
dev.off()
```


## Endorsement Experiment

This endorsement experiment is a measure of prejudice where respondents are asked their support for a public policy.  Half are asked their support when the policy is endorsed by the outgroup.  The greater the decrease in support due to the outgroup endorsement, the higher the prejudice.

In Nas: respondents didn't care about outgroup endorsement at baseline, but at endline control cared much more than treatment.  In Ben: lots of dislike towards outgroup at baseline in both TR & CO; at endline slightly worse in control group.

```{r}
# nas
(endComm.plot_nas <- plot.fun(var='end_exp', thedf=plot.df[plot.df$state %in% "nas",], time='survey', title="Endorsement Experiment - Nassarawa Communities", 
         xlab="Survey", ylab="Average Change in Support for Policy Endorsed by Outgroup",
         ymin=0.1, ymax=-0.8))

png(file="endComm_plot_nas.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
endComm.plot_nas
dev.off()

#dev.copy(pdf,file="endComm_plot_nas1.pdf")
#dev.off()

#pdf(file="endComm_plot_nas2.pdf", bg="transparent", width=7.8, height=6)
#endComm.plot_nas
#dev.off()


# ben
(endComm.plot_ben <- plot.fun(var='end_exp', thedf=plot.df[plot.df$state %in% "ben",], time='survey', title="Endorsement Experiment - Nassarawa Communities", 
         xlab="Survey", ylab="Average Change in Support for Policy Endorsed by Outgroup",
         ymin=0.1, ymax=-0.8))

png(file="endComm_plot_ben.png", bg="transparent", units="in",
   width=8, height=6, res=300)
par(mar=c(0,3,4,0),mgp=c(1.5,.5,0),oma=rep(0,4))
endComm.plot_ben
dev.off()

```
